\documentclass[10pt]{article}
% \usepackage[margin=1in]{geometry}
% \newcommand\hmmax{0}
% \newcommand\bmmax{0}
% % % Fonts% %
% \usepackage{luatexja}

\usepackage[T1]{fontenc}
   % \usepackage{textcomp}
   % \usepackage{newtxtext}
   % \renewcommand\rmdefault{Pym} %\usepackage{mathptmx} %\usepackage{times}
\usepackage[complete, subscriptcorrection, slantedGreek, mtpfrak, mtpbb, mtpcal]{mtpro2}
   \usepackage{bm}% Access to bold math symbols
   % \usepackage[onlytext]{MinionPro}
   \usepackage[no-math]{fontspec}
   \defaultfontfeatures{Ligatures=TeX,Numbers={Proportional}}
   \newfontfeature{Microtype}{protrusion=default;expansion=default;}
   \setmainfont[Ligatures=TeX,BoldFont={*-Semibold}]{Source Serif Pro}
   \setsansfont[Microtype,Scale=MatchLowercase,Ligatures=TeX,BoldFont={*-Semibold}]{Source Sans Pro}
   \setmonofont[Scale=0.8]{Atlas Typewriter}
   % \usepackage{selnolig}% For suppressing certain typographic ligatures automatically
% % % % % % %
\usepackage{amsthm}         % (in part) For the defined environments
\usepackage{mathtools}      % Improves  on amsmaths/mtpro2
\usepackage{xfrac}

% % % The bibliography % % %
\usepackage[backend=biber,
  style=authoryear-comp,
  bibstyle=authoryear,
  citestyle=authoryear-comp,
  uniquename=false,
  % allinit,
  % giveninits=true,
  backref=false,
  hyperref=true,
  url=false,
  isbn=false,
  useprefix=true,
  ]{biblatex}
\DeclareFieldFormat{postnote}{#1}
\DeclareFieldFormat{multipostnote}{#1}
% \setlength\bibitemsep{1.5\itemsep}
\newcommand{\noopsort}[1]{}
\addbibresource{Thesis.bib}

% % % % % % % % % % % % % % %

\usepackage[inline]{enumitem}
\setlist[enumerate]{noitemsep}
\setlist[description]{style=unboxed,leftmargin=\parindent,labelindent=\parindent,font=\normalfont\space}
\setlist[itemize]{noitemsep}

% % % Misc packages % % %
\usepackage{setspace}
% \usepackage{refcheck} % Can be used for checking references
% \usepackage{lineno}   % For line numbers
% \usepackage{hyphenat} % For \hyp{} hyphenation command, and general hyphenation stuff

% % % % % % % % % % % % %

% % % Red Math % % %
\usepackage[usenames, dvipsnames]{xcolor}
% \usepackage{everysel}
% \EverySelectfont{\color{black}}
% \everymath{\color{red}}
% \everydisplay{\color{black}}
\definecolor{fuchsia}{HTML}{FE4164}%Neon Fuchsia %{F535AA}%Neon Pink
% % % % % % % % % %

\usepackage[export]{adjustbox}
\usepackage{subcaption}

% \usepackage{pifont}
% \newcommand{\hand}{\ding{43}}
\usepackage{array}


\usepackage{multirow}
% \usepackage{adjustbox}

\usepackage{titlesec}

\usepackage{multicol}

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\usepackage{tikz}
\usetikzlibrary{bending,arrows,positioning,calc}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{patterns}
\usetikzlibrary{fadings}
\usepackage{tikz-qtree} %for simple tree syntax
% \usepgflibrary{arrows} %for arrow endings
% \usetikzlibrary{positioning,shapes.multipart} %for structured nodes
\usetikzlibrary{tikzmark}
\usetikzlibrary{patterns}

\usepackage{graphicx} % for images (png/jpeg etc.)
\usepackage{caption} % for \caption* command

\usepackage{tabularx}

\usepackage{bussalt}

\usepackage{Oblique} % Custom package for oblique commands
\usepackage{CustomTheorems}
\usepackage{FuturePromisedEvents}

% \usepackage{svg}
% \usepackage[off]{svg-extract}
% \svgsetup{clean=true}

\usepackage{dashrule}

\newcommand{\hozline}[0]{%
  \noindent\hdashrule[0.5ex][c]{\textwidth}{.1pt}{}
  %\vspace{-10pt}
  % \noindent\rule{\textwidth}{.1pt}
}

\newcommand{\nf}[1]{#1\ensuremath{^{{*}}}}

\newcommand{\WR}[0]{\textsf{Witnessing}}
\newcommand{\AR}[0]{\textsf{Attribution}}


\newcommand{\tri}[2]{\emph{#2}\(_{\text{\tiny\emph #1}}\)}

\newcommand{\hozlinedash}[0]{%
  \noindent\hdashrule[0.5ex][c]{\textwidth}{.1pt}{2.5pt}
  %\vspace{-10pt}
}

\usepackage{contour}
% \usepackage{pdfrender}

\usepackage{extarrows}

% % % My commands % % %
% https://tex.stackexchange.com/questions/21644/how-do-you-superimpose-two-symbols-over-each-other
\makeatletter
\newcommand{\superimpose}[2]{%
  {\ooalign{$#1\@firstoftwo#2$\cr\hfil$#1\@secondoftwo#2$\hfil\cr}}
}
\makeatother

\newcommand{\veewedge}{\mathpalette\superimpose{{\vee}{\wedge}}}
\newcommand{\lessgreater}{\mathpalette\superimpose{{<}{>}}}
\newcommand{\strikeQ}{\mathpalette\superimpose{{\text{---}}{Q}}}
\newcommand{\RS}{\mathpalette\superimpose{{\text{R}}{\text{S}}}}

% % % % % % % % % % % %

\usepackage{xskak} % For chess diagram

\usepackage[hidelinks,breaklinks]{hyperref}

\title{Ability to reason and reasoning with ability}
% \subtitle{\dots and you don't need me to tell you}
\author{Ben Sparkes}
% \date{ }

\begin{document}

% \tableofcontents

% \newpage

\maketitle

\section{Introduction}
\label{sec:introduction}

{
  \color{red}
  Topic is claims of ability.
  Specifically, ability to reason from some premises to a conclusion.
  Argue that these show an intuitive claim is false\dots
}

Argue against:
\begin{itemize}
\item\label{denied-claim} \emph{An agent may appeal to reasons in support of a conclusion only if the agent used those reasons in some reasoning that yielded the conclusion.}
\end{itemize}

{
  \color{red}
  This is false because the agent draws what would be achieved by witnessing their ability.
}

{
  \color{red}
  Ability statements aren't too interesting for ideal agents.
  For, idealisation often assumes that any ability the agent has is witnessed.
  In particular, with factive verbs.
  Ability to demonstrate \(\phi\), then an ideal agent is assumed to have demonstrated \(\phi\).
  However, for bounded agents like us, resources.
  Cost is not reasoning, but reasoning performed.
}

Contraposition seems clear.
If agent used reasons in reasoning, then they may appeal to those reasons in support of the conclusion.
May be challenged and so on, but here interested in when the agent is forming the conclusion.
Unless give a strong normative reading of may, there doesn't seem any way to object.
Would deny that the reasoning is any good, not that the agent can cite their own reasoning.

Instead, contrast \emph{may} with \emph{must}.

Perhaps constitutive of reasoning, but then talk of raesoning instead.

Sketch argument for the conditional.

\begin{enumerate}
\item\label{opp:sketch:1} If conditional is false, then it is possible there are cases in which an agent is unaware of how the conclusion is supported by favoured reasons.
\item\label{opp:sketch:2} If agent is unaware of how a conclusion is supported by reasons, then conclusion may not be supported by those reasons.
\item\label{opp:sketch:3} If conclusion may not be supported, then the conclusion is not supported (from the agent's perspective).
\end{enumerate}

So, the agent may do as they please, but they will fail to establish support, the appeal would be in name only.\nolinebreak
\footnote{
  Alternative sketch:
  \begin{itemize}
  \item Agent to hold \(A\) on the basis of \(R\) requires \(R\) to do some explanatory work.
  \item If agent does not directly respond to \(R\) then \(R\) does not do any explanatory work.
  \item Therefore, reason only if directly respond.
  \end{itemize}
}

Contraposing and re-expressing, the last proposition, reads:

\begin{itemize}
\item If conclusion is supported by reasons, then it is a fact that the conclusion is supported by reasons.
\end{itemize}

Variation on a familiar thought that reasons are factive.\nolinebreak
\footnote{
  For example, \textcite[673]{Cunningham:2020aa}, summarising \textcite{Hornsby:2007aa,Hornsby:2007ab,Hornsby:2008aa} defends:
  \begin{quote}
    Necessarily, if S \(\phi\)'s because p then S knows that p
  \end{quote}
  Where the `because' is a rationalising `because'.
  If \emph{S} knows that \emph{p}, it is a fact that \emph{p}.
}
Here, relation of support is factive.

I think the last premise is more-or-less true, depending on how `may' is understood.
Perhaps the agent does not \emph{know} that the conclusion follows from the premises, but is \emph{confident} that the conclusion follows from the premises --- it would be bizarre if were not a fact that the conclusion is not supported by the premises.
Even so, it seems intuitive that an agent could not have the appropriate confidence without being away of how the conclusion is supported by the premises, and so some variation of \ref{opp:sketch:2} holds.
It seems plausible at least some variation of \ref{opp:sketch:1}--\ref{opp:sketch:3} is sound.\nolinebreak
\footnote{
  Alternative may be to argue for representationalism, or dispositionalism.
  \citeauthor{Neta:2019aa} for example of how these would go.
  Broad, and don't seem quite as informative.
}

I do not think some variation of \ref{opp:sketch:2} holds.
I think an agent may be unaware of how a conclusion is supported by reasons while the conclusion is supported by those reasons (from the agent's perspective and so on).

Focus is on a particular type of ability claim.
For example:
\begin{itemize}
\item ???
\end{itemize}

Argue for reading this as providing an agent with a \emph{license} to appeal to the reasoning (or reasons) that the agent is able to do.

Licenses recast a problem raised by \citeauthor{Davidson:2001aa}:
When we look to explain why an agent performed an act (here, adopting a conclusion), we find there are various account that \emph{could} explain.
(\citeauthor[7--8]{Davidson:2001aa})
\begin{quote}
  But then something essential has certainly been left out, for a person can have a reason for an action, and perform the action, and yet this reason not be the reason why they did it.
  Central to the relation between a reason and an action it explains is the idea that the agent performed the action \emph{because} they had the reason.\nolinebreak
  \mbox{}\hfill\mbox{(\citeyear[9]{Davidson:2001aa})}
\end{quote}
As \citeauthor{Hieronymi:2011aa} expresses, we seek `an explanation which shows, not merely what, from another’s point of view, \emph{could} count in favour of acting, but why that person did, in fact, act' (\citeyear[417]{Hieronymi:2011aa}).

Following \citeauthor{Davidson:2001aa}, then, reasons or reasoning only explain an action provided there is a causal relation between the reasons the agent had or the reasoning the agent performed, and the action.\nolinebreak
\footnote{
  Note on the inclusion of reasoning here.
  Later \citeauthor{Davidson:2001aa}: `I do not see how the right sort of causal process can be distinguished without, among other things, giving an account of how a decision is reached\dots' (\citeyear[232]{Davidson:2001aa}), etc.
  And, my focus.
}
If this is sound, then the difference between what \emph{could} explain and what \emph{does} explain is only a matter of what happened --- a causal relation does not distinguish explanation from non-explanation, but actual explanation from potential explanation.\nolinebreak
\footnote{
  In \citeauthor{Hieronymi:2011aa}'s phrasing: Without a causal relation we get an answer to ‘from so-and-so’s point of view, why do so such and such?’ rather than ‘why did so-and-so do such-and-such?’ (\citeyear[417]{Hieronymi:2011aa}).
}\(^{,}\)\nolinebreak
\footnote{
  {
    \color{red}
    This is different to the relationship that \citeauthor{Neta:2019aa} notes between reasons why and reasons for which.
    In short, reasons why are not always reasons for which, because there are explanatory relations which are in a sense `structural' and therefore are not seen as reasons from the agent's point of view.
    So, I'm colourblind, but that is not a reason for which I believe the two different colours are the same colour, though it explains why.
    Rather, the reasons for which is that both objects appear the same colour to me.

    The distinction I am interested in can be seen as distinction between the way a reason \emph{which} may support an attitude.
  }
}

Even if causal relations to not resolve the problem of distinguishing what could explain from what does explain, I take this problem to be genuine.
There is often no unique explanation for an action, potential explanations \emph{do} explain, but (merely) potential explanations do not explain what actually happened.
Yet, if potential explanations do explain, and an agent has a guarantee that a potential explanation obtains, then the agent has the guarantee of an explanation.

\begin{note}[Neta on Davidson/Anscombe]
  \citeauthor{Neta:2019aa} reconstructs this in terms of explanatory reasons in response to Anscombian `Why' questions.
\end{note}

% One does not need the theoretical backing to observe that the integer expression of \(7^{3}\) may be obtained by either mental arithmetic or a calculator.
% And that if one is confident in their ability to perform mental arithmetic, then the use of the calculator demonstrates what they would obtain by performing the reasoning.
% So, if one is provided with the information that one has the ability to perform the mental arithmetic to see that \(7^{3} = 343\), or that the calculator will show \(343\) after typing \(7^{3}\) in and hitting enter, it seems that either of these potential explanations may be cited as the explanation for holding that \(7^{3}\) is \(343\).

% What explains why I hold that \(7^{3}\) is \(343\) is that the calculator would demonstrate that it is so, or \dots is that I have the ability to demonstrate that it is so.
% The information provides only states that \(7^{3} = 343\) is the result of some process, and so I take that process to support holding that \(7^{3} = 343\).

{
  \color{red}
  The \citeauthor{Davidson:1963aa} motivation is quite general.
  I end up focusing on a particular case, where there are additional constraints to draw on.
  However, the result is of this kind, and I take this to be partial motivation for the possibility of these cases even when the additional constraints do not apply.

  Even so, role of ability in reasoning is interesting, and an instance of this type of thing.
}


\begin{note}[Fine distinction]
  The fine distinction is between an agent responding to reasons and an agent's action being supported by reasons.
  {
    \color{red}
    \emph{This!!!}
  }
  It is important to distinguish between the state of the board and the rules of chess, which are sufficient to derive the particular reasons, from this specific reason for which the move is possible.
  That it is a knight, knights can move, etc.
\end{note}

\begin{note}[Rationality]
  Another way to look at this is in terms of a distinction between kinds of irrationality.
  Admittedly, claims to rationality are strong.
  So, distinguish between the failure to respond to reasons, and the absence of reasons to respond to.
\end{note}

\hozlinedash

That an agent is able to reason may not be necessary, but helps with the explanation being potential --- a helpful divide between potential explanations and hypothetical explanations, perhaps.
Sufficient, at least.
Necessary and sufficient conditions aren't of interest.


Causal relations may not be correct.
Well, seems must not be correct.
This only goes part of the way.

Potential seems redundant.
Section ???

Here, agent obtains a license to a potential explanation.
Information about ability provides the agent with the information that the explanation could hold explain, or could stand in the appropriate causal relation.
Hence the agent performs the action `because' of the reasons or reasoning that would be invoked in the potential explanation.

{
\color{red} This skips over some details, esp.\ about how reasons/potential explanations are under-specified.
}

If the thing licensed isn't a potential explainer, then the agent would not have the ability, etc.\

Problem tasked with as theoreticians --- identifying the explanation --- is, in a sense, exploited by the agent given certain conditions.

Straightforward incompataibility.
Yes.
But only if assume (or demand) that the causal explanation is complete\dots

{
  \color{red}
  First part of the paper is walking through this carefully.
}
The upshot of denying~\ref{denied-claim} is flexibility in understanding agency.
Isolating, illustrating.



An important feature is that in the cases of interest, the conclusion does depend on reasoning to be true.
Some cases fail.
For example, agent cannot conclude that they have reasoned to the conclusion.
As, it is only the case that the agent has reasoned to the conclusion if the agent has performed the reasoning.
Reflexive content is often a source of trouble, but here the problem is more mundane.
An agent cannot turn on a light by reflecting on their ability, the agent must flick the switch in order for the light to turn on --- and reflexively referencing one's own reasoning requires a similar witnessing event.

Reasoning is great for various things other than obtaining a conclusion.
Agent goes with licensed reasons, they do not get this stuff.
However, the agent does get other things.

\subsection{Overview}
\label{sec:overview}

This section has set out the general goal.
It is quite broad.
The argument is quite focused.

Three sections that follow.
\begin{enumerate}
\item General argument, issues, etc.
\item Specifics of failure.
\item Potential for potential.
\end{enumerate}
This includes two passes for both arguments.
First in the general outline, and again in the specifics.

This involves some redundancy.
However, this permits details where they matter.
Primary upshot of this compromise is that the first section will be sufficient for the big picture.
Also, isolated conclusions.
Second section provides results about expansion of ability.
Third section provides results about how to understand a plausible reasoning pattern.

\section{Abilities}
\label{sec:abilities}

\begin{note}[Outline of section]
  The goal of this section is to isolate a particular pattern of reasoning:
  \begin{enumerate}
  \item Information that agent possesses ability to reason \(\phi\).
  \item Endorsement of ability (not simply testimony).
  \item `Factive' inference to \(\phi\) being the case.
  \end{enumerate}

  Ability statements of interest are of the form:
  \begin{itemize}
  \item Agent \(a\) has ability to \emph{V} that \emph{p}.
  \end{itemize}
  Where \emph{V} is some verb and \emph{p} some proposition.
  For example:
  \begin{enumerate}
  \item Sam has the ability to prove that the central limit theorem is true.
  \item Taylor has the ability to see that there is a red barn in the field.
  \item Gray has the ability to 
  \item 
  \end{enumerate}

  Differ.
  \begin{enumerate}
  \item Riley has the ability to measure the table.
  \item Avery has the ability to find where Quinn is hiding.
  \end{enumerate}

  \begin{enumerate}
  \item Riley has the ability to measure that the table is six foot long.
  \item Avery has the ability to find that Quinn is hiding behind the hedge.
  \end{enumerate}
  These variants sound bad, but express a straightforward situation.
  There is some action that Riley has the ability to perform whose witnessing results in a measurement that the table is six foot long.
  Likewise, there is some action that Avery has the ability to perform whose witnessing results in finding Quinn hiding behind the hedge.

  What matters is not the particular choice of verb, but that there is some action.

  Certain preconditions need to be in place.
  Central limit theorem is true, there is a red barn in the field, and so on.

  Examples given are all `factive', in that the proposition must be true of the relevant witnessing event.
  So, we get:
  \begin{itemize}
  \item For any strategy, an agent has the ability to demonstrate the existence of the strategy only if the strategy exists.
  \end{itemize}

  Non-factive variants.
  Here, the same principle applies, but may not get the requirement of the relevant proposition.
\end{note}

\begin{note}[Potential, not hypothetical]
  The ability is not that there `might' be some event.
  Given the information available, agent does the action, and establishes the result.
  Do not need to assume that certain things are the case.
\end{note}

\begin{note}[General and specific]
  Above are examples of specific abilities.
  Also general abilities.
\end{note}

\section{Potential strategies}
\label{sec:potential-strategies}

\begin{note}[Narrowing cases]
  The motivating idea behind licensing is broad.
  It applies to any situation in which an agent is confident that a potential explanation is available.

  However, the argument for licensing is narrow.
  Look to specific cases.

  In the same way that there may be multiple potential explanations available to the agent, there may be multiple accounts to us as theorists.

  If an account can be given that does not involve licensing (or that do not involve the idea of licensing as anything other than a mistake), then the test is whether licensing is a best account.

  Assume that an account can be given that does not involve licensing.
  I doubt that it is possible to show that any given account is necessary.
  However, whether or not an account is best is not determined by the particular case.
  Depends also on the role of the account in other cases.
  Secure licensing in particular cases provides some support over alternatives when there is competition.\nolinebreak
  \footnote{
    Maybe a note here about the principle of charity.
    This is, I think, also a Davidsonian idea.
    Charity in the sense that one assumes that there is a rationalisation --- a (complete) explanation --- available.

    Charity, assume that if an agent's action is the result of reasoning then it may be rationalised --- in the sense of providing a complete explanation.
    Even a poor, but complete, explanation is preferable to an incomplete explanation (and hence absence of rationalisation).

    % May motivate with ideal cases.
    % Ideal cases seem to include possession of an explanation.
    % Soften the ideal by relaxing standards governing the quality of the explanation, rather than the existence of an explanation.
    % A poor explanation remains an explanation; potential explanation is only a \emph{potential} explanation.

  Corollary is the denial of this ordering on explanations.
  Sometimes appeal to a potential/incomplete explanation is better than a complete explanation.

  Conflicts with charity only if explanation is understood as complete explanation.
  Hence, I do not think that this conflicts with the spirit of charity, though it may conflict with particular accounts of charity.
  }

  This is about theory of explanations/reasons/reasoning.

  This limits attention.
  May be that licensing is rarely a best account.
  However, so long as it is a contender, then the main goal has been achieved.
\end{note}


Consider the following claim\nolinebreak
\footnote{
  To ease discussion, stipulate a use of `claim' as offering the receiver the support for the proposition claimed.
  Therefore:
  \begin{enumerate}
  \item\label{cond:claim-to-opt-supp} If an informer claims that \(\phi\), then the informed has the option of obtaining support for \(\phi\) via the informer's claim.
  \end{enumerate}\vspace{-10pt}
}\nolinebreak
made to an agent:
\begin{enumerate}
\item\label{chess:claim:1}\label{chess:claim:1:conditional} If you are able to reason with the rules of chess, then you have the ability to demonstrate that White cannot prevent Black from occupying c4 on their (Black's) second move given the game state (described in figure~\ref{fig:chess:board}).
\end{enumerate}



\begin{figure}[h]
  \centering
  \mbox{ }
  \hfill
  \begin{subfigure}{.4\textwidth}
    \begin{adjustbox}{minipage=\linewidth,scale=0.7}
      \centering
      \newchessgame[
      setwhite={ka5,pa3,pb4,pc4,pe5,pf6,bg5,bh5}, %{rc1,kh1,pa2,pb2,ph2,pf6,pg6,nc7,qf7},
      addblack={pa6,pb7,pc6,pe6,pf7,kc7,nd7,nd4}, %{rg2,pb5,pe5,qd6,pa7,pb7,ra8,bc8,kd8,bf8},
      ]%
      \setchessboard{showmover=false}%
      \chessboard
    \end{adjustbox}
    \caption{
      Game state\newline
      \mbox{ }\newline
    }
    \label{fig:chess:board}
  \end{subfigure}
  \mbox{ }
  \hfill
  \mbox{ }
  \begin{subfigure}{.4\textwidth}
    \begin{adjustbox}{minipage=\linewidth,scale=0.7}
      \centering
      \newchessgame[
      setwhite={ka5,pa3,pb4,pc4,pe5,pf6,bg5,bh5}, %{rc1,kh1,pa2,pb2,ph2,pf6,pg6,nc7,qf7},
      addblack={pa6,pb7,pc6,pe6,pf7,kc7,nd7,nd4}, %{rg2,pb5,pe5,qd6,pa7,pb7,ra8,bc8,kd8,bf8},
      ]%
      \setchessboard{showmover=false}%
      \chessboard[
      arrow=latex,
      linewidth=1pt,
      shortenstart=.8ex,
      shortenend=.5ex,
      pgfstyle=straightmove,
      strokeopacity=0.4,
      fillopacity=0.4,
      color=black,
      pgfstyle=border,
      markfields={c4,a3,a5,g6,c5},
      % markmoves={b7-b6,c6-c5,d4-c2,d4-b5,d4-f5,d4-e2,d4-f3,d4-b3,d7-c5,d7-b6,d7-b8,d7-f8,d7-f6,d7-e5,d7-e5,c7-c8,c7-b8,c7-d8,c7-b6,c7-d6}%{f7-g8,f7-e6,f7-d5,f7-c4,f7-b3,f7-e8,c7-d5,c7-b5,c7-a8,c7-e8,g6-g7,a2-a3,b2-b3,c1-a1,c1-b1,c1-d1,c1-e1,c1-f1,c1-g1,h2-h3,h1-g1,c1-c2,c1-c3,c1-c4,c1-c5,c1-c6}
      ]
    \end{adjustbox}
    \caption{Example fields White cannot prevent Black from occupying after two moves.}
    \label{fig:chess:move}
  \end{subfigure}
  \hfill
  \mbox{ }
  \caption{Black to checkmate in four moves.\protect\footnotemark}
  \label{fig:chess}
\end{figure}
\footnotetext{
  \citeauthor{Emms:2000aa}' Puzzle 150 (\citeyear[33]{Emms:2000aa}).
  \citeauthor{Emms:2000aa} provides the following solution:
  \begin{quote}
    \variation{1... Nb6!}
    (threatening \variation{2... Nb3\#})
    \variation{2. b5}
    (or \variation{2. Bd1 Nxc4+} \variation{3. Ka4 b5\#})
    \variation{2... c5!}
    \variation{3. bxa6 Nxc4+}
    \variation{4. Ka4 b5\#}
    \textbf{(0-1)}\nolinebreak
    \mbox{}
    \hfill
    (\citeyear[46]{Emms:2000aa})
  \end{quote}
}

{\color{red}
  \begin{note}[Alternate claim]
    Implicit in~\ref{chess:claim:1} is that the (specific) ability to demonstrate the existence of a strategy is an instance of the agent's (general) ability to reason with the rules of chess.

  Less natural, but perhaps more accurate, the informer may claim:
  \item\label{chess:claim:1:conditional:extend} If you are able to reason with the rules of chess, then an instance of the mentioned ability allows you to demonstrate that White cannot prevent Black from occupying c4 on their (Black's) second move given the game state (described in figure~\ref{fig:chess:board}).
  \end{note}}

\begin{note}[Status of the claim]
  We assume claim~\ref{chess:claim:1} is true, but not immediately obvious to the agent.
  And, in particular, that some reasoning from the rules of chess and the game state is required to verify that the agent is able to demonstrate that White cannot prevent Black from occupying c4 on their (Black's) second move.

  For, in order to show that White cannot prevent Black from occupying c4 on their second move, the agent would need to consider the moves that would be possible for Black on their second turn given the move that White made on their first turn in response to the move that Black made on their first turn, and so on.
  A (general) ability to reason with the rules of chess may ensure that the agent is able to demonstrate the existence of the (particular) strategy for Black.
  However, it does not follow that the agent is in a position to recognise that the (general) ability to reason with the rules of chess requires the agent to recognise that they are able to demonstrate the existence of the (particular) strategy.

  To illustrate, Black may move the pawn from b7 to b5 on their first turn, and so be in a position to capture White's pawn on c4 in their second turn.
  However, White may then prevent Black from occupying c4 on their next turn by using their pawn on c4 to capture Black's pawn on b5.
  So, Black moving their pawn from b7 to b5 on their first turn is not an initial move of interest.

  Still, there are only (a little more than) a handful of alternative moves and countermoves to consider.
\end{note}

\begin{note}[Some motivation for holding claim 1 to be true]
  Perhaps you have an effective method for identifying a strategy for Black.
  Perhaps you are able to exhaust all the strategies available to Black and identify those which ensure c5 is occupied on Black's second move.
  Perhaps you have solved a sufficient number of sufficiently challenging chess puzzles.

  Or, you solved a lot of chess problems.

  Whichever way, general ability.
\end{note}

\begin{note}[Parallel example with theorems]
  To take a parallel example, an agent's (general) ability to reason with some sound and complete proof system for propositional logic means that the agent is able to demonstrate various (particular) theorems of propositional logic, but the agent may not recognise that they have the (specific) ability to demonstrate any (particular) theorem prior to witnessing their (specific) ability, or being otherwise informed of the theorem.
\end{note}

\begin{note}[Role of conditional]
  Claim~\ref{chess:claim:1} is distinct from the claim that the agent has the ability to demonstrate a strategy --- the unembedded consequent of claim~\ref{chess:claim:1}
\begin{enumerate}
\item\label{chess:claim:2}\label{chess:claim:1:conditional} You are able to reason from the game state (described in figure~\ref{fig:chess:board}) to the proposition that White cannot prevent Black from occupying c4 on their (Black's) second move.
\end{enumerate}
\end{note}

% Precisely, I assume the agent holds claim~\ref{chess:claim:1} to be true at some interval between the point at which I claimed~\ref{chess:claim:1} is true and the present time or the point at which you demonstrated claim~\ref{chess:claim:1} to be true.\nolinebreak
% \footnote{
%   If a fresh instance of claim~\ref{chess:claim:1} is desired, one may substitute (e.g.) `a3', `a5', `g6', or `c5' for `c4'.
% }
% For ease of exposition, I will adopt the perspective of some point in that interval.

\begin{note}[Reasoning sketch]
  With the above, sketch out simple reasoning.
  \begin{enumerate}[label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:cond:ant} I have the ability to reason with the rules of chess.
  \item\label{inf:cond} If I have the ability to reason with the rules of chess then I have the ability to demonstrate the existence of a (particular) strategy.
  \end{enumerate}

  As~\ref{inf:cond:ant} is the antecedent of~\ref{inf:cond} and the consequent of~\ref{inf:cond} is novel information,~\ref{inf:cond:ant} and~\ref{inf:cond} combine to provide support for:

  \begin{enumerate}[resume, label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:cond:conq} I have the ability to demonstrate the existence of the (particular) strategy that White cannot prevent Black from occupying c4 on their second move.
  \end{enumerate}

  Note, however, that~\ref{inf:cond:conq} is not considered a straightforward application of \emph{modus ponens}.
  Rather,~\ref{inf:cond} captures conditional information about how some ability the agent has extends, if it is indeed the ability to reason with the rules of chess.

  Sub-conclusion~\ref{inf:cond:conq}, is the antecedent of the following quantified conditional:

  \begin{enumerate}[resume, label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:gae} For any strategy, an agent has the ability to demonstrate the existence of the strategy only if the strategy exists.
  \end{enumerate}

  Therefore:

  \begin{enumerate}[resume, label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:sse} The (particular) strategy (that I am able to demonstrate) exists.\newline
    White cannot prevent Black from occupying c4 on their second move.
  \end{enumerate}
\end{note}

\begin{note}[Support for (general) ability]
The agent has background support for having the ability to reason with the rules of chess (\label{inf:cond:ant}).
For example, the agent may have read various accounts of the rules of chess, played numerous games without apparent fault, solved diverse chess problems, and so on.
Still, we assume the agent recognises that their support for having the ability to reason with the rules of chess may be mistaken.
Perhaps the agent considers it possible that are certain rules that the agent has either misunderstood or not yet understood.

It may seem implausible at first glance to obtain support for the (general) ability to reason with the rules of chess while maintaining the possibility of some mis- or missing-understanding.
The agent may have a complete grasp on the rules of chess, and while no specific mis- or missing-understanding is of interest, it is fairly easy to generate plausible variants of the rules of chess which may have persisted through a somewhat cursory reading of any introductory text and persisted through games and problems.

For example,
\begin{itemize}
\item A knight may move two squares horizontally and one square vertically (but not one square horizontally and two squares vertically).
\item Knights may not `leap over' other pieces.
\item \emph{En passant} to involve any piece moving two squares vertically from the fifth row.
\item Rooks move any number of (free) squares diagonally and bishops move any number of (free) squares horizontally or vertically.
\item The king may only move to a square which is adjacent to a piece of the same colour.
\end{itemize}
Perhaps none of these variants are plausible in practice, but mentioned to a causal player may result in some pause.

It is clear that the agent is able to something, but from the agent's point of view it is possible that the ability is not reasoning with the rules of chess.
To clarify, we may reformulate~\ref{inf:cond:ant} as follows:
  \begin{enumerate}[label=(S\arabic*\('\)), ref=(S\arabic*\('\))]
\item\label{inf:cond:antp} I have an ability \(\mathcal{A}\), and \(\mathcal{A}\) is the (general) ability to reason with the rules of chess.
\end{enumerate}
\end{note}

\begin{note}[Extending general ability]
  As noted, we will consider the information conveyed by the informer's claim~\ref{chess:claim:1:conditional} with some rigour in section~\ref{sec:role-conditional}.
  For now, we assume that~\ref{inf:cond} is the only relevant information obtained from the informer's claim.
  Given the alternative statement of~\ref{inf:cond:ant}, we may recast~\ref{inf:cond} to read:
  \begin{enumerate}[resume, label=(S\arabic*\('\)), ref=(S\arabic*\('\))]
  \item\label{inf:condp} If \(\mathcal{A}\) is the ability to reason with the rules of chess, then \(\mathcal{A}\) is (also) the ability to demonstrate the existence of a particular strategy.
  \end{enumerate}
  The role of the information provided by the informer is to allow the agent to expand what follows from their (general) ability \(\mathcal{A}\), so long as the agent is not mistaken about what their (general) ability \(\mathcal{A}\) is.
  Intuitively, then, the informer does not provide information about whether \(\mathcal{A}\) is (also) the ability to demonstrate the existence of a particular strategy, as \(\mathcal{A}\) may not be the (general) ability to reason with the rules of chess.

  Hence, we may likewise recast~\ref{inf:cond:conq} to read:
    \begin{enumerate}[resume, label=(S\arabic*\('\)), ref=(S\arabic*\('\))]
  \item\label{inf:cond:conqp} I have an ability \(\mathcal{A}\), and \(\mathcal{A}\) allows me to demonstrate the existence of the (particular) strategy.
  \end{enumerate}
  The required background to our primary interest in the reasoning sketch is that the agent obtains~\ref{inf:cond:conq} by using the information provided by the informer to expand what follows from the ability \(\mathcal{A}\), given the support the agent has for considering \(\mathcal{A}\) to be the (general) ability to reason with the rules of chess.
\end{note}

\begin{note}[More on extending general ability]
  I take the broad outline of this reasoning to be compelling. Agents possesses general abilities. And, an agent is not required to understand specifics that follow from general ability in order to posses the general ability. So, an informer may observe specific abilities which (would) follow from the agent's general ability (if the agent possesses the ability), and once informed agent may incorporate this information.

  The hedging is important. In some cases, the informer may have an independent understanding of the ability, such as understanding the rules of chess themselves, and so provides information about what follows from the general ability, so to speak. In other cases, the informer may observe the agent's action and extrapolate a specific ability on the basis of this. In the latter kind of cases, the informer provides information about what follows from the agent's ability, so to speak, no from the general ability itself.

  May assume is in the latter kind of case. Hence, the conditional formulation is to some extent natural. However, the informer may make the conditional statement in either case.

  So, interest is in how this works when the only information the informer provides is a conditional linking general to specific. Motivated by the possibility of the second kind of case, from the agent's point of view. So, not support for the particular fact otherwise.
\end{note}

\begin{note}[Two options for understanding ability]
  Our primary interest is in how~\ref{inf:cond:conq} combines with~\ref{inf:gae} to provide the agent with support for~\ref{inf:sse}.
  For, there are two distinct aspects of having the (specific) ability to demonstrate the existence of a (particular) strategy which may be stressed:
  \begin{enumerate}
  \item\label{Ab:asp:A} Possessing the \emph{attribute} of having the (specific) ability to demonstrate the existence of the (particular) strategy.
  \item\label{Ab:asp:W} The (potential) event of \emph{witnessing} the (specific) ability by demonstrating the existence of the (particular) strategy.
  \end{enumerate}
  We describe \label{Ab:asp:A} and~\label{Ab:asp:W} as aspects of having the (specific) ability to demonstrate the existence of a (particular) strategy as they entail one another, given the relevant understanding of ability.

  If there is no (potential) event, then the agent doesn't have the ability.
  If there is a (potential) event, then as this involves the action of the agent, an attribute is generated.
\end{note}

\begin{note}[Expanding]
  \label{Ab:asp:A} and~\label{Ab:asp:W} as aspects of having the (specific) ability to demonstrate the existence of a (particular) strategy, but lead to distinct interpretations of the reasoning from~\ref{inf:cond:conq} to~\ref{inf:sse} via~\ref{inf:gae} of the argument sketch.

  \begin{multicols}{2}
    Attribution (Property):
    \begin{enumerate}
    \item If general then specific.
    \item Prior support for general
    \item Have the general ability
    \item Have the specific ability
    \item Strategy exists
    \end{enumerate}

    Witness (Action):
    \begin{enumerate}
    \item If general then specific
    \item Prior support for general
    \item General to witness of specific
    \item Provide witness
    \item Strategy exists
    \end{enumerate}
  \end{multicols}
  We label these \AR{} and \WR{}.
\end{note}

\begin{note}[\WR{}]
  A brief sketch of the argument sketch developed given the \WR{} interpretation is:
  \begin{enumerate}[label=(W\arabic*), ref=(W\arabic*)]
  \item I am able to demonstrate the existence of a (particular) strategy.
  \item Therefore, possible to witness event of demonstrating the existence of the (particular) strategy.
  \item Event of demonstrating provides support for the existence of the (particular) strategy.
  \item So, attribute of ability secures availability of support for the existence of the (particular) strategy.
    However, it is the available reasons that do the work.
  \end{enumerate}

  In short, the distinction is between appealing to ability as a prerequisites of the relevant event, versus appealing to ability for the outcome of the relevant event.
  The former doesn't require any consideration about the event, as it's based only on the possibility of the event.
  The later does require consideration about the event, because it appeals to the result.
\end{note}

\begin{note}[Why there's interest]
  The interest is in the reasons available to the agent.

  Agent obtains support for the ability, this much we assume.
  And, argument sketch gives a clear account of the reasons.
  So, attribution is quite nice.

  Witnessing is not.
  The agent hasn't demonstrated the existence of the strategy, and the witnessing event is potential.

  Consider snooker balls.
  Different kind of skill.
  Here, though, access to reasons.
\end{note}

\begin{note}[Quick argument/upshot/stakes]
  Turn this into something of an argument.
  \begin{enumerate}
  \item\label{supp:arg:claim} Claim
  \item\label{supp:arg:need-supp} Would not be reasonable without support.
  \item\label{supp:arg:supp} Hence, if inference is okay then must be provided with support.
  \item So, either some additional support, or the agent rejects the conditional, or reduces confident in antecedent.
  \item\label{supp:arg:reasonable} Reasonable for the agent to hold true, and retain confidence.
  \item Additional support.
  \end{enumerate}

  Above, background reflections provided additional support.
  If not, then the agent would be required either to reject the conditional or lower confidence in ability.

  Inclined to think that [the toy argument from~\ref{supp:arg:claim} to~\ref{supp:arg:supp}] holds most of the time.
  Hence, the interest with \emph{ability} claims, and \AR.
  Often there is no other route provided, but here there is.

  So, agent has information about potential reasons, so to speak.

  Replace with:
  \begin{enumerate}
  \item So, either some additional support, or the agent rejects the conditional, or if ability then licenses support from ability.
  \end{enumerate}

  Focus of the paper is motivating this additional option.
  I haven't yet argued that no parallel to the background reasoning works in all cases.

  The upshot is that this opens up understanding of agents.
  However, argument is somewhat limited in scope.
  Specific cases, therefore open to further constraints.
  The most straightforward is strengthening the antecedent of the conditional, so that it only applies when the agent lacks additional support.

  Still, two options are not exclusive, and I counterpart argument will highlight a handful of cases to demonstrate potential.
  And, note that the focus on ability allows deviations from familiar accounts to be isolated.
  Of course, this limits generalisations, rationality goes beyond responding to reasons.
  However, given the relative uniqueness of ability, many of the arguments in support of general positions will continue to hold, and as such licensing supplements preferred theory.
\end{note}



\begin{note}[A little more]
  Easy to see when given some simple rules.
  For example, mathematics or logic.
  This isn't simply the ability to establish any theorem in the logic case.
  Some proofs may be out of reach.

  A little more straightforwardly by reversing, absence of a witness does not show inability.
\end{note}

\begin{note}[Tangential ex. for att. vs. witt.]
  An tangential example may help illustrate the difference.

  Height barrier to a ride.
  Attribute, particular height.
  Witness, walking under the bar.

  Here, arbitrary.
  Depends on the administration.
  Height is key, and the bar is a test.
  Or, bar is key, and height is an approximation.

  Rough around the edges.
  Taller, but slouching.
  Shorter, but hair.

  Preserved under transformations.
\end{note}

\begin{note}[Two ways of reading the argument, 2]
  Analogy does not stretch beyond illustrating basic difference.
  Ride entrance is defined in this way.
  Support is not.
  Still, difference.
  Potential for this to reflect difference in whether support flows.

  The characterisation of attribution and witnessing is rough, and will be detailed in time --- the following paragraphs, and the main argument.

  The latter, witnessing, reflects opening ideas.
  The agent appeals to potential reasons, as the agent hasn't done the reasoning.
  The former does not require this.

  The former is problematic.
\end{note}

\begin{note}[Two ways of reading the argument, 3]
  Worry that this is very much in the weeds, so to speak.
  Yes.
  Limitations from ability and from information.

  Still, significant.
  If witnessing is required in some cases, then question of whether this holds in cases where it is not required.
  And, significant because\dots (no detailed account).
\end{note}

\begin{note}[Hum]
  So, need to go through the reasoning sketched, and show that attribution doesn't quite work.
\end{note}


\hozlinedash

\begin{note}[Support and the distinction between propositional and doxastic justification.]
  Our use of support falls closer in line with doxastic justification as opposed to propositional justification.
  Roughly, following \textcite{Silva:2020aa}:

  \begin{quote}
    Propositional Justification (PJ): S has propositional justification to believe that p iff S has sufficient epistemic reasons to believe that p.

    Doxastic Justification (DJ): S has a doxastically justified belief in p iff
    \begin{enumerate*}[label=(\roman*)]
    \item S has propositional justification to believe that p,
    \item S believes that p, and
    \item S’s belief in p is appropriately connected to S’s sufficient epistemic reasons to believe it.
    \end{enumerate*}
  \end{quote}
  The difficult issue is whether an un-witnessed ability to demonstrate that something is the case constitutes having sufficient epistemic reasons to be confident the strategy exists.
\end{note}

\hozlinedash

\begin{note}[Attribution sketch: Novel information]
  {
    \color{red}
    Key point here is that the agent's support for \(A(\psi)\) just is the agent's support for \(A(\phi)\).
    Rather, if the agent has support for \(A(\psi)\) then the support is irresolute.
  }
  General ability with novel information provides irresolute support for (specific) ability.

  {
    \color{red}
    Similar to hardiness of knowledge --- explored in detail further along.
    Just as agent is not free to ignore potential counterevidence, the agent is not free to extend their ability to anything which follows.
  }
\end{note}


\begin{note}[Attribution sketch, part 2.5 --- trouble with transmission]
  Failure of transmission means that the agent does not obtain support for \(\psi\) from attributive reasoning.

  So, if support for \(A(\psi)\) then commitment to \(\psi\).
  Hence, either no support for \(A(\psi)\) or commitment to \(\psi\).\nolinebreak
  \footnote{
    Possible for both disjuncts.
    Though, hard to see why the agent would be committed if not for irresolute support.
  }
  And, counterpart proposition to commitment which is irresolutely supported.

  Issue is whether this is satisfactory.
  Tension is intuitive grasp on reasoning contrasted with limited conclusion from attributive reasoning.
  Could restrict the agent.

  Doubt there is any argument to show that the agent must have support.
  Still, seems to be something about understanding of ability.

  \begin{enumerate}
  \item\label{intuition:attitude-to-fact-from-ability-to-demonstrate} If agent is confident that they are able to show something which is true independent of ability, then it seems that agent does not have the option of withholding attitude toward that thing while retaining confidence in ability.
  \end{enumerate}

  Argument shows that this idea is incompatible with reasoning via attribution.

  Problems are about support for \(A(\phi)\) extending.
  Agent's support for \(A(\phi)\) remains the same (roughly, information could have an impact).
  Key issue is that the informer provided new information.
  However, the new information doesn't influence ability itself.

  The problems here arise because of attribute and novel information.
  Limited to type of reasoning.

  Note, this isn't particularly strong.
  It's from the agent's epistemic standpoint.
  It may be that the rules of chess require the fact (this seems likely).
  And, the fact may be sufficiently simple to indicate a failing of general ability (also likely).
  However, the agent does not have the strategy.

  So, support for general ability.
  Don't need the conditional to apply the ability to reach \(\psi\).
  Problem is coming from the having support for ability, rather than execution of ability.

  So, backwards looking, in a sense.
  With the novel information, agent is required to hold that \(\psi\) is the case.
  However, \(\psi\) follows from witnessing ability.
  Limit to commitment clashes with confidence in ability.

  Clash only if there is no alternative.

  Plausibility of~\ref{intuition:attitude-to-fact-from-ability-to-demonstrate} motives interest in witnessing.

  Would put the agent in position of resolute support for \(\psi\).
  However, agent has not done the reasoning.

  Still, novel information doesn't put the agent in a worse position with respect to application of the general ability.
  Novel information, and this shouldn't be taken against \(A(\phi)\).

  If the agent has the general ability, and the information is true, then the agent has the specific ability regardless of informer providing the information that this follows.

  \hozlinedash

  Intuition~\ref{intuition:attitude-to-fact-from-ability-to-demonstrate} is weaker than some nearby relatives.
  If committed and no opposing reason, then confidence.
  Seems strong.
  Perhaps too strong for what I need.

  Familiar to entitlement.
  Here, entitlement doesn't apply.
  However, executing ability does.

  Key difference to sight example, is that there is no need to deny confidence.
  The problem identified is appeal to some collection of reasons.
  Grant the agent license to appeal to these, then confidence seems fine.
  However, if deny this, then reject conditional or withhold consequence.
  {
    \color{red}
    Interest in the latter is this overstepping, but with option.
    Return to some parallels later.\nolinebreak
    \footnote{
      Basically, with the seeing case, the agent possesses the relevant reasons, but is not able to distinguish them.
      This is somewhat close to Pritchard's disjunctivism.
    }
  }
  Maybe in line with the \citeauthor{Harman:1973ww} idea, the novel information doesn't show that the agent doesn't know, but prevents the agent from expanding their prior knowledge.
\end{note}



\hozlinedash

\section{Negative part --- Attribution}
\label{sec:negative-part}

{\color{red}
\begin{note}[Irresolute support]
  In the following I make use of the notes of resolute and irresolute support.
  The distinction is temporary, and basic.
  \begin{itemize}
  \item Resolute support allows an agent to discard possibilities incompatible with the proposition the agent has support for.
  \item Irresolute support by contrast allows an agent (only) to consider possibilities incompatible with the proposition the agent has support for unlikely.
  \end{itemize}
  For example, it is plausible that in normal circumstances an agent has resolute support for the digits of their phone number --- the agent may rule out the possibilities that an apparent misprint on a business card turns out to be correct.
  Contrasting, it is plausible that in normal circumstances an agent has irresolute support for the location of their car keys if they haven't driven if a few days --- it may be likely that the keys are in the bowl by the front door, but it may also be the case that the keys were left in a jacket.

  The support of interest throughout this section is irresolute support.
  The agent may be mistaken about their general ability to reason with the rules of chess, that the informer is providing truthful information, that the agent possess the ability to demonstrate the existence of the (particular) strategy, and that the (particular) strategy exists.

  Of course, if the agent demonstrated that the strategy existed then the agent would plausibly obtain resolute support for the existence of a strategy, but given the agent is reasoning from possession of the ability, the present interest is in whether the failure of a strategy to exists is unlikely.
\end{note}

\begin{note}[Expanding a little]
  Indeed, it seems there is a clear problem if the agent attempt to rule out the possibility of a strategy not existing by the reasoning sketched.
  For, given that the agent may be mistaken about possessing the general ability, then it seems the agent cannot rule out the possibility that a strategy does not exist, as the agent is assumed not to have independent support (either resolute or irresolute) for the ability to demonstrate the existence of the (particular) strategy, nor for the existence of the (particular) strategy.

  Still, if the agent is mistaken, this is not to say that it is a mistake for the agent to hold an attitude such as belief toward the relevant proposition given the (irresolute) support the agent has for the proposition.
  Rather, the agent would be mistaken about what is the case, and misled by the support possessed.
\end{note}
}

The overarching goal is to motivate interest in \WR.
The introduction focused on the distinction between \AR{} and \WR.
Here, we also focus on whether the agent has an alternative route to support for the existence of the (particular) strategy via \AR.

Two parts.
\begin{itemize}
\item Conditional information --- any support for \(A(\psi)\) is locked behind \(A(\phi)\).
\item Failure of transmission --- agent is not able to leverage any support for \(A(\psi)\) to get \(\psi\).
\end{itemize}

The first part helps set up \WR{} and \AR{} as the relevant options.
And, highlights some observations useful when examining \AR{} in detail --- and \WR{} down the line.

The second part is where the primary interest is.
Goal, again, is to develop problematic case in which \WR{} is favoured over \AR.
So, sufficient, but not necessary.
Rather, given motivation for \WR{} over \AR{} in some case, then see how \WR{} fares over \AR{} in cases where there are alternatives to \AR{}.

\subsection{The role of the conditional}
\label{sec:role-conditional}

\begin{note}[Perspectives on \(A(\phi)\)]
Key here is that the agent is working with their ability.
\(\psi\) is novel information.
Hence, \(A(\phi)\) is given an evidential role.
This is because \(A(\phi) \rightarrow A(\psi)\) is novel information to the agent and the agent did not have support for \(A(\psi)\) previously.

Some definitions will help.
\(A^{-}(\phi)\) before informer's information.
and
\(A^{+}(\phi)\) after the informer's information.\nolinebreak
\footnote{
  The notation is oblique, but as we're only dealing with a single piece of information, I think it is okay.
}
So, whether or not \(A(\psi)\) is new evidence.
This has a similar role to misleading evidence.

Regardless of the agent's prior confidence of their ability, upon accepting the informer's conditional, \(A(\psi)\) has the potential to change.
So, grant that the informer provides evidence, and this then places the agent in a position where their prior confidence in ability provides defeasible support for the enhanced ability attribution.

The key point, then, is that the agent doesn't have a demonstration of \(\psi\), and therefore the agent is soft with respect to \(A(\psi)\).

In turn, the evidential status of \(A^{+}(\phi)\) raises two problems.
Blocks a deductive inference.
Gives rise to failure of transmission.

This is sensitive to the information conveyed.
It is possible that the informer could have addressed \(A^{-}(\phi)\).
On the one hand, we are looking for cases, and can ignore this.
On the other, it seems bad.
This does not say anything about \(A(\phi)\).
And, finally, \(A^{-}(\phi)\) being bad does not require \(A^{+}\) to be good.
Rather, I take the former to be straightforward, and the latter to require some thought.
\end{note}

\begin{note}[Informer's reasoning]
  Note that the informer is in a different position, if we assume the informer did the reasoning.
  For, the informer assumes \(A(\phi)\).
  Does the reasoning.
  Hence, \(A(\psi)\) conditional on \(A(\phi)\).

  For now, assume that reasoning is fine, and if the agent has reasoned then that reasoning is okay.
  Detail further along.
\end{note}

\begin{note}[Sketch]
  As noted above, the problem is in part due to the conditional.
  The purpose of this section is to isolate the conditional as the agent's only route to \(\psi\).

  In part, this involves clarifying the conditional.
  In part, this considers other options.
\end{note}

\begin{note}[Introduction]
  First step is to isolate the reasoning.
  Going via the conditional.

  This impacts both lines of reasoning.
  One the one hand, no problem if the agent does not need to assume \(\psi\).
  On the other hand, if there are available reasons, then the agent doesn't need to appeal to potential reasons for \(\psi\).

  Looking for the existence of cases.

  Still, existential with a universal.
  So, a little more difficult.
  Further, properties preserved in other cases.

  So, two properties.

  \begin{enumerate}
  \item No alternative support (Novel information, could fail).
  \item Conditional on ability.
  \end{enumerate}

  The second property reduces to two further parts.

  \begin{enumerate}
  \item The informer does not need to be confident that \(\psi\).
  \item The informer is talking about the agent's abilities, and does not commit to whether the agent has the antecedent ability.
  \end{enumerate}

  The first requires support to come from the informer.
  The split of the second looks at the consequent and the antecedent.
  The informer doesn't have a positive attitude toward the consequent.
  And, the informer doesn't have a positive attitude toward the antecedent.
\end{note}

\begin{note}[Difficulty in what needs to be shown]
  The arguments attempt to make a case for restricted information.
  Searching for an existential, but with an embedded universal.
  Hence, do not rule out support somehow being provided.
\end{note}

\begin{note}[Clarifying the conditional]
  Key here is that the conditional states that if the agent has a general ability then the agent has a specific ability.

  Understand ability in terms of something like events.

  Key point is that this may be established by the informer on the basis of the agent having some ability, but without a stance of whether this is the ability to reason with chess.
\end{note}

\begin{note}[Conditional - informer's reasoning doesn't offer support - main point]
  The first main point is that the informer is linking ability.
\end{note}

\begin{note}[Initial point --- information is directed at the particular agent]
  Here, not talking about ability in general.
  Point noted above.
  If the agent had the option of substituting in a different agent, then seems the agent gets support.
  For, can only make the conditional if it's true that anyone with an ability general that fits the description has the specific ability.
\end{note}

\begin{note}[Conditional - informer's reasoning doesn't offer support]
  Important consequence of no commitment to the rules of chess is even if the agent is confident that the informer has witnessed some instance of the agent's ability, this does not provide support for \(\psi\).
  For, it is still on the agent to classify the witness as an instance of demonstrating \(\psi\).
\end{note}

\begin{note}[Informer doesn't need to be confident of ability]
  Following from not offering support, the informer doesn't need to be confident of either the antecedent or consequent.

  Second, the informer does not need to think that \(\psi\) is the case.
  Again, chess is useful.
  Here, the main idea is that the informer is sufficiently uncertain.
  So, the informer is not taking a stance on whether the agent actually has the ability to reason with the rules of chess, though the informer is informing the agent about where the agent's reasoning will lead the agent.
\end{note}

\begin{note}[Conditional confidence, further clarification]
  May help to contrast to a case which doesn't have this restriction.

  Classical and intuitionist.
  The intuitionist provides a classical proof.
  Does not intend to provide support (similar to the second case), but for the classical it does provide support.
  Even if the intuitionist does not show the working, testimony of a classical proof seems sufficient.

  Here, different.
  For, same argument as above.
  The informer is indifferent on whether they have witnessed a strategy.
  And, the difficulty for the agent is that the agent doesn't have access to the strategy.

  If your grasp on classic is good, then demonstrate \(\psi\).

  So, the reasoning is still the agent's, so to speak.
  Hence, the agent is still required to endorse the antecedent of the conditional.

  Further, stated in terms of kind of proof, then distinct from the particular ability of the agent.
  And, get a similar problem if this extends beyond proof into modelling.
  For, then the intuitionist isn't going to endorse some modelling hypothesis, and it is on the classical to add this assumption in order to get a particular `factive' result.

  \hozlinedash

  An important point, then, is that the agent doesn't have the option of taking the informer to have done anything other than witness the agent's ability.
  The informer does not provide a statement of fact and a statement of ability.
  Rather, the statement of fact follows from statement of ability, if other premises are secured.

  Hence, attribution and witnessing.
  Both relate to ability in different ways.\nolinebreak
  \footnote{
    Reasoning by the informer is similar to witnessing as sketched.
    Return to this observation.
    Short insight, though, is that as things stand there doesn't seem to be anything significant about someone other witnessing the same ability.
    Allows the informer to state what follows, but other than that, nothing much.
    Indeed, separate the witnessing from the informer.
    Possible for the agent to do most of the witnessing depending on how the example is constructed.
    Describing the specific ability as solving a particular chess puzzle which just is the problem that the agent has solved.
    Though, it's a little murky as to whether these kind of cases would really provide an interesting counter to the opening conditional.
    In contrast, the cases of focus, the agent hasn't done reasoning given referential opacity.
  }
\end{note}

\begin{note}[Main clarification complete]
  Points about linking ability and confidence are most important.

  Offer a handful of minor observations, and so additional illustrations before turning to transmission.
\end{note}

\begin{note}[Distinguish from close relatives]
  Important is that this is not the same as \(A(\psi)\).
  Then \(A(\psi) \rightarrow \psi\).
  Hence \(\psi\).

  To be detailed later.
\end{note}

\begin{note}[Observation on dynamics]
  Observe that intuitively, if the agent were to attempt the reasoning, they would drop confidence in general ability before dropping confidence in fact.

  Minor observation that one would expect the agent to initially drop confidence in ability, even if going by conditional.
  Hence, this should not be taken to indicate that the agent has greater support for consequent.
\end{note}

\begin{note}[Alternatives to conditional]
  If there is an alternative line of support for \(A(\psi)\), then it is plausible that this also supports \(\psi\).
\end{note}

\begin{note}[Possible altnerative: Support is required, so informer provides]
  Novel information, so the agent has no antecedent support for \(\psi\).
  The informer does not need to be confident that \(\psi\), so the informer cannot be reformulated to intentionally communicating that \(\psi\).
  Agent's abilities, so even if the agent is confident that the informer has done the reasoning, the agent doesn't have the option regardless of the informer's intention.
\end{note}

\begin{note}[Possible alternative: Information itself]
  Assumption that either the agent would already have support for \(\psi\) or that the information provides support.
  Possibilities that void this.
  For example \(\mathcal{C}(A(\phi) \rightarrow A(\psi)) \rightarrow \psi\).
  Maybe.
  This would relate conditional to content in some way.
  Assuming that the informer is only good for the conditional if they're also good for the content.
  So, additional information that comes paired with the explicit information provided by the informer.

  This kind of reasoning doesn't require the conditional.
  So, for example, flip the background information and it's good support for no strategy.
\end{note}

\begin{note}[Additional examples]
  The first is straightforward.
  Chess is a nice example here.
  Other examples work well.
  For example, logic or arithmetic.

  In these examples, core set of actions, so to speak.
\end{note}

\begin{note}[Useful information]
  General to specific makes sense, and is useful information.

  Still, in these examples, the general ability doesn't require specific abilities.
  Again, chess neatly demonstrates this.
  It is clear that at some point there are problems that go beyond a particular agent's ability within the context.
  This is not to deny that the agent may acquire the ability.

  Same with sufficiently difficult logic problem.
  Used to examples with relatively short proofs.
  However, sufficiently long, and it becomes increasingly easy to overlook premises and exhaust oneself in dead ends.
\end{note}

\begin{note}[Summary]
  Focused on the information provided by the informer.
  Main focus was the conditional.
  And, that this is conditional on the agent's ability.
  Something of a check/elaboration on initial reading.
  So, proceed to the problem.
\end{note}

\begin{note}[The conditional is targeted toward the agent]
  The agent is the one with the ability, and also the one who receives the information.
  Minor, but worth noting.

  Interest in witnessing is due to this convergence.
  When the agent is different, seems the third party gets irresolute support for \(A(\psi)\).
  But, still lack for \(\psi\), as this needs to be assumed.

  Contingent on witnessing, then.
\end{note}

\begin{note}[From the above]
  One possibility was that:
  \begin{itemize}
  \item General ability \(\rightarrow\) (Specific ability \(\land\) fact).
  \end{itemize}
  So, the agent's general ability provides support for both the specific ability and the fact.

  This isn't quite right.
  At most, the agent obtains support for the specific ability.

  So, the agent is the required to use the support obtains for the specific ability to obtain the background requirements.

  The agent does not obtain support for the existence of the strategy from their support for their general ability and the conditional information.
  This is distinct.
  Can substitute in the conjunction.
  Why is this different?

  Well, the point is that if the agent were to receive the conjunction, then the agent would be in a position to simplify.
  And, if the agent simplifies, then it's straightforward to observe that the agent possessing the general ability is irrelevant to the existence of the strategy.
  Therefore, it seems the informer provides the informer that the strategy exists.

  This, intuitively, is not required.
  The information is only about the expansion of the agent's general ability, and the route to the existence of the strategy is that the existence of a strategy is required.
\end{note}

\subsection{Transmission}
\label{sec:transmission-overview}

\begin{note}[The reasoning (failure of deduction)]
  So, \(A^{+}(\phi)\) is not support for \(A(\phi)\).
  And, in turn, extends to \(A(\psi)\) given the informer's information.
  So, support for \(A(\psi)\).

  So, reasoning via modus ponens isn't right.
  The problem is that \(A^{+}(\phi)\) isn't the same as \(A(\psi)\), and so the agent doesn't detach \(A(\psi)\).
  Instead, the agent is in a position where \(A^{+}(\phi)\) supports \(A(\psi)\), given the information that the agent has.

  The issue is whether the agent gets \(\psi\).

  For, assumed that this still puts the agent in position of having support for \(A(\psi)\).
  The informer's information doesn't suggest that \(A(\psi)\) nor \(\psi\) fails to be the case.

  Interest is in how the support transmits.
\end{note}



\subsubsection{Transmission overview}
\label{sec:transm-overv}

\begin{note}[Transmission]
  An understanding of transmission is important to outline.
  The key is that the agent `obtains' support.
  There are many arguments where transmission is not require, and the relevant observation is that the support the agent has for some proposition is also support for some other proposition.
  So, this is repurposing, rather than transmission.
  Very simple example is \(p\) to \(p \lor q\).

  This is somewhat intuitive.
  Easiest to consider when we're dealing with \dots
  This isn't so clear.

  Thinking about:
  \begin{itemize}
  \item The wall is red.
  \item So, the wall is coloured.
  \end{itemize}
  The conclusion is understood to state that the wall is not white.
  Then, this looks like transmission.
  However, this also comes from re-describing/weakening the proposition.
  So, in line with the disjunction instance.
  Well, not quite, as this doesn't seem to violate the template.
  There's no relevant cognitive project which would separate the two.
\end{note}

\begin{itemize}
\item Previous section focused on the information provided by the informer.
\item \emph{If} agent has ability to \(\phi\) \emph{then} the agent has the ability to \(\psi\).
\item Requires confidence that \(\psi\).
\item This section, two reasoning patterns sketched.
\end{itemize}

\begin{note}[Goals]
  Have two ways of approaching the conditional.

  First, attributive.
  Intuition is that the agent attributes themselves the general ability, and reasons from the attribute of having the ability.
  On first pass, attribution of ability combines with the conditional information.
  This is, roughly, extending, rather than an instance of modus ponens, as noted.

  Goal is to highlight problem with attributive.
  Reasoning from possession of general ability to possession of specific ability.
  So, the agent does not appeal to the reasoning that they are able to do.
\end{note}

\begin{note}[Two distinct arguments]
  Have to distinct observations about \AR.
  \begin{itemize}
  \item First, we suggest that there is transmission failure to the existence of a strategy.
  \item Second, we argue that if --- contrary to the first argument --- there is transmission to the existence of the strategy, understanding this as a result of \AR{} leads to successful transmission to other propositions, which do seem problematic.
  \end{itemize}
  We treat these as two separate arguments, as the two conclusions are important.
  However, from a broader perspective the section is an extended look at \AR.
\end{note}

\begin{note}[Structure]
  This section is split into three parts.
  \begin{enumerate}
  \item A review of \AR{} and transmission.
  \item Inertia.
  \item \citeauthor{Wright:2016wl}.
  \end{enumerate}
\end{note}

\subsection{Understanding transmission}
\label{sec:underst-transm}

\begin{note}[Introduction, summarising previous section and interest]
  This section of the paper considers whether an agent is able to obtain support for the existence of a chess strategy on the basis of support for possessing the general ability to reason with the rules of chess and informer from an informer that if the agent is able to reason with the rules of chess, then the agent is able to demonstrate the existence of a particular strategy.

  Our interest is with the following pattern of reasoning.
  \begin{enumerate}[label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:cond:ant} I have the ability to reason with the rules of chess.
  \item\label{inf:cond}\label{inf:cond} If I have the ability to reason with the rules of chess then I have the ability to demonstrate the existence of a (particular) strategy.
  \end{enumerate}
  As~\ref{inf:cond:ant} is the antecedent of~\ref{inf:cond} and the consequent of~\ref{inf:cond} is novel information, \ref{inf:cond:ant} and~\ref{inf:cond} combine to provide support for:
  \begin{enumerate}[resume, label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:cond:conq} I have the ability to demonstrate the existence of the (particular) strategy.
  \end{enumerate}
  Sub-conclusion~\ref{inf:cond:conq}, is the antecedent of the following conditional:
  \begin{enumerate}[resume, label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:gae} For any strategy, an agent has the ability to demonstrate the existence of the strategy only if the strategy exists.
  \end{enumerate}
  Therefore:
  \begin{enumerate}[resume, label=(S\arabic*), ref=(S\arabic*)]
  \item\label{inf:sse} The (particular) strategy (that I am able to demonstrate) exists.
  \end{enumerate}

  In the previous section we argued that an informer providing the agent with~\ref{inf:cond} does not provide the agent with support for~\ref{inf:cond:conq}.
  Rather, an informer providing the agent with~\ref{inf:cond} allows the agent to extend their support for~\ref{inf:cond:ant} to~\ref{inf:cond:conq}.

  In turn,~\ref{inf:gae} to obtain~\ref{inf:sse}.

  In short, the agent's support for~\ref{inf:sse} rests on expanding their general ability to a specific ability.

  The type of argument here is familiar.
  The agent's goal is to \emph{transmit} support for~\ref{inf:cond:conq} to~\ref{inf:sse} \emph{via} the entailment noted in~\ref{inf:gae} --- from the ability to demonstrate the existence of a (particular) strategy across a (known) entailment to obtain support for the existence of a (particular) strategy.

  For, the information provided by the informer is conditional, and so in turn the support the agent has for the ability to demonstrate the existence of a (particular) strategy is primarily premised on the support the agent has for being able to reason with the rules of chess.
  So, the agent does not have support for~\ref{inf:cond:conq} nor~\ref{inf:sse} that is independent of their general ability to reason with the rules of chess.

  Hence, with the result of the previous section in hand, we may now turn to \emph{how} the agent obtains support for~\ref{inf:sse} given support for~\ref{inf:cond:conq}.

   Our interest in the reasoning is from~\ref{inf:cond:conq} and~\ref{inf:gae} to~\ref{inf:sse}, and in particular how ~\ref{inf:gae} is applied.
\end{note}

\begin{note}[Introduction, two different types of reasoning]
  In the opening section we canvassed two distinct ways in which the agent may obtain support for~\ref{inf:sse} given support for~\ref{inf:cond:conq}.
  We termed these \AR{} and \WR{}.

  Roughly, \AR{} observes that support for~\ref{inf:cond:conq} may be understood as support for the \emph{attribute} of having the ability to demonstrate the existence of a particular strategy.
  And, in turn,~\ref{inf:sse} follows from the attributive understanding of~\ref{inf:cond:conq} and~\ref{inf:gae} by understanding~\ref{inf:gae} to highlight conditions that must be in place in order for the agent to possess the attribute.
  Intuitively, an agent may have the attribute of being able to demonstrate the existence of a strategy only if the strategy exists.

  By contrast, \WR{} observes that support for~\ref{inf:cond:conq} may be understood as support for the \emph{generating a witnessing event} of demonstrating that the (particular) strategy exists.
  For, to have the ability to demonstrate the existence of a particular strategy is just for there to be some (potential) event in which the agent applies their understanding of the rules of chess to obtain a demonstration of the relevant strategy.

  The `problem' with \WR{} is that the relevant witness is potential.
  The agent has not (yet, nor necessarily will) reasoned with the rules of chess and the state of the board to demonstrate the existence of the (particular) strategy.
  Hence, if the agent appeals to a (potential) witness, then the agent appeals to \emph{potential} reasons (or reasoning).

  Intuitively, \AR{} avoids the noted problem with \WR{}.
  For, the attribute of having the ability to demonstrate the specific strategy is an attribute of the agent as they are.
  The agent may not, as a matter of fact, have the ability, but granting that the agent has support for possessing the attribute, the agent is not required to appeal to potential events.
\end{note}

\begin{note}[Transmission, the basics, definition]
  From a broad perspective, transmission may be characterised with respect to the state of an agent, premises, and conclusion.
  Failure of transmission is when, relative to the state, the support the agent has for the premises does not transmit to the conclusion.

  Following \textcite{Moretti:2018we,Moretti:2018tl}, with minor adjustments,\nolinebreak
  \footnote{
    Replace justification with support, logical consequence with entailment, omit belief in the last.
    Template works for both propositional and doxastic, differs on reading of support.
    Given focus is doxastic, suppress.

    Most important is dropping requirement for knowledge in~\ref{sep:trans:ii}.
    
  }
  (first time) transmission of support is be characterised as follows:
  \begin{quote}
    \emph{S}'s support for \emph{A} based on \emph{E} transmits from \emph{A} to \emph{B} if and only if:
    \begin{enumerate}[label=(T\arabic*), ref=(T\arabic*)]
    \item\label{sep:trans:i} \emph{S} has support for \emph{A} based on \emph{E},
    \item\label{sep:trans:ii} \emph{S} is confident that \emph{B} is entailed by \emph{A}, and
    \item\label{sep:trans:iii} \emph{S} obtains (\emph{first time}) support for \emph{B} \emph{in virtue of} the satisfaction of \ref{sep:trans:i} and \ref{sep:trans:ii}.
    \end{enumerate}
  \end{quote}
\end{note}

\begin{note}[After observations]
  A non-transmissive triad of \emph{E}, \emph{A}, and \emph{B} may be due to the failure of either~\ref{sep:trans:i},~\ref{sep:trans:ii}, or~\ref{sep:trans:iii}.

  For, if~\ref{sep:trans:i} fails then the agent does not have support to transmit from \emph{A} to \emph{B}.

  If~\ref{sep:trans:ii} fails then the agent is not confident that \emph{A} entails \emph{B}, and hence lacks an appropriate relation between \emph{A} and \emph{B} for support to transmit over.

  Finally,~\ref{sep:trans:iii} fails if
  \begin{enumerate*}
  \item the agent already has support for \emph{B},
  \item either~\ref{sep:trans:i} or~\ref{sep:trans:ii} are unsatisfied, or
  \item the satisfaction of~\ref{sep:trans:i} or~\ref{sep:trans:ii} do not provide the agent with support for \emph{B}.
  \end{enumerate*}
  Note, the agent may still obtain support for \emph{B} from some other basis.
\end{note}

\begin{note}[Transmission characterisation applied to argument]
  With respect to the case of interest:
  \begin{transmission}[Chess]
    \begin{enumerate}
    \item[\tri{C}{E}]
      The result of combining:
      \begin{enumerate}[label=\tri{C}{E}\arabic*.]
    \item\label{C:tr:E1} the agent's support for the general ability to reason with the rules of chess, and
    \item\label{C:tr:E2} the conditional information provided by the informer that if the agent has the general ability to reason with the rules of chess then the agent has the specific ability to demonstrate that some (particular) strategy exists.
    \end{enumerate}
    \item[\tri{C}{A}] The attribute of having the (specific) ability to demonstrate that some (particular) strategy exists
    \item[\tri{C}{B}] The (particular) strategy exists.
    \end{enumerate}
    Or, alternatively:
    \begin{enumerate}
    \item[\tri{C}{B\('\)}] Any apparent demonstration of a conflicting strategy is the result of a mistake.
    \end{enumerate}
  \end{transmission}

  Condition~\ref{sep:trans:ii} is satisfied by the recognised entailment from the ability to demonstrate a specific strategy to the existence of the strategy --- if the (particular) strategy did not exist, the agent would not have the ability to provide a demonstration of it.

  Further, given that the information about the particular strategy provided is novel, any support obtained for \tri{C}{B} will be \emph{first time} support.
  And, as the agent has no other information regarding \tri{C}{B}, any support obtained for \tri{C}{B} will be in virtue of the agent's support for \tri{C}{A} (~\ref{sep:trans:i}) and the entailment from \tri{C}{A} to \tri{C}{B} (~\ref{sep:trans:ii}).
  For, we have assumed the information provided by the informer is novel, we have no need for a broader characterisation of transmission.\nolinebreak
  \footnote{
    See \textcite{Moretti:2018we,Moretti:2018tl,Moretti:2013wd}, for more.
  }

  Our interest primarily concerns condition~\ref{sep:trans:iii}.
  Whether the agent obtains support for the existence of some (particular) strategy in virtue of their (irresolute) support for the ability to demonstrate the existence of the strategy and the relevant entailment.
  However, also~\ref{sep:trans:i} --- specifically, the way in which the agent obtains support for \tri{C}{A} based on \tri{C}{E} (~\ref{sep:trans:i}).
\end{note}

\begin{note}[The two arguments]
  The `inertia' argument focuses on \ref{inf:cond}, the information provided by the informer.

  The `other' argument focuses on whether~\ref{inf:gae} is suitable for transmission.
  Tension between transmission from ability and transmission from the relevant witnessing event.
\end{note}

\begin{note}[A little more on transmission]
  \AR{} fits the transmission template.
  \WR{} does not fit the transmission template, though the relevant instance of reasoning presumably does fit the template.

  So, required transmission of \AR{} and the deferred transmission of \WR{} looks like something of interest.
\end{note}

\begin{note}[Still]
  If~\ref{inf:gae} then support transmits to propositions for which transmission would fail given the relevant witnessing event.

  In short, because the agent obtains support for prerequisites of event independent from the relevant witnessing event.
\end{note}

\begin{note}[Handful of observations]
  Still, before moving to transmission failure, let us make a handful of observations that will help maintain continuity between the reasoning sketched and the type of argument we will be using as an example.
\end{note}

\begin{note}[Role of factivity]
  First, the factivity of the verb `demonstrate' is the foundation of the entailment from the agent possessing the (specific) ability to demonstrate the existence of a strategy to the existence of a strategy.
  We may replace demonstrate with other factive verbs and obtain the same entailment.

  For example, see, receive testimony, learn, and so on all have the same entailment and lend to similar constructions.
  \begin{enumerate}[label=(FV\arabic*), ref=(FV\arabic*)]
  \item\label{FV:1} An agent has the ability to see that it is raining only if it is raining.
  \end{enumerate}
  The conditional is silent on what constitutes the ability to see that it is raining, but the antecedent requires the consequent in order to be true.
  There is some subtly, however.
  For, in absence of the entailment the antecedent may be ambiguous.
  \begin{enumerate}[label=(FV\arabic*), ref=(FV\arabic*)]
    \setcounter{enumi}{1}
  \item\label{FV:2} An agent has the ability to receive testimony that it is snowing.
  \end{enumerate}
  On one reading,~\ref{FV:2} states that if we suppose that someone were to testify, then the agent has the ability to receive that testimony.
  For example, the agent is not so prejudiced against the idea of snow to discount the message of anyone attempting to inform the agent.
  Still, on the reading of interest, the `factive inference' is required.
  Examples can be found to show that verbs such as argue, suggest, recommend, don't exhibit the same `factive inference'.
\end{note}

\begin{note}[Relation between attribute and event]
  Second, the ability to demonstrate, see, receive testimony that, and so on is a property of the agent.
  However, the factive inference is due to a verb.
  Hence, that the agent has the property of having the ability to demonstrate, see, receive testimony that, and so on is in part secured by the resultant state of event in which the agent demonstrates, sees, receive testimony that, and so on, and these verbs impose that the relevant fact must be part of the event.
  In turn, for any ability to \emph{V} \(\phi\) there is a corresponding possibility of an event in which an agent \emph{V}s \(\phi\), and vice-versa.
\end{note}

\begin{note}[Chaining entailments]
  Third, it is possible to chain entailments.
  The agent has the ability to see that it is raining only if it is raining, but it is raining only if the atmospheric conditions are not sufficient for hail.
  Therefore, the agent has the ability to see that it is raining only if the atmospheric conditions are not sufficient for hail.

  There are not too many entailments that follow from the ability to demonstrate the existence of a (particular) strategy.\nolinebreak
  \footnote{
    E.g.\ unique answer, rules aren't open to interpretation.
  }
  However, in other cases, more interesting entailments.
  Foreshadowing, see a donkey then not a cleverly disguised mule.
\end{note}

\begin{note}[Wrapping up observations]
  Let us wrap up these observations.
  Our interest is in whether support extends from the ability to demonstrate the existence of a (particular) strategy to the existence of a the (particular) strategy.
  The first observation allows us to generalise to other factive verbs such as seeing.
  The second observation, links the agent possessing the ability to do something to the possibility of an event in which the agent does the things.
  And, finally, the third observation, broadens the relevant entailments from the ability to \emph{V} \(\phi\) to \(\phi\) to any \(\psi\) entailed by \(\phi\).
\end{note}

\subsection{Two arguments}
\label{sec:two-arguments}

\begin{note}[Overview]
  We have a basic understanding of transmission and where our interest lies.
  We now turn to the two arguments.

  First, focusing on relation of support between \tri{C}{E} and \tri{C}{A} is sufficient for~\ref{sep:trans:iii}.
  Second, assuming that the relation of support between \tri{C}{E} and \tri{C}{A} is sufficient for~\ref{sep:trans:iii} and questioning whether~\ref{sep:trans:iii} holds.
\end{note}

\subsubsection{Inertia}
\label{sec:inertia}

\begin{note}[Overview]
  The first argument concerns the relation between the support the agent has for their (general) ability to reason with the rules the chess, the information provided by the informer, and the (specific) ability to demonstrate the existence of the (particular) strategy.
  The move from~\ref{inf:cond:ant} and~\ref{inf:cond} to~\ref{inf:cond:conq}.

  We argued in section~\ref{sec:role-conditional} that the agent does not obtain support for the existence of the (particular) strategy from the informer.

  Here, we consider how support moves given the conditional information.
\end{note}

\begin{note}[Not modus ponens]
  The move from~\ref{inf:cond:ant} and~\ref{inf:cond} to~\ref{inf:cond:conq} is on the basis of conditional information.
  Etc.\
  This has been detailed above.

  Rather, the agent is extending their general ability to a specific case.
\end{note}

\begin{note}[No support for the consequent]
  The key here, then, is a lack of independent support for the consequent.

  Further, 
\end{note}

\begin{note}[What the informers claim does]
  The claim made by the informer does two things:
  \begin{enumerate}
  \item Provides information about how the agent's ability extends.
  \item Requires the agent to:
    \begin{enumerate}
    \item Hold that they have the specific ability if they have the general ability.
    \item Give up the general ability.
    \item Not incorporate the claim.
    \end{enumerate}
  \end{enumerate}

  The agent may no incorporate the claim.
  Of course, but grant that the informer seems fine.

  Else, the conditional is something of a consistency constraint.

  If the agent doesn't think that they have the (specific) ability to demonstrate the existence of the (particular) strategy, then the agent should hold that they do not have the (general) ability to reason with the rules of chess, as the informer has claimed that the ability puts them in a position to provide the informer.

  Likewise, if the agent thinks they have the (general) ability to reason with the rules of chess, then the (specific) ability to demonstrate the existence of the (particular) strategy is merely an instance of the (general) ability that they have.
\end{note}

\begin{note}[Still, compatible with both]
  So, argue that this is a consistency constraint.

  Still, also notice that the conditional is compatible both with the agent having the (general) ability and with the agent not having the (general) ability.

  If the agent has the (general) ability, then the conditional is true because the general ability extends to the specific case.

  If the agent does not have the (general) ability, then the conditional is true because the antecedent condition is not met.
  As the ability referenced isn't the ability to reason with the rules of chess, then it trivially follows.

  From one perspective this is something of a technicality, information with a conditional structure only matters when the antecedent is true.
  Still, it does not follow that the informer is mischievous if they do not think that the agent has the general ability.

  It may be that the informer is indirectly showing the agent that they do not have the general ability.

  For example, given the lack of specifics, this then allows the agent to work out where their misunderstanding of chess lies by themselves.
\end{note}

\begin{note}[Combining the two observations]
  Here, we have a combination of constraint and compatibility

  So, if the agent holds that they have the specific ability, then it's as the result of constraint which is compatible with the agent not having the general ability.

  So, the agent is obtaining support for the specific ability on the basis of support they have for general ability.
  The agent has no direct support either way for the specific ability, prior to witnessing the ability.
\end{note}

\begin{note}[Rejection]
  Given the compatibility observation, may wish to withdraw.

  However, the claim made by the informer doesn't suggest that there's anything problematic.
\end{note}

\begin{note}[Inertia]
  Term this `inertia'.

  Obtain support by inertia if it's the result of a constraint on attitudes which is compatible with the agent being mistaken about the relevant antecedent.
  Intuitively, the support the agent has built for the antecedent tilts the consistency constraint to the consequent.
  If the agent didn't have the support already, the constraint wouldn't much.
\end{note}

\begin{note}[Inertia and transmission]
  Question, now, is whether support obtain by inertia is suitable for transmission.

  Intuitively, the `momentum' will carry through to entailments.

  However, this means that the agent is allowed to appeal to propositions for which they have no `direct' support.
  The extension of the support the agent has for the general ability to the specific ability is insensitive to whether or not the agent has the specific ability.
  
\end{note}

\begin{note}[Fire alarm case]
  Consider the fire alarm case.

  If conditional is given before fire alarm, then not inertia, as the structure of support is now that the alarm sounding entails that there's a fire.

  If conditional is given after fire alarm, then not inertia, because then wouldn't be hearing the fire alarm.

  The source of the problem, so to speak, is that the agent doesn't have any way of holding that they would not have been given the information if they did not have the general ability.
\end{note}

\begin{note}[Zebra case]
  Here, helpful to look at some other cases.

  With the zebra, 
\end{note}

\begin{note}[Something with how the agent gets to ability]
  It's straightforward to observe that the information provided by the informer is compatible with the agent having the general ability, and with the agent not having the general ability.

  In turn, it seems as though the agent is okay with using the conditional, because the agent has quite good support for the antecedent of the conditional, and no support (independent of the conditional) either way for the consequent.

  However, this itself seems to be a problem.
  Here, there's a parallel to \citeauthor{Wright:2016wl} in that on \citeauthor{Wright:2016wl}'s understanding the agent assumes certain things in order to employ the relevant method, and this blocks transmission.
  Here, in turn, it seems that because the agent relies solely on the conditional which is compatible both ways, the agent likewise takes it for granted, in some sense, that the conditional is to be used.

  The basic idea, then, is that support then fails to transmit when the relevant proposition is the result of something that could go either way.

  \begin{itemize}
  \item If support for some proposition \(\phi\) is obtained by inertia, then it is not possible to transmit the support to any consequence \(\psi\) of \(\phi\), on the basis of support for \(\phi\) alone.
  \end{itemize}
  Where:
  \begin{itemize}
  \item Support for \(\phi\) is obtained by inertia if
    \begin{enumerate}
    \item \(\phi\) not being the case is compatible with the support appealed to, and
    \item \(\phi\) is obtained solely on basis that the agent would be required to hold that the support appealed to would be misleading if \(\phi\) were not the case.
    \end{enumerate}
  \end{itemize}
  In this sense, because the agent is relying on the inertia provided by previous support, the agent is not in a position to incorporate \(\phi\) as the basis of support for further consequences.

  Intuitively, the support the agent has is insufficiently sensitive to \(\phi\), but given the information the agent has, the agent does not have the option of withholding an attitude toward \(\phi\) without also holding that the support they have is misleading.

  The label of `inertia' is fairly intuitive.
  It's also independent from \citeauthor{Wright:2016wl}.
  And, it really focuses in on the idea that the agent is being required to extend the support they already have.
  Properly speaking, it does seem as though the agent isn't being provided with any `new' support.
  Rather, it's information about what the agent's support already does, and given that it doesn't say whether the agent's support is leading, there's some tension.
\end{note}




\newpage

\begin{note}[Only the ability]
  So, from the above, the agent only gets the ability.
  Have seen that there are two ways to understand.
  Attribute.
  Question is whether support transmits from attribute.
  Or, whether there is failure of transmission.

  Failure of transmission, but two distinct arguments.
  \begin{enumerate}
  \item Direct failure for the fact.
  \item Indirect failure due to implausibility of transmission on the basis of attribution alone.
  \end{enumerate}
  Each argument is sufficient for the desired conclusion.
  Still, the first is more straightforward, while the second establishes interest in witnessing.
  Further, the second argument follows even if there is some flaw in the first.
\end{note}

\begin{note}[Hum]
  The basic observation would be that the agent requires the existence of the strategy in order to have support for attribute.
  It's a required background condition.
  So, then, this blocks the agent from using the attribute of the (specific) ability to obtain support for the existence of the strategy.

  This would be resolved if the conditional provided support for both the ability and the existence of the strategy.

  This, I think, is difficult.
  If the agent obtains support for the existence of the (particular) strategy, then it is because the existence of the (particular) strategy is a requirement for the agent to have the ability.

  There is, then, something odd about the order of things.
  The agent relies on support for having the ability to establish the relevant precondition.
  However, without the relevant precondition the agent would not have the relevant attribute.
\end{note}


\begin{note}[Sgaravatti]
  Justified belief in premises only if justified belief in conclusion.

  This doesn't work.
  For, it would then be the case that as the agent doesn't obtain support for the existence of the strategy, the agent doesn't obtain support for the ability.
  Here, may add in a disjunction to the effect that the agent presupposes the conclusion.
  Or, that the conclusion is a background condition for the premises.
  However, this plausibly extends to most logical consequences.

  It's more that the agent must already make use of the existence in some way.
\end{note}

\begin{note}[Helpful point]
  It's fairly clear that the existence of the strategy needs to `come with' the ability to demonstrate the existence of the strategy.
  However, it's also clear that the agent isn't being provided with support for the existence of the strategy.
  (As seen above, the informer does not provide support for the existence of the strategy.)

  In order for the agent to obtain support for \(\psi\) from \emph{E}, the agent requires \(A(\psi)\).
  And, \(A(\psi)\) does not follow if \(\psi\) is not the case.

  There's no way other to obtain \(\psi\) other than by \(A(\psi)\).
  So, there's no using \(A(\psi)\) to support \(\psi\).

  \begin{itemize}
  \item In order for the agent to obtain support for \(\psi\) from \emph{E}, the agent requires \(\phi\) to be the case.
  \item And, \(\phi\) does not follow from \emph{E} if \(\psi\) is not the case.
  \end{itemize}

  \begin{itemize}
  \item In order for the agent to obtain support for \(\psi\) from \emph{E}, the agent must be committed to \(\phi\) to be the case.
  \item And, \emph{E} does not provide support for \(\phi\) without the agent appealing to \(\psi\).
  \end{itemize}

  Not sure this works in the case of fire.
  For, in order to be hearing the alarm, there must be a fire.
  And, don't get support for there being a fire unless the agent appeals to the alarm sounding.
  So, it seems as though the agent would not obtain support for there being a fire.

  And, one would expect this to generalise to most necessary conditions.
  If there's a fix, it's with the relevant notion of commitment.

  Well, kind of.
  The problem is that it's really not clear in what sense the agent needs to hold that there's a fire in order to hear the alarm.

  In order for the agent to obtain support for \(A\), the agent requires \(\lnot\lnot A\) to be the case.
  And, \(\lnot\lnot A\) doesn't follow if \(A\) is not the case.

  This isn't right, something about being antecedently committed.
\end{note}


\begin{note}[Restricted access]
  It's very important that there's no alternative way for the agent to obtain \(\phi\).

  With ability, argued that the agent doesn't get support for \(\phi\).
  Likewise, in the zebra case, it seems there's no way for the agent to go directly from visual perception to the animal not being a cleverly disguised mule.
  This, of course, is compatible with the animal not being a \emph{badly} disguised mule, as that may be sufficiently obvious.
  Likewise for the animal being a gecko, or a stain glass portrait.

  Hence, it seems the relevant \emph{A} step is important.
  And, in particular, that \emph{A} is taken without \emph{E} being restricted to \emph{A}.
\end{note}

\begin{note}[Account?]
  Maybe:
  \begin{itemize}
  \item \(A_{1}, \dots, A_{n}\) are compatible with \(E\).
  \item \(B\) follows from \(A_{1}\) but not from some \(A_{i}\) (where \(1 < i \leq n\)).
  \end{itemize}
  These two conditions ensure that \(B\) does not straightforwardly follow from \(E\).

  These two conditions aren't sufficient.
  For, these hold with the fire example.
  It's possible that the agent is not hearing the alarm, and if so then it doesn't follow that there is a fire.

  Still, with the fire example, the problem arises because the agent has the information.
  It is, still quite possible for the agent to lack the information that the alarm sounds only if there is a fire, and still obtain support for hearing the alarm.
  So, it's possible for the agent to lack the information that if the alarm is ringing there is a fire while retaining support for the alarm ringing.

  It is not possible for the agent to lack the information that if the agent has the ability then the strategy exists while retaining support for having the ability.
  For, the entailment is constitutive of how ability is understood.

  \begin{itemize}
  \item If \emph{B} is not the case, then the agent does not obtain support for \emph{A}.
  \end{itemize}
  Or, equivalently:
  \begin{itemize}
  \item Agent obtains support for \emph{A} only with \emph{B}.
  \end{itemize}
  And this is where there is some trouble.
  Because, it seems plausible that the agent obtains support for \(A(\psi)\) without worry about whether \(\psi\) is the case.
  It may well be that the support the agent has amassed for \(A(\psi)\) is simply misleading with respect to \(A(\psi)\).
\end{note}

\begin{note}[Counterfactual]
  It seems right to think that the agent would continue to hold that they have support for the ability even if the strategy did not exist.
  By contrast, it seems right to think that the agent would not hear the alarm if there wasn't fire.

  Maybe it's not the counterfactual, so to speak, but simply the contraposition.
  \begin{itemize}
  \item No fire, then no alarm.
  \item Cleverly disguised mule, then no zebra.
  \item No strategy, then no ability.
  \end{itemize}
  It seems the agent would distinguish alarm from no alarm.
  The difficulty is with no zebra and no ability.
  For, in these cases, the relevant support is still going to suggest zebra and ability.
  It's fairly intuitive in these cases that there's a lack of sensitivity.
\end{note}

\begin{note}[Obvious?]
  It seems this simply captures what transmission failure is.
  There's some body of support \emph{E}.
  \emph{E} supports \emph{A}.
  \emph{A} entails \emph{B}.
  However, \emph{E + A} is insensitive to \emph{?B}.

  The difficult part is arguing that \emph{E + A} really is insensitive to \emph{?B}.
  For, there is an entailment from \emph{A} to \emph{B}.
  However, \emph{A} to \emph{B} doesn't ensure that the support is sensitive to \emph{not-B}.
  It shows that the support is sensitive to \emph{+A}.
  However, this is not the same as being sensitive to \emph{-B}/\emph{-A}.

  If it is not the case that there's a strategy, then everything would remain as it is, granting the conditional.
  For, then, the support I have for the general ability would be misleading, and the informer would still be in a position to make the claim that they did.
  For, the antecedent is false.

  Hence, it seems that it's not possible to transform the support I have for the general ability into support for \(\psi\).
  For, it is clear that the support I have may be quite indifferent to whether or not \(\psi\) is the case.

  However, it seems the informer allows the agent to go to \(A(\psi)\), \dots
  Why?
  If I don't have the general ability, then everything would remain as it is.
  Something has to go, though.
  Either the general ability, or the informer's information.
  Given the agent doesn't have a position of \(\psi\) nor \(A(\psi)\), it seems okay, at least, for the agent to take \(A(\psi)\).
  Built up a decent body of support, so even though the informer's claim could be made either way, \(A(\psi)\) goes through.
\end{note}



\begin{note}[Not \emph{required}]
  Question over whether there's an alternative.
  Is there some other way for an informer to extend ability other than via inertia?
  (Without also providing support for the ability?)

  Unclear, though it doesn't really matter.
\end{note}


\subsubsection{Failure of transmission}
\label{sec:failure-transmission}

\begin{note}[Previous section]
  The previous section argued for a failure of transmission to the existence of the strategy.

  May with to deny that `inertia' is a problem.
  So, having the attribute of being able to demonstrate the existence of the (particular) strategy is on par with other things the agent has support for.
  In short, it's able to be used a premise in further reasoning.

  This section argues that there remains some tension.

  As noted, `inertia' did not depend on ability.
  If `inertia' is a problem, then it extends to other instances of reasoning.
  By contrast, our attention here will be on ability.
  And, in particular, that if the agent obtains support for the existence of a strategy, it is because the existence of the strategy is a background constraint on the relevant witnessing event.
  The tension, in brief, lies in further background conditions.

  An upshot of this second pass at \AR{} is a suggestion that \WR{} provides an account of the relevant intuitions.
\end{note}

\begin{note}[Introduction, attribution and dilemma]
  For, if observing that the (particular) strategy must exist in order for the agent to have the attribute of being able to demonstrate the existence of the strategy, then it seems the agent may obtain support for further conditions required in order to have the attribute of being able to the demonstrate the existence of the strategy.
  For example, that any apparent reasoning to a conflicting strategy involves a mistake.

  If successful, this suggests a dilemma.
  For, we will have established the following two conditionals:
  \begin{enumerate}[label=(D\arabic*), ref=(D\arabic*)]
  \item\label{RDil:W} If the reasoning pattern is understood as an instance of \WR{}, then the agent obtains support for the existence of the particular strategy by virtue of reasoning that is (merely) potential.
  \item\label{RDil:A} If the reasoning pattern is understood as an instance of \AR{}, the agent obtains support for the existence of the particular strategy by virtue of reasoning performed, but the same reasoning may be extended to obtain support for propositions that (intuitively) the agent does not have support for.
  \end{enumerate}
  Therefore, if either \WR{} or \AR{} is the correct interpretation of the argument sketch, then it is the case that either the agent does not obtain support for the existence of the (particular) strategy on the basis of reasoning the agent has performed, \emph{or} the agent is able to obtain support for propositions that intuitively the agent is not able to obtain support for.

  We have sketched why \AR{} does not face the problem highlighted with \WR{}, but in order for this dilemma to be genuine we also need to observe that \WR{} does not face the problem highlighted with \AR{}.
  Part of the argument for~\ref{RDil:A} will establish that this is so.
\end{note}


\begin{note}[Assumptions for attribution horn of dilemma]
  Ideally, argument for~\ref{RDil:A} with few premises.
  This is not the case.

  The argument relies on failure of support to transmit from premises to conclusion, and in particular the broad stokes of \citeauthor{Wright:2016wl}'s characterisation of transmission failure.

  We begin by outlining a general understanding of transmission of support and observe that the \AR{} interpretation of the reasoning sketch is a straightforward instance of transmission.
  In broad strokes, as the agent does not have support for the existence of the (particular) strategy prior to the conditional information provided by the informer, if the agent obtains support for the existence of the (particular) strategy via an entailment, then the agent does so as a result of \emph{transmitting} the support the agent has for the supporting premises to the relevant conclusion across the noted entailment.

  In order for \ref{RDil:A} to be the case, it must follow from \AR{} that the agent plausibly obtains support for certain premises if the agent obtains support for the existence of a strategy form the attribute of having the relevant ability, but for the proposed support to be (intuitively) unavailable to the agent.

  In particular, we grant that the agent obtains support for the ability to demonstrate the existence of the (particular) strategy on both \AR{} and \WR{} interpretations of the reasoning sketched.
  Likewise, we will not argue that the agent fails to obtain support for the existence of the (particular) strategy.
  Rather, our focus will turn to additional conditions that must obtain in order for the agent to have the attribute of being able to witness the existence of a strategy.

  Prior to turning to transmission failure proper, and \citeauthor{Wright:2016wl}'s characterisation of transmission failure, we argue for the following premise which will lies at the core of our understanding of support and transmission failure:
    \begin{enumerate}[label=(A\arabic*), ref=(A\arabic*)]
  \item\label{Att:Prem:Presupp}
    Obtaining support for some proposition \(\phi\) is:
    \begin{enumerate}
    \item\label{Att:Prem:Presupp:1} a process, and
    \item\label{Att:Prem:Presupp:2} an agent may presuppose that certain conditions obtain, where failure of the relevant presupposed conditions would entail failure of the process.
    \end{enumerate}
  \end{enumerate}
  The premise is not novel to this paper.
  However, the argument for the premise is tailored to our interests.

  With the premise in hand, we now turn to the argument for~\ref{RDil:A}.
\end{note}

\begin{note}[Limitations of the argument]
  However, it may be useful to note that the core idea does not entail transmission failure.
  And, that the use of transmission failure is fairly non-committal about instances of transmission failure.

  So, there is hope for an argument with broader appeal.
  For now, transmission will do.
  In addition, it will help clarify some of the differences in the type of reasoning.
  And, we will observe a need to generalise \citeauthor{Wright:2016wl}'s requirement, though in letter and not in spirit.

  So, to those sympathetic, there's an argument.
  To those unsympathetic, here are some of the issues.
\end{note}


\begin{note}[Goal]
  So, idea about getting prerequisites for event.
  The argument is that this allows the agent to obtain support for propositions that the agent, intuitively, does not have support for.

  Limited by the prerequisites of the event.
  Hence, logical entailments.
  Therefore, transmission failure.

  This is a relatively weak argument.
  First, transmission failure is somewhat contentious.
  Second, rely on a specific account of transmission failure, \citeauthor{Wright:2016wl}.
  Third, \WR{} provides a solution, but lack an argument for the uniqueness of the solution.

  So, reject transmission failure.
  Reject \citeauthor{Wright:2016wl}'s understanding of transmission failure.
  Find alternative solution.

  On the other hand, the argument is sufficient.
  Therefore, \WR{} does not require transmission failure, the specific account, nor uniqueness.
  Still, there's going to be some tension.

  So, for those sympathetic to transmission, argument.
  For those sympathetic to \WR{}, an exploration of some of the issues.
\end{note}

\begin{note}[Outline]
  Start with transmission, to clear up how support is working.
  Show that this characterises the function of the argument.

  Start the argument with key premise regarding support.
  Link this to the two types of reasoning (\AR{} and \WR{}).

  Then, build up transmission and the tension.
\end{note}

\subsection{Preliminaries}
\label{sec:preliminaries}

\begin{note}[Mistakes and presuppositions, introduction]
  Before dealing with transmission failure proper, we begin by outlining a basic premise regarding support.
  The basic premise is
  \begin{enumerate*}
  \item at the core of our understanding of support and transmission failure, and
  \item provides the basic structure of an important objection.
  \end{enumerate*}

  The basic premise is:
  \begin{enumerate}[label=(A\arabic*), ref=(A\arabic*)]
  \item\label{Att:Prem:Presupp} Obtaining support for some proposition is
    \begin{enumerate}[label=(A1\alph*), ref=(A1\alph*)]
    \item\label{Att:Prem:Presupp:1} a process, and
    \item\label{Att:Prem:Presupp:2} an agent may presuppose that certain conditions obtain, where failure of the relevant presupposed conditions would entail failure of the relevant process.
    \end{enumerate}
  \end{enumerate}
  The relevant processes are captured by specific verbs such as, `demonstrate', `see', `receive testimony', and so on.
  In turn, the agent may presuppose that the agent has not made a mistake, is not being presented with an illusion, the informer providing (apparent) testimony is speaking truthfully, and so on.

  The examples given involve factive verbs, and our interest is limited to factive verbs.
  For, a factive verb requires that certain things must be the case in order for the agent to witness the relevant process.
  If the specific strategy does not exist, then it is not possible for an agent to demonstrate the strategy exists.
  If there is no tree, it is not possible for an agent to see the tree.
  If Sam is not taller than Taylor, it is not possible to receive testimony that Sam is taller than Taylor.

  Still, the basic premise is not so limited.
  For example, `doubt' and `foresee' both describe processes which for which the agent may presuppose certain things.
  For example, in doubt that Sam is taller than Taylor the agent may presuppose that they would have recognised decisive support to the contrary if they possessed such support.
  Likewise, in foreseeing that it will rain tomorrow the agent may presuppose that their tools for measuring atmospheric pressure are functioning correctly.
  The contrast with respect to the factive verbs of interest is that an agent may doubt that Sam is taller than Taylor even if it is the case that Sam is shorter than Taylor, and the agent may foresee that it will rain tomorrow even if it is sunny tomorrow.

  In line with our understanding of non-ideal agents.
  And, focus on doxastic matters.

  Part~\ref{Att:Prem:Presupp:1} is assumed without further argument.

  Part~\ref{Att:Prem:Presupp:2} includes the important qualification that the agent \emph{may} presuppose that certain conditions obtain.
  Hence, it is not a requirement that the agent does presuppose any condition does obtain.
  Agent may have sufficient support that they are demonstrating, seeing, estimating, and so on.
  Or, an agent may decline to appeal to demonstrating, seeing, estimating, and so on if they are required to presuppose conditions are suitable for demonstrating, estimating, etc.

  Still, it is plausible that non-ideal agent's like you and I do presuppose certain things in order to hold that support is obtained by the relevant process.
  For, it is typically quite straightforward to observe that from the agent's point of view there is a possibility that the agent has performed some other processes which would not yield support.

  For example, after completing it a demonstration it is possible some error has been made at some step of the (proposed) demonstration.
  It is possible the seen tree is a telephone pole.
  It is possible to overlook some movement of the Gulf Stream.

  Observe that each of these possibilities is incompatible with a witness of the relevant process.
  If the agent has made an error at some step of their reasoning to the existence of a strategy, then the agent has not \emph{demonstrated} the existence of a strategy.
  If the apparent tree is a telephone poll, then the agent has not \emph{seen} a tree.
  And, if the agent has overlooked some movement of the Gulf Stream, then (arguably) the agent has not \emph{forecasted} tomorrows weather (given a suitably rigorous understanding of forecasting).

  It may well be the case that the agent demonstrates, sees, forecasts, and so on, but successfully witnessing the relevant verb is compatible with the agent presupposing that certain conditions are in place while witnessing the relevant verb.
  If so, the agent may have propositional support for the relevant conditions, but lack the appropriate doxastic support of interest, as the would not be in a position to claim the event is an instance of the verb without presupposing the conditions obtain.
  (This diverges from \citeauthor{Wright:2016wl} whose interest in with failure of transmission for propositional support, and would deny the agent obtains propositional support.)

  Given premise~\ref{Att:Prem:Presupp}, transmission failure occurs when the agent attempts to obtain support for a presupposition made in order to claim an instance of the relevant process by virtue of some result of the process.
  Demonstrating, then no transmission from demonstration to absence of mistakes.
  Or, from seeing to (mere) appearance.

  For now the sketch is sufficient to outline object, and remaining details will be filled in as we move along.

  Premise~\ref{Att:Prem:Presupp} is difficult because it allows for an agent to obtain support for some proposition without obtaining support against any presuppositions employed.

  The alternative requires support all the way through.
  \begin{enumerate}[label=(\(\lnot\)A1b), ref=(\(\lnot\)A1b)]
  \item\label{Att:Prem:No-Presupp} No presuppositions.
  \end{enumerate}
  If so, then agent support all the way through.

  Hence,~\ref{Att:Prem:No-Presupp} suggests that support transmits in the cases of interest.
  There's no limits on witnessing, and hence no argument that \AR{} over-generates support.
  (Note that in the case of circular reasoning, transmission fails because the agent already has support.)

  The key is which incompatibility.
  If~\ref{Att:Prem:No-Presupp}, then it seems support for \(\phi\) will go all the way through and count against any proposition incompatible with \(\phi\).
  If~\ref{Att:Prem:Presupp} then support may not count in favour of the relevant presuppositions.
\end{note}

\begin{note}[Tension]
  \mbox{}
  \begin{itemize}
  \item So, we now have transmission and the key premise.
  \item The idea is that we get failures of transmission.
  \item However, \AR{} allows the agent to avoid such failures.
  \end{itemize}

  \begin{itemize}
  \item Key is that by \AR{} agent obtains support for requirements of witnessing event.
  \item Some such requirements would be presupposed by the agent were the agent to witness the relevant ability.
  \end{itemize}

  With transmission and premise~\ref{Att:Prem:Presupp} in hand, we may now state the consequent of second conditional of the proposed dilemma \ref{RDil:A} in greater detail.

  Grating \AR{}, an agent may:
  \begin{enumerate}[label=(X\arabic*) , ref=(X\arabic*)]
  \item\label{tension:Support} Obtain support for \(\psi\) given attribute of being able to \emph{V} that \(\phi\) on the basis of conditional information about how a general ability expands and support for possessing the general ability,
  \item\label{tension:Presuppose} recognising that they may need to presuppose that \(\psi\) is the case in order to consider the relevant event as an witnessing event of \emph{V}ing that \(\phi\).
  \end{enumerate}
  % Alternatively:
  % The agent recognises that \(\psi\) must be the case given ability to \emph{V} that \(\phi\) but does not expect to be able to obtain support for \(\psi\) by \emph{V}ing that \(\phi\).

  \ref{tension:Support} and~\ref{tension:Presuppose} seem, at least, logically compatible.
  The key idea behind \AR{} is that an agent need not appeal to a potential witnessing event of an ability in order to obtain support for what follows from the ability.
  Hence,~\ref{tension:Support} and~\ref{tension:Presuppose} concerns two distinct ways of obtaining support for a proposition.
  And, as these are two distinct ways of obtaining support may diverge in the propositions supported.

  Indeed, weakening~\ref{tension:Support} to read that the agent obtains support that they \emph{have} the specific ability without needing to leverage the support they have for the general ability is may fail to generate tension.
  For, it may be held that that the required background conditions are satisfied in order for the agent to be provided with the information that they have the specific ability --- if they are not then the agent may claim to be misled.

  For example, if the agent is informed that they have the (specific) ability to demonstrate that the  strategy exists, then the agent may claim support for the proposition that reasoning to an incompatible strategy would involve a mistake, as no informer would be in the position to inform the agent that they have the (specific) ability if the (particular) strategy did not exist.

  I have some doubts about whether the agent would obtain support given such information, but for now we have the stronger requirement stated in~\ref{tension:Support}, the agent is required to leverage the support they have for the general ability.

  The tension, then, is that the agent obtains support for the required background conditions primarily in virtue of the support they have for the general ability.
  The agent has no `direct' support for possessing the (specific) ability to demonstrate the existence of the (particular) strategy.
  It seems, rather, that because the agent is relying on extending their general ability to a specific case, the agent is not able to obtain support for propositions they may be required to presuppose when witnessing their general ability.


  % Agent's ability is doing the work with~\ref{tension:Support}.
  % The attribute is that there's a witnessing event.
  % Agent may be mistaken about this.
  % Agent may not \emph{V} that \(\phi\).
  % Fine for the agent to presuppose certain conditions to hold that they \emph{V} over some other verb.
  % However, this suggests that the agent doesn't obtain support for \(\psi\), etc.\ because without the relevant presuppositions, it's not clear that the agent would \emph{V} that \(\phi\).

  % Still, \AR{} would provide the agent with support for \(\phi\), and it is hard to see why the support would not extend to any \(\psi\) entailed by \(\phi\) if the relevant witnessing event explain why the agent obtains support.
\end{note}

\subsection{Transmission failure}
\label{sec:transmission-failure}

\begin{note}[Transmission]
  Literature on transmission has various parts.
  Some general pointers to useful papers will be added at a later date.
  There are concerns about
  \begin{itemize}
  \item the understanding of transmission,
  \item which arguments are instances of transmission or failure of transmission,
  \item the relationship between transmission and the distinction between proposition and doxastic justification,
  \item and so on.
  \end{itemize}
  Here, I intend to stay fairly neutral.
  The primary commitments are that there are instances of transmission failure, and \citeauthor{Wright:2011wn}'s (\citeyear{Wright:2011wn}) template is successful in diagnosing potential instances of transmission failure.

  This does not necessarily commit agreement with \citeauthor{Wright:2011wn} about which arguments satisfy the template.
  In part, because it is not clear that the reasoning sketched satisfies \citeauthor{Wright:2011wn}'s template.
  Instead, \citeauthor{Wright:2011wn}'s framework/template allows us to explore certain widely recognised instances of transmission failure in a fairly systematic way, and it may be expected that the conclusions draw with the aid of the framework may be reformulated without it.
\end{note}



\begin{note}[Failure of transmission, classic]
  With the prerequisites covered, we now turn our attention to failure of transmission proper.

  We begin with an instance of the transmission template based on an intuitively problematic instances of reasoning noted by \textcite{Dretske:2005vy}.
  \begin{transmission}[Zebra]
    \begin{enumerate}
    \item[\tri{Z}{E}] It looks as though the animal in the pen is a zebra.
    \item[\tri{Z}{A}] The animal in the pen is a zebra.
    \item[\tri{Z}{B}] The animal in the pen is not a cleverly disguised mule.
    \end{enumerate}
  \end{transmission}
  There is something intuitively problematic about obtaining \tri{Z}{A} on the basis of the support given by \tri{Z}{E} and in turn extending \tri{Z}{E}, the visual impression that the animal in the pen is a zebra to discount some possibility that would suggest some fault in obtaining \tri{Z}{A} on the basis of the support given by \tri{Z}{E}.

  Of course, if a groundskeeper were to testify that the animal in the pen is a zebra, the agent may obtain support for \tri{Z}{B}.
  Still, it seems odd that the agent may obtain support for \tri{Z}{B} given the particular support the agent has for \tri{Z}{A}, even though from \tri{Z}{A} to \tri{Z}{B} is straightforward entailment.
\end{note}

\begin{note}[Mistakes and presuppositions, example w/ zebra]
  Not a cleverly disguised mule.
  Not an incompetently disguised mule.
\end{note}

\begin{note}[Potential intuitive diagnosis]
  Here, in line with the basic premise outlined above, the agent has some method, but this is compatible with other things.
  So, going to get failure of transmission.

    The problem, roughly, is that it's not clear that the support the agent has distinguishes between \tri{Z}{A} and \tri{Z}{A\('\)}.
  \begin{enumerate}
  \item[\tri{Z}{A\('\)}] The animal in the pen is a cleverly disguised mule.
  \end{enumerate}
  So, given \tri{Z}{E}, it seems we obtain the weaker disjunction.
  \begin{enumerate}
  \item[\tri{Z}{(A or A\('\))}] The animal in the pen is a zebra or the animal in the pen is a cleverly disguised mule.
  \end{enumerate}
  \tri{Z}{(A or A\('\))} does not entail \tri{Z}{B}, as \tri{Z}{A\('\)} does not entail \tri{Z}{B}.
  And, given further possibilities this suggests expand this disjunction with further possibilities.

  So, it seems the agent is granted support for \tri{Z}{A} over \tri{Z}{(A or A\('\))}, but this means the agent focuses on some subset of what is possible, hence the agent takes for granted \emph{not}-\tri{Z}{A\('\)}.
  In turn, because \tri{Z}{A\('\)} remains compatible with support the agent has, the agent is not in a position to claim that the support the do have extends.
\end{note}

\begin{note}[Classic]
  Granting for the moment that there is something odd about obtaining \tri{Z}{B} from \tri{Z}{E} and the entailment from \tri{Z}{A} to \tri{Z}{B}, we may reformulate \citeauthor{Dretske:2005vy}'s case with the use of a factive verb to establish closer surface parallels to the chess case.
  \begin{enumerate}
  \item[\tri{Z}{A\(^{+}\)}] I am seeing that the animal in the pen is a zebra.
  \end{enumerate}
  The support from \tri{Z}{E} to \tri{Z}{A} seems preserved in going from \tri{Z}{E} to \tri{Z}{A\(^{+}\)}.

  For, given that it looks as though the animal in the pen is a zebra, then it seems this supports seeing that the animal in a pen is a zebra.
  While this involves some speculation, I doubt that \tri{Z}{E} plausibly supports \tri{Z}{A} without also supporting \tri{Z}{A\(^{+}\)}.
  Introducing the factive verb makes explicit the previously implicit assumption that it looking as though the animal in the pen is a zebra puts me in a good position to move from how things look to how things are.

  \tri{Z}{A\(^{+}\)} entails \tri{Z}{A}, and hence also entails \tri{Z}{B}.
  Reformulating \citeauthor{Dretske:2005vy}'s example in this way skips over \emph{A}, that the animal in the pen is a zebra, but the move from \tri{Z}{A\(^{+}\)} to \tri{Z}{B} seems equally problematic.

  A slight worry here is that it is entailment that is at issue, and therefore if moving from \tri{Z}{A\(^{+}\)} to \tri{Z}{A} is problematic, then moving from \tri{Z}{A\(^{+}\)} to \tri{Z}{A} is equally problematic.
  For now we leave this aside, noting only that the agent need not move from \tri{Z}{A\(^{+}\)} to \tri{Z}{A}, as \tri{Z}{E} seems to support both \tri{Z}{A} and \tri{Z}{A\(^{+}\)}.
  The source of the puzzle seems to be the relations between \tri{Z}{E}, \tri{Z}{(A or A\('\))}, and \tri{Z}{B}.
\end{note}

\begin{note}[Potential intuitive diagnosis --- sketch, \emph{very} tentative, continuing]
  Now, given some doubts about specific ability, have a similar \emph{A or A'} problem.
  Does the agent demonstrate, or perhaps it's the mere appearance of a demonstration.

  Following the parallel, suggests that agent takes for granted that they are not mistaken about the rules of chess.
  So, question about whether the agent gets support for existence of strategy.

  As things stand, inconclusive, given that \emph{A} seems alright in the zebra case.
  So, existence of strategy may be alright in this case.
  Further, even if there is some worry, then it's not clear it matters, because the agent has an direct route.

  Second difference is that zebra works with event, while chess works with property.
\end{note}

\begin{note}[Still some ways to go]
  As things stand, reformulating \citeauthor{Dretske:2005vy}'s case in terms of a factive verb has established some surface parallels to the reasoning from ability to demonstrate the existence of a (particular) strategy to the existence of a strategy.
  Namely, the use of a factive verb.

  Two important differences remain.
  First, \citeauthor{Dretske:2005vy}'s case involves an event of (seemingly) witnessing the factive verb.
  Second, the support the agent has for the witnessing the verb also extends to the fact --- \tri{Z}{A} and \tri{Z}{A\(^{+}\)} are both supported by \tri{Z}{E}.
\end{note}

\begin{note}[Moving on]
  Our attention now turns to a framework/template developed by \citeauthor{Wright:2011wn} in order to capture the intuition that there is something problematic about obtaining support for \tri{Z}{B} in \citeauthor{Dretske:2005vy}'s case and other related cases.

  We will note the template in general, how it applies to \citeauthor{Dretske:2005vy}'s case, and observe that it does not (at least immediately) apply to the reasoning from the rules of chess.

  In the short term, this may be seen as promising for the agent obtaining support for the existence of a strategy from attribution alone.
  However, we build up to argue that if the agent does obtain support for the existence of a strategy, then there problematic variants of \citeauthor{Dretske:2005vy}'s case which likewise evade \citeauthor{Wright:2011wn}'s template/framework.
\end{note}

\begin{note}[\citeauthor{Wright:2011wn}'s template, 1]
  \textcite{Wright:2011wn} has a (revised) template providing sufficient conditions for the failure of transmission.

  \begin{quote}
    Where \emph{A} entails \emph{B}, a rational claim to warrant for \emph{A} is not transmissible to \emph{B} if there is some proposition \emph{C} such that:

    \begin{enumerate}[label=(\roman*), ref=(\roman*)]
    \item\label{Wright:revised-template:1} The process/state of accomplishing the relevant putative warrant for \emph{A} is subjectively compatible with \emph{C}'s holding: things could be with one in all respects exactly as they subjectively are yet \emph{C} be true
    \item\label{Wright:revised-template:2} \emph{C} is incompatible (not necessarily with \emph{A} but) with some presupposition of the cognitive project of obtaining a warrant for \emph{A} in the relevant fashion, and
    \item\label{Wright:revised-template:3} Not-\emph{B} entails \emph{C}.\hfill\mbox{(\citeyear[93--94]{Wright:2011wn})}
    \end{enumerate}
  \end{quote}

  The notion of a presupposition of the cognitive project, detailed by \citeauthor{Wright:2011wn} in a previous passage, is\dots
  \begin{quote}
    \dots any condition \emph{P} such that to doubt \emph{P} (in advance of executing the project) would rationally commit one to doubting the significance, or competence of the project, irrespective of its outcome.\newline
    \mbox{}\hfill\mbox{(\citeyear[92]{Wright:2011wn})}
  \end{quote}
  \citeauthor{Wright:2011wn} suggests a handful of example presuppositions, including normal and proper functioning of relevant cognitive faculties, reliability of instruments or the soundness of principles of inference used obtaining support, and so on. (\citeyear[92--93]{Wright:2011wn})

  In short, find some \emph{C} entailed by not-\emph{B}, and as \emph{C} is a presupposition, it follows that without the presupposition, the support that the agent has would be under-determined.

  {
    \color{red}
    This goes back to notes about verbs and support.
  }
\end{note}

\begin{note}[The zebra, failure]
  \citeauthor{Wright:2011wn}'s template is straightforward to apply to the zebra case.
  \begin{enumerate}
  \item[\emph{not}-\tri{Z}{B}] The animal in the pen is a cleverly disguised mule.
  \item[\tri{Z}{C}] Those animals are not zebras. (\citeyear[90]{Wright:2011wn})
  \end{enumerate}

  Then, relevant presupposition.
  \begin{enumerate}
  \item \emph{Cg}: Appearances are not misleading.
  \end{enumerate}

  \tri{Z}{C} is entailed by \emph{not}-\tri{Z}{B}.
  And, seems sufficient to generate a problem.
  If appearances are misleading, then it looks as though the agent isn't in a position to appeal to appearance.

  Intuitively, if the agent has support for the animal in the pen being a zebra, then the agent should be able to discount the consideration that the animal in the pen may be a mule.
  However, the support the agent has doesn't distinguish between zebras and mules.
  So, the agent isn't in a position to move from their support for zebras to support for not mules, because if those animals are mules then appearances are misleading, and I lose support for zebras.

  This doesn't really touch on whether the agent does have support for zebras.
  The point is that if the agent has support, then the agent can't leverage the support against some proposition that could be the case given the support that the agent has.

  So, issue is not that the agent may be mistaken about there being a zebra.
  It \emph{may} be the case that the animal in the pen is a cleverly disguised mule.
  Rather that without something more the support the agent has is underdetermined without some presupposition.
  Without the relevant presupposition, the agent is not in a position to separate zebra from cleverly disguised mule given the information they have.
\end{note}

\begin{note}[\citeauthor{Wright:2011wn}'s template, 2]
  Before moving to ability, stress the role of presupposition.
  The key here is that \emph{C} needs to be incompatible with some presupposition of the cognitive project.

  \citeauthor{Wright:2011wn}'s condition~\ref{Wright:revised-template:2} replaces the following condition from previous template:
  \begin{quote}
    \begin{enumerate}[label=(\roman*\(^{-}\)), ref=(\roman*\(^{-}\))]
      \setcounter{enumi}{2}
    \item\label{Wright:revised-template:2:bad} that \emph{C} is incompatible with \emph{A}.\hfill\mbox{(\citeyear[88]{Wright:2011wn})}
    \end{enumerate}
  \end{quote}
  As \citeauthor{Wright:2011wn} observes, condition~\ref{Wright:revised-template:2:bad} over-generates (\citeyear[90--92]{Wright:2011wn}).

  \begin{center}
    [\citeauthor{Wright:2011wn} notes a problem with testimony, the same problem or a helpful variant is to be added in here.]
  \end{center}
\end{note}

\begin{note}[Hard line]
  One may wish to deny support for the zebra.
  If the agent isn't in a position to claim support for \emph{B}, that the animal in the pen is not a cleverly disguised mule, then the agent does not have support for \emph{A}, that the animal in the pen is a zebra.
  Rather, the agent has support for the animal in the pen being a cleverly disguised mule, a zebra, or any other possibility which is compatible with the support the agent has.

  In short, we are granting that the agent obtains support for \emph{A} or \emph{A'} via \emph{E}, and one may deny this is support is required to be closed under entailment.
  This is a hard line, but yields an immediate result with respect to the reasoning sketch in the chess case.
  For, as the agent is not in a position to rule out that they do not have the ability to reason with the rules of chess, and hence the possibility that the agent is not able to demonstrate that the (particular) strategy exists, the agent seems in trouble as the ability to demonstrate the (particular) strategy exists entails that the agent is not mistaken about having the ability to demonstrate the (particular) strategy exists.
  And, just as the possibility of a cleverly disguised mule is troubling, substituting absence of mistake for the existence of a strategy seems equally troubling.
  Hence, as the agent doesn't seem to have sufficient support for not being misled, on the hard line we may also deny support for the existence of a strategy.
  % Conversely, thy the agent obtains support for the finer proposition.
  % This is unclear, grant that the agent has presuppositions of a cognitive project, but why?
  % Even so, intuitively clear that if the agent makes use of presuppositions, then the agent isn't in a position to use the support they obtain against something that is ruled out by those presuppositions.
\end{note}

\begin{note}[\citeauthor{Wright:2011wn}'s template, 2.5]
  The observation about the cognitive project is important.
  It is not sufficient to merely find some alternative that is subjectively compatible with the agent's cognitive state.
  Rather, the concern is some alternative that \emph{could} be the case which would lead the agent to doubt the support they have from the relevant \emph{A}.
  And note in particular that following \citeauthor{Wright:2011wn}'s template, the source of potential transmission failure is with the support the agent has for the relevant \emph{A}.

  If the negation of the entailed \emph{B} in question does not entail some \emph{C} that could be true given the subject state of the agent which is incompatible with some presupposition of the cognitive project of obtaining support for \emph{A}, then \citeauthor{Wright:2011wn}'s template does not apply.

  Our interest, then, is whether the failure of a strategy to exist entails some \emph{C} which is incompatible with the agent obtaining support for the ability to demonstrate the existence of a strategy.
  Of course, the failure of a strategy to exist is incompatible with the ability to demonstrate the existence of a strategy, but from this it does not immediately follow that there is some fault in the cognitive project of obtaining support for the ability to demonstrate the existence of a strategy given the agent's prior support for the general ability to reason with the rules of chess and the conditional information provided by the informer.
  The support obtained may be simply be misleading.

  Unlike with \citeauthor{Dretske:2005vy}'s case, it is not clear that the agent is required to make some presupposition in order to hold that the support amassed for the general ability to reason with the rules of chess nor the conditional information provided by the informer is indeed support for those propositions.
  Nor, in turn, that there is some relevant presupposition made in order for the agent to extend the support noted to the proposition that the agent is able to demonstrate the existence of the (particular) strategy.

  Hence, our main focus is on whether a plausible argument may be made for the existence of such a presupposition.

  Still, even if the reasoning does not satisfy \citeauthor{Wright:2011wn}'s template, the template does not include a necessary condition for transmission failure.
  Instead, the intermediary result is the absence of a diagnosis of transmission failure, rather than transmission success.
  The lack of diagnosis remains a concern, as our goal is to establish that there is failure of transmission to existence based on attribute.
  % Useful pointer, \citeauthor{Wright:2011wn} focuses on event, whereas with the attributive case the agent skips over the relevant event.
  After working through the ability case, we will turn our attention to whether insights from \citeauthor{Wright:2011wn}'s template generalise.
\end{note}

\begin{note}[\citeauthor{Wright:2011wn}'s template, no failure 1]
  Does the (revised) template proposed by \citeauthor{Wright:2011wn} diagnose transmission failure with the attributive argument?
  \emph{A} is the agent possessing the ability to demonstrate the existence of a strategy, and \emph{B} is the existence of the strategy, and our interest is in whether the agent's (irresolute) support for \emph{A} transmits to \emph{B}.

  Is there \ref{Wright:revised-template:1} some \emph{C} subjectively compatible with \emph{A} such that \ref{Wright:revised-template:2} \emph{C} is incompatible with some presupposition of the cognitive project of obtaining support for \emph{A} in the relevant fashion  such that \ref{Wright:revised-template:3} Not-\emph{B} entails \emph{C}?

  Starting from the last, \emph{C} needs to be entailed by the non-existence of a strategy.
  Simple suggestion, then, is to take \emph{C} as the the non-existence of a strategy.
  As we have argued by irresolute support, this leads \ref{Wright:revised-template:1} being satisfied, as the agent is not in a position to rule out that a strategy does not exist.
  And, it seems plausible that~\ref{Wright:revised-template:2} is satisfied.
  For, the non-existence of a strategy is incompatible with either the agent possessing the general ability, or with the informer providing truthful information.

  So, this is the delicate distinction between whether the non-existence of a strategy is merely in line with a mistake, or whether it conflicts with a presupposition of how the agent obtains support for the ability to demonstrate the existence of a strategy, rather than some broader proposition.

  Here, the relevant project is broader than seeing, in contrast to \citeauthor{Dretske:2005vy}'s case.
  The final stage is combining support for general ability to reason with the rules of chess with the conditional information provided by the informer.

  The conditional information provided by the informer seems fairly robust.
  For, the non-existence of a strategy seems sufficiently unrelated to obtaining information from a third party.
  Indeed, the relevant information is a conditional which may remain true if a strategy does not exist (due to the agent then lacking the general ability to reason with the rules of chess).

  So, our focus to the general ability to reason with the rules of chess.
  Now, plausible that this turns on mistakes.
  Support the agent has for general ability comes via testing.
  Presuppositions that the tests and so on are fine, and indicative of a general ability and so on.
  In contrast to the conditional information provided by the informer, there is a plausible relation between the non-existence of a strategy and whether the agent has the general ability to reason with the rules of chess.
  However, it is not clear whether there is a relevant presupposition of the cognitive project.
  For example, the agent did not need to presuppose that the relevant ability was to reason with the rules of chess rather than some other ability, as reasoning with the rules of chess seems sufficiently identifiable that working through games, practice problems, and so on would reveal to the agent that they weren't reasoning with the rules of chess.
  So, intuitively, mistake rather than presupposition.

  % Given that we're looking for something entailed by the failure of a strategy to exist, the only thing we're going to get before causing some trouble is that the agent doesn't have the specific ability.
  % For then either general or informer doesn't hold up.
  % However, no clear reason why either presuppose.

  Tentative conclusion is that if the agent doesn't have the ability, then this holds because the support ended up being misleading, rather than the agent having some presupposition which led to/favoured support for ability to reason with chess over some other possibility.

  Doubt that a fully satisfactory argument may be given here.
  Denying that any apparent mistake is really due to conflict with a presupposition.
  % Worked through the non-existence of a strategy, so this is not fully general.
  % And, most general candidate for \emph{C} before conflict doesn't suggest presupposition, then go for mistake.
\end{note}

\begin{note}[\citeauthor{Wright:2011wn}'s template, no failure 2]
  Worry, then that the brief argument given was motivated by condition~\ref{Wright:revised-template:2:bad}, rather than the more carefully construction condition~\ref{Wright:revised-template:2}.

  If the agent recognises that their support for having the ability to demonstrate the existence of a strategy is irresolute, then it is not clear that the non-existence of a strategy is incompatible with some presupposition of the cognitive project of obtaining (irresolute) support for the ability to demonstrate the existence of a strategy.

  Our next step is to construct a parallel to the chess case which relates to \citeauthor{Dretske:2005vy}'s case.
  Briefly stated, the present line of reasoning suggests that an agent may obtain support for the existence of a strategy given support for the ability to demonstrate the existence of a strategy.
  As noted, this places no requirement on the agent to demonstrate the existence of a strategy.
  By contrast, the failure of transmission identified by \citeauthor{Wright:2011wn} in \citeauthor{Dretske:2005vy}'s case relied on the agent making certain presuppositions in order to obtain support for witnessing a factive verb.
  Therefore, is it possible for the agent to obtain support for the proposition that the animal in the pen is not a cleverly disguised mule on the basis of support for the ability to see that the animal in the pen is a zebra while simultaneously failing obtain sufficient support for seeing that the animal in the pen is a zebra without presupposing that they are seeing.
\end{note}

\begin{note}[Warping Zebra]
  Zebra, as before.
  However, before the pen, an informer.
  \begin{enumerate}[label=(Z\arabic*), ref=(Z\arabic*)]
  \item If you have the ability to visually identify zebras, then you have the ability to see the animal in the pen is a zebra.
  \end{enumerate}
  So, general ability to specific ability.

  Agent has support for having the ability to visually identify zebras, in line with support for ability to reason with the rules of chess.

  So, the agent works up to support for:
  \begin{enumerate}[resume, label=(Z\arabic*), ref=(Z\arabic*)]
  \item I have the ability to see a zebra in the pen.
  \item\label{warpedZebra:ability-to-fact} I have the ability to see a zebra in the pen only if the animal in the pen is a zebra.
  \end{enumerate}
  Therefore:
  \begin{enumerate}[resume, label=(Z\arabic*), ref=(Z\arabic*)]
  \item There is a zebra in the pen.
  \end{enumerate}
  Here, end the parallel to the chess case.

  However, our present interest is in taking an additional step.

  \begin{enumerate}[resume, label=(Z\arabic*), ref=(Z\arabic*)]
  \item\label{warpedZebra:zebra-to-not-mule} If the animal in the pen is a zebra then the animal in the pen is not a cleverly disguised mule.
  \end{enumerate}
  So, by a quick argument, go from~\ref{warpedZebra:ability-to-fact} and~\ref{warpedZebra:zebra-to-not-mule} to:
  \begin{enumerate}[resume]
  \item\label{warpedZebra:ability-to-not-mule} I have the ability to see a zebra in the pen only if the animal in the pen is not a cleverly disguised mule.
  \end{enumerate}

  Repeating the argument with~\ref{warpedZebra:ability-to-not-mule} in place of~\ref{warpedZebra:ability-to-fact}, the agent obtains:
  \begin{enumerate}[resume, label=(Z\arabic*), ref=(Z\arabic*)]
  \item The animal in the pen is not a cleverly disguised mule.
  \end{enumerate}

  Reformulating in terms of the familiar \emph{E}, \emph{A}, and \emph{B} triad:
  \begin{itemize}
  \item[\tri{Z\('\)}{E}] The agent seems to have the ability to visually identify zebras and the information that if the agent has the ability to visually identify zebras, then they have the ability to see the animal in the pen is a zebra.
  \item[\tri{Z\('\)}{A}] The agent has the ability to see the animal in the pen is a zebra.
  \item[\tri{Z\('\)}{B}] The animal in the pen is not a cleverly disguised mule.
  \end{itemize}
\end{note}

\begin{note}[Still works]
  Note, the role of the informer here is important.
  For, if the agent reasons to the attribute from the appearance of zebra, then it's plausible that there is failure of transmission in the same way as the initial zebra example.
  For, this requires the same presupposition that conditions are suitable for seeing rather than seeming, so to speak.

  If successful transmission in the ability case, then it seems there would be parallel success in the variant zebra case.

  Primary thought is that even if the agent is required to engage in presuppositions, then the agent may amass enough support for the ability that the agent does get support for ability.
  The presuppositions required to distinguish the ability to visually identify zebras over some other ability may be different from the presuppositions required to move from the visual appearance of a zebra to their being a zebra.
  The agent gains support for the general ability, while recognising that they may need to presuppose certain things in order to appeal to witnessing their ability.

  Here is the important of the agent appealing to the attribute of having the ability, rather than to witnessing the ability.

  In line with the idea suggested for chess, above.
  It seems plausible to grant that the agent is misled about having the ability, given the possibility of diverse support for possessing the ability.

  To take another example.
  General ability to reason demonstrate theorems in propositional logic.
  Broad background of classes, homework, tests, proof checkers, textbooks, recognised mistakes, and so on.
  In each of these cases, I take same verification of a valid proof to support general ability.
  Each instance of verification may require certain presuppositions.
  E.g.\ that instructors were trustworthy, that there were no bugs in the proof checker, that problem exercises in the book were sufficiently checked, and so on.

  It seems, in summary, plausible that though I may be misled, and not have the ability, that the agent's support for having a general ability need not inherit the presuppositions required for any particular witness of that ability, if presuppositions are required.
  This is not to say that there will be no presuppositions, but that something more needs to be said in order to motivate the idea that there is a failure of transmission from possession to fact.

  Tackle one head on.
  Specifically, visually appearance reflects what is actually the case.
  This is the presupposition noted in the zebra case which leads to transmission failure.

  And, previous instances of visually identifying zebras relied on presuppositions.
  Agent had to presuppose sight was reliable, etc.
  However, in obtaining support for the general ability to visually identify zebras it is plausible that after visually identifying something as a zebra the agent took further steps to verify that their visual identification was correct.
  The presupposition that the agent's vision is in good order may be important on any particular event of apparent visual identification to support witnessing the ability as opposed to \nf{witnessing} ability, but the informer provided allows the agent to bypass troubles that may arise from witnessing in favour of having the ability to see that there is a zebra in the pen on the basis of support for general and the information provided by the informer.
\end{note}

\begin{note}[Basic issue]
  Being informed of ability puts the agent in a position to obtain support for propositions that the agent would not obtain support for by witnessing the ability without support for possessing ability, so long as attribution premise is not obtained from (apparent) witnessing of ability.

  The key point is that the support the agent has traces back primarily to general ability.
  The agent may be mistaken about ability.
  And, quite plausibly, results from instances of ability leading to general ability suffer from transmission failure in the same way.

  In this sense, the understanding of ability is that of obtaining support only when there is a zebra.

  This is quite important.
  Agent obtains support for the attribute, the agent has the ability, but this doesn't show that the agent is in a position to avoid presuppositions in witnessing the ability.

  So, agent has ability, but presuppositions were involved in generating the ability.
  Suggested that this doesn't matter for overall support for attribute.
  This is because in developing support for general ability, agent isn't relying solely on support from witnessing, but also on verifying.

  Still, this doesn't rule out the same presuppositions when witnessing.
\end{note}

\begin{note}[Leading to tension]
  The tension arises because the agent doesn't go via witnessing the ability.
  Rather, because having the attribute ensures there's an event with the appropriate requirements.

  Tension between support from requirements on relevant witnessing event, and the support the agent would get from witnessing the presence of a zebra.
  
  The point is that the agent doesn't rely on witnessing to obtain the relevant fact, and therefore support spreads to incompatible propositions.

  May be questions about whether the agent has the ability to see that something is not a cleverly disguised mule.
  This doesn't matter, at least on the proposed reasoning.
  For, so long as the agent has the ability to see a zebra, and obtains from this support that there is a zebra, then there's an entailment from zebra to not a mule.

  Closest is ability to see that something is not a cleverly disguised mule so long as it's a zebra.
  
\end{note}

\begin{note}[Limiting agent's ability]
  In this sense, one may be tempted to recast the agent's ability.
  It's not identifying zebras, but something weaker.
  However, it is then the case that the agent does not obtain support for a zebra.
  \emph{That} does not follow from the ability to spot zebras or cleverly disguised mules.
  So long as transmission failure occurs, it is implausible to allow the agent to obtain support with presuppositions while denying that the agent is witnessing an ability to obtain support.
\end{note}

\begin{note}
  So, given understanding of transmission failure, the agent is going to recognise that witnessing the relevant ability is plausibly going to lead to some transmission failure.
  Subjectively compatible with the animal in the pen being a cleverly disguised mule.
  The agent is not in a position to hold that the apparent witnessing of ability extends to subjectively compatible.

  Understand this as a limitation of ability.
  Ability to identify as a zebra does not entail ability to identify a zebra and not a cleverly disguised mule.
  In particular, due to the relevant presuppositions involved with witnessing the ability.

  Difficulty is that this makes reference to the relevant witnessing.
  Attribute is the derivative of witnessing event.



  However, only if there's a link between the attribute and the witnessing of the ability.
  
\end{note}

\begin{note}[Where does this put us?]
  So, established some tension.
  Agent has some doubts about general ability, so leaves open the possibility that the agent doesn't have the general ability.

  Given this, some uncertainty about whether the agent is in a position to secure the relevant witnessing even \emph{as} a witnessing event without presuppositions.
  These presuppositions lead to transmission failure for certain propositions.
  However, the relevant presuppositions don't apply to the attribute of possessing the ability.

  Therefore, it seems some prerequisites are needed in order to claim witnessing of ability.
  However, \AR{} skips over ability.

  
\end{note}


\hozlinedash

\begin{note}[Hum]
  Things are fine so far.
  There's a problem with mule if the agent relies on presupposition.
  However, so long as the agent has general ability and informer, then the agent avoids needing to make the relevant presupposition that led to transmission failure.

  Still, expand a little.
  Note that if the agent looks in the pen, then there remains the possibility of transmission failure.
  The same worry about vision leads to a worry about whether the agent is instantiating their ability.

  Suppose the agent looks in the pen, it looks as though its a zebra, but it still could be a cleverly disguised mule.
  Discount this possibility given the general ability and remarks from the informer.
  Given that it's possible the agent is mistaken about possessing the ability, it seems odd to leverage the possession of ability given that it is subjectively indistinguishable to the agent whether they are witnessing their ability.

  Key here is that the informer has not claimed that the agent has the ability to see a zebra in the pen.
  The agent has only made the conditional.
  In turn, the agent is confident that they do have the ability to see a zebra in the pen.
  Still, there's a possibility that it is a mule, and in turn that the agent lacks the general ability that their support for the specific ability rests on.

  So, there are two related problems here.

  The apparent risk is that so long as the agent is informed about specific instances of a general ability, then the agent skips potential counterexamples to the general ability and limitations imposed by underdetermination.

  The question is whether these are problems to live with, or whether these are generated by grating transmission via attribution of ability.
\end{note}

\begin{note}[Where things go wrong]
  The basic idea is that \citeauthor{Wright:2016wl}'s template focuses on the result of an event.

  With ability, avoid any particular event.

  Features of the relevant event may block transmission of support through entailment.
  In the original example, seeing.
  Modified, that the agent is witnessing seeing.

  Still, ability relies on events.
  If the agent has the ability, then there is some event in which the agent witnesses the ability.
  However, this doesn't ensure that the agent will be in a position to appeal to their ability in the relevant event without presuppositions.

  Hence, because the agent isn't in a position to secure witnessing without presuppositions, there's a problem with appealing to the relevant entailment.

  This provides a fairly straightforward account of the failure to obtain support for the proposition that the animal in the pen is not a cleverly disguised mule.
  For, given the relevant doubts about ability and so on, it is possible from the perspective of the agent prior to looking in the pen that they may need to presuppose that the animal in the pen is not a cleverly disguised mule.

  In \citeauthor{Wright:2016wl}'s template there is some event of obtaining support for \emph{A} on the basis of \emph{E}.
  In the ability cases, the same event is present to a degree --- the possibility of the event does the relevant work.

  Therefore, it seems there's a problem with appealing to the entailment that relies on the event.

  So, we generate an account of how transmission failure may occur when reasoning with the possession of ability.

  Goes on to predict failure in the same cases, most likely.

  This motivates restrictions on certain entailments, based primarily on the antecedent of the entailment.
  Though, no significant difference to \citeauthor{Wright:2016wl}.

  This remains a step away from denying transmission to the existence of a (particular) strategy.
\end{note}

\begin{note}[Blocking presuppositions]
  In the zebra case, grant that the agent obtains support for the proposition that the animal in the pen is a zebra.
  Cases in which the agent fails to move from \emph{E} to \emph{A}.
  Here, the problem is failure of support rather than failure of transmission.
  However, if there's failure of support, then this may correspond to failure of transmission from ability.

  Twins is an interesting example.
  It seems unclear on whether there is an appropriate presupposition.

  First issue is how ability is understood.
  In particular, whether it may be the case that the agent has the ability, without it necessarily being the case that the agent is able to witness the ability without making some trivialising presupposition.

  Intuition is that the agent is going to have trouble with accessing ability.
  This, then, relies on some difference between having the ability and witnessing the ability.
  So, on this understanding, possessing the ability does not require that there is an event in which the agent recognises that they have witnessed the ability.

  The trouble in turn is that I kind of want this.
  For, otherwise it is difficult to see how the alternative reasoning works out.

  So, at least on one reading, there's going to be a problem.
  However, it's not clear that I'm going to be able to make a decent alternative if I pursue this reading.

  The weaker reading is that possession of ability does require the possibility of the agent recognising an witness without some trivialising presupposition.
  In the chess case, demonstrating the existence of a (particular) strategy without trivialising presuppositions.
  It doesn't matter too much what the trivialising presuppositions could be, so long as built into the understanding of ability in this context is the idea of an appropriate demonstration.

  Though, there is some leeway.
  The point is that the agent has the property of having demonstrated.
  Hum, it's tricky.
  For, it's really not clear that the agent has seen a zebra if the agent has doubts about whether they've seen a zebra.
  There is a reading on which this makes sense.
  And, as the agent is reasoning via the attribute, this reading is available.

  Yet, this does seem difficult from the alternative style of reasoning.
  For, it doesn't secure anything about the agent being able to internalise the relevant demonstration, and hence it doesn't seem as though the agent should be in a position to appeal to the relevant reasons.

  Well, I don't find this too worrying, personally.
  However, the real difficulty is the plausibility of the reading.
  I'm in some sense happy with the possibility that the agent is not going to be able to recognise the appropriate demonstration and so on.
  Yet, there is a sense in which this is required, and in turn even if I like the high-risk externalist friendly approach, that the argument isn't so plausible if it requires this as a premise.

  There is potentially an issue in that the agent isn't clear on what presuppositions they may need to make.

  However, I'm thinking that the way in which ability gets entrenched is the most interesting.
  For, failure to witness does not show lack of ability.
  And, it is possible given the information state of the agent that they do not have the ability.
  Still, if this blocks the fact, then it's still going to be the case that the ability remains entrenched.
  This holds on the basis of ability, and whether the agent also gets support for the fact is irrelevant.

  However, there is a slight difference.
  For, going via the attribute, the existence of a strategy stays fixed regardless of any demonstration.
  


  Thing is that there's the possibility of mistake.
  And if the agent were to advance, then this goes against mistake?

  This is interesting in part because failure is not sufficient to demonstrate lack of ability.
  
\end{note}

\begin{note}[Maybe different?]
  The cases of transmission failure suggest that the agent appealing to the ability to demonstrate is tied to the way in which the agent demonstrates.
  So, this suggests a slight reformulation.
  For, if there are constraints on entailment, then the reasoning itself matters.
  The agent isn't claiming support for the fact independent of how the agent reasons.

  In this respect, it's not obvious that the agent appeals only to the ability itself.
  So, I don't \emph{need} anything more.

  The winding tour through transmission failure shows that it is implausible to hold that appealing to the attribute can be separated from appealing to a witnessing event.

  For, if the agent didn't need to appeal to any witnessing event, then the agent wouldn't be constrained by potential transmission failure.
  Hot.

  Right, simple conditional is that if the agent had ability alone, then not constrained by witnessing event.
  If agent appeals to witnessing event, then not by ability alone.

  I mean, there is some interference demonstrated by transmission failure.

  Right, so I've shown that the attribute is contrained by the witnessing event.
  For, one doesn't obtain certain entailments because the agent isn't in a position to secure the relevant reasons, so to speak.
  The agent isn't able to secure that they have reason to hold that the animal is not a cleverly disguised mule.

  So, the unavailability of support for certain entailments is due to lack of supporting reasons, so to speak.
  Does this, in turn, support the idea that the availability of support for certain entailments is due to presence of supporting reasons?
  Not quite, I've got one direction of a conditional.
  Wait.
  If there is a lack of supporting reasons then there is transmission failure.
  If there is transmission success, then there is presence of supporting reasons.

  Of course, not super clear, though, that this really gets the relevant dependency.
  It doesn't show that the agent is appealing to the reasons, rather than their existence.

  Right, the key difference is between being able to appeal and appealing.
  From transmission failure, I have no appealing, so no being able to appeal.
  I need, something a little different.

  Well, hold on, the agent does need to appeal to the availability of the relevant reasons.
  If the reasons aren't available, then it seems there's going to be transmission failure.
  So, get appeal to reasons, as required.
\end{note}

\begin{note}
  Assume \(\phi\) entails \(\psi\).
  \begin{itemize}
  \item If the agent isn't in a position to hold that there is a possible event of obtaining support for \(\psi\) by \emph{V}ing \(\phi\), then the ability to \emph{V} that \(\phi\) does not provide support for \(\psi\).
  \end{itemize}
  Case of interest is when \(\psi \coloneq \phi\).
  \begin{itemize}
  \item If the agent isn't in a position to hold that there is a possible event of obtaining support for \(\phi\) by \emph{V}ing \(\phi\), then the ability to \emph{V} that \(\phi\) does not provide support for \(\phi\).
  \end{itemize}
  So, this suggests that the agent doesn't have the option of appealing only to their ability to demonstrate, independent of the reasons available to the agent by witnessing the demonstration.
\end{note}

\newpage


Established relation between ability and events.
Then, suggested separation.
Ability is something agent has access to, while the events are potential.
Hence, go for ability, and there's a neat link to reasons the agent has.

The first part of the argument involved constructing a scenario in which agent relies on ability.
Establishing a conditional.
The importance of the conditional is that the informer doesn't make available any reasons --- the specific ability rests on the agent.
Saw that it's not clear that in this case the agent even needs to appeal to their ability in order to secure the existence of a strategy.
However, with conditional information, it seems there's a possibility, especially going by surface form of reasoning.

This section, argue that the idea is untenable.
Below the surface the appeal to ability relies on witnessing.
So, there is no plausible account of how the agent reasons with ability alone.


\subsection{Gist}
\label{sec:gist}

Construct parallels to transmission failure.
Observe failure of transmission.

Okay.
Then failure of transmission extends from attribution of ability.
Sure.
Problem, however.
Appeal to attribute avoids any reasoning.
If this is the case, then unclear why there is any relevant failure of transmission.


\begin{note}[Misleading and presupposing]
  The argument relies on failure of transmission.
  This is somewhat of an ask.
  It's not transparent that there is transmission failure.

  The basic idea is clear.
  Alternatives, but one is favoured.

  Distinction between being misled, and with failure of transmission.

  That's a zebra in the pen.
  \begin{enumerate}
  \item The animal in the pen is not a badly disguised mule.
  \item The animal in the pen is not a cleverly disguised mule.
  \end{enumerate}
  Both of these follow.
  In particular, both follow from:
  \begin{enumerate}
  \item The animal in the pen is not a mule.
  \end{enumerate}
  The adjective does some work.
  It seems the first is okay, while the latter is not.

  This is with the assumption that things could be the subjectively the same.
  If the mule were badly disguised, then presumably it would be quite easy to see through the disguise.
  So, this would be misleading.
  If the mule were cleverly disguised, then presumably it would not be at all easy to see through the disguise.
  So, this would be a presupposition.

  I mean, the agent may be wrong about both.

  A little easier with a painting.
  Certainly not the work of an amateur forger.
  At some point there's still an alternative that the agent isn't in a position to do anything about, and in turn would lead to some fairly general problems if at fault.
  Issue is not quite that the forgery may be so good.
  Rather, if the painting is a forgery, then it's unclear what support the agent has for anything regarding paintings if their method is bad.
  So, it's not possible to claim that the support the agent has counts against a clever forgery, because there is the possibility of fault in the methods used to obtain support, which the agent can't rule out.
  However, because this is a fault in the method, it is distinct from misleading support, because that would assume soundness of the relevant method.
\end{note}

\begin{note}[Toy example]
  Ruler is a difficult example, because it seems the disjunction works out.
  If one isn't confident that the ruler is the right length, then prefix `about'.
  Hard to motivate an exact measurement.

  However, expand this so that the specifics are important.
  Maybe.

  Or, a little better, that conditions are such that the measure has not expanded/contracted.
\end{note}

There is, then, some distinction.
Misleading and presupposing.
This is non-committal about where the divide falls.
However, cases on either side of the divide.
Assume that Zebra falls on presupposition.

There are two important things here, then.
The distinction, and the role of method.
Follow \citeauthor{Wright:2016wl} and hold that method limits.


This will lead to the result that there's some limitations on ability.
In turn, that the execution of the ability itself is important.

Granting this, the argument is not quite immediate.
Still some work to show that the agent isn't in a position to appeal to property alone.
Hint, however, as limits on method, but assumption that agent is able to bypass method.
This seems like it should be trouble.


\begin{note}[Something]
  This section argues that attribute reasoning doesn't work out.
  The argument rests on puzzles concerning transmission failure.
  Some reasoning fails to be transmissive.
  If attributive reasoning works out, then we have cases in which the agent relying on ability is transmissive, while witnessing ability is not transmissive.
  The puzzle here is that the agent obtains more from relying on ability than witnessing ability.

  This is something of a problem.
  Understanding of ability is via witnessing events.
  Attributive ignores witnessing events.
  However, then we get support for propositions that would not be supported given witnessing events.

  Given ability, support for \(\phi\).
  However, fail to obtain support for \(\phi\) by witnessing ability.

  This is a problem.
  If go via witnessing, then agent isn't aware of support appealed to, but limited by the witnessing events.
  If go via attribution, then agent is aware of support they have, but extends beyond witnessing events.

  The disjunction is not obvious.
  There's still some work to show that denying the second provides the first.
  That is, if one places limits on attribution, then one gets to witnessing.
  The idea here is that understanding of why transmission fails rests on details of the witnessing event.

  
\end{note}

The odd thing is that it almost feels as though the conclusion really should be limits on attribution.
Well, ability allows one to get \(\phi\), but not necessarily any \(\psi\) such that \(\phi \vdash \psi\).
That's not what's claimed by an ability attribute.
However, the point is that this is a struggle.
Because, one goes via \(\phi\).
Lots of things need to be in place in order for an agent to have an ability.
The only plausible way to obtain the relevant limits is to consider the agent appealing to witnessing the ability.
In turn, it is the witnessing that provides support.
For, if not, then the obtainable entailments are unconstrained.

Alternative is to argue that, well, same presuppositions apply to the attribute, but I have an argument against this.
For, obtaining support for possessing the attribute is a completely different thing.
There's no particular link between presuppositions required for the attribute and presuppositions required to witness the attribute.

The relevant understanding of the claim, then, is simply that there's some non-trivial reasoning that the agent can do.
This is also interesting if the agent is required to correct mistakes in their present understanding.
However, it's not clear how to construct a case like this.

\begin{note}
  There are two conclusions in this section.
  First, that attributive reasoning doesn't work out.
  Second, that \citeauthor{Wright:2016wl}'s template for transmission failure requires some additional qualifications.
  The two conclusions are obtained more-or-less in step.

  Argument goes with transmission failure.

  The goal is to show that attempting to obtain results on possession of ability alone runs into trouble.
  The argument is that if the agent were to obtain results on possession of ability alone, then the agent obtains too much.
  Roughly, possession of ability would generate support were support is unexpected.

  This argument assumes there are limits on what may be obtained.
  Transmission failure.

  The core of the argument is fairly straightforward.
  Construct parallel examples where ability would allow an agent to obtain support for propositions which intuitively the agent does not have support for.
  If so, then some caution with reasoning from abilities.

  However, there's a little more to be said.
  For, this may show that there is transmission failure with respect to support from ability.

  So, the details are a little more complex.

  Outline transmission failure.
  Introduce \citeauthor{Wright:2016wl}'s template for transmission failure.
  Here, we rely on the general picture, there are parts of \citeauthor{Wright:2016wl}'s template that matter in determining when transmission fails to occur.
  However, these specifics are largely irrelevant to the argument.
  So long as there are cases, and \citeauthor{Wright:2016wl}'s template catches the gist, then we'll be set.

  We then outline an argument that the attribute reasoning outlined is transmissive, following \citeauthor{Wright:2016wl}'s template.
  Then, construct some scenarios.
  This leads to some problematic situations.
\end{note}



\newpage

\begin{note}[Warping zebra]
  Now, I look into the pen.
  It definitely looks like a zebra.
  However, recognise that it's no different from the donkey case.
  Given general ability, there are various things I that on first blush I don't seem to be able to rule out.
  This is the same kind of failure as before.
  It for sure looks as though it's a zebra, and support for that.
  However, there's some issue in going from support to gaining support with subjectively compatible propositions which are incompatible with going from appearance.
  In turn, it's not clear whether `instantiating' ability.
  It looks like a zebra, and I'm not sure what more could be going on, but there are possibilities.

  I have the ability, though.
  And the reasoning to zebra, and therefore support for entailments is based on possession of the ability, and not on `instantiating' the ability.

  So, even though I'm not sure whether I have `instantiated' the ability, support transmits.

  Now, in one respect this isn't interesting.
  Two ways of attempting to obtain support.
  One could fail to transmit while the other transmits.
  I'm looking at a painting, and I get support that it's real, but to the entailment that it's not a forgery.
  At the same time, curator provides testimony that it's genuine, as part of some backstory.
  Seems I then get support, even if it may turn out to be misleading.

  Still, in the pair of zebra cases, the agent isn't clear on whether they're instantiating the ability that's doing the work in transmitting.
\end{note}

\begin{note}[Sight and demonstration]
  Question whether the same applies to ability to demonstrate.
  Here, there is a slight variation.
  With sight, things are quite difficult.
  With a demonstration, things are a little more straightforward.
  If the agent has support for general ability, then the agent isn't going to be in a position where they're not confident whether they've `instantiated' the ability.
  Given a demonstration, it's likely clear to the agent.
  This is not to say that the agent will be in a position to rule out being mistaken.
  However, it is to say that the agent will not need to lean on some presupposition.

  So, we're not looking to construct a direct parallel.
\end{note}

\begin{note}[Constructing a parallel]
  Prior to demonstrating.
  Agent has support for specific ability.
  So, build up support for `instantiating' ability.
  Agent may generate quite good support for providing a witness.

  Agent may brute force if needed.

  `Will produce a demonstration' (given caveats about forgetting the problem, forgetting rules, etc.)
  Hence strategy exists.

  However, the agent has not demonstrated.
  And, it seems, there's a failure of transmission.
  Here, because the agent isn't in a position to distinguish between whether or not they have the specific ability at this point in time.
  So, the two futures, one in which the agent produces a demonstration and the other in which the agent has made a mistake are subjectively possible.


  {
    \color{red}
    This is really messy.
  }


  {
    \color{blue}
    Is the agent in a position to claim support to a witness?
    It seems not.
    The agent isn't able to distinguish as of now whether they have the ability.
    And, plausible entailment from ability to possibility of providing a witness.
    So, this is kind of odd.
    It seems as though, given the possibility of mistake, the agent isn't in a position to lay claim to providing a demonstration.
    Even if support for having the attribute, this doesn't allow the agent to lay claim to doing anything with the attribute.
    The agent would not merely been mislead if they were to claim the possibility of a demonstration.
    Rather, the agent would be leveraging the support they have for possessing the ability against a possibility that is open.
    Simply possessing the ability does not grant the agent the same stuff as would be gained by going on to witness the ability.
    Nor does recognising possession.

    So, here, doxastic?
    What the agent doesn't get is appropriate relation.
    This goes beyond the template.
    What i am interested in.
    So, not guarantee that were the agent to reason, they'd go via ability.
    So, agent doesn't get to leverage for doxastic support.
    Nuance here is it's in the entailment.
    Not getting support.

    Puzzle here is kind of support.
    Ability works because there is a witness, but agent isn't in a position to get the witness.
    So, truth but not appropriate relation?

    So, if strategy doesn't exist, agent would either make an error and not have a demonstration, or keep searching for an error in contrary/seemingly failed demonstrations.
    

    So, this is an argument that the agent doesn't get support for the possibility of a demonstration.
    
  }

  {
    \color{green}
    This then goes in the opposite direction of the zebra case.
    For, in the zebra case, oh, well, sort of.
    The point is that in the zebra case the agent isn't sure that they've seen a zebra, still.
    Here, the agent is not able to claim that they're going to be able to witness the existence of a strategy.

    So, just by information provided about how ability extends, the agent does not get into a position where they may claim that conditions are suitable for the agent to provide a demonstration.

    If this is the case, then does the proposed entailment hold up?
    
  }

  {
    \color{red}
    How bad is this?
    Well, good in the sense that it puts some pressure on the entailment from \(A(\psi)\) to \(\psi\) from one perspective.
    However, no clear problem with the existence of an ability.
    Except for tension with ability not able to demonstrate.
    
  }


  

  (Note here that the agent is not relying on the demonstration.
  This is important, because in the alternative type of reasoning, the agent holds the existence on the basis of the reasons they would generate.)
\end{note}


\begin{note}[\citeauthor{Wright:2011wn}'s template, related argument 1]
  Interesting thing about the attributive argument is that it does not rely on the agent doing anything with the ability.
  Consider the following:

  \begin{enumerate}
  \item Support for ability.
  \item Therefore, support for able to generate witness/possible future point in time where I have demonstrated the existence of a strategy/I will demonstrate the existence of the strategy.
  \item Only possible future with demonstration if strategy exists.
  \item So, existence of strategy.
  \end{enumerate}

  Here, the premise is slightly stronger.
  Not merely that the agent possesses the ability, but will demonstrate.

   If the agent gets support for having the ability, then argument that this extends to being able to generate a witness.
  The items in play are somewhat delicate.
  Initial premise is that the agent has the attribute of being able to demonstrate the existence of a strategy.
  The revised premise is a result of having that property --- the possibility of having generated a witness for the existence of a strategy.

  Agent may possess, but not have any interest in demonstrating.
  For example, propositional logic, lots of theorems, no interest, and won't demonstrate even if I have the ability to do so.
  Or, have no opportunity to do so.
  Still, for the scenario we're considering, the premise is viable.

  Agent has support for possessing the ability, assumed.
  And, by inspection of the board, there's certainly not too much.
  Agent has some resources, but if the strategy exists, the agent isn't going to run out of resources.
  At the limit, the agent can brute force, explore every possibility, and recognise which is correct.\nolinebreak
  \footnote{
    \color{red}
    Here, it should be fairly easy to approximate.
    \(7 \times 8 \times 7\), possible sequences.
    As, \(7\) Black pieces and \(8\) White pieces.
    However, increases given the potential for some pieces to move in different ways.
    \(31 \times 15 \times 31 = 14,415\), rough limit.
    As, 31 possible moves for Black, and 15 possible moves for White, given the way the board is set up, assuming each piece is able to move freely and that en Passant is open to the Black pawns on row 7.

    240 hours for a minute per strategy, but not okay as a generous approximation for brute forcing.
  }

  So, this requires additional support, but support that is available.

  No clear entailment from possession of ability to providing witnesses.
  {
    \color{red}
    There is a sense in which an entailment holds.
    For, read in a certain way, ability to demonstrate just is ability to generate a witness.
    Well, possible for the agent to generate a witness.
    Here, realising that possibility.
  }

  So, support for demonstrat\emph{ing}.
  Again, there's an entailment for this to the existence of a strategy.

  Does support transmit?

  Well, this is difficult.
  If the agent doubts that they have the ability, then doubts about demonstrating.
  The agent has support for attribute.
  However, if the agent doesn't have the attribute, then the result of obtaining this support is questionable.

  Interest is in the role of the attribute.
  The support for demonstrating is sensitive to whether the agent has the attribute.
  If possible that the agent doesn't have the attribute, then it doesn't seem as though the agent is successful in obtaining support.
  

  


  
  
  So, no, it looks as though the agent is in trouble.
  For, the agent isn't in a position to distinguish between whether or not the possess the ability.
  Hence, we have a clear candidate for \emph{C}.

  \begin{enumerate}[label=(C\arabic*)]
  \item The agent doesn't possess the specific ability.
  \end{enumerate}

  The remaining condition is \ref{Wright:revised-template:3}.
  Does the failure of existence entail that the agent does not have the ability?
  Easily, as it's the specific ability that's in question.\nolinebreak
  \footnote{
    This isn't so clear for the general ability.
    However, there's something to be said, given that the agent seems firm with the relation between general and specific.
    And, template is sufficient, allowing for other cases of transmission failure.
  }

  The failure here is due to presupposition.
  Hum, I have some doubts about this.
  The issue is that there needs to be some doubt about the cognitive project of obtaining support for ability to witness.
  Possible doubt here is that the agent isn't in a position to maintain this presupposition, given their cognitive state.
  So, here, right, the point is that the agent doesn't get an entailment for possessing the ability to providing a witness.
  
\end{note}

\begin{note}[\citeauthor{Wright:2011wn}'s template, related argument 2]
  Here, then, something is strange.
  If the agent has support for ability, then this leads through to failure of transmission to the same conclusion.

  The difference came with presupposing possession.

  The puzzle here is doxastic.
  Case in which support that something is true, but without support for providing an account of why it is true.
\end{note}

\hozlinedash

\begin{note}[\citeauthor{Wright:2011wn}'s template, related argument 2]
  The issue is a distinction between the agent having the ability to demonstrate the existence of a strategy, and the agent being in a position to appeal to the demonstration in order to settle how things are.

  Consider a closely related scenario.
  Here, the agent proceeds to reason from their understanding of the rules of chess to a witness of the existence of a strategy.
  There is a corresponding entailment from the witness of the existence of a strategy to the existence of a strategy.

  Still, let us assume that the agent retains the same doubts as in the main scenario --- the agent considers it possible that a strategy does not exist, and hence that what appears to be a witness of the existence of a strategy is not a witness of the existence of a strategy.

  Intuitively, there is a failure of transmission.
  For if the agent is open to doubt that they have the ability to reason with the rules of chess, then the agent is rationally committed to doubting the significance of any execution of the ability.
  Following this intuition, it seems the closely related scenario satisfies \citeauthor{Wright:2011wn}'s template.
  A witness of the existence of a strategy entails the existence of a strategy.

  Condition~\ref{Wright:revised-template:1} is satisfied.
  The agent applying their ability and accomplishing support for producing a witness for the existence of a strategy is subjectively compatible with not possessing the ability to reason with the rules of chess: things could be the agent in all respects exactly as they subjectively are yet the agent is mistaken about this ability.

  Following, condition~\ref{Wright:revised-template:2} is satisfied as not possessing the ability to reason with the rules of chess is incompatible with producing a witness for the existence of a strategy by exercising the ability to reason with the rules of chess.

  Likewise, condition~\ref{Wright:revised-template:3} is (plausibly) satisfied, as if a strategy does not exist, then the agent does not possess the ability to reason with the rules of chess, as the reasoning identified with the agent's ability commits the agent to the existence of a strategy.

  The difference with the main scenario is that the agent does not reason to a witness.
  And, recognises that they may be mistaken.
  The template identifies a problem with appealing to an execution of the ability.
  However, the agent relies on broader support for possession of ability.

  The relevant cognitive project is not applying the ability to obtain a witness which entails existence, but noting that the agent could not have the ability without existence.

  The agent avoids witnessing their ability, and by noting the possibility of mistake, avoids the incompatibility of the possibility of a strategy not existing with the support the agent has for the ability to reason with the rules of chess and the information provided by the informer extending the agent's support for the general ability to reason with the rules of chess to the specific ability to demonstrate the existence of a strategy.

  Part of the puzzle is resolved by noting that the doubt in the main scenario --- the agent considers it possible that a strategy does not exist --- may be resolved by the agent witnessing the existence of a strategy.
  The closely related scenario assumes that the agent would not overcome doubt about the existence of a strategy by witnessing their ability.
  However, the basis for doubt in the main scenario for the failure of a strategy to exist is motivated by noting that the agent has not yet exercised their ability.

  Still, a puzzle remains.
  The attributive argument does not rely on the agent producing a witness for the existence of a strategy.
  The relevant entailment is form the possession of ability to demonstrate the existence of a strategy to the existence of a strategy.
  However, as observed in the closely related scenario, ability alone does not ensure that the agent would be able to appeal to the ability in order to obtain support for the existence of a strategy.
  For, in the closely related scenario, the (parallel) doubt present in the main scenario prevents the agent extending their support for a witness to the existence of a strategy to the existence of a strategy.

  Possession alone seems insufficient.
  In turn, some fault with the agent appealing to the entailment from possession of ability to demonstrate the existence of a strategy to the existence of a strategy.
\end{note}


\newpage

\subsection{Old notes on transmission to be repurposed}
\label{sec:old-notes-transm}

\begin{note}[Expanding on the final premise, first pass]
  Bringing forward the arguments of this section:

  The entailment from \(A(\psi)\) to \(\phi\) is a state-world factive inference.
  If an agent has the ability to demonstrate, then this is because the agent is in a position to ensure that what follows from their state holds of how things actually are.
  If the agent is not in a state that reflects how things actually are, then the lacks the ability to \emph{demonstrate} that a strategy exists --- though the agent may have the ability to persuade others that a strategy exists, etc.

  In other words, whether or not the agent has the ability to demonstrate the existence of a strategy is a matter of how things actually are, but because the ability to demonstrate is a cognitive feature of the agent in question, the matter of how things are includes a requirement that the agent is not mistaken about how things actually are with respect to their specific ability.

  In turn, if it is possible for the agent to be mistaken about how things actually are, then the agent is not in a position to apply an inference which requires that the agent is not mistaken about how things actually are.

  The difficulty for the agent in attempting to obtain support for the existence of a strategy in virtue of their (irresolute) support for the ability to demonstrate the existence of a strategy is that:
  It is possible, given the support the agent has, that the agent does not (actually) have the ability to demonstrate, and hence that they are in a position to appeal to the required link between the ability to demonstrate and how things actually are.
\end{note}

\begin{note}[Expanding on the final premise, second pass]
  This is complex, so a second pass may help.

  If the agent has the ability to demonstrate the existence of a strategy, then a strategy must exist --- if a strategy does not exist, then no demonstration of its existence is possible.
  In turn, this means that the agent is in a position to move from what follows from their cognitive state to what holds true of the actual world.
  By demonstrating the existence of the strategy, the agent would show not only what they think is the case, but also show what is actually the case.
  Yet, if the agent only has irresolute support for their ability to demonstrate, then the must consider it possible that any proposed witness of their ability would only show what the agent things is the case, and may fail to show what is actually the case.

  Irresolute support for the ability to demonstrate the existence of a strategy, then, falls short of ensuring from the agent's point of view that any witness of the agent's ability would amount to a demonstration.
  The agent is not in a position to apply the factive inference to the support they have for the ability to demonstrate the existence of a strategy.
\end{note}

\begin{note}[Limitation of the final premise]
  This is not to say that the agent does not have (irresolute) support for the ability to demonstrate the existence of a strategy.
  This is only to say that there would be a mistake to transmit the support they have for the ability to demonstrate the existence of a strategy to the existence of a strategy.
  For, the support the agent has does not secure the required relation between how things appear to the agent and how things actually are.

  So, the agent falls short of securing that their support for the ability to demonstrate the existence of a strategy does not mislead them about how things actually are.
  The agent is not in a position to be sure that their support for the ability to demonstrate the existence of a strategy reflects how things actually are, and hence that the relation between the ability to demonstrate and the corresponding fact holds.
\end{note}

\begin{note}[Failure of transmission terminology]
  Term this failure of transmission, as there are sufficient similarities to the literature on transmission failure.
  However, in contrast to the focus of the literature, focus is on doxastic support.
  It may be the case that the agent is a way for the agent to get the existence of a strategy --- in particular by witnessing their ability --- however even if the agent is in a position to demonstrate the existence of a strategy, the information the agent has is insufficient to secure this.
\end{note}

\begin{note}[Plan for section]
  Begin by sketching out the transmission and the problem.
  Link to transmission failure literature.
  Observe difference.
  Expand on the initial sketch.
\end{note}

\hozlinedash

\begin{note}[\citeauthor{Wright:2011wn}'s template, moving on]
  The template provided by \citeauthor{Wright:2011wn} identifies transmission failure by commitments made in order to obtain support for \emph{A}.
  The present issue is whether the agent the entailment from \emph{A} to \emph{B} is `available' to the agent.

  If the agent has the ability to demonstrate the existence of a strategy, then a strategy exists.
  Still, if the agent admits of mistake, then the agent is not in a position to hold that it \emph{is} the case that a strategy exists.
  Yet, the role of the entailment from the ability to demonstrate the existence of a strategy to the existence of a strategy is for the agent to move from what holds of their cognitive state to how things actually are.

  There may, then, be some tension between
  \begin{enumerate*}
  \item the agent recognising that the relation from having the ability to demonstrate the existence of a strategy to the existence of a strategy requires a suitable connexion to how things actually are, while
  \item admitting that the support they have for demonstrating the existence of a strategy does not provide a (suitable) connexion to how things are.
  \end{enumerate*}

  Stated a little more broadly, there may be some tension between the agent
  \begin{enumerate*}
  \item appealing to an entailment that relies on the agent not being mistaken about how things actually are, while
  \item recognising that they may be mistaken about how things actually are.
  \end{enumerate*}
\end{note}





\begin{note}[Oracle]
  So, think about an oracle intervening and providing the agent with guarantee that they have the ability.
  Then, there doesn't seem anything problematic about the reasoning.
  The problem lies with some doubt that they have the ability to demonstrate the existence of a strategy.
\end{note}

\begin{note}[Factive and belief, example 0]
  The focus point here is the relation between the agent's cognitive state and what holds given what the agent has support for.
  The argument is that the agent may be in a cognitive state which support some fact, but is not in a position secure entailments of the fact given the cognitive state they are in.
\end{note}

\begin{note}[Factive and belief, example 1]
  To illustrate, consider an agent reasoning with belief.
  For example, the first two premises of the following argument entail the conclusion.
  \begin{enumerate}
  \item\label{belief:strange:1} Shay is shorter than Taylor.
  \item\label{belief:strange:2} If Shay is shorter than Taylor, then Taylor is taller than Sam.
  \item\label{belief:strange:3} Taylor is taller than Sam.
  \end{enumerate}
  It seems plausible that if the agent has support for believing that Shay is shorter than Taylor, then the same support transmits to Taylor being taller than Sam.\nolinebreak
  \footnote{
    If worried that the support is the same in both cases, then expand to a chain of inequalities.
  }
  In particular, the agent may have propositional support/warrant for believing that Taylor is taller than Sam, regardless of how the agent reasons from~\ref{belief:strange:1} and~\ref{belief:strange:2} to~\ref{belief:strange:3}.

  Still, there is something puzzling about the following reasoning:
  \begin{enumerate}
  \item I believe that Shay is shorter than Taylor.
  \item So, Shay \emph{is} shorter than Taylor.
  \item The fact of Shay \emph{being} shorter than Taylor entails that Taylor \emph{is} taller than Sam.
  \item So, I believe that Taylor is taller than Sam.
  \end{enumerate}
  The included stress on the copula indicates that the reasons to the belief that Taylor is taller than Shay by taking their initial belief that Shay is shorter than Taylor to reflect how things actually are.

  The agent's attitude toward the proposition that Shay is shorter than Taylor is recognised by the agent as belief because the agent recognises that it may be the case that Shay is not (actually) shorter than Taylor.
  While, the agent's belief that Taylor is taller than Shay is premised on the agent's belief that Shay is (actually) shorter than Taylor.
  Given the agent's cognitive state they (the agent) considers it possible that Shay is not (actually) shorter than Taylor, so it is unclear why the agent has support to believe that Taylor is taller than Shay based on what is (actually) the case.

  {
    \color{red}
    The agent fails to obtain support for their belief that Taylor is taller than Shay by the proposed reasoning.
    For, the support the agent has for the proposition that Shay is shorter than Taylor is not support for Shay (actually) \emph{being} shorter than Taylor.\nolinebreak
    \footnote{
      It may be useful to contrast this to the agent \emph{knowing} that Shay is shorter than Taylor.
      For, if the agent knows that Shay is shorter than Taylor, then Shay \emph{is} shorter than Taylor.
      So, if the agent is position to appeal to their knowing, no fault is found in the agent's reasoning --- though this leaves open whether the agent could be in a position to appeal to their knowing.
    }
  }

  There are similarities to \citeauthor{Wright:2011wn}.
  Something incompatible with the agent's cognitive project --- here with the reasoning from the support the agent has for \emph{A} to \emph{B}.
  For, if the agent doubts that their support for some proposition \emph{A} reflects how things actually are, then it seems this doubt rationally commits the agent to doubting the significance, or competence, of reasoning on the basis that \emph{B} must be the case if \emph{A} is how things actually are, irrespective of the outcome.
  (Compare to \cite[92]{Wright:2011wn})

  % In line with \citeauthor{Wright:2011wn}, then successful transmission of support form \emph{A} to \emph{B} requires at least (and on the present understanding of support) \emph{depends} on something that might not be the case.
\end{note}

\begin{note}[Factive and belief, example, 2]
  To contrast, suppose the agent reasons that, even though they may be mistaken about how things actually are, the support they have points to Shay being shorter than Taylor, and hence the given the most plausible candidate for how things are, Taylor is taller than Sam.
  The minor difference is that the agent does not move from their belief about how things are to how things are.
  Even if the agent is mistaken and Shay is (actually) taller than Taylor, Taylor is taller than Shay given the information the agent has support for.
  The agent need not depend on how things actually are.
\end{note}

\begin{note}[Factivity and belief, to ability, 1]
  Turning our attention back to ability and the attributive argument, our question is whether the agent's reasoning from their (irresolute) support for possessing the ability to demonstrate the existence of a strategy to the existence of a strategy depends on something that might not be the case.

  Specifically, does the agent's reasoning depend a tight connexion between the agent's cognitive (state supporting their possession of the ability to demonstrate the existence of a strategy) and how things actually are.

  The agent has support for thinking that they have the ability to demonstrate the existence of a strategy.
  So, even if the agent is mistaken, it still follows that the agent's support for possessing the ability extends to the existence of a strategy.
  As with the second case of belief, the agent's reasoning is not threaded through how things actually are.
  Therefore, the agent's reasoning does not depend on how things actually are, and the possibility that the strategy does not exist only limits the strength of the support available to the agent for the existence of a strategy.

  As attractive as this quick argument may be, something is not quite right.
  The agent has support that they are able to demonstrate the existence of a strategy.
  And, this can only be if a strategy exists.
  True.
  However, to move from possession of ability to fact depends on moving from the cognitive state to how things are.

  The agent recognises that the support they have for their possession of an ability to demonstrate the existence of a strategy does not allow them (the agent) to claim that as a matter of how things actually are they have the ability to demonstrate the existence of a strategy.
  And, this possibility of mistake is preserved even if the agent does have the ability to demonstrate the existence of a strategy.

  Recognising the possibility of mistake given how things actually are limits the agent to the same possibility of mistake granting how things would be given the agent's support for how things are.

  The support the agent has for the ability to demonstrate the existence of a strategy does not ensure that the agent can transition from possession to the existence of a strategy.
  For, possession only ensures that the agent may witness the existence of a strategy, possession does not ensure that the agent is in a position to guarantee a witness prior to executing their ability.

  The difficulty with the present line of reasoning is that the agent's (irresolute) support that they possess the ability is compatible with the agent doubting whether any witness they produce is informative about how things are.
  The desired transmission of support from the ability to demonstrate the existence of a strategy to the existence of a strategy fails because, lacking resolute support, the agent's doubt that they possess the ability commits the agent to doubting their cognitive state supports reasoning from what appears to be the case to what is the case.
\end{note}

\begin{note}[Factivity and belief, to ability, 2]
  Consider belief one last time.
  The fault was going from the support for how things are to how things actually are.
  When things worked out, the agent moved from Shay is shorter than Taylor to Taylor being taller than Shay.
  The agent did not move from their belief that Shay is shorter than Taylor to (the assumed truth) of Shay being shorter than Taylor.
  The agent is still not in a position to rule out that Shay is not shorter than Taylor, and so move from cognitive state to how things are.
  The lack of resolute support for Shay being shorter than Taylor remains even if Shay is shorter than Taylor.
  It is not possible for an agent to move from what they believe to be the case to what is the case, even if what the agent believes is the case.

  The difficulty with ability is that the agent is required to move from a cognitive state to how things are in the case of interest.
  Simply possessing the ability to demonstrate the existence of a strategy does not put the agent in a position to hold that a strategy exists, as the agent may witness the demonstration without being in a position hold that the witness reflects how things are.

  The agent has support that the posses the ability to demonstrate the existence of a strategy, but the agent's support is irresolute, and does not ensure that they (actually) have the ability to demonstrate the existence of a strategy.
  Hence, even if the agent does have the ability to demonstrate the existence of a strategy, the possibility of mistake prevents the agent from transitioning to the existence of a strategy.
  Given the support available to the agent, the agent possesses the ability to demonstrate the existence of a strategy, and so a strategy must exist.
  However, the support available to the agent does not ensure that the agent would not be mistaken in moving from the cognitive state associated with the ability to how things are given the (irresolute) support available currently to the agent.

  No matter the existence of a strategy, the agent is not in a position to transition from ability to fact.

  If the agent doubts that the support they have for the ability to demonstrate the existence of a strategy reflects on how things are, then this commits the agent to doubting the significance of the reasoning from the possession of the ability to demonstrate the existence of a strategy to the existence of a strategy.
  For, even grating the ability to demonstrate the existence of a strategy --- and hence the existence of a strategy --- the agent is not in a position to appeal the (irresolutely supported) relation between their cognitive state and how things are.
  Not for how things actually are, nor for how things are given the support available to the agent.
\end{note}

\begin{note}[Factivity and belief, to ability, 3]
  The trouble for the agent is that the novel information provided by the informer requires the agent to consider the possibility that they do not have the ability to demonstrate the existence of a strategy.
  In turn, either that they do not have the ability to reason with the rules of chess, or that the information provided by the informer is misleading.

  The mere possibility that that the agent does not have the ability to reason with the rules of chess, or that the information provided by the informer is misleading does not undercut the support the agent has for the ability to reason with the rules of chess and the informer providing information.

  Still, the possibility prevents the agent from extending the resulting support for the ability to demonstrate the existence of a strategy to the existence of a strategy.
  For, the possibility is incompatible with the agent transitioning from their cognitive state to how things are.
  Even if the agent does have the ability, the (mere) possibility that the agent is mistaken is sufficient to cast doubt on the competence of transitioning from how things seems to the agent to how things are.
\end{note}

\begin{note}[Factivity and belief, to ability, 4]
  To wrap up.
  Support for ability.
  Doubt that a strategy exists.
  Witnessing ability would resolve doubt.
  However, agent goes from possession to existence.
  So, does not resolve doubt that a strategy exists.
  Allows possibility that the agent is not in a position to appeal to their ability.

  Agent doesn't secure that that they are suitable related to their ability.
  Hence, isn't in a position to think that they obtain support for the existence of a strategy from possession of ability.

  Possession of ability does not put agent in position to appeal to possession.
  Similar to how truth of \(\phi\) does not put an agent in a position to appeal to \(\phi\).

  Support does not transmit, because with resolving doubt, entailment from possession to existence does not establish that the agent can move from cognitive state to how things are.

  Failure of transmission, but not due to the support the agent has for the premises.
  Rather, due the support for possession of ability being distinct from the agent being in a position to appeal to what follows from possession.
\end{note}

\subsection{Concluding the negative argument}
\label{sec:concl-negat-argum}

\begin{note}[Main premises]
  Handful of key premises:
  \begin{enumerate}
  \item Conditional information.
  \item If support for specific ability, then irresolute.
  \item Irresolute then no transmission to fact.
  \end{enumerate}
\end{note}

\begin{note}
  Focus has been on attribution.
  To come is licensing.
\end{note}


\hozline

\newpage

\begin{note}[Davies]
  \begin{quote}
    LP. The justification from \emph{E} for believing the premise(s) \emph{A} of a valid argument with conclusion \emph{B} cannot be transmitted from premise(s) to conclusion if doubt about \emph{B} would directly rationally require acceptance of a defeater for the justification from \emph{E} for \emph{P}.
  \end{quote}
  Defeater for the justification from \emph{A} to \emph{B}, rather than from \emph{e} to \emph{A}.
\end{note}

\begin{note}[Potential mistake]
  If consider irresolute support across possible worlds, then the agent doesn't get \(\psi\) anywhere.
  Each of the states aren't factive, then there's no requirement that \(\psi\).

  And, if not factive with respect to the initial point of evaluation, then not factive with respect to most plausible worlds.
  For, this amounts to the agent enhancing their information state in the relevant worlds.

  A subtle point.
  Key is that there are two steps to get to \(\psi\).
  First, \(A(\phi) \rightarrow A(\psi)\), and second \(A(\psi) \rightarrow \psi\).
  After getting \(A(\phi)\), non-factive, so if the agent attempts \(\psi\), then move to different point of evaluation.

  There is something compelling about this idea.
  Roughly, the agent doesn't have \(A(\psi)\), but \(A(\psi) \lor \nf{A}(\psi)\).
  And, \(\psi\) only follows from \(A(\psi)\), not from \(\nf{A}(\psi)\).

  Seems to quickly over-generate.
  \(\phi \lor \nf{\phi}\).
  Amounts to denying support for \(\phi\).
  Sufficient to block (most) entailments.

  Instead, the problem identified is that there is \emph{some} possibility of a \(\lnot A(\psi)\)/\(\lnot\psi\) world.
  Hence, the agent is not in a position to route their reasoning through what holds at the actual world.
  Hence, factive inference isn't secure.
\end{note}

\newpage

\begin{note}[Outline]
  Understanding of transmission.
  Literature on transmission failure.
  Divergence by focus on particular type of inference --- factive.
  Weaker than literature, as generates failure regardless of inference.
  Upshot is a cleaner understanding in specific cases, and helps with understanding where witnessing differs.

  In the previous sections we argued
  \begin{enumerate*}
  \item Conditional information, and
  \item If support for \(A(\psi)\) then support is irresolute.
  \end{enumerate*}
  This section, we assume irresolute support for \(A(\psi)\) and argue that the agent does not obtain support for \(\psi\) from \(A(\psi)\) by observing that \(A(\psi)\) only if \(\psi\) is the case.
  In other words, the support the agent has for \(A(\psi)\) fails to transmit to \(\psi\) via the entailment \(A(\psi) \rightarrow \psi\).
\end{note}

\begin{note}[Outline, part 1.5]
  In short, the argument, roughly is:

  \begin{enumerate}
  \item Prior to information from informer, agent is confident that \(A(\phi)\) is true of the actual world.
  \item Given information, agent is not in a position to ensure that \(A(\psi)\) is true of the actual world.
  \item This means that \(\psi\) does not follow from the agent's information state after processing the information provided by the informer.
  \item That is, the agent isn't in a position to rule out \(\lnot\psi\) as the actual world.
  \item In turn, this means that the agent is not in a position to apply the factive inference.
  \item For, the factive inference requires the agent to have a sufficiently strong connexion to the actual world.
  \item This is the difficulty with factive inferences.
  \item However, the agent has support for thinking that \(A(\psi)\) is the case, and hence that \(\psi\) is the case.
  \item Yet, not that \(\psi\) holds of the actual world.
  \end{enumerate}

  This is a complex situation.

  \begin{itemize}
  \item Support for \(A(\phi)\) holding of the actual world.
  \item Novel information leads to further considerations about the actual world that the agent can't rule out.
  \item So, the agent doesn't have the same support for \(A(\psi)\).
  \item Hence, the support for \(A(\phi)\) independent of new information doesn't extend to \(A(\psi)\), and in turn not to \(\psi\), as the last step requires a factive inference.
  \end{itemize}

  The primary interest is that any support for \(\psi\) is insecure.
  Because, this means the agent lacks security of the factive inference.

  \begin{itemize}
  \item From \(A(\phi)\) to \(A(\psi)\), there's the possibility of misleading support.
  \item From \(A(\psi)\) to \(\psi\), there's the possibility of invalid reasoning/failure of entailment.
  \end{itemize}
  If the agent doesn't have support for a factive state, then the agent doesn't have the option of transmission via factive inference.

  Note, in particular that \(A(\phi)\) to \(A(\psi)\) comes from informer, so this isn't impacted by failure of factivity.

  There remains a sense in which the agent may have some support for \(\psi\).
  For, the agent doesn't have any particular reason for failure of factivity.
  May term this provisional support.
  For, expect to be able to rule these out.
  However, this falls short of providing the agent with support for \(\psi\) in an important sense.
  Specifically, that the agent will, given the opportunity, make good on the provisional support.

  Slight difference to other cases of transmission failure.
  Here, it is plausible the agent still has good reason to believe that the actual world is a \(A(\phi)\) world.
  Difference to skeptical cases, where it seems that if the skeptical hypothesis is taken then there is, at least, some question about support for the actual world.
\end{note}

\begin{note}[Understanding of transmission]
  Transmission failure with respect to conclusion from premises with support.
  This does not show that the agent does not have support for \(\psi\).
  Rather, that the agent does not obtain support for \(\psi\) from the support the agent has from the premises.

  In this sense, failure of transmission is easy.
  Take some argument where the conclusion is unrelated to the premises.
  Interesting cases is where there is some path to the conclusion --- esp.\ entailment.

  Zebra deduction.

  Important to include support.

  In the present case:
  Conclusion is \(\psi\).
  Entailment is from \(A(\psi)\) to \(\psi\).
  Support for \(A(\psi)\) is \(A(\phi)\) and \(A(\phi) \rightarrow A(\psi)\).

  Assume that the agent has support for \(A(\psi)\).
  From previous section, this is irresolute support.
  Here, failure of transmission when irresolute support combines with a factive inference.

  Important to our understanding of transmission is that the inference moves from one state to another.
  In the sense that, there's the state prior to the inference, and the state posterior to the inference.
\end{note}



\hozlinedash

\begin{note}[Role of the factive inference]
  First, repeat the importance of the factive inference.
  The agent takes irresolute support for \(A(\psi)\).
  In turn, most plausible candidates for the actual world are worlds at which \(A(\psi)\) is true.
  And, \(A(\psi) \rightarrow \psi\) leads to \(\psi\) at these worlds.

  As \(A(\phi) \rightarrow A(\psi)\) is novel information, the agent doesn't have independent support for \(\psi\).
  So, if the agent doesn't have \(A(\psi) \rightarrow \psi\), then things don't work out.

  Note again that \(A(\psi)\) is a description of what follows from state.

  Argument is attributive.
  Noted difference between factive and non-factive variants.

  Truth of \(A(\psi)\) at the worlds of interest require \(\psi\) to be true.
  However, this then doesn't reflect on the agent getting support for \(\psi\) from their current state.
  For, this details what follows from \(A(\psi)\) independent from the agent's relation to \(A(\psi)\).
  Switched from state supporting \(A(\psi)\) to the truth of \(A(\psi)\) at a point of evaluation, and the requirements this places on the corresponding information state to ensure that \(A(\psi)\) is true.

  So, this doesn't provide any guarantee that the agent is in a position with respect to that information state to appeal to the presumed truth of \(A(\psi)\).
  All this ensures is that \(A(\psi)\) is true regardless of the support that the agent has at the relevant points of evaluation.

  Yet, the question is whether the support the agent has for \(A(\psi)\) extends to \(\psi\).

  If we consider the support the agent has at the relevant points of evaluation, then unless it is assumed that the agent has resolute support, then the agent will not be in a position to apply the support they have to obtain the truth of \(\psi\) at the point of evaluation.

  For, if the agent has irresolute support, then the agent doesn't have the guarantee that the point of evaluation is within the worlds the agent considers most plausible at that point of evaluation.
  The phrasing here is a little complex, but the idea is straightforward.
  As the agent doesn't have sufficient support for the actual world being among the most plausible world given their support for \(A(\psi)\), then the same holds for any other world.

  If the support the agent has leads them to a mistake about whether they have the ability in the actual world, then even if one assumes that the agent does have the ability, and hence that \(\psi\) is true, this doesn't change the potential for mistake \emph{given} the support the agent has.

  Accepted that the agent was not looking to establish \(\psi\) at the actual world.
  Still get \(\psi\) at the most plausible worlds.

  However, it doesn't follow that the agent is in a position to reason to \(\psi\) at the most plausible worlds.

  If the agent has granted the potential failure of \(\psi\) to hold, then factive inference doesn't inform the agent about what follows from their information state.
  The agent fails to get support for \(\psi\) because the agent lacks reason to think that their information state is sufficient to ensure they consider \(\psi\) to be the case even if \(\psi\) is true.

  So, \(\psi\) is true at the most plausible worlds, but without factivity of the information state, the most plausible states for the current information state are not information about what follows from the information state at those plausible states.
  So, this doesn't secure support for \(\psi\) from the present information state of the agent.
\end{note}

\begin{note}[If not the factive inference]
  The key here, in relation to the previous discussion, is that the is engaged in attempting to obtain support for \(\psi\) from their support for \(A(\psi)\).
  This fails, because, if the agent gives up on factivity, then the agent gives up reason to think that \(\psi\) holds.

  Now, run a different idea.
  Belief \(\phi\), and \(\phi\) entails \(\psi\).

  Well, the basic point is that there should be a failure of entailment between \(A(\psi)\) and \(\psi\).

  Standard entailments are world-world.
  Here, state-world.
  So, the diagnosis is that the agent doesn't have an entailment to appeal to.

  The flaw in the agent's reasoning is taking the most plausible worlds to be those in which \(A(\psi)\) holds.
  Rather than those in which \(\nf{A}(\psi)\) holds.
  If the agent can't be sure that \(A(\psi)\) holds of their current state, then it is a mistake to think that \(A(\psi)\) holds in the most plausible worlds, over \(\nf{A}(\psi)\).
  Hence, the inference is unavailable.

  So, this argument is limited to state-world entailments.
  And, in particular, those in which the entailment may be unavailable due to the state involved.

  For example, support for \(\phi\), then support for \(\phi \lor \psi\).
  Straightforwardly because the entailment is secure.
  However, if the support for \(\phi\) does not distinguish between \(\phi\) and \(\nf{\phi}\), then unless \(\nf{\phi} \vdash \phi \lor \psi\), then the agent doesn't get support for \(\psi\).

  The key here is that the agent may still have support for \(\phi\).
  Reason to think that \(\phi\) holds in the most plausible worlds.
  The problem is that as the information does exclude \(\nf{\phi}\), the required entailment is not available.
\end{note}

\begin{note}[Contrast to Wright]
  The difference between this observation and of \citeauthor{Wright:2011wn} is that identify the source of failure prior to the proposed inference.
  Whether the entailment from \emph{A} to \emph{B} is available to the agent.

  This avoids the interesting features of transmission failure, that the argument is deductively valid.
  

  Therefore, weakening the cognitive project doesn't help.

  There is a caveat.
  In that this is potentially doxastic.

  Still, aligns with the template, in a sense, because the template suggests that there's got to be some doubt about whether the identified entailment actually holds.
  One way to put this is in terms of the cognitive project being the change of information state by particular entailment.

  If an instance of the template, then it is just that, an instance.
  The template may have other applications besides.
  Still, the idea given stands independent of the template.
  Motivated by question of whether an entailment is available to an agent.

  So, similarities and differences.
  Enough similarities to think that in broad strokes there's not too much to separate, and here identified a specific instance of the template.
\end{note}

\begin{note}[Available entailment]
  Arguing for the failure is the easy part, in a sense.
  The bar to entailment is high, and may seem it's going to be easy to find some way to generate failure.

  However, relative to the state and type of inference.

  So, the problem is what follows from the attribution of a state to oneself with the possibility of that state failing.
  This then blocks what appears to be the case from the information state to any particular fact that the information state would entail.

  So, it seems as though the agent should also fail to have support that they're in the information state.
  For, if the agent continues to have support that they're in the information state, then that's going to require that the relevant fact is true.
  But this isn't quite right.
  The point is that the information state supports the proposition, but not entailment applies to the information state because it doesn't have the guarantee for the inference.

  To put things in a model, there's a core of the information state, prior to novel information, where the agent would get \(\psi\), where they in a position to retain.
  For, if the actual world lies in the core, then \(A(\phi)\) is supported in the core, and so \(\psi\) ends up following.

  The problem for the agent, is that with the addition of \(\lnot\psi\) states, the agent isn't in a position to restrict their attention to that core.

  So, there's a possibility of \(\lnot\psi\) given the information state of the agent.

  Hence, \(\psi\) follows from that core, but this doesn't help the agent, because they lose guarantees about that core with the novel information.

  So, if instead the idea is that the agent is engaged in some reasoning that doesn't require factivity, then the agent doesn't require the actual world to be part of the core, and in turn this doesn't restrict the availability of any inference from the core.

  Hence, the issue is not that \(A(\psi)\) and \(\nf{A}(\psi)\) are plausible at \emph{any} state.
  Rather, that \(A(\psi)\) and \(\nf{A}(\psi)\) are plausible for the actual world.
  And, in turn, by holding \(\psi\) then agent loses the factivity of the information state.

  Then, if the agent weakens the core, they still get some support for \(\psi\), in a sense, as the agent doesn't have any particular reason to think the prior core was misleading.
  However, with this weakening there's a loss of the support of interest.
  That \(\psi\) was thought to follow for the actual world.
  In turn, it may not be the case that \(A(\phi)\) holds at the actual world.

  So, this doesn't require transmission failure from states that don't require factivity.
  It's possible, for, novel information is going to introduce failure worlds.
  However, discarding these from the core may be fine.

  Tweety being a bird to Tweety flying.
  Still plausibly transmits support, though weaker, to Tweety flying.
  For, does not require the agent to Tweety flying.
  Only the weaker condition that Tweety flying is not ruled out by their information about the actual world.

  Inference where admit possibility of mistake about the actual world.

  The FBI case is somewhat similar.
  Shifting focus.
  Support for thinking that it's not a robbery is a result of support for thinking that it's the FBI.
  However, support here is not threaded through the actual world, rather, through through the compatibility with the entailment with the actual world given information, even if this turns out to be mistaken.

    {
    \color{red}
    Still, perhaps this is the best that can be done without demonstration of ability.
    However, it is surprisingly weak.
    Assumption was that \(A(\phi)\) was sufficiently linked to the actual world.
    Mere possibility is enough to break this.
  }
\end{note}

\begin{note}[Key difference to skepticism]
  With the skeptical cases, this raises problems for the actual world being part of the initial information state.
  With ability, this isn't so clear.
  For, the problem is that the agent can't stop the actual world bouncing around, not that there's a problem with it being there.
\end{note}



\begin{note}[Notes of from SEP]
  Looks as though there is failure with (ii).
  This is not the case.
  The issue is that the agent isn't in a position to ensure that deducing preserves their information state.
\end{note}


\newpage






\begin{note}[Difficulty with the template]
  For, state-world inference, relies on the state being factive.
  If non-factive, then there is no entailment from the state.

  In this respect, the issue identified is not transmission over entailment, but whether an entailment is available to transmit warrant.

  Consider \citeauthor{Wright:2012uy} basic suggestion:
  \begin{quote}
    My basic suggestion about transmission failure, in the most general (somewhat overstated) terms, is this: \emph{that you cannot rationally transmit a claim to warrant for certain premises across an entailment to anything that is an authenticity-condition for (any among) the very cognitive project(s) which purportedly generate(s) that claim to warrant}.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[467--468]{Wright:2012uy})}
  \end{quote}
  A straightforward (though perhaps naive) reading of the suggestion is that the entailment is available, but fails to transmit.

  This holds in some of the standard examples.
  For example, zebra, and may more in a footnote.

  I am inclined to agree, but this isn't too important.

  However, here, substitute in a proposition describing an information state.
  There is an entailment from \(K\phi\) to \(\phi\).
  However, if it is not the case that \(K\phi\), then the agent doesn't have access to this entailment from their state.
  So, the issue is whether the entailment is available to the agent.

  This is a delicate point.
  It is assumed that the agent has some support/warrant for \(\phi\).
  However, this is different from the proposal that the support/warrant to be obtained from entailment from \(K\phi\) to \(\phi\).
  For, if the agent were to obtain warrant for \(\phi\) from \(K\phi\), then the entailment goes through.

  Of course, distinction between a claim to warrant to \(\phi\) and a claim to warrant to \(K\phi\).
  However, it seems this goes through in the relevant cases.
  Visual perception goes to \(K\phi\) just as to \(\phi\).

  Strange that this blocks.
  However, it's blocking transmission.
  This does not require that the agent does not have support/warrant for \(\phi\).
  Rather, the agent would not obtain via the apparent support they have for knowing that \(\phi\).

  So, this is a relatively clean argument to the failure of transmission by the entailment corresponding to the factive inference from the template provided by \citeauthor{Wright:2011wn}.

  And, leading to a general problem with the attributive style of argument.

  Noted that this does not necessarily block warrant for the fact.
  However, in the case of ability, there's no route other than the factive inference.
  Hence, suggests that the agent does not obtain warrant for the existence of a strategy via attribution.

  Still, the wrinkle with this attributive argument is that it requires entailment.
  The issue is that the agent goes with the attributed state.
  There is no entailment from this state to \(\psi\).
  And, as template is sufficient for failure of warrant, this leaves a gap.

  Perhaps implausible, but worth investigating.

  For, in the simple example, the agent roughly says, forget about my warrant for \(A(\psi)\).
  So long as \(A(\psi)\) is true, then \(\psi\) is true.

  Given what I consider plausible, \(\psi\) must be part of that.


  So, look, given that I recognise that I only have irresolute support for \(A(\psi)\), I am not appealing to an entailment.
  Rather, I am claiming that, it is plausible that \(A(\psi)\).
  If \(A(\psi)\) is true, then \(\psi\) is true, regardless of whether I have support or not.
  And, because I have support for \(A(\psi)\) being the case, that extends to \(\psi\) simply by the requirement of entailment.

  So, the agent has claimed their warrant transmits.
  However, by a claim to warrant for the plausibility of \(A(\psi)\).
  Which in turn seems to lead to the plausibility of \(\psi\).

  No matter the initial response to this argument, this seems to evade \citeauthor{Wright:2011wn}'s template.

  Primarily, by weakening.

  % I have irresolute support for having hands.
  % This does not entail that I have hands.
  % However, irresolute support means that in all the cases I consider most plausible, I have hands.
  % And, if it is true that I have hands then it is true that there is an external world.
  % Therefore, the irresolute support for having hands extends to irresolute support for the existence of an external world.

  % In some respects, this is no better than claiming that it seems to be that there is an external world.
  % However, I'm in no worse position, and the position of irresolute support for having hands is quite good.
  % So, the position of irresolute support for the existence of an external world is also quite good.

  % Unsatisfactory for skeptical purposes, but our interest is in ability.
  % Does the agent end in a position of support for it being the case that \(\psi\) given support for \(A(\psi)\).

  Lingering question of whether the warrant for defeasible having hands is also warrant for having hands.
  Well, now we're considering defeasible support, the second condition of \citeauthor{Wright:2011wn}'s template is at issue.
  Failure is compatible.
  [See Tweety.]

    \hozline

  The interest now is with the entailment.
  Claim that there remains a failure of transmission.
  For, the factive entailment is unavailable when the agent grants irresolute support.
\end{note}

\subsection{Factivity and states}
\label{sec:factivity-states}

\begin{note}[Starting from the top]
  Goal is to argue that the agent does not obtain support for \(\psi\).
  We have seen that this is predicted by the template.
  Here, we offer a distinct argument focusing on factive inferences.

  One reason is that the template is general.
  Undergone some revision.
  So, providing independent argument avoid reliance, and also provides some support for the template.

  Main reason, however, is that helps understand the difference between attribution and witnessing.
\end{note}

\begin{note}[Complex fault]
  Still, support for \(\psi\), and obtaining resolute from irresolute wasn't the goal.

  The information state offers irresolute support for \(A(\psi)\).
  Hence, the truth of \(A(\psi)\) at each world is different from the irresolute support for \(A(\psi)\) that the agent has.
  It's true that \(\psi\) follows at each world given the truth.
  Hence, this isn't an account of what follows from the support the agent has.
  This is an account of what follows if the support the agent has is true.

  Still, our interest is what follows from the information state.
  And that's the importance of the shortcoming.
  \(\psi\) doesn't follow, as the information state isn't factive.

  The key observation is that the factive inference is a state-world inference.
  If an agent's information state is sufficient to secure a demonstration of \(\psi\), then \(\psi\) is true of the actual world.

  So, the truth of \(A(\psi)\) at the relevant worlds constituting the agent's information state on the basis of support requires the agent to be in a stronger information state than they are in.
  It assumes that the information state at each world is factive.

  Ability is like knowledge, belief, desire, etc.

  Take belief.
  Take it to be clear that one cannot move from the belief that \(\phi\) to \(\phi\).
  Diagnosis is the same.
  For, belief isn't a factive state, and therefore the factive inference doesn't apply.

  Of course, \(\phi \vdash \psi\), then \(B\psi\), and this is because \(\phi\) holds at all worlds in the relevant information state, and so \(\psi\) also holds.
  However, doesn't extend to anything beyond the information state.
  \(B\psi\) is the limit.

  The slip with the simple argument is the enhancement of the respective information states.
  In the belief, the entailment from \(\phi\) to \(\psi\) on a world-world basis.
  Here, state-world.
  Hence, the agent doesn't get that \(\psi\) follows from their information state.
  Rather, \(\psi\) follows an enhanced information state.

  If one substitutes the truth of \(A(\psi)\) form irresolute support for \(\psi\), then it is possible that \(\psi\) does not hold at any world in the agent's information state.

  Irresolute support means that from the agent's perspective, the most plausible worlds are those in which the corresponding information state of the agent is factive.
  Hence, \(\psi\) follows.

  Still, because there is a difference in kind between the information states, this doesn't reflect on the agent's non-factive information state.

  In this respect, support for \(\psi\) is close.
  For, the agent has some reason for thinking that their current information state is likely factive.
  Yet, this doesn't allow the agent to discharge the required assumption that they are in a factive information state.

\hozline

  Hence, this is due to the factivity constraint.
  The same argument doesn't hold for other entailments.
  Take other inference.
  Candle is red, so the candle is coloured.

  Every world candle is red, the candle is also coloured.
  Block is, it appears there is a red candle, so there is a coloured candle.
  That's bad.

  Similarly, \(\phi\) to \(\phi \lor \psi\) is fine, but I can't go from appearance of \(\phi\) to \(\phi \lor \psi\).

  Factive inference is unique in this respect, because it goes from some state to some fact.
  However, if there's no guarantee that the state reflects the actual world, then there's no ground for obtaining the fact.
\end{note}

\begin{note}[Summarising]
  The point here is a simple one.
  One doesn't put oneself in position to apply a factive inference by possessing irresolute support --- support which does not ensure that the state from which the inference is performed is factive.
  Equivalently, if an agent notes that the have irresolute support for a proposition, then noting what follows if they were to have resolute support does not contribute to what follows from their irresolute support.
  For, this requires assumptions that their irresolute support does not guarantee.
\end{note}

\begin{note}[Reading this into Wright]
  \begin{quote}
    My basic suggestion about transmission failure, in the most general (somewhat overstated) terms, is this: that you cannot rationally transmit a claim to warrant for certain premises across an entailment to anything that is an authenticity-condition for (any among) the very cognitive project(s) which purportedly generate(s) that claim to warrant.
    [Book, 467--468]
  \end{quote}
Where:
  \begin{quote}
    In general, authenticity-conditions thus include such things as: normal and proper functioning of relevant cognitive faculties, the reliability of instruments utilized, the amenability of the circumstances to the proposed method of investigation, the correctness of relevant theory, the soundness of relevant principles of inference utilized in developing and collating one’s results, the good standing of relevant concepts used in any aspect of the enquiry, and so on.
    [Book, 467]
  \end{quote}

  Can read the preceding argument as focus on a specific authenticity condition for a specific cognitive project.

  There is a question whether the argument is substantially different.
  The general phrasing of Wright is in part due to the scope.

  Still, there may be said for the variant approach.

\begin{quote}
  \dots you cannot, merely by looking at the animal, or the wall, get in position rationally to claim that conditions are suitable for the identiﬁcation of animal species, or surface colours, just on the basis of unaided vision.
    [Book, 467--468]
  \end{quote}
\end{note}

\begin{note}[No reduction to confirmation]
  The key part here is the lack of factivity.
  Without this, no degree of confirmation is going to help.
\end{note}

\hozline



\begin{note}[Factive inference]
  Additional constraint on factive inference is that it's an non-causal factive inference, for lack of better term.

  Goal of the factive inference is to obtain some matter of fact.
  And, in particular, that the fact holds true of the actual world.

  Initial contrast to belief.
  It is not the case that \(B\phi \rightarrow \phi\).
  For, the doxastic state of an agent has a lose relation to the actual world.
  The platitude is that \(B\phi \rightarrow \lnot K \lnot \phi\).
  If the agent believes \(\phi\), then the agent does not know that the agent world is not a \(\phi\) world.

  Of course, with an entailment, belief follows, in the sense that if \(\phi \rightarrow \psi\) and \(B\phi\) then either the agent has some attitude to \(\psi\) which requires revision, or the agent is free to believe \(\psi\).
  However, \(B\phi\) and \(\phi \rightarrow \psi\) doesn't get the agent to \(\psi\) holding of the actual world, just as \(\phi\) holding of the actual world is problematic.

  Of course, complexities.
  And, might argue about extent of belief.
  Key is that the interest in factive inference is that it goes beyond an attitude.

  This is the goal of the reasoning sketched.
  Ability to demonstrate is factive in this sense.
  Independent of attitude.

  The {\color{red} preceding argument} put the agent in a position of belief with respect to \(A(\psi)\).
  Irresolute support.
  Explain why the parallels continue despite the semantic factivity of \(A(\psi)\).
  This is because, in short, irresolute support for \(A(\psi)\) reduces \(A(\psi)\) to \(\nf{A}(\psi)\).
  In other words, the factivity of \(A(\psi)\) is primarily a function of the factivity of the relevant state.

  This may seem overly strong.
  However, this is just about support.
  Just as \(B\phi\) blocks factive inference, but still leaves commitment, it is plausible that \(\nf{A}(\phi)\) does the same.
\end{note}

\begin{note}[Key point with the factive inference]
  The key point with the factive inference is that it's a proposal to refine the agent's state.
  The result of the factive inference is a state in which \(\psi\) is true.
  The inference is not observing that all \(A(\psi)\) worlds are \(\psi\) worlds, but that \(\psi\) is true of the actual world.

  Hence, the result is going to be a refinement of the agent's state.
  And, then the trouble is that this isn't compatible with the potential failure of factivity of \(A(\psi)\) given the novel information.

  This is the difference between observing that \(\psi\) holds in most states, and inferring \(\psi\).

  The agent gets that \(\psi\) holds in most states by reflexivity of \(A(\psi)\).
  However, this can't be lifted to a definitive statement about the actual world.
  In a sense, this provides the agent with conditional support.
  If any \(A(\psi)\) world is the actual world, then the agent gets support for \(\psi\).

  Hum, so this works out easier if this are phrased in terms of support for the actual world being a certain way.
  If so, then the novel information rules this out.

  Hum, support between states.
  So, it looks as though the agent is unable to maintain factivity with respect to \(A(\phi)\).
  However, due to lack of information.
\end{note}

\begin{note}[Intuition behind factive inference]
  Factive inference works on the idea that the agent works on their factive state.
  Here, understood to mean that the agent includes the actual world.
  Factive inference is available is the inclusion of the actual world is preserved from the initial state to the result state.

  If an agent is not in a position to ensure the resulting state is factive, then there's a problem.
  The factive inference would work out if the agent were to have a factive state.
  So, the problem doesn't arise from the inference.
  Rather, it arises because the agent isn't in a position to make the inference.
\end{note}

\begin{note}[Failure to be in position]
  So, the agent would need to assume that the \emph{resulting} state is factive.
  Indeed, the agent may be confident that their present state (prior to the inference is factive).
  For, the agent has good support for \(A(\phi)\), and no reason to think this ruled out the actual world.
  The issue is now excluding the introduced \(\lnot\psi\) states.

  The agent isn't in a position to narrow down the actual world to a \(\psi\) world.
  However, this then blocks the factive inference, which would allow the agent to narrow the actual world to a \(\psi\) world.

  So, basically, these two things cannot simultaneously hold.
  1. Question over whether the actual world is a \(\psi\) world.
  2. Application of the factive inference.

  From this, the inference in unavailable.
  And, as the agent can't make the inference, support does not transmit via the inference.

  This provides the relevant insight into \citeauthor{Wright:2003aa}'s ideas.
  For, the agent needs to assume the relevant information in order to be in a position to perform the factive inference.
  Hence, there's a kind of loop.
\end{note}

\begin{note}[Non-factive version]
  Key here is that the proposed inference is factive.
  Alternative is for the agent to go non-factive with the inference.

  So, factivity of \(A(\psi)\) relative to a world.
  For sure.
  But the agent isn't in a position to ensure the actual world is a \(A(\psi)\) world.

  Difference between worlds and state.
  Factive inference is simple restricted to individual worlds.
  Of course, this is why the agent isn't able to avoid confidence that \(\psi\) is the case.

  So, in a sense this suggests that there are two distinct inferences that the agent can make.

  The issue is support.
  Only goes with the global.

  Factive inference works because it preserves factivity of mental state.

  Distributed factivity doesn't work for support, because it doesn't preserve factivity.
  So, support doesn't transmit, because when the agent reasons in this way, the agent obtains the stronger position of preserving factivity.

  The problem is, the factive inference is state-state, not world-world.

  Hm, so each world is also a \(\psi\) world.
  However, if the agent gives up on the actual world, then the agent gives up on the factive inference.
  If the agent `merely' believes that \(A(\psi)\) is the case, then they don't obtain support for \(\psi\) being the case.

  So, the problem is that reflexivity doesn't apply.
  For, the agent doesn't have any guarantee that they're considering actual worlds, in a sense.

  That is, for each of the worlds, it's possible that \(A(\psi)\) doesn't actually hold.
  The reflexive inference only holds if the worlds are potential actual worlds.

  So, this is a lot to untangle, but the key idea is that the inference from believe \(\psi\) to \(\psi\) is bad.
  This doesn't provide support for \(\psi\).
  Instead, \(B(\phi)\) and \(\phi \rightarrow \psi\) then \(B(\psi)\) --- though this isn't required, unless \(\phi \rightarrow \psi\) is entailment proper.
  Here, with ability, same thing.
  There's no real issue with the agent getting to \(B\psi\), in the sense that the agent has support for taking a doxastic position toward \(\psi\).
  I doubt, though cannot be sure, that there's no issue with Moore providing an account of why they believe that there is an external world.
\end{note}

\hozline

{
  \color{red}
  Various notes on factive inference and failure.
  To be deleted.
}

\begin{note}[Example]
  Start with \(A(\phi)\).
  Assumed factivity.
  So, you've got the actual world as part of the state, and the state makes \(A(\phi)\) true.
  Now, informer provides information.
  \(\psi\) is novel.
  Well, if the actual world was part of the \(A(\phi)\) state, then can discard possibility of \(\lnot\psi\).
  This seems wrong.
  Instead, there's got to be a different way of understanding how the actual world works here.
  Well, one way to understand is that the agent hasn't ruled out the actual world.
  So, the property is that the actual world has not been ruled out.
  Hence, either it is a state the agent considers possible given their current descriptive capabilities, or would consider possible were the agent to expand their descriptive capabilities.
  Okay.
  So, then, the agent considers, and they haven't ruled out \(\lnot\psi\).
  So, given descriptive, the agent is no longer able to maintain that the actual world is a \(A(\phi)\) world.
  Still, support points to this.
  It's just that the support is irresolute.
  In turn, this means that the agent can't rely on factive inference, 
\end{note}


\begin{note}[Note]
  So, there's still something surprising.
  For \(A(\phi) \rightarrow A(\psi)\) requires \(\psi\) to be true.
  However, this only provides irresolute for \(A(\psi)\).

  So, \(\psi\) needs to be true in order for \(A(\psi)\) to be the case.

  If \(\psi\) is not true, then not in a position to perform the factive inference.
  That's the key idea.

  So, question is whether the agent has the option of performing the factive inference.
  The factive inference is sound only if it is the case that \(\psi\).
  The agent is interested in using the factive inference to obtain support for it being the case that \(\psi\).
  Hence, the agent is required to have the support that they are attempting to obtain.

  So, in general.
  Factive inference.
  \(fa(\psi) \rightarrow \psi\).
  If agent has the attitude, then \(\psi\) follows.
  However, it is only possible for the agent to have the attitude if \(\psi\) is the case.
  Interest in the inference is to obtain support for \(\psi\) being the case.
  Therefore, the agent lacks adequate support for soundness of the inference.

  Okay.
  If this holds up, then in the cases of interest, the factive inference is sound because \(\psi\) is the case.
  For, if \(\psi\) isn't the case, then the agent can't have the attitude.

  Distinguish from other inferences, hum.
  So, \(p\) to \(p \lor q\).
  If \(p\) is true, then \(p \lor q\) is true.
  If \(fa(\psi)\) is true, then \(\psi\) is true.

  Well, if the agent has support for \(p\) then the agent has support for \(p \lor q\).
  If the agent has support for \(fa(\psi)\) then the agent has support for \(\psi\).

  It's not possible for \(p\) to be true and \(p \lor q\) to be false.
  Same with factive.
  It's not possible for \(fa(\psi)\) to be true and for \(\psi\) to be false.

  And, it also seems true that it's not possible for the agent to have support for \(p\) without support for \(p \lor q\).
  While, it is possible for the agent to have support for \(fa(\psi)\) without \(\psi\) being true.

  How to clean this up, though?

  Every \(p\) world is a \(p \lor q\) world.
  Not every \(A^{*}(\psi)\) world is a \(\psi\) world.
  If the agent has irresolute support for \(A(\psi)\), then the agent cannot distinguish between \(A(\psi)\) and \(A^{*}(\psi)\) worlds.
  So, the agent doesn't have soundness of their position.

  Right, the agent needs to be in a \(A(\psi)\) world for this reasoning to work out.
  However, the upshot of the reasoning is that the agent is in a \(\psi\) world.

  Agent needs to be in a \(\psi\) world in order to apply the premise.
  Hum, there's something interesting.

  If no irresolute support for \(p \lor q\), then no irresolute support for \(p\).
  If no irresolute support for \(\psi\), then no irresolute support for \(A(\psi)\)?

  Right, it's useful to note that \(A(\phi) \rightarrow \psi\) ends up being the case.
  This was not previously available.

  So, novel relation of support between \(A(\phi)\) and \(\psi\).
  No extra support for \(A(\psi)\), by assumption.

  Feels interesting.

  So, in the diary case, get diary \(\rightarrow\) apple exists.
  So, this is a new conditional.
  Failure of transmission because the agent doesn't seem to really get this conditional.
  The agent doesn't have enough information to rule out the \(A(\phi) \land \lnot\psi\) worlds.

  So, the problem is that because the agent can't be sure that \(A(\phi) \rightarrow \psi\), the agent cannot be sure that \(A(\psi) \rightarrow \psi\) would be sound if support holds up.

  Nice point here is that this involves the failures of transitivity noted in the literature.
  The insight is that these impact the apparent soundness of an inference.

  This is a neat argument.
  The trouble is that it doesn't show that there's no transmission.
  In the sense that support could in principle transmit to the extent that \(A(\phi) \rightarrow \psi\) does hold up.

  Would need stronger premise that support only transmits over sound inferences in order to rule this out.
\end{note}

\begin{note}[Figuring out factivity]
  One way to understand factivity is from the perspective of entailment.
  So, \(A(\phi) \rightarrow \phi\).

  However, possible to understand this with respect to epistemic state.
  So, \(A(\phi)\) is a description of the agent's epistemic state.
  And, there's a condition on whether this state is factive or not.
  For, it depends on whether the actual world is in the state.

  In this sense, factive inference holds because when the agent narrows information, they have a guarantee that the actual world will remain in their epistemic state.

  This property is not guaranteed in the cases of interest.
  For, the agent isn't able to rule out \(\lnot\psi\).
  Hence, the agent doesn't have a guarantee that restricting to \(\psi\) would preserve the presumed factivity of their epistemic state.

  Contrast to inferences where factivity is not required.
  Because factivity is not assumed, the inclusion of the actual world is not of interest.
  Therefore, the agent is not at risk of failing to preserve this property.

  So, this suggests that there's an account of why the agent does not have the option to apply the inference.
  And, it seems that this is insensitive to the confidence of the agent.

  Hence, no matter how strong the agent's confidence of \(A(\phi)\) is, with novel information there's a failure of factivity, and once factivity fails, the agent doesn't have the option of applying inferences which rely on the factivity of their mental state.

  So, this is illustrated by failures of knowledge.
  Create a dependency chain, and a failure at the end impacts the whole thing.

  So, here, difference between this kind of factive inference and other kinds of inference.
  For, if the agent does not need to assume some relation to the actual world, then there's no particular worry.
\end{note}

\begin{note}[Main claim]
  The main claim here is that the factive inference requires the agent to ensure a property of their mental state.
  In particular, that the state is factive.
  If the state is not factive, then the agent has no guarantee of the validity of the inference.
  If the agent doesn't have validity of the inference, then the inference doesn't transmit warrant.

  Puzzle about warrant is that on surface reading, the arguments appear to be valid.
  Modus ponens.
  Difficult is securing the appropriate interpretation of the premises.
  If factive, then the inference is valid.
  If non-factive, then the inference is not valid.

  So, the relations given by the conditional are firm.
  These are loosened when the agent has support.
  And, the important observation is that if the relations rely on truth, then things work out okay, because the relevant entailments do not rely on the agent's epistemic position.

  However, when the entailments do rely on the agent's epistemic position, then this becomes fragile when there is irresolute support.
  And, so, the validity of the inference doesn't go through.
\end{note}

\begin{note}[Still some puzzles]
  If \(F \rightarrow \psi\), then \(\psi\) is true of the actual world.

  If \(\phi \rightarrow \psi\), then \(\psi\) is true of worlds in which \(\phi\) is true.

  So, if the agent is in a position to make a factive inference, the agent must be sure that they consider the actual world possible.
  So, when the agent makes an inference, then agent is narrowing down the actual world.

  Factive inference is successful only if the actual world is preserved.
  So, the agent narrows down the range of possibilities, and the actual world is present in the narrowed range.
  In turn, because the agent is narrowing down, this assumes that the actual world is present in the agent's initial epistemic state.

  If the agent is not able to guarantee that this property is going to be preserved, then the agent doesn't have the option of the factive inference.

  Key here is that the factive inference talks about the actual world.
  Consider \(K\phi \rightarrow \phi\) because the actual world is always part of the agent's knowledge state, by assumption.

  With non-factive inferences, do not require this.
  Narrow down with beliefs without worrying about factivity, because if premises are true, then the conclusion is sufficiently likely to be true.

  This is true of factive inferences too.
  However, factivity is preserving the presence of the actual world, and sufficiently likely that \(\psi\) is true is not the same as preserving the actual world.
\end{note}

\begin{note}
  Evaluating reasoning with respect to an agent.

  Hence, with respect to some epistemic state.

  Wait, can do this?

  Hum, so, there's going to be a difference in terms of whether the actual world is in the set.

  Interested in the agent.

  Distinguish two sets.
  First is doxastic, second is epistemic.

  Factive inference only applies to the epistemic set, as it's about the actual world.

  So, now, consider these sets as collections of worlds.
  Relation between the two, is that doxastic is a subset of epistemic.

  Key thing is that because doxastic is a subset, it's no guaranteed to contain the actual world.

  Okay.

  Then, observed doxastic relation to \(A(\psi)\).


  Well, it seems easier to frame this in terms of a type different between inferences.
  Factive inferences require the agent to be sure that the result applies to the actual world.
  Non-factive inferences do not require the agent to be sure that the result applies to the actual world.

  \(A(\psi) \rightarrow \psi\) is a factive inference.
  It works because the agent can be sure that \(\psi\) applies to the actual world if \(\psi\) applies to the actual world.

  \(p \rightarrow q\) is not a factive inference.
  For, it doesn't require \(q\) to be true of the actual world.
  Well, yeah, this shows up in the logical form in a way, by the semantics of things.

  So, ability to demonstrate is factive in the same way that knowledge is.
  The relevant embedded proposition must be true of the actual world.

  Hence, the reasoning works, only if the agent has guarantee that by performing the reasoning they preserve the actual world as part of the state.

  This requirement has two parts.
  First, that the actual world is part of the agent's state, and
  Second, that it is preserved when the agent restricts attention by performing the reasoning.

  Assume that the agent has good reason to think that the actual world is present in the state which supports having the ability.
  Incoming novel information from the informer doesn't change this.
  However, the novel information requires the agent to add some worlds.
  And, then, the agent isn't in a position to guarantee that the actual world is going to be preserved.
\end{note}



\begin{note}[Still\dots]
  So, agent isn't in a position to apply the factive inference.
  For, the agent isn't in a position to ensure that \(A(\phi)\) is factive.
  If \(A(\psi)\) were factive, then the agent would be able to expand.
  The issue isn't that \(\psi\) must already be true, so to speak --- this only arises as a consequence of the information and the requirement on the factivity of \(A(\psi)\).

  \emph{Still}, the agent does not have the option to avoiding \(\psi\).
  So, where does this leave the support for \(\psi\)?
  Even if the agent does not have the option of performing the factive inference, the agent is in a good position with respect to \(\psi\).
  Well, in this case, there's still the observation that the support for \(\psi\) drops below some threshold.

  So, this is the failure of transitivity.
  In turn, failure of transmission.

  Perhaps the key point is that the agent can't then use whatever support they have for \(\psi\) for other purposes.
  So, the claim here is that the agent ends up with some attitude toward \(\psi\), but there's a broken link.

  In this sense, there's no \emph{transmission} of support.

  The problem is that there is something missing in the reasoning.
  And, the reasoning doesn't point to a fix.
\end{note}

\begin{note}[The entailment]
  \(A(\psi) \rightarrow \psi\) is clear.
  Follows from understanding of \(A(\psi)\).

  For, some sequence of actions that would establish \(\psi\).
  No semantic analysis needed --- true on any.

  If the agent were to fail to recognise, then this reflects their understanding of \(A(\psi)\).

  Different from \(A^{*}(\psi)\), then non-factive variant.

  Agent plausibly has resolute support for \(A^{*}(\psi)\).
  For, \(A(\phi)\) and informer's information.
  And \(A(\phi) \rightarrow A(\psi)\) leads to \(A^{*}(\phi) \rightarrow A^{*}(\psi)\).
  And, no challenge to \(A^{*}(\phi)\).
\end{note}

\begin{note}[Two sides to the transmission debate]
  These seem to be the two sides of the debate.
  For Wright, with the zebra, background conditions are part of the reasoning in the required cases.
  For Pryor, these are not required to be part of the reasoning.
  The disagreement is about whether these things are required as parts of the reasoning (SEP 5.1).

  The position here, then, is perhaps conservatism when reasoning from general ability, but liberalism when reasoning with ability.
  The key difference, really, is whether the assumption of general ability features in the reasoning.
  Well, the separation between general ability and execution of ability.

  The same distinction applies to the zebra case.
  Issue is whether the agent can start with the premise of sight.
  Difficulty is that there seems no way to resolve (e.g.\ disjunctivism).
  By contrast, clear difference between reflecting on general ability and witnessing ability.
  So, conservatism and liberalism are applied to two different things, and can be maintained.

  And, lastly, captures the intuitive different between \(A(\phi) \rightarrow \psi\), which seems odd, versus \(W_{\phi}\psi\) which seems okay.
\end{note}

\begin{note}[Parallel to Donkey]
  Claim is that the problem with the donkey reasoning is that the agent doesn't go from appearance to sight.
  The factive requirement on sight breaks things.
  So, parallel would be replacing ability with ability\(^{*}\), which isn't factive in the same way.

  So, with the donkey, the basic idea is that appearance + factivity -> sight.
  And, the problem is that the agent doesn't have factivity.

  With the ability, it's a little more simple: general ability + psi -> specific ability.
\end{note}

\begin{note}[Difference with witnessing]
  Looking ahead, the same problem does not arise with witnessing.
  The agent does not need to assume that \(\psi\) is the case in order to do the reasoning.
  In particular, information provided by the agent may be discarded.
  And, though the agent may still appeal to their ability in order to be confident that they have demonstrated \(\psi\), the demonstration itself does not require the agent to assume \(\psi\) in order to be performed.

  If the agent were to doubt that \(\psi\) then either ability or reasoning, in a similar way.
  However, as obtained without assumption of \(\psi\), these two things support \(\psi\) being the case.

  The Davis condition is nice.
  What assumptions are there if the agent goes through the reasoning?
  It seems there aren't any relevant assumptions.
  The agent has support for their understanding of the rules of chess.
  Perhaps there is scope if the agent extends too far, but for the agent they are confident that a strategy exists to the degree they understand and have no made a mistake.

  Reasoning from ability does not work in the same way, because the agent doesn't obtain adequate support for \(A(\psi)\) if they doubt that \(\psi\).

  Of course, going by a potential witness doesn't produce the same.
  However, possible to fill in.
  This is a property of these kinds of arguments.
  Background information matters.
  Failure in the twins case is because agent doesn't have ability to distinguish.
  This changes the argument.
  With potential, the difference is assumption of \(\psi\) versus assumption of reasoning demonstrating \(\psi\).
  Filling in \(\psi\) would make the rest of the argument redundant.
  By contrast, with the reasoning demonstrating \(\psi\) this \emph{is} the remaining piece of the argument, as the agent does not rely on support for \(A(\psi)\).
\end{note}

\begin{note}[Teasing out]
  \cite{Otero:2018we} highlights Jackson wrt.\ teasing out, and how this is fine with failure of transmission.
  Here, this is not the case.
  The informer is not teasing out a prior commitment of the agent, for the agent does not have the commitment without the informer's information.
  For, even if commitment wrt.\ the actual world, the agent's epistemic state without the conditional isn't sufficient.
  Well, because the informer provides novel information, this isn't a case of teasing out.
\end{note}

\begin{note}[Repurposing]
  In some cases, failure of transmission because of repurposing.
  This fails here, because the support for \(A(\phi)\) and the support for \(A(\phi) \rightarrow A(\psi)\) are insufficient alone to support \(A(\psi)\).

  Contrast.

  Experience of red.
  Object is red.
  Object is coloured.

  This is bad, because of factivity.

  Experience of red.
  Object appears red.
  Object appears coloured.

  Fine, but no transmission.
  In Tucker's terminology, inefficient structure.

  \citeauthor{Tucker:2010wn} argues that doxastic transmission works out.
  Depends on understanding of transmission.
  For, propositional is included.
\end{note}

Simple example.
Informer claims that they have hands.
So, if they have hands, there's an external world.
So, informer has provided support for an external world.


So, this is standard failure.
However, distinguishing between the two kinds of support, it seems to be the case that the conditional doesn't do enough.
This is a type mismatch.
So, similar with perception cases.


\begin{note}[Some details]
  Agent reasoning from general ability.
  Confident I have general ability.
  Confident that the informer's information is fine.
  Do not have support for \(\psi\).
  If \(\psi\) is not the case, then general ability does not extend.
  
\end{note}


\begin{note}[Summary]
  To summarise this section.
  Distinction between general ability and witnessing.

  Failure of transmission with general ability.
  For, conditional introduces new information, and places agent's confidence in ability in a evidential role.
  This then blocks transmission, because the agent outreaches the evidential limits by going for \(\psi\).
  Primary focus in terms of transmission failure.
  However, relevant to \citeauthor{Harman:1973ww} also.

  Similar to literature on transmission, but doxastic.
  And, independent of cases other than ability.

  Fault with general ability.
  Distinct from agent doing the reasoning.
  Distinct in turn from appealing to the potential reasoning.
  This is what we turn to next.
\end{note}


\newpage

\section{Witnessing}
\label{sec:witnessing}



\section*{Old sections}
\label{sec:old-sections}


\subsection{The information provided by the informer}
\label{sec:inform-prov-inform}


The agent is confident to some degree that the informer is providing them with the information that
\begin{itemize}
\item If the agent is competent, then they may apply their understanding to demonstrate the existence of a strategy.
\end{itemize}
The agent combines this with their confidence that they are able to reason with the rules of chess, and is confident that they are able to demonstrate the existence of a strategy.

As observed, this requires the agent to be confident of the existence of a strategy, because the agent is confident that they have the specific ability, and it would not be possible to have the specific ability without the existence of a strategy.
However, the agent has not demonstrated the particular strategy.

\hozlinedash

Linked this to similar failures.
Required background information in order for the conditional to be accepted.
For the moment, this failure is a promissory note.
I take the parallels to failures of warrant to be sufficient to maintain initial interest.

\hozlinedash

Furthermore, plausible that there is interesting puzzle here only if the agent is required to be committed to the existence of a strategy without appropriate support.
I have sketched out a possible line of reasoning, but it may be the case that the agent has the option of independently reasoning to the existence of a strategy, and hence the problematic reasoning can be avoided.
If so, simple resolution.
Answering yes or no to a loaded question commits the agent to the truth of something, but if the agent does not need to answer yes or no, the commitment goes away.

The plan for this section is to clarify why the agent does not \emph{necessarily} have the option of obtaining support for the existence of the strategy.
There are various ways to detail the scenario so that the informer does provide support.
Simplest case is where the informer makes the claim while demonstrating the strategy.
Another case, sketched above, is to note that the claim must hold regardless of the specific agent, and so the informer must have demonstrated \(\psi\) in order to make the claim.

So, goal is to motivate the existence of cases that require the sketched reasoning.
The core observation is that in relevant cases the informer is requiring the agent to appeal to their general ability.
This makes sense for a link between general and specific.
However, it does not make sense for a link between general and fact.
So, the problem comes about because the agent cannot avoid commitment to what follows from witnessing.
However, would not need to witness if the agent were licensed from general ability.

While these cases may be comparatively rare, if the reasoning is fine, then it may be performed when there are other options, and hence potential for understanding of agency.

Start with a quick sketch of why this kind of information is desirable.

Student with logic problem.
On the one hand, tells the student where to look if they've got things correct.

One the other hand, tells the student where things are going wrong if they've got some misunderstanding.
If well chosen, this would help the student identify the general mistake.
And, the instructor has avoided giving away whether \(\psi\).

Not all cases are like this, the running chess example is comparatively gentle.
Merely attempting to withhold support and raise the possibility of the agent reconsidering their skill at chess.
However, this remains a possibility.

This examples are in part illustrative, and in part highlight an important initial observation, stressing the conditional relation between to pieces of information in the informers claim.
Our primary interest is in the case where the agent's confidence in their general ability remains high.
However, it is possible for the conditional to be true because both antecedent and consequent are false.

If the agent is confident of general ability, then confident of specific application.
If the agent doubts the specific application, doubt the general ability.

So, reasoning following the pattern of modus ponens, but also modus tollens.

Next, understand why the conditional holds.
Loose notion of support to avoid substantial commitments.
The downside is that lack specifics, still fairly intuitive.
The components of the general ability piece together to the specific.
It might be the case that there is something that blocks the agent, but this is nothing too strange.

For example, Lego sets.
Ability to construct basic, I observe this, reasonable to consider a step up.

Same for chess, the main example.

And, same for similar examples, such as proofs, dexterity puzzles, etc.

Note, that in all these cases the specificity of the specific ability is due some particular application, but the success of the particular application is not limited.
Hence, the reasoning is that given sufficient opportunities there will be a successful attempt.

Similar reasoning holds, for example, with a football match.
However, here there is no relevant factive inference.
Given the form of X, they are able to beat Y at Z.
Though, it may be that X fails Y wins, and the result at Z is fixed.
And, as it is not possible to repeat Z, do not get that there is a success event, leading to a general fact.

Of course, similar constraints can be placed on the above examples, but they are not.

So, repeated attempts, success on one, hence \(\psi\) must be true.
The problem sketched above relied on the agent requiring support for \(\psi\).

An initial minor note is that this do not need to rule out any support for \(\psi\), the puzzle arises if the agent is required to raise their confidence that \(\psi\) due to the agent's confidence that the informer's claim is correct and the agent's confidence that they possess the antecedent/general ability.

For example, unreliable informer mentioned that \(\psi\) holds, lending some support, but ability requires the agent to be more confident.
Or, the informer mentioning \(\psi\) may lend some support.
So long as the agent's confidence in \(\psi\) is in part due to their confidence in the general ability and the informer's claim, there is a problem if the agent does not acquire support.

So, agent's confidence is primarily due to the truth of \(\psi\) being a requirement from incorporating the informer's claim.

In other words, the agent reasons via the conditional.

\hozlinedash

So, have clarified the conditional nature of the informer's claim, and why this is plausible.
Turn to the issue of \(\psi\).

\hozlinedash

The informer's claim does not include support for \(\psi\).
This requires some argument.
Again, distinct from the idea that the agent may obtain support through the entailment --- this will be considered later.

Sketch out a plausible case, and then work through the details.

\begin{itemize}
\item Informer has claimed that if I have the ability to \(\phi\) then I have the ability to \(\psi\).
\item Ability to \(\psi\) requires \(\psi\).
\item Therefore, informer has provided support that if I have the ability to \(\phi\) then it is the case that both \(\psi\) and that I have the ability to \(\psi\).
\end{itemize}

Note, the second conditional distinguishes what is said from what is conveyed.
Agent extracts support, and do not need to assume anything stronger, regardless of whether something stronger can be obtained.

A quick pair of examples demonstrates that inferences of this kind do not necessarily differ when made from information provided by the informer in contrast to the agent reasoning directly from the premise.
Here, entailment.\nolinebreak
\footnote{
  Also holds where additional information is used, but here we are assuming that no additional information is available.

  For example:
  If you take a delay, we will put you on the next flight.
  Support that I will leave in two hours if I take the delay.
}


First, a straightforward unproblematic case.

If you look run the code, you will get the first n primes.

Follows that if the numbers are primes, then not divisible.

Hence, the informer provided support the conditional that if the agent runs the code, they will get non-divisible numbers (primes).

Second, a problematic case.

If you look inside the pen, you will see a goat.

If zebra, then not a cleverly disguised sheep.

If you look inside the pen, you will see an animal that is not a cleverly disguised sheep (specifically a goat).

Seems as difficult as the immediate inference.
For, background condition for the informer, and remains a background condition when the agent makes use of the information.\nolinebreak
\footnote{
  A little more vivid with the external world, but here it is hard to raise the problem without also questioning whether the informer has been provided by an independent informer.
}

Ability is a little different.
The code inference, if obtained prime then property.
If the agent were to witness their ability they would be in the relevant position.
So, this is similar.
Contrasts to the zoo inference, where this wouldn't work out.
The agent would not be in a different position to the informer, and the informer fails to secure support for not a cleverly disguised sheep.

Still, this does not advance too far.
Granted that the agent would get support for \(\psi\) were they to witness specific ability.
Issue is whether the agent gets support without witnessing.

Difference with the code example is that the antecedent doesn't matter.
If prime, then property.
By contrast, if agent doesn't have ability, then block \(\psi\).
\(A(\psi)\) requires \(A(\phi)\).
prime to property does not require the agent to run the code.

Hence, parallel to the goat case, depends on how the agent and informer arrive at the information.
Assume that DNA test is sufficient to declare something as a sheep.
If you do a DNA test, then goat.
Okay, so not a cleverly disguised sheep.

Likewise, if anyone who is able to \(\phi\) is able to \(\psi\) then \(\psi\).

So, still focusing on conditional.

The problem is a little more subtle.
The issue is whether this is a plausible construction of the informer's information.
Or, whether it's plausible that the informer is providing this information.

Simplify to \(A(\phi) \rightarrow \psi\).
For, need to get \(\psi\) independently of \(A(\psi)\).
Natural to understand \(\phi \land A(\psi)\) as simple strengthening.

\begin{itemize}
\item \(A(\phi) \rightarrow A(\psi)\), and
\item \(A(\phi) \rightarrow \psi\)
\end{itemize}
Are significantly different claims.

Intuitive difference.
With the original, expansion of ability.
Relation between two ability claims.
Here, relation between an ability and a fact.

Made a case for the first above.
Here, the difficulty with the latter.

Deny that the informer claims that the agent may be confident that a strategy exists based on their competence.

Gist of the argument is that information that \(A(\phi) \rightarrow \psi\) is quite different to \(A(\phi) \rightarrow A(\psi)\) because \(A(\phi)\) and \(\psi\) are independent in a way \(A(\phi)\) and \(A(\psi)\) are not.

{
  \color{red}
  The similarity to failures of transmission is obtaining a factive condition from a non-factive condition.
  As it is possible that the relevant antecedent does not extend, it does not provide sufficient support.
  This, I think, is well recognised.
  When the agent does the reasoning, the agent obtains the relevant factive support.
  The reasoning stands independent of the agent's general ability.

  So, perhaps in the zoo case, the agent is already in the appropriate factive state.
  With the reasoning, this is not the case, as for sure the agent has not done the reasoning.

  Bracket similar concerns about whether the agent has in fact reasoned.
  This is somewhat significant.
  Still, there remains a difference granting the possibility.
}

\hozlinedash

Recall the basic idea behind the conditional.
Relation between abilities, and support comes from witnessing.
If \(A(\phi) \rightarrow \psi\) then no need to witness.
For, possessing the ability is sufficient for \(\psi\).

Informer did not plausibly aim to provide the agent with support for \(\psi\) independent of application of their general ability.
The agent may be confident through application of their ability, but not in virtue of possession of ability.

\hozlinedash

Well, it is clear that there is a difference in truth function relevance.

General ability is relevant to specific ability.
General ability is not relevant to existence of strategy.

Hence, \(A(\phi) \rightarrow \psi\) requires \(\psi\) to be true.
\(A(\phi) \rightarrow A(\psi)\) requires \(\psi\) to be true \emph{if} \(A(\phi)\) is true.
And, so, as it is possible for the agent to drop \(A(\phi)\) and be neutral on \(\psi\), the agent doesn't get \(A(\phi) \rightarrow \psi\).
For, as the informer has only linked two abilities, it is possible that the agent lacks both (, and for the presumed fact to be false).

Given the informer's claim, confidence in \(\psi\) depends on confidence in \(A(\phi)\).

However, \(A(\phi) \rightarrow \psi\).
Then either the agent should be confident of \(\psi\) regardless of ability or the agent should be confident that they lack the ability.
For, either \(\psi\) is true, and the ability doesn't make a difference.
Or, \(\psi\) is false, and the agent does not have the ability.

Therefore, informer needs to have determined either position.
By contrast \(A(\phi) \rightarrow A(\psi)\).
The agent may doubt that the agent has ability, but remain confident that if the agent has the ability, then they have the specific ability.

This point is perhaps easier to illustrate with the logic variant.

If able to reason with system, then \(\Sigma\).

It seems either must be confident that \(\Sigma\), or that you have no ability.

For, agent's ability to reason with the system does not affect whether \(\Sigma\) follows.
Hence, I do not consider the agent's ability to support \(\Sigma\).
Therefore, I must be confident that \(\Sigma\), or that the agent lacks the ability.

Contrast.
Able to reason, then able to show \(\Sigma\).
I may be unsure about whether \(\Sigma\) follows from the system, but be confident that the steps the agent took can be replicated to demonstrate that \(\Sigma\).
If the agent does in fact have the ability, then \(\Sigma\) does indeed follow.
Still, as the informer I am free to withhold commitment to this.

It is perhaps important to note here that there are instances where there is an appropriate dependence relation between ability and fact.
For example:

If able to show system is sound, then \(\Sigma\).

For, now \(\Sigma\) follows from ability.
For, if the agent has the ability to show the system is sound, then the system is sound, and therefore my prior reasoning combines with the agent's demonstration.

Suggests that independence from fact is a key feature.

\hozlinedash

This reasoning also applies to the left nested \((A(\phi) \rightarrow A(\psi)) \rightarrow \psi\).
Independence in this case.

\hozlinedash

Suggests a final option to consider.
Informer reasoned from general ability to specific.
So, this provides support for thinking that \(\psi\), because the agent is confident of general ability, and the informer has provided information that the agent's ability may be witness in this way.

\hozlinedash

Strays from the original idea?
Informer provided an instantiation in order to make the conditional.

This is a subtle variation.
Does not require the agent to go from general ability to fact.
Instead, the informer is taken to perform the reasoning that the agent would do.
Analogous to the informer being a solver, with the additional feature of reporting on ability.
So, the conditional is read to state the informer applied the agent's ability to show that \(\psi\).

\(A(\phi) \rightarrow A(\psi)\).
So, is a witness.
Witness provides \(\psi\).
Hence, confidence in \(\psi\).

Informer's conditional, roughly, reads:

\begin{itemize}
\item If you are able to reason with the rules of chess, then, I have applied the actions available and shown that there exists this strategy, you are able to demonstrate the existence of this strategy.
\end{itemize}

In contrast to the proposed idea of potentiality, here the informer themselves witness the potential.

So, this is different from the initial problem, where there's a failure of transmission.
As here the idea is to reason via the informer's witness of the agent's potential reasoning.

Note, this is not the informer's reasoning.
The key idea here is that the informer is talking about what the agent could reason to.
The informer could follow this up with a demonstration of \(\lnot\psi\), for example, requiring the agent to either consider the informer mistaken or an abandonment of the agent's confidence in their general ability.
Hence, this does not require any assumptions about the informer's abilities, other than their ability to reproduce the agent's reasoning.

The agent may have some doubt about the informer, but this will be incorporated into their confidence that \(\psi\).

Key here is that the informer's reasoning provides support.
Granted that the informer's reasoning would provide support if replicated by the agent.

(Part of) Distinction is that the informer has worked form what the agent is able to do, \emph{not} the agent's ability to reason with chess.
So, the agent is on the hook for relating the steps performed by the informer to a demonstration of \(\psi\), as opposed to a need for the agent to work on their understanding of chess.

So, the agent is still relying on their general ability to do the work.

This means that this is really no different from the original inference.


Constructive vs.\ intuitionist to make sense of this.
Not claiming that the system demonstrates.
Rather, follows from ability.

Little doubt that the agent is in some sense fine.
However, doesn't show that this is fine.

Of course, the reasoning performed by the agent is (by assumption) the reasoning that the agent would do.
{
  \color{red}
  The key difference is that if the agent were to do the reasoning they would be able to give up \(\psi\).
  Whereas by relying on the informer the agent cannot give up \(\psi\).

  If the agent does the reasoning, then they are not required to assume \(\psi\) prior to doing the reasoning.
}

This is what separates the case from a standard solver.
The standard solver is run without assumption of \(\psi\).
By contrast, the informer includes information about the result of the solver with the run.
This prevents the agent from obtaining support, because the agent could not be neutral without discarding the informer's information.
In contrast to the solver, where the agent is neutral.

Right, so agent cannot adopt interrogative attitude without losing \(\psi\) given informer's information.
But, this is not simply because the informer has told the agent that \(\psi\) follows.
This happens all the time.
Rather, it's because the informer hasn't directly told the agent that \(\psi\) follows.
The agent still needs to link this via the general ability.
And, so the agent doesn't have the option of being neutral on \(\psi\) given general ability given the proposed information.

So, similar to the above, general ability leading to \(\psi\).
However, here established the potential link.
And, the problem is the status of this link.
For the informer has not presented this is support for \(\psi\).

Here, again, relying on the agent having the general ability to reconstruct the informer's reasoning as a demonstration of \(\psi\).

So, this is a subtle difference with the intuitionist and the constructivst.
For, if the question is whether there is a classical proof, the issue is reasonably settled.
If the issue is the relevant interpretation of the proof, then support does seem to be lacking.
However, this goes beyond the natural interpretation.
Of course, reconstruct the scenario to focus on this information.
If able to demonstrate adequacy of \(\phi\) then able to demonstrate \(\psi\).

Intuitively the agent is fine.
However, the issue is why this is so.
Argument is that it is not due to the ability doing the work.

\hozlinedash

Back to the left-nested \((A(\phi) \rightarrow A(\psi)) \rightarrow \psi\).
Here, the point is now that this is \(\mathcal{C}(A(\phi) \rightarrow A(\psi)) \rightarrow \psi\).
So, the informer claiming the entailment gives support.
Again, because the informer has performed some reasoning from the available action of the general ability to some specific.
Yet, still a problem because \dots
Well, I fail to see why this makes sense.

\hozlinedash

Agent leverages their general ability to be confident that the informer's (assumed) reasoning is correct.
And, this goes beyond the information that the informer provided.
Possession of ability is not equivalent to demonstration of ability.

Agent is confident that they can replicate the same reasoning, but the support from the replicated reasoning would go via the particular steps, and not be based on the general ability.
By contrast, here we require the general ability to license the particular steps taken by the informer.

Paraphrase helps make this explicit.
For, the informer only talks about the application.
Agent is required to be confident that \(\psi\).
However, because the agent cannot avoid the same reasoning.

Failure of dependence?
For, informer would do these steps whether or not they reflect the ability.

The subtle difference is the availability of the solver prior to the information.
This is (part of) what is excluded when the informer only makes the conditional claim.

Consider the solver.
The agent writes this, so their reasoning is now that the solver produced this.
The agent is not aware of the particular strategy, but it's also not the case that the agent is relying on their general ability.
Solver shows that actions the agent is able to perform are sufficient.
Confidence is strategy is based on these, but flows through the resolution of the solver.

Key difference is that the agent is not using their general ability to ensure the existence of a solver.
The agent's confidence in their general ability \emph{strengthens} their attitude given the results of the solver.

By contrast, with the informer, the agent's confidence in their general ability is \emph{first time} for the solver.
If the agent were not confident in their ability, the agent would not be confident that the informer has provided information about a demonstration.

(Solver + confidence) > psi

vs.\

confidence  > solver > psi.

So, it may be the case that the agent posits an application of their general ability in reasoning to \(\psi\) from the informer's claim.
However, as the agent leverages confidence in their general ability to infer the application, it remains the case that the agent is assuming \(\psi\) in order to infer the application.

The informer could have presented their reasoning without conditioning on the agent's ability.

General ability is often applies to demonstration.
Still, demonstration is independent.

So, this returns to the same point.
Maybe this gives some reason.
However, the informer has premised on the agent's ability.
In order for this to work out, the agent is assuming that their ability licenses this particular witness.

So, again, the agent is reasoning from general to fact, without any demonstration.


Distinct from the witness.
For this does not rely on the agent's ability.

Difference between proofs.
So, student who has rough grasp, and produces a correct proof.
Contrast to the student who has a rough grasp with no proof.

So, confidence of ability is required in order to extract something for particular applications.
If I doubt my logic skills, I won't form a belief even through a competent deduction.

However, confidence in ability is not enough alone.
For given a demonstration this stands independent of ability, the demonstration screens off the need to appeal to ability.
Ability is optional.
TA marks the proof as correct.
This doesn't flow through ability.




\newpage

\section{Negative argument (Old)}
\label{sec:negative-argument}

\subsubsection{Kind of ability claim}
\label{sec:kind-ability-claim}

Distinct from cases where factive inference fails.

\begin{note}[No clear ability to decide]
  This may need to go in a footnote, but the conditionals are useful in helping to illustrate that the agent does not necessarily have the ability to decide.
  The agent may be confident that they'll find a strategy if it exists, but not be able to rule out the existence of a strategy.
  In some cases this is less plausible, in particular the chess example amounts to brute forcing, and hence deciding.
  Proofs are an easier example.
  Here, start out confident, but failed proofs don't give a hint as to whether or not the theorem is true, and hence the agent gets somewhat lost.
\end{note}

\begin{note}[Ability does not make conclusion true]
  In the cases of interest --- ability to reason --- the ability does not \emph{make} the conclusion true.
  The conclusion is available to the agent because it holds independently of the agent's ability.
  Contrast to other instances of ability, such as running a 5K, where the executing the ability would make the relevant proposition true, but without the execution there is no way to obtain the truth of the proposition.

  Hence, in the case of ability to reason, there must be something other than the agent's reasoning which is securing the truth of the (relevant) proposition.
\end{note}

\subsubsection{General and specific}
\label{sec:general-specific}

\begin{note}[GandS]
Assume that the general ability is sufficient to entail that \(\psi \rightarrow A(\psi)\) for some collection of \(\psi\), but it does not follow that the general ability reduces to this.
  In part, because I do not see how to determine the relevant collection of \(\psi\) without grasp of the general ability.

  Some cases are easy, such as the option of moving a pawn.
  Others are more complex.
  In particular, it seems counterfactuals in terms of awareness etc, might be included.

  If there were a reduction, then extensional characterisation.
  And, then singular counterexamples would be sufficient.

  Some counterexamples, such as moving the pawn are sufficient.
  However, stand somewhere between the two extremes.
  One being a clear counterexamples, and the other extreme being rejection of the instance.

  In turn, this means that the claim made by the informer is understood in terms of confidence --- high confidence that there's a link with the possibility that the agent may retain the ability.
  The informer does not claim that the agent does not have the general ability if they are unable to demonstrate the strategy.
  However, the agent's confidence is sensitive, if the strategy exists and the agent is unable to demonstrate, then the agent should be somewhat worried without further support for their ability.

  So, the agent's interest in the informer's claim is tied to the relation between the general ability and the specific instances.
  This goes beyond the surface, but is important (and implicit).
  For, if the agent doesn't endorse this, then the agent would not be able to leverage their general ability.

  Note, this is plausible for the example.
  There are not too many pieces on the board, and the strategy is two steps.

  So, even without a witnessing strategy, this seems a fair interpretation of the informer.
\end{note}

\begin{note}[Relation between general and specific]
This does not depend on any particular strong views about the nature of these abilities.
General ability may be a bundle of specific abilities, etc.

The relation between the general and specific is complex.
General entails some specific, and sufficient specific may suffice for general.
Hence, agent may be confident from generalising from specific cases.
This is reasonable support.

For example, working through various chess problems.
Fair indicator that the agent posses the general ability in this case.

Converse is that specific failures are `counterexamples' to the general.
At least to agent.

Key is that this is from the agent's point of view.
Independent of the actual relations, these kind of relations govern confidence.

Illustrated with simple chess examples.
And, some go beyond the basic ability.
Here, the chosen particular claim is plausibly of the former category.

This may seem coarse, but a few points:

The main points here are
\begin{enumerate}
\item The coarseness is to be expected, and
\item This results is soft dynamics, due to the nature of abilities.
\end{enumerate}

There is a common core, and this is the lack of ability, which is in turn distinct from details of how the agent witness the ability.
Consider a simple checkmate.

First, general supports specific.
Else, it is difficult to see how reasoning of this kind could work out.

Second, common core suggests that failure here extends to other specific claims.
The specific ability is not isolated, so to speak.
In part, this is what allows the agent to generalise from the general to the specific.

Third, does not require that the agent is competent with exercising the ability.
It may take the agent a significant amount of time to recognise that the opportunity is there.
However, this is different from failing to understand the possibility.
Even if the agent misses the checkmate, this does not show that they failed to have the ability.
Though, it may suggest that the agent lacks competence with the ability.
So, failure of understanding rather than execution.


In turn, this means that the agent is unlikely to establish a counterexample.
At least, not without further information.
So, this ties to confidence.
The conditional itself is coarse, but the reasoning is fine grained.

I suspect that things are much more difficult when ability is also time sensitive, etc.
Set these concerns aside.
\end{note}

\subsubsection{Ability and witness}
\label{sec:ability-witness}

\subsubsection{The conditional}
\label{sec:conditional}

\begin{note}[Conditional]
  Observe that there's a reliance on conditionals here.
  In general, not so much of a problem.
  If we see something that requires something else, then we know the requirement is satisfied.
  The problem here is that things \emph{could} go either way.

  So, \(A \rightarrow B\)
  Can't be sure whether \(B\) is an unexpected counterexample to \(A\).
  Or, whether the evidence for \(A\) allows one to be confident that \(B\).

  For example.
  Fire safety checklist.
  Go through, and see that some parts are missing, but there's what appears to be a sign-off.
  So, does one infer through to the rest of the conditions, or do these show that the signature is invalid.

  The addition with ability is that antecedent doesn't just suggest, but rules out counterexample.
  Though, this isn't unique, that's kind of the point of counterexamples.
  That's what, roughly, makes the thing a counterexample, rather than potentially independent.

  So, informing that if your theory is right, then there's an explanation of \(X\) is fundamentally equivalent.
  There are going to be many examples here.
  Where, got good reason to think that this is something that is explained, rather than a counterexample.
\end{note}

The natural language conditional here isn't important.
Rather, employed because it captures relationship.

If you have the ability, then you are able to demonstrate.
If you do not have the ability, then either you are not able to demonstrate, or it is not a fact.
It is not the case that you have the ability to demonstrate and it is not a fact.

{
  \color{red}
  Dependence.
}
However, \emph{epistemic} dependence.

This is the idea that the consequent is not arbitrary for the agent.
The antecedent sets limits.
And, in addition, that this does not come from ruling out possibilities.

So, this is somewhat neat.
If we have a demonstration of \(P \rightarrow Q\), then the \(P \land \lnot Q\) worlds are ruled out.
By contrast, in this case the agent doesn't have sufficient information to rule these states out, but instead considers them unlikely.

This is not the case with the factive entailment, which \emph{does} rule out.

So, this is part of the tension.
On the one hand, the agent doesn't get to rule out, but by the content of the antecedent, the states are `functionally' ruled out.

So, this is what's strange.
It's hard to replicate this.
I'm confident that A knows that P.
Well, this works.
A has told me that P, and I'm confident that this is knowledge.
Still, it's not clear that I can rule out P.
So, in addition to ruling out, there's something about being in a position to rule out.
Well, this is the point about having propositional support, in a way.

Epistemic dependence.
If X isn't at the party, Y isn't at the party.
Something like this.

Contrast to many other cases of ability.
Eligible to enter the race.
Well, this depends on whether you are able to run 5k.

So, the agent is informed of epistemic dependence.

In part, this is why I hold that no account of detailed account of why you hold the existence of a strategy follows.
For, endorsing the epistemic dependence, going for the antecedent, and detaching doesn't trace any explanation.
Because the two things are independent, obtaining the fact from the ability doesn't inform about why the ability is true.

However, the execution of the antecedent is not independent.

Clear from the propositions related that the fact does not depend on your ability.

Yet, it the ability is witnessed, then you have something more than epistemic dependence.
This is basically the hook.
In general, there is no restriction on what is witnessed.
In chess example, have something like dependence.
However, may imagine that there are a variety of ways to show, and so this isn't dependence in the sense used here.
For example, truth functionally incomplete set of operators will be sufficient to demonstrate some tautologies, but these can also be demonstrated in other ways, by rewriting given a full set.

To speak generally, term this a demonstration.
So, in the case of these statements, epistemic dependence with an underlying demonstration.

This outdoes the epistemic dependence.

The key point with epistemic dependence was that general ability doesn't say anything about the truth.
However, with demonstration, we have premises and conclusion.
It can't be the case that the premises are true, the reasoning is sound, and the conclusion is not true.

Clearest way is that the demonstration is typically transferable.
It's not merely the case that the agent is committed to holding true, but the demonstration allows the agent to convince others that it is true, regardless of the agent's ability.
This holds even if the agent's ability is in doubt.

Likewise, the agent may lose confidence in their ability, but relation the demonstration.
With chess, it's a little outlandish, but note that there are no rooks.
This would impact general grasp of chess, and so the epistemic dependence is broken.
However, if the agent has done the reasoning, then they'd keep the demonstration.

Intuitively, then, with ability in the antecedent, the agent ends up in the position of the epistemic dependence tracking the demonstration --- whatever that demonstration turns out to be.
Witnessing the ability provides the demonstration, and goes beyond epistemic dependence.

However, also the fact that, with the claim, the consequent is a necessary condition.
So, this is \emph{more} than simple epistemic dependence.
Or, maybe not.
Perhaps \emph{strong} epistemic dependence.
For, it seems that in the case of epistemic dependence, the counterexample property doesn't really hold.
There's some overlap, and it's enough to create this relation, but not enough to do modus tollens.

This is the `strong' case.
Clear that something is gained by witnessing the ability.
Question is whether the epistemic dependence provides \emph{sufficient} support.


\begin{note}[Nothing super strong]
  It's probably important to note here that everything is relative to the agent.
  In that, the demonstration is limited to whatever support the agent has for the premises.
\end{note}

\begin{note}[Conditional and epistemic dependence]
  So, it's easy to observe here that the conditional is establishing something like `epistemic' dependence.
  For, it is obvious from the viability of the factive inference that there's no `metaphysical' dependence here.
  If the strategy exists, then it exists whether or not the agent has the ability to demonstrate it.
  So, the inform is not communicating that the ability is sufficient for a strategy.

  This point is helped by noting that if the agent has an alternative source, then the conditional seems uninteresting.
  For example, assume that the informer is aware that the agent has a solver.
  They'll type in the board, desired position, and see whether there's a strategy.
  Now, the conditional remains true.
  However, it now serves as a test of the agent's ability.
  For, the agent's confidence in the consequent is independently secured by the solver's guarantee of the existence.
\end{note}

\begin{note}[Independent support breaks epistemic dependence]
  This is clear, as the consequent no longer depends on the agent's confidence in the antecedent.
\end{note}


\subsubsection{Expected dynamics}
\label{sec:expected-dynamics}

\begin{note}[Type of argument]
  This is rough.
  However, the key idea is expected dynamics.
  The first thing to note is how the squeezing works.
  Then, the second thing to note is that the agent can come to be in the failure of transitivity position, and this still be consistent with what the informer has claimed.

  Problem with this type of argument is that it's somewhat difficult.
  There is more to language than semantics.

  Informer claims that they think \(X\) is at the door, and this pushes to thought, and then various interpretations of \(X\), but this doesn't show that the informer didn't provide support for a particular individual being at the door.
  Except, in some cases it does, right?
  It feels as though something more is going on, but I'm not sure what it is.

  Difference with the though case is that you don't have good reason for thinking \(\phi\) unless I also have good reason for thinking \(\phi\).
  However, with the ability case, you may have good reason for thinking \(\phi\) even if I don't have good reason.

  So, it isn't the case that we're only relying on semantics here.
  The conditional form was chosen.
  There are other options.
  The informer could have presented a conjunction.

  With this in hand, note that the informer adding their lack of confidence doesn't seem to change things.
\end{note}

\begin{note}
  Here, I want to sketch what makes this interesting.

  \begin{enumerate}
  \item The agent has not yet witnessed their reasoning, so based on ability and conditional information.
  \item Given confidence, if agent witness their ability, then they have supporting reasons.
  \item Given confidence, declining existence is not viable.
  \end{enumerate}

  The third point here is a little subtle.
  The idea is that the agent either takes the existence or does not form any opinion.

  Key idea is that so long as the agent is confident in base ability and holds the conditional, the agent is required to hold the existence of a strategy, but the third, and cites their potential reasoning by the second.

  Unclear that the second and third are separate.
  For, the witness is basically always the defeating strategy.
  {
    \color{red}
    They are, in the sense that the factive inference holds.
    This is sufficient to commit the agent.
    This also sets the case apart from reflection.
    For, with reflection there's no factive constraint.

    It is then the second premise that sets the case apart from skepticism.
  }

  Entailment from second to third rules out the agent suspending.
  If this is ruled out, then agent adopts \(\psi\). (This is showing that \(\lnot\psi\) is not the case, not merely failing to show \(\psi\)).
  If agent adopts \(\psi\), agent has some support for \(\psi\).
  However, ability doesn't provide support for \(\psi\).
  Therefore, those reasons which require \(\psi\).

  This is a neat little argument.
  And, the key is, that the requirement of support, once shown to be fulfilled by ability, is preserved.

  The tricky part is that the ability rules out the option, but doesn't provide support.
  One may worry that only ruled out if the agent witnesses.
  However, I don't think this is so, because the premises supporting the no choice premise only rely on ability.
  However, ability itself doesn't support fact.
  Which is still somewhat odd.
  The agent doesn't establish that it is not the case that a strategy doesn't exist when narrowing the options.

  Then, problem is that this doesn't translate into support for \(\psi\).
  This follows by the Wright-type argument.

  So, agent required support.
  Either independent or ability.
  But that comes after establish ability as a viable option.
\end{note}


\subsection{The Main Problem}
\label{sec:problem}

\subsubsection{Overview/Recap}
\label{sec:overviewrecap}

\begin{note}[Overview]
  The problem is that it doesn't seem as though there's a good inference to the fact via the epistemic relation.
  So, we have a choice.
  \begin{enumerate}
  \item Independent support, or
  \item No conditional.
  \item Lower confidence.
  \item Allow potential support/licensing.
  \end{enumerate}
  Once this has been shown, then the bulk of the argument is requiring a choice between the latter three options.
\end{note}

\begin{enumerate}
\item\label{simple:claim} I am able to reason from the rules of chess and the game state to the proposition that White cannot prevent Black from occupying c4 on their second move.
\item\label{simple:necessity} If it is not the case that White cannot prevent Black from occupying c4 on their second move then \ref{simple:claim} is false.
\item\label{simple:focus} White cannot prevent Black from occupying c4 on their second move.
\end{enumerate}

Premise~\ref{simple:necessity} is key.
Factive observation.
Some ability claims are true only if some corresponding fact is true.
It may be that all ability claims admit factive inferences to some degree.
For example, I have the ability to travel to Naples only if Naples exists.
However, the factive ability instances of interest have two important properties.
\begin{enumerate*}
\item establish novel information, and
\item this information is (more-or-less) stated within the ability claim.
\end{enumerate*}
Likely already knew that Naples existed, and the claim presupposed the existence of Naples.
In contrast, White cannot prevent Black from occupying c4 on their second move is novel, and is stated in the ability claim.



\begin{note}[Relation and antecedent]
  This was sketched above.
  The key is that the relation is epistemic, at the level of inference, but factual at the level of entailment, roughly.
\end{note}

If an ability claim is compatible with a factive observation of this kind, then agent gets a fact.
However, applying the factive observation does not provide the agent with support for holding the fact to be true.
Instead, it draws out a necessary condition for holding the ability claim true.
The agent must be committed to the existence of a strategy for Black in order to hold that they have the ability to demonstrate such a strategy.


\begin{note}[Sketch from \cite{Roche:2014ww}]
  If the agent is already confident that \(A(\psi)\) or \(\psi\), then \(A(\phi)\) is unneeded.
  The agent's general ability is superseded by the application to the specific case.

  And, if the agent is in doubt about \(\psi\), then reflecting on their general ability \(A(\phi)\) is troublesome because the agent's general ability applies to a specific case only if the specific case holds.

  As such, processing the informer's claim requires the agent to tacitly assume \(\psi\), or else withdraw either their confidence that their general ability extends, or the link provided by the informer.

  Rejecting the general ability seems worse than rejecting the link, in general, because this should only be dropped if the agent lacks the general ability, but this will only be the case if \(\psi\) does indeed follow.
  Hence, it seems the agent should reject the conditional.

  A similar point holds in skeptical scenarios.
  Here, however, the conditional is fixed.
  Hence, failure of transmission.

  However, the information seems fine.
  It is useful information, it is a remarkably nice hint, for example.
  Therefore, `non-transmissive', as the general ability would not do the work without the assumption.
  While this highlights the general problem, there are details about failure of transmission that matter.
  In particular, failure of doxastic transmission, as if the conditions are met, then the failure at the propositional level is trivial, as the agent had the ability regardless of the conditional.
  Rather, failure at the doxastic level.
  The agent doesn't have the appropriate relation to \(\psi\) by \(A(\psi)\).
  In short, because there could not be propositional transmission.
\end{note}

Four parts to this problem:
\begin{enumerate}[label=?\alph*., ref=(?\alph*)]
\item\label{prob:part:condit} The agent is okay with the information provided by the informer.
\item\label{prob:part:n-supp} The agent lacks support for the fact independent from the claim made by the informer.
\item\label{prob:part:embedd} The fact is (in the cases of interest) embedded --- The agent does not obtain direct support for the fact from the informer making the claim.
\item\label{prob:part:endors} The reasoning inference is non-transmissive.
\end{enumerate}

\begin{itemize}
\item Given~\ref{prob:part:condit}, the claim is okay.
\item Given \ref{prob:part:n-supp}, if the agent obtains support, then this comes from the claim.
\item Given~\ref{prob:part:embedd}, the agent does not obtain support from the claim without some reasoning.
\item Given~\ref{prob:part:endors}, the agent does not have the option of lifting the support they have for their general ability to the specific case.
\item Therefore, the fact only follows given the antecedent, but the antecedent does not provide support.
\end{itemize}

If any of these parts can be resisted, then the problem clears up.
For, then it is the case that the agent has support that the fact obtains independent from their endorsement of the ability claim, and so the agent does not assume the fact by endorsing their ability.

{
  \color{red}
  Still, ability supported, and hence support for fact.
  The only reason the agent presently has is the informer's claim.
  Still, intuitively, this is the point of citing ability.
  The agent's confidence requires the assumption of \(\psi\), but this is licensed as an assumption because, so long as \(\psi\) is the case, the agent's assumption can be discharged.

  This is, unsurprisingly, a stronger assumption that merely that \(\psi\) is the case, but the upshot is that the assumption is testable.
  In contrast to skeptical cases, the assumption is not entrenched.
  It is, roughly, superficial --- it is not thorough.

  Hence, even if you hold that the agent is not rational, there is room to distinguish between two kinds.
}

Recall, the factive inference is a symptom of the problem.
The agent does not need to make the factive inference\dots

The goal is to provide sufficient conditions to necessitate granting the agent access to reasons prior to witnessing those reasons.
It may be that in most, or many, cases involving ability claims one of~\ref{prob:part:n-supp}---\ref{prob:part:endors} fails, and the agent has the option of independently establishing the fact required for the agent to possess an ability.
(Some of these options will be detailed in the following two sections.)

Therefore, if \ref{prob:part:n-supp}---\ref{prob:part:endors} obtain, and the situations in which they obtain are not too far-fetched, then the option is either granting the agent access to reasons prior to witnessing those reasons or requiring the agent to abstain from endorsing the relevant ability claim.
The argument for the former disjunct will be implicit through the following two sections.
Still, the broad idea is simple; information that one has the ability to do something is useful, and granting access to reasons prior to witnessing those reasons is a fair price for such information.

{
  \color{red}
  First is two argue that the three parts hold together.
  It is reasonable, because the ability does the work, in a sense.
}

After the two parts of this problem have been argued for, section~\ref{sec:licensing} will the idea of access to reasons prior to witnessing those reasons will be explored in greater detail, and section~\ref{sec:counterpart-argument} will provide a counterpart argument, highlighting scenarios which benefit from granting access to reasons prior to witnessing those reasons, even if the scenarios do not require such access.


{
  \color{red}
  Narrow the situation so that alternative routes to the fact are ruled out.
  First by arguing that the informer's claim does not directly provide the agent with support, and second by arguing that the agent does not have the option of (somehow) obtaining support prior to their own endorsement of the ability.
}

\begin{note}[Still independent support]
  So, independent support is an option.
  The agent is then confident that they can offer a `direct' line of support for the fact.
  So, there may remain some interest.

  Would be useful to illustrate some of the differences.
  For example, different pragmatics upshots.
\end{note}

\newpage

\begin{note}[Moving to the argument]
  The goal here is an existence argument.
  Therefore, two parts.
  \begin{enumerate}
  \item Construction
  \item Witness
  \end{enumerate}
  First, outline the theoretical background detailing how witnesses may be constructed.
  Second, provide some witnesses.

  There are a couple of features of this approach.
  The specific witnesses provided are somewhat redundant.
  The construction provides enough,
  Some witness is required for this to be interesting.
  But you only need to deal with the construction to deny a witness, and I don't need to lean to heavily on the details.

  Second, the construction, if successful, will establish something stronger.
  The construction is sufficient for the required witness.
  Narrowing on particular information.
  This may be robust for other contexts.

  Style of argument:
  \begin{itemize}
  \item May be the case that the informer typically provides the option of support.
  \item However, look at the semantics and see that this is not entailed --- it is possible for the speaker to make the claim with endorsing the conclusion.
  \item Then search for witnesses.
  \item Then, this lifts to all scenarios --- given some constraints.
  \item Hence, in some situations this is the only thing that is possible.
  \item Due to a feature that holds in all situations.
  \item Therefore, this option is available in all situations.
  \item Other routes may end up being available, but this is never ruled out.
  \end{itemize}
  The last step comes by a general assumption about semantic preservation.
  I think it is fine.
\end{note}

\begin{note}[Quick overview]
  The basic idea is quite straightforward.
  \begin{itemize}
  \item The form of the claim as a conditional `requires' the agent to go via the antecedent.
  \item The content of the antecedent requires the agent's endorsement.
  \end{itemize}
\end{note}

\subsubsection{\emph{Only}/Influences}
\label{sec:only}

This is really difficult.
The use of (self programmed) calculators seems fine.
The chess program the same as using a calculator.
So, seems the agent obtains sufficient support from program.
And, it seems this is roughly because the program is a witness of the agent's ability.
However, there seems little significant difference between the witness and the program.
And, if the agent is concerned that the informer made some assumptions, then this will affect confidence in \(\psi\) and \(A(\psi)\) equally.
Hence, it seems the informer is functionally equivalent to a witness of the agent's ability.
And, therefore, this provides the agent with support that \(\psi\).

This may be simplified by stating that the agent is \emph{only} informed of the conditional.
In this sense, the agent's confidence after incorporating the claim is solely due to the claim.
However, as noted above, this isn't required.
It is sufficient that there is some difference.
For, then the conditional has some effect.

\begin{enumerate}
\item Informer is not required to be confident of the fact.
\item Informer is not required to be confident of the fact independent of the agent's ability.
\end{enumerate}


\begin{note}[Strategy follows?]
Has the informer claimed that the strategy follows from the general ability?

Example: the informer doubts the existence, but reasons form observing the principles employed by the agent.
If you really do have an understanding of chess, then able to demonstrate.
The informer must be confident that the strategy exists given the agent understands chess.

So, even though the informer has not claim \(A(\phi) \rightarrow \psi\), it seems the informer is committed to this claim.
Hence, argue that if the agent is okay with the informer's claim, this provides a defence of \(\psi\).

However, \(A(\phi) \rightarrow \psi\) is somewhat useless, because it shows the same thing?
The agent commits to \(\psi\) to maintain their confidence in their general ability.
The informer has not provided the agent with support \(\psi\).

To help illustrate this point, consider the agent constructing a solver.
They construct a program reflecting their understanding of the basics of chess, and then run the program.
If the solver returns the existence of a strategy, then the agent may be confident, because they can be sure that a strategy follows by applying the understanding that they have.

This isn't quite right.
For the agent doesn't reason from ability.
Hum, this seems odd, though.
Because, in this case, the agent's confidence in their general ability is what governs their confidence that the solver is correct.
So it seems that the agent gets \(A(\phi) \rightarrow \psi\).
At least, the reasoning here is similar to the informer working from \(A(\phi)\) to \(\psi\).
Still, the agent is confident that the programming is correct.
Though, similarly, the agent should be confident that the informer's reasoning is correct.
At least, it seems there won't be any significant difference.

Well, the informer is only confident that \(\psi\) from \(A(\psi)\).
Or, from \(A(\phi) \rightarrow A(\psi)\).
In other words, it is possible for the informer to only be confident that \(\psi\) because of the extension of ability.
So, from this it follows that the informer is confident that \(\psi\) follows from ability.
However, it does not follow that the agent can separate \(\psi\) from \(A(\psi)\) from the informer.

In contrast to the program, where the two are separable.

Basically, then, the issue is that informer also reasons that \(A(\psi) \rightarrow \psi\), whereas with the program the agent reasons \(\psi \rightarrow A(\psi)\).
In other words, the informer may drop any confidence in \(\psi\) when \(A(\psi)\) is dropped.
Whereas, with the program, the agent should remain confident that \(\psi\) even if \(A(\psi)\) drops.

So, \(A(\phi) \rightarrow \psi\) is also problematic.
However, this provides less information.
For, the same problem arises depending on why the informer is confident that \(\psi\).
However, leaves open that the informer may take \(A(\phi)\) as a boost to their confidence that \(\psi\).
I.e.\ paralleling the program.

Note, however, that this is a distinct reasoning pattern.
This goes from ability to existence of strategy.
And, whether the agent is also able to themselves demonstrate without the computer program is then a further step.

In contrast, the claim provided goes via the specific ability.
If the agent does not have additional information, then their confidence that a strategy exists is in virtue of their confidence in general ability and informer's claim.
Run the same problem on the solver, if successfully implemented a basic understanding of chess, then the solver will be able to find a strategy.
Again, only if the strategy is there to be discovered.
\end{note}


So, the argument here is simple.
Identify desired dynamics.
Observe that these are incompatible with the informer providing support for the fact.

This, then, puts the agent in the bind.
Either no ability.
No informer.
Fact.

This is \emph{only} an epistemic relation.
There's something to this.
No definition, causality, etc.

In general, it's quite difficult to argue from natural language statements involving conditionals.
Take something simple.
\(P \rightarrow Q\).
Could be that not \(Q\).
Could be that \(P\) so then \(Q\).
Could be that \(P\) is so obvious that I'm asserting \(Q\).
Could be biscuit conditional.
Could be that \(Q\) is only relevant when \(P\).

That the claim of the informer has the syntactic structure of a conditional is not of particular interest.
For, interested in the goals of the informer and the uptake of the speaker.
Goal is that the informer communicates, and the agent processes, a relation between two abilities.

Later, particular examples.
Here, the dynamics.
In particular, desired dynamics are incompatible with independent support for the fact.

Here, expected dynamics, and these fit a conditional.

Key points are:
Ability pushes up.
Lack of ability gives little information.

For both of these to be the case, then informer cannot provide support for the fact.
For, this would rule out the second.
Informer is required to highlight the fact in order for the first.

Unlike conjunction, the agent is required to push down their confidence before coming to doubt the fact.
This is one of the main points.
So, the \emph{potential} uncertainty is key.

The second is that because the confidence comes via confidence of ability, the agent's ability is given focus.
If the agent had independent verification, then there's no epistemic relation established.
The agent is informed that if they have the skill then can show, but the agent is not required to take a stand on their skill.

Dynamics we expect are the dynamics of a conditional.
Note, however, that these require that the agent does not have independent support.
For, needs to be the case that the agent may become uncertain that the consequent holds.
This part comes due to the ability claim of the antecedent, primarily.
For failures to witness ability don't seem, in general, to be counterexamples to the relevant fact.

Independence, therefore possibly biscuit.
Examples of this.
Question is why expressed in conditional form.
Relation.
This isn't satisfactory, relate while explicit.

Key is failure.
Conveys that the informer doesn't offer anything if you don't have the ability.
Dynamics follow this.

\subsubsection{Technical}
\label{sec:technical}

To start, a broad sketch of the phenomena we are looking to provide instances of.

Goal is to provide instances where the agent recognises that some fact follows from an ability, and becomes confident by endorsing the ability.

Key here is that each of the possible truth conditions for a conditional are epistemically possible.
This, then, results in the relevant epistemic dependence.

Hence, assume that the informer has provided a conditional, and argue that no lines are closed.

So, possible that the agent has the ability and it is a fact --- given by novel information.
Possible that it is a fact and the agent doesn't have the ability --- given by the factual independence of the two.
Possible that the agent lacks the ability and it is not a fact --- given by possible intentions of the speaker.\nolinebreak
\footnote{
  Note the possibility of a preface type paradox here.
  The agent may not wish to endorse that they can show all of the things that follow from their ability.
  For, intersection of all of these may be too small.
}

The agent is not in a position to rule any of these out.

Assuming these possibilities are open, then we get the desired dependence.
Basically, the agent's confidence in their ability is going to influence their confidence in the fact.
In short, due to inclusion between two subsets in the space of epistemic possibilities.

The agent's lack of confidence in the fact is limited by their confidence in their ability.

Broad strokes, this deals with the two key points noted above.
On the one hand, the form of the conditional requires the agent to perform something like modus ponens.
On the other, the agent has no guarantee of the antecedent.

Conditional.
Claim rules out antecedent and not consequent.
No support for the fact keeps open possibility of the claim being made while both are false.
Fact relies on confidence of ability.

So, it's important that, for the agent, it's possible for both to be false.
They lack the ability and the fact is false.

On the other, the content of the conditional, specifically the ability claim requires the agent to endorse.
In general, the agent will have a clearer grasp on their ability than the informer.
This prevents the agent from verifying that a necessary condition obtains by noting the presence of what it is the necessary condition is for.

For, example, necessary for there to be a gas leak in order for the warning light to be on.
The light is on, hence a gas leak.
Clear that the light is on, while by contrast it may be the case that the agent lacks the ability, and hence the agent assumes.

\begin{note}[Informer's reasoning]
  The informer needs to be confident that \(A(\phi) \land \psi \rightarrow A(\psi)\).
  And, also \(A(\phi) \rightarrow \psi\).
  This then simplifies to \(A(\phi) \rightarrow A(\psi)\).
  And, note that this does not require the agent to have any unconditional/flat commitment to \(\psi\).

  Hence, the agent may consider this as the reasoning performed by the informer.
\end{note}

\hozlinedash

\begin{note}[Simple idea]
  The simple idea is that:
  \begin{itemize}
  \item If the informer provides support, then it will be possible for the agent to deny the ability claim while obtaining sufficient support to consider the proposition as a fact.
  \end{itemize}
  This doesn't hold for all cases, as the agent may not be able to deny the ability claim.
  However something like this is right.
  The two things are separable, and therefore:
  \begin{itemize}
  \item In all cases it will be possible for the agent to obtain sufficient support for the proposition independent of any particular stance on the ability claim.
  \end{itemize}
  This is basically a rephrasing of what it means for the informer to provide independent support for the fact.

  % The problem with the \(\Box_{i} B \phi \rightarrow E_{a}\phi\) is then that the agent needs to endorse the ability claim for this to work, and hence this reduces to a variant of the factive inference.
\end{note}

Task is to show that the informer does not provide independent support for the fact.

Primary motivation here comes from viewing claiming in this case as in instance of testimony.\nolinebreak
\footnote{
  Simple is non-reductionist, where the claim of the existence of a strategy supports.
  Reductionist is also possible.
  The use of `claim' is to ensure that the agent obtains support, hence ruling out --- for example --- assurance views of testimony where support for the fact remains with the informer.
  The difficulty here is that the (working hypothesis is that) factive inference provides support, and so views of testimony which do not satisfy~\ref{cond:claim-to-opt-supp} will not help.
  {
    \color{red}
    Maybe a discussion of an particular instance in a footnote here?
  }

  Variety of views satisfy \ref{cond:claim-to-opt-supp}.
  Straightforward to illustrate with the `Liberal Fundamentalist' view of testimony sketched by \citeauthor{Graham:2006vs}.
  On this view `it is a priori necessary that comprehending an attester's presentation as-true that P confers justfication on the recipient's belief that P' (\citeyear[94]{Graham:2006vs}).
  % If \ref{chess:claim:1:conj}, then it seems the informer presents as-true the existence of a strategy, and so confers justification on the agent's confidence (or belief) that a strategy exists.
  % This (broadly sketched) position, then, involves claiming providing support.

  A related view is that claiming makes available pre-existing support.
  For example, on the Belief Expression model of testimony of \textcite{Owens:2006tw}, an agent `taps into' the support that the informer has.
  \begin{quote}
    Trusting an expression of belief by accepting what a speaker says involves entering a state of mind which gets its rationality from the rationality of the belief expressed.
    This state’s rationality depends on the speaker’s justification for the belief he expresses, not on his justification for the action of expressing it.
    And to hear a speaker as making a sincere assertion, as expressing a belief, is ceteris paribus to feel able to tap into that justification (whether or not his assertion was directed at you) by accepting what he says.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[123]{Owens:2006tw})}
  \end{quote}
  For \citeauthor{Owens:2006tw}, \emph{expressing} a belief `differs both from indicating to others than you have it and from giving them an assurance that it is true' --- expression is characterised by the option for the audience to acquire a `belief with the same justificational status'.
  (\citeyear[106]{Owens:2006tw})

  \citeauthor{Owens:2006tw} is interesting as the agent isn't aware of the specific reasons.
  However, not quite the same.
  As the informer has support, the agent's reference goes through.
  So, this is a descriptive problem, in a sense.
  With ability, the agent hasn't yet done the reasoning, reference is counterfactual, in a way.
}
May also infer by the status of the informer, and so on.

So, though for present purposes `claiming' is an artificial construction, it seems plausible that an account of how the agent acquires support for the existence of strategy is available, if the informer claims that the agent is able to demonstrate a strategy exists.

However, the informer does not need to be committed.
Hence, the informer does not need let slip their beliefs even if they are committed.

Consider the following statement.\nolinebreak
\footnote{
  The main line of argument pursued attempts to show that it is possible (and plausible) for the informer to withhold providing support for the fact.
  However, there is an additional, though less forceful problem with the informer providing support for the fact.
  For, if the informer provides support for the fact then slight reformulations of the ability claim are made trivial.
  In the primary claim, demonstrating is a distinct kind of support, not grated by the informer.

  However, informer may make the a more general claim.

  This seems a little more natural to me.
  (Maybe some examples for normal literature.)

  Then , similar to \(\phi \land \lnot K \phi\), as one obtains knowledge of \(\phi\).
  Here, trivial that the agent is able to support the fact by citing the claim made by the informer.

  Two options are to restrict to specific kind of support in claim.
  Or, argue from pragmatics.

  Still, add in degree of confidence, and things get weird.
  For, it's not just the factive inference, but the idea that there's a link between confidence of ability and confidence of fact.
  Therefore, independent support limits degree of confidence in ability.

  This is interesting because if the claim is paralleled, then it seems trivial that the agent has support.
  However, the alternative is that the triviality suggests some alternative way.
}

\begin{itemize}
\item\label{i:claim:no-supp} No, I was careful to not provide you with support for the existence of a strategy for Black.
  The claim made was about the relationship between a handful of propositions.
  {
    \color{red}
    And something a little more.
  }
\end{itemize}

If~\ref{i:claim:no-supp} is successful, then the informer does not provide the agent with (the option of) support for the existence of a strategy --- this much is given by the first part of the informer's claim.
And, without (the option of) support the informer has not claimed the existence of a strategy.

The second part of the claim helps in providing success conditions.

{
  \color{red}
  Important here is that as the informer is only linking, they can be understood as speaking about confidence from the agent's point of view.
  And, this is not necessarily hostile.
  The informer doubts that the agent really have this ability, however, the informer doesn't take a stand on this.
  They simply note that this is how things would go.

  In this sense, fragile.
  For, if the agent were to press, the informer would refrain from stating that this holds for everyone.
  Of course, this is already true, as the two abilities are separable.
  However, refrain in that the informer won't want to even hint that the agent has the base ability.

  So, the agent asks `but do I have the ability?' and the informer smiles.
}

Important points here.

\begin{itemize}
\item It's the agent's ability --- no an arbitrary individual.
\item If there's a mismatch, it could be either the agent or the informer.
\item Ability does some important work here, because the informer isn't necessarily evaluating from their point of view.
  \begin{itemize}
  \item This is, in part, what distinguishes the case from ordinary conditionals.
  \item Ordinary conditionals have the same property, however, the relations are different.
    On the one hand, there's not typically a circularity problem.
    The antecedent is often enough to establish the consequent.
    On the other hand, there's common ground, of a sort.

    If the rules of chess permit \(X\), we can do \(Y\), and so \(Z\) holds.
  \end{itemize}
\end{itemize}

\begin{note}[Chess background]
  Look, I'm confident that knights move in a certain way.
  But I've seen you move them in what seems to me the `wrong' way.
\end{note}

\begin{note}[Then with the student]
  If you've confident that you're able to show that this rule is sound, then \dots

  The point here is that the student could take this either way.
  On the one hand, the rule is sound.
  On the other, it isn't.

  Perhaps the student needs to revise their understanding.
  Or, perhaps this is a hint that this particular rule is very important.

  So, in a sense, this really is a nice claim to make.
  It's a hint that can go either way.
  Ability is sort of important here, though perhaps not necessary.
  For, if stating the bare facts, then it's not clear that this provides any useful information to the student.
  Who knows about \(\psi\), etc.

  However, if you are confident, then I've given you information about where to look.


  So, if the student has a grasp, then they'd have the ability to find a counterexample.
  The thing here is that there's really no relation between the two.
  The point being I expect the student to quickly realise that there's no way that these two things are connected.
  So there's no way to obtain transitivity, and hence really should not be confident that they have a good grasp.
\end{note}

View from two perspectives
\begin{enumerate}
\item The informer intends to withhold (the option) of further support (regardless of agent's position).
\item The agent does not have the option of acquiring provided support (regardless of informer's intent).
\end{enumerate}

Breaking some Gricean maxims.
But not necessarily.


% \newpage

% \begin{tikzfadingfrompicture}[name=myfading]
%   % must be 2cm*2cm in size
%   \clip (0,0)rectangle(2,2);
%   \shade [left color=transparent!0,
%   right color=transparent!50,
%   fit fading=false,]
%   (0,0) rectangle (.25,2);
%   \shade [left color=transparent!50,
%   right color=transparent!75,
%   fit fading=false,]
%   (.25,0) rectangle (.5,2);
%   \shade [left color=transparent!75,
%   right color=transparent!100,
%   fit fading=false,]
%   (.5,0) rectangle (1.85,2);
%   \shade [left color=transparent!100,
%   right color=transparent!100,
%   fit fading=false,]
%   (1.85,0) rectangle (2,2);
% \end{tikzfadingfrompicture}

% The first figure is suggestive of the relation constraints.

% \begin{tikzpicture}
%   \draw[pattern=dots, pattern color=black!60!white, path fading=myfading, rounded corners] (0,.5) rectangle (1.5,2.75);
%   \draw[pattern=north east lines, pattern color=black!60!white, path fading=myfading, rounded corners] (.5,.25) rectangle (2.25,3);
%   \draw[pattern=north west lines, pattern color=black!60!white, path fading=myfading, rounded corners] (1,0) rectangle (3,3.25);
% \end{tikzpicture}

% The second figure demonstrate failure of transitivity.

% \begin{tikzpicture}
%   \draw[pattern=dots, pattern color=black!60!white, rounded corners] (0,.5) rectangle (1.5,2.75);
%   \draw[pattern=north east lines, pattern color=black!60!white, rounded corners] (.5,.25) rectangle (2.25,3);
%   \draw[pattern=north west lines, pattern color=black!60!white, rounded corners] (1,0) rectangle (3,3.25);
% \end{tikzpicture}

% The third figure demonstrates the important of the agent's confidence in their ability.

% \begin{tikzpicture}
%   \draw[pattern=dots, pattern color=black!60!white, rounded corners] (0,.5) rectangle (2.75,2.75);
%   \draw[pattern=north east lines, pattern color=black!60!white, rounded corners] (.5,.25) rectangle (2.875,3);
%   \draw[pattern=north west lines, pattern color=black!60!white, rounded corners] (1,0) rectangle (3,3.25);
% \end{tikzpicture}

\newpage


Heck, this is almost \emph{exactly} what I want out of the student case.
I link together these, so the student gets confident in the basics, and then goes on to tackle.

The really devious case is where the second link breaks down with sufficient mastery of the basics.
Though this seems odd.

So, the goal is to establish ??? by outlining the construction of scenarios in which the informer \emph{only} communicates to the agent their ability to \(\phi\).
(In turn, scenarios in which \ref{i:claim:no-supp} would be a successful response to presumed support for \(\phi\) from the informer.)
Hence, the informer will not give enough information for the agent to have the option of obtaining support for the fact.

\citeauthor{Grice:1989uf}\footnote{
One of the Gricean Maxims of Quantity.
Do not make your contribution more informative than is required.

As the ability claim is something communicated, it may be the case that one do not have the option of communicating such restricted claim.

The other maxim of quantity.

Make your contribution as informative as is required.
}

Hence, the goal shift the burden, and show that the informer must be communicating more than they intend to if they are interpreted to have claimed the existence of a strategy.
Failed intentions happen all the time --- detective cases etc.
Still, possibility claim.
Push the restricted claim as strongly as possible through background considerations.

{
  \color{red}
  On the one hand, the informer may not have the option of sharing the support they have.
  Therefore, it seems the agent does not have the option of obtaining support if the agent were to seek some kind of transmission.
  And, one the other hand, the informer may not intend to provide the agent with support, and so avoids communicating any information that would provide support for the fact independently of what (necessarily) follows from making the ability claim.
}

\hozlinedash

\begin{note}[The things of interest]
  There are a few different propositions to distinguish between.
  \begin{itemize}
  \item That the fact is true.
  \item That the fact is true and the agent has the ability.
  \item That the agent has the ability \emph{given} the fact is true.
  \end{itemize}
  The thing to observe here is that the agent should be as confident that they have the ability \emph{given} the fact is true to the same degree that they are confident that the fact is true.
  If this is the case, then the agent is going to be slight more confident that the fact is true than they are confident that they have the ability and the fact is true.
  That is, unless they are certain that they have the ability.

  So, then, the dynamic is sort of unique in this sense.
  The point is that the agent may reflect on the basic nature of things and come to the conclusion that it's a little more likely that the fact is true than their ability to demonstrate given that the fact is true.
  So, that the agent is more confident that the fact is true is no argument \emph{against} the position that I am arguing for.

  Hence, one doesn't need independent support in order for the agent to lose confidence in truth `quicker' than ability in absolute terms.
  However, it doesn't follow that this works in relative terms.

  The key question is whether the ratio fails.
  Or, whether a loss of confidence in the conditional leads to loss of confidence in truth.

  Though, nothing is quite so straightforward.
  As there will be further considerations about how the ratio works.
  Hence, a strict equality is something of a simplification, the question is whether there is something of a function governing the ratio.

  Simple idea, really, is that drop in confidence leads to a drop in truth.
  And, one might think this is so.
  For, it doesn't seem as though there is sufficient information to separate.
  Very simple idea is that I can't, without something special happening, determine whether I'm showing that my ability is false, or whether the fact is false.

  The claim made by the informer doesn't seem to offer any sort of input here.

  The key objection is that \emph{somehow} the rolls point against both.
  So then, in a sense, the agent does have support for the fact.
  However,

  Hold up.
  There is an intuitive idea that the rolls point against the fact or the ability.
  Yet I have no idea how to make sense of this.
  For, from the agent's perspective this seems indeterminate.
  The agent needs some way of separating the two.
  This is exactly what happens in the homework cases --- the ability drops.

  You might think that, here, the same happens, but one gets to a stage where the failure to exercise the ability ends up dropping the confidence of truth.
  That's the real puzzle.
  If there is independent support, then it's hard to see why this should be the case.

  One possible explanation is that the agent gets into a position where the lose faith in the informer.
  So, the support for both claims ends up being hollowed out.

  \begin{itemize}
  \item In general, the inability to distinguish between two hypothesis given some evidence does not show that the two hypothesis share the same support.
    \begin{itemize}
    \item This is shown with a courtyard case, where to independent pieces of evidence, one with agent being in the courtyard, the other with bgent being in the courtyard.
      Information that only one person is in the courtyard.
      So, seems balanced between agent and bgent being in the courtyard.
      I can split the difference, but this doesn't show that I am unable to separate the two pieces of evidence.
    \end{itemize}
  \end{itemize}

  So, in the ability claim case, it could be that the agent has two independent pieces of support, and the failed rolls are inconclusive.
  Hence, until the agent doubts both, there's no reason not to grant the agent independent support for the fact.

  However, there still seems to be something of a dis-analogy.
  In the courtyard case, there's some confirmation.
  So, information is that one (or more) of the agents is lying.
  Then, no confirmation.
  Same upshot.

  Still, something seems different.
  For, there's some relation between the two propositions in the ability case.
  Know for sure that the ability claim is weaker.
  This demonstrated by the homework example.
  It's clear that in this case there is independent support, and therefore the agent only doubts their ability.

  And, the problem is that this does not seem to be the case when rolling the die.
  Here, it is possible that the agent is granted to sources of support.
  Yet, the agent, from their point of view, has no hope of distinguishing between the two.
  Which, should be enough, no?
  Yet the courtyard case is a puzzle, as it's clear the agent has independent sources of support without the option of leveraging.

  At the least, this is inconclusive.
  Both options work.

  Why not default to the weaker proposition, though?
  In part, because it's not clear that it \emph{is} a weaker proposition.
  The conditional may be just as a strong as the fact.

  Okay, main difference is that with the ability claim, in contrast to the courtyard case, I have a conditional.
  Here, I'm not sure whether this makes a significant difference, though.

  The contrast to the homework case is the most striking.

  The main contrast to the courtyard case is that there is a single source in the ability case.
  So I want to say something like, if a single source is providing two independent pieces of support, then the receiver should be able to distinguish between these.
  Otherwise, the source is providing (at best) interwoven support, and this fails to be independent in the appropriate sense.

  This is somewhat intuitive.
  Single source saying \(A \land B\) is different from independent source saying \(A\) and another \(B\).
  Single source may also mark \(A\) and \(B\) versus \(A \land B\).
  This is clear with doubt.
  But also with belief, as you can't infer whether \(A\) or \(B\) is significantly dragging down the conjunction.

  Hum, there's something interesting with the observation that the agent can be confident that the informer has made a correct ability claim, but doesn't come to view the fact as true.
  This, however, blocks the factive inference.

  Heck, this is a really important observation.
  It's clear that an ability claim \emph{in general} does not provide independent support.
  For, the agent can form a conditional and remain suspicious about whether they actually have the ability.
  Which is almost the exact position that I want.
  The puzzle really is in these cases, where the agent could be suspicious, but ends up endorsing the ability.
\end{note}


\hozlinedash


\begin{note}[Moving to the logic student]
  Here, slightly different.
  If able to \(\phi\) then able to \(\psi\).
  Mistake to infer \(\phi \rightarrow \psi\).
  I'm so confident that you lack the ability to show that \(\psi\), I've chosen an arbitrary \(\psi\) that is suitably out of reach.

  Conditional, but this doesn't really change anything in terms of the factive inference problem.
  Can reformulate the chess example in a similar way.
  If able to reason from chess then able to find strategy.
\end{note}

The particular support the informer has isn't support for the agent.
However, there is a clear route for the agent obtaining support.
So, here the agent it seems --- in contrast to pure reasoning cases --- does not have propositional support for the fact.

However, given the primary interest is with cases in which it seems plausible to think the agent does have propositional support, this point isn't so important.

Have a fairly clear way to interpret \ref{i:claim:no-supp}.
I did not pass on the background context.
As observers, we can see what the background context is.
However, the agent is in the dark.

This distinguishes the case from other potential failures of transmission, in which the relevant support is made available.
Either through the speaker providing the support --- though not necessarily endorsing it --- or from the context constraining.
Doctors and teachers are institutions positions.
There are some gaps here, but the differences are substantial.

There's no independent path, and no (explicit) statement of fact.

Ability to flip coins isn't quite right.
So there are two possible explanations for a distribution.
Either the coin is biased, and I flip like a normal person.
Or, the coin is fair and I flip in a strange way.
Deny the ability statement, so really I have no idea.
You're going to have to do some additional work in order to get me to hold an opinion about the bias of this coin.

{
  \color{red}
  This relates to the choice objection later.
  And, distinguishes the case from the pure reasoning cases.
  For, in the pure reasoning cases there is no real option if the agent has the ability.
}



Putting this together, form an argument for the restricted form of information.
As there is a difference, the informer \emph{only} claims the ability, and hence does not (in addition) provide support for the fact --- this is kept for the informer alone --- but this is permissible because the agent's ability ensures that it is possible for the agent to independently obtain support for the fact.

(If this works, the same can be said for the chess example, as I did not consider \emph{every} possible move for white, but you may feel the need to given your understanding of chess.
And, same for logic student, it's a different proof system, but the instructor has done soundness and completeness, so has support that the fact can be derived, and is confident that the student has a good grasp of the rules --- yes, some proofs turn out to be quite tricky, but requiring anything more than a high degree of confidence seems excessive.
Or, less charitably I jump and skip in ways that wouldn't work for the student.
I.e.\ back to `pure' reasoning.)

Before turning to whether this is possible, let us not that it is desirable.
Students in class, giving a hint.
I give the student some information, but refrain from providing any support.

\begin{note}[Student]
  The main problem with the no presupposition idea is that this does not seem to be the case in general.
  This is the case with the student.
  Here, I am doing my best to avoid providing the student with any justification \emph{other} than what they would obtain by witnessing some reasoning that they are able to perform.
  In doing so, I tie the agent's ability to perform the factive inference to their confidence that they have the ability.
  Hence, obtain the next statement emphasised as a description of these cases.
\end{note}

The goal of the interaction is clear.
I wish to provide the student with information that \(\phi\) follows from \(\Sigma\) without providing the agent with any independent support for this.

Intuitively, only the proof supports, but then someone like \citeauthor{Owens:2006tw} will suggest that I provide the students with access to my support, and the external pressures of not only believing but also providing a proof do the work.\nolinebreak
\footnote{
  And, if I were to give a conditional, then the factive inference is blocked.
}

So there are two parts here.
On the one hand, the informer does not have the option of sharing the support they have.
Therefore, it seems the agent does not have the option of obtaining support if the agent were to seek some kind of transmission.
And, one the other hand, the informer does not intend to provide the agent with support, and so avoids communicating any information that would provide support for the fact independently of what (necessarily) follows from making the ability claim.

There's is no knock down argument against expanding the basic position of \citeauthor{Owens:2006tw} here.\nolinebreak
\footnote{
But there's something of a problem.
The support I have for holding that this coin is `weakly' conflict with the support I have for my confidence that these other coins are fair/unfair.
However, this doesn't seem too compelling as it also seems to hold for memory, where the support drawn on for a memory may also weakly conflict with other propositions that the agent holds to be true.
}
The agent still `taps into' the support that the informer has, against the informer's intent.
However, in the logic case, for example, it's hard to draw a distinction between tapping into the support the instructor has, and tapping into the axiomatic system itself.

Distinction between propositional and doxastic justification, it's unclear.
It seems, at least, the given the ability claim the agent has something more than propositional justification, even if the agent simultaneously lacks full blown doxastic justification.\nolinebreak
\footnote{
  \textcite{Wright:2016wl} has a nice note about the usefulness of making the distinction between prop.\ and dox.\ just.\
  \begin{quote}
    The idea is that the speaker believing that \(\phi\) is a necessary condition of the speaker having a justified belief that \(\phi\), but it isn't a necessary condition of a speaker merely having justification for \(\phi\).
    And since justification transmission, \dots merely appeals to a speaker having justification for what she says, the speaker can have justification in the relevant sense by having a merely propositional justification for what she says.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[10]{Wright:2016wl})}
  \end{quote}
}


\begin{note}[Final intuition]
  The tracking example.
  Look, these are\dots but you have to take my word for it.
  Versus, these are\dots but you have to figure it out by yourself --- literary examples of this.
\end{note}

\newpage

\subsubsection{The conditional is non-transmissive}
\label{sec:argum-non-transm}

\begin{note}[Overview]
  Have shown that the fact depends on the conditional.
  Now to argue in a little detail for the claim that the argument is non-transmissive.
\end{note}

The intuition is straightforward.
As the agent has not demonstrated the ability, they do not have support for the fact.

In endorsing the conditional, the agent presupposes that there is a strategy.

Sort of get the intuition a little cleaner in the twins case.
If it's Sam, then you'll be able to check.
Still bad.

Or,

If you have the general ability to distinguish between Leon and Noel, then you'll be able to decide who won the arm wrestle.

Fairly reasonable, but the issue is that you must be confident that you have a piece of information that you've overlooked.
If you don't assume this, then you have no reason to think the general ability extends to this case.

This is basically the same issue as noted in the original twin case, as expected.
{
  \color{red}
  Difference is that this hasn't been Incorporated yet.
  Confidence is high, but the agent isn't required to know.
}

\subsubsection{Path 2}
\label{sec:path-2}

\begin{note}[Logic example]
  The logic example would be nice here.
  For, it's clear that the instructor has some uncertainty about the student's grasp of the rules.
  And, neither wants to provide too much of a hint.
  So there's a back and forth about figuring out what the student is able to do.
  And the student may well reject the claim of the instructor --- \emph{for sure!}.
\end{note}

\begin{note}[\citeauthor{Emms:2000aa}'s problem]
  The same kind of thing works with \cite{Emms:2000aa}'s original problem, where it's really not clear that I have the ability.
  However, this is also going to be mentioned earlier in setting up the ability claim.
\end{note}

\begin{note}[Path 2 overview]
  General structure:
  \begin{enumerate}
  \item Informer is confident that agent has the ability.
  \item Some of the information is about what the agent is able to do.
  \item The informer's confidence is tied to the/contingent on information available to the informer.
  \item The informer does not, in general, have a superior position.
    \begin{itemize}
    \item If the agent were to signal otherwise, then barring confusions, the informer would revise their assessment.
    \item Chess is an example --- agent isn't aware that they know \emph{all} of the rules --- is there something similar to \emph{en passant} for knights?
    \end{itemize}
  \item It is therefore up to the agent to endorse the informant's position in some cases.
  \end{enumerate}
\end{note}

\begin{note}[Notes on path 2]
  This is a subjective evaluation.
  Given the information the informer has, the have this degree of confidence.

  So, as the agent and the informer may have difference information, the agent needs to also endorse.

  For example, you may know that you do not understand how knights move.
  The informer seems fine with the confidence that they have --- they've seen you work through a number of puzzles and the absence of any knight move was not particularly noticeable, but this has been weighing on your mind.

  Hence, something along these lines shows the need for additional endorsement on the part of the agent.

  However, with the requirement of some endorsement in hand, the agent can not support \(\phi\) being the case.
  This holds even for \emph{confidence} that \(\phi\) is the case, as the relation of support is constrained.

  So, this pushes for either licensing or no inference.
  An additional point to make here is that this is not the \emph{only} motivation for licensing.
  For, there is also the difference between preservation of a designated value and construction of a witness.
  So, this forms a pair of a necessary and a sufficient observation.

  So, either the agent does not have support, or the support is licensed.

  There's no straightforward argument that the agent has (licensed) support.
  Idealised agents aren't to useful here, as we may assume that the ability will be witnessed.
  For agents like us, however, it seems we can use ability in reasoning.
  Though it is risky.
\end{note}

\begin{note}[Does not hold for all cases of ability]
  This may not be true in all cases of ability.
  For example, coach telling an athlete that they are able to perform a particular routine.
  Here, the coach may be an authority.

  Same may be true in some cases of reasoning, though this is trickier, due to lack of certainty.
  Rule following, etc.
  But then it seems that perhaps both the agent and the informer would be unsure, and it would remain the case that the informer could still be in a position of authority.
  Hence, narrower claim.

  This is about comparative positions, then.
\end{note}

\newpage



\section{Licensing}
\label{sec:licensing}

\begin{note}[Guarantee]
  Note, this is compatible with the informer `being on the hook' for support.
I am inclined to think the agent is `on the hook', and so the agent may avoid endorsing the ability claim and request the informer provide support.
Maybe this would in turn provide the agent with support\nolinebreak
\footnote{
  Though not clear why this would be the case in general.

  May think that exercises without solutions are an example.
  Not quite.
  Details are in the following section.

  Perhaps the agent is piecing together different pieces of information.
  A has solved, B is at least as capable as A, hence B has ability, etc.
}
but even if this is granted, the agent may not wish to make the request of the informer.
The chess problem is simple, and on a good day there is some enjoyment to be had from this.

In turn, the informer may end up doing some work, if they aren't in a position to share the support they have.
Taking from the examples, the informer ends up flipping the coin with the agent, or working through the proof.
\end{note}

\begin{note}[Async]
  This is sort of the main idea here.
  The primary use is that there's the option for the agent to act on their confidence prior to witnessing the reasons.
  The agent then cites those reasons, but fills in the details at some later date.
\end{note}

\begin{note}[Required conditions]
  Need:
  \begin{enumerate}
  \item Information that some conclusion follows from some reasoning.
  \item Confidence that the agent is able to perform the reasoning.
  \end{enumerate}
  If both these conditions obtain, then the agent may be confident that they are able to generate an {\color{red} relevant kind of} explanation.
\end{note}

If you were to do the reasoning you are able to do, you would demonstrate a witnessing strategy for Black on the basis of the rules of chess and the game state.

\begin{itemize}
\item Note also that the ability claim would not be required here.
\item Here, witnessing what substantiates the ability claim.
\item So, would not have the problem noted above.
\end{itemize}

In this way, claim~\ref{chess:claim:1} may be understood as guaranteeing a relation between your ability to reason from the rules of chess and the game state to the demonstration of a strategy for Black.

\emph{License} to appeal to what ability would witness.
Factive inference is not supported by ability.
Instead, supported by the reasoning the agent is able to do.

Agent is in the dark about what this support is.

Need to be clear that the agent is not providing support for the conclusion.
This is where we obtain the denial of the main conditional.

As the agent does not claim to possess support for the conclusion, then the problem of circularity is avoided.
Yet, from this it does not follow that the agent does not claim the conclusion is supported.

Information about what the agent is able to do permits an agent to infer contingent on the agent witnessing the ability.

Put in terms of reasons.
The reasoning that the agent is able to do constitutes a reason for holding that a strategy for Black exists.
As the agent has not witnessed their ability.
Potential explanation.

One way to capture this is by rewriting.
For example:

\begin{enumerate}
\item\label{potential:claim} I am able to reason from the rules of chess and the game state to the proposition that White cannot prevent Black from occupying c4 on their second move.
\item\label{potential:necessity} The reasoning I am able to perform provides support for the proposition that White cannot prevent Black from occupying c4 on their second move.
\item\label{potential:focus} White cannot prevent Black from occupying c4 on their second move (is supported by reasoning I am able to perform).
\end{enumerate}

There's not really new information here.
The second step rewrites the first, and the conclusion rewrites the second step to focus on the relevant proposition.

If so, the factive inference is misleading.
Do not obtain the fact, but bring the fact into focus.

This is not completely satisfactory.

The interest of a factive inference is the possibility of independently reasoning with the fact.

Rearranging, or placing the agent's ability to establish the fact in parenthesis does not change the structure of the proposition.

Consider the following sketch:

\begin{enumerate}
\item Black's king is on c7.
\item Black cannot occupy c4 on their first move.
\item If White can place Black in check on their move, then Black would need to defend their king on their second move.
\item Moving a piece to c4 would not protect the king.
\item\label{sketch:MTCond} If White can place Black in check on their move, White can prevent Black from occupying c4 on their second move
\item\label{sketch:factive:premise} White cannot prevent Black from occupying c4 on their second move.
\item\label{sketch:conclusion} White cannot place Black in check on their move.
\end{enumerate}

It is not possible to replace step~\ref{sketch:factive:premise} with \ref{potential:focus} while maintaining valid reasoning.

For, the agent needs the fact that White cannot prevent Black from occupying c4 on their second move in order to perform \emph{modus tollens} on step~\ref{sketch:MTCond}.
That \emph{White cannot prevent Black from occupying c4 on their second move (is supported by reasoning I am able to perform)} only contradicts the consequent of step~\ref{sketch:MTCond} given the factive inference.



So, treat this as a propositional attitude on par with belief, desire, intention, etc.



The reasoning is then appropriate from the perspective of the agent.
From the perspective of us as theorists, we have a collection of propositions believed with a proposition licensed.


To say a little more here.
The ability statement is already a modal statement.
The distinctive claim is that this in some cases this takes the form of an attitude, and in turn the functional profile of the attitude determines how the proposition interacts with other propositions the agent has attitudes toward.


Agent holds the proposition true, but without claiming the possession of support for the relevant proposition.
It is bundled with a license.
This is the distinctive trait.

\begin{note}[License + Reasoning]
  Also note here about an indirectly licensed conclusion.
  However, part of the value here is that if the agent provides support for the licensed premise, then the agent obtains support for the indirectly licensed conclusion.

  This is a nice parallel to promises and futures.
\end{note}

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[->,>=stealth',node distance=0cm, every text node part/.style={align=center}]

  \node (1) [] {Information about \\ result of ability};
  \node (2) [right of=1, xshift=4cm, yshift=.5cm] {Ability};
  \node (3) [above of=2, yshift=1cm, xshift=2cm] {Premises};
  \node (4) [below of=2, yshift=-1cm, xshift=2cm] {Conclusion};

  \draw [dashed, ->] (1) to [bend right=10] (4);
  \draw [dashed, ->] (1) to [bend left=10] (2);
  \draw [->] (3) to node[left] (mid) {} (4);
  \draw [dotted, ->] (2) to (mid);
\end{tikzpicture}
\caption{Sketch of support.
  Continuous arrow is direct.
  Dashed is indirect from information.
  Dotted is indirect from agent.}
\label{fig:dynamics}
\end{figure}


\begin{note}[Variation on a familiar problem]
  This is a twist on a familiar problem.
  Lots of ways to explain why an agent performed an action.
  Here, the agent is picking one of those ways.

  Problem is to identify the actual from the potential reasons.
  Here, our agent has a guarantee of potential reasons, and acts on the basis of those.
  If the agent could, then the agent is.

  With sufficient information about potential reasons, may an agent from appealing to those reasons when performing an action?

  justification footnote\nolinebreak
  \footnote{
    A different way to motivate the idea is through propositional and doxastic justification.
    As, the agent has a guarantee both that they are propositionally justified, and that they have the ability to be doxastically justified.
  }
\end{note}

Still, even though you would be able to demonstrate claim~\ref{chess:claim:2} without my testimony, my claim remains important in order for you to be confident that you have the ability --- even if you are confident that you understand the rules of chess and the game board, you would not be able to establish that White cannot prevent Black from occupying c4 on their second move without demonstrating a strategy for Black.
Claim~\ref{chess:claim:1} \emph{licenses} you to hold that claim~\ref{chess:claim:2} is true on grounds that are independent of my testimony.

Colloquially, you may cite the reasoning that you are able to do (or the strategy that would result from the reasoning) as support for holding that claim~\ref{chess:claim:2} is true.
And my testimony that claim~\ref{chess:claim:1} is true is then cited in support of your ability to do the reasoning.\nolinebreak
\footnote{
  Similar phenomena with `do you also hold \(\phi\) to be true?'
  Well, you hold \(\phi\) to be true, etc.
  So on the basis of you asking this, I may hold \(\phi\) to be true.

  Or, may reason to \(\phi\).
  So, alternative paths is not unique to ability attributions, though this differs in an important way, as you do not gain from this confidence that you can demonstrate that \(\phi\) is the case independently of the interaction.
}

{
  \color{red}
  facts we take into consideration in reasoning are reasons \\
  reasons as items in pieces of reasoning, where reasoning is thought (or possible thought) directed toward some conclusion (\citeyear[421]{Hieronymi:2011aa})
}
Reasons that reasoning took into account, then a distinction between the reasons which led to the conclusion and the reasons that the agent takes to support the conclusion.


Re-express the problem, the reasons why the agent holds that the Black has a strategy are those reasons that I (the agent) have the ability to reason with.

This cuts across both `normative' and `explanatory' uses of `reason'.
Why did the agent, in fact, act?
If the agent is appealing to those witnessing reasons, then they are part of the explanation.
If the agent is appealing to those witnessing reasons, then these affect whether the outcome was appropriate.

\hozlinedash



\section{Counterpart argument}
\label{sec:counterpart-argument}

The argument above is narrow.
Focused on the issue of whether or not the agent has support for a particular proposition.

Constrained so that the agent needed to endorse ability.
Hence could not obtain support.
These are the considerations I am inclined towards.
Support is important, but it does not necessarily need to be realised.

However, defensive.
May be that any realised support would do better.
The counterpart to the defensive argument is assuming that licensing is okay and suggesting when it may be preferred to realised support.

Scenarios, and then a big picture argument, where the big picture is different kinds of support.

\subsection{Failure Scenarios}
\label{sec:failure-scenarios}

\begin{note}[Failure scenario]
  Return to the logic classroom.

  \begin{itemize}
  \item If you are able to show \(\phi\), then by similar reasoning you are able to show \(\psi\).
  \item \(\phi \coloneq \exists x(Px \land Qx) \vdash \exists x(Px \lor Qx)\).
  \item \(\psi \coloneq \exists x (Px \land \exists x Qx) \vdash \exists x(Px \lor Qx)\).
  \item Student has some support for this --- whether the conditional holds isn't so important, so long as the agent is confident it does.
  \item The problem for the student is how the rules for instantiation work.
  \item Student isn't able to explain why the same instantiation on the two separate existential statements in \(\psi\) is bad.
  \item Tricky issue of whether the student really gets the antecedent of the conditional.
  \item Problem is that the result of luck doesn't seem to result in an ability.
  \item Still, sufficient grasp of working with single existential statements where no constants are involved.
  \item So I think it is fair to assume this --- if not, then things get difficult for most proofs --- not looking for mastery.
  \end{itemize}

  Student shows \(\phi\).
  Confident that the consequent holds.
  Hence, writes down \dots

  The student is correct, but the reasoning is not \emph{identical} --- different values for the distinct quantifiers.
  Instantiate, take the antecedent conjunction, and then introduce latter disjunct.
  Slight variation, and the student doesn't have the ability to show.

  This is suggested in a later proof, where the agent fails to appropriately use the rule.\nolinebreak
  \footnote{
    \begin{itemize}
    \item For example, \(Qa \rightarrow Ra, Pa, \exists x Qx, \forall x \lnot \exists y (x \ne y)\).
    \item Straight \(Qa\) for existential, with assumption of redundant premises.
    \end{itemize}
  }
  Let us stipulate that the student would obtain \(Pa \land \exists x Qa\).
  Rules governing quantifiers --- and quantifier scope --- are nuanced.

  Conditional doesn't hold because abilities are sufficiently distinct.
  Or, antecedent doesn't hold because success doesn't entail ability --- in contrast to exercising an ability, the student lucked the proof.

  Still, what the agent claimed is true, at least on a passable reading of `similar reasoning'.
  Instantiate the first existential, conjunction elimination, disjunction introduction, and existential generalisation.

  Student was unlucky, misled.
  Still, conditional/antecedent does not yield the conclusion without a factive inference from the agent's ability to show \(\psi\) by similar reasoning to the claim that \(\phi\) follows by similar reasoning.
  Misguiding confidence, but misguided confidence doesn't provide a complete picture.
  For example, thought it was going to be sunny today, but need to add that I left my umbrella behind to see how I was misguided.
  With the student, I claim, led the student to license reasons that they were not able to witness.\nolinebreak
  \footnote{
    May argue that the agent ought to have made the proof.
    Some fault for allowing student to make claims.
    Well, maybe.
    However, it seems as though ability statements can be used, and still have the problem of why the agent answered the problem in the way they did.
    And, agent was fine to be confident, hard to argue with this.
    If stakes are important, lower these as satisfactory.
    E.g.\ bonus problem, good grades, unneeded class, other things are more important, etc.
  }
  \hozlinedash

  The agent doesn't have the ability.
  The agent took the risk, and it didn't work out for them.
  The agent is not able to provide an explanation for the claim made.
\end{note}

\begin{note}[Factive reasons]
  This is somewhat similar to cases which suggest that reasons cannot be facts.
  Parallel in the sense that the agent needs to have the ability.
  Difference is the appearance/non-appearance of a reason.
  Similarity in the failure of an ability.
  However, if the similarity is pursued then difference is whether the agent possesses some input.
  Still, for now focusing on reasoning which involves explicit mention of ability.
\end{note}


\subsection{Three Positive Cases}
\label{sec:positive-cases}

\begin{note}[Cases]
  Here, deal with a number of cases.
  \begin{enumerate}
  \item Shopping \(\leadsto\) positing a simple relation between agents desire and action, tighten account of supporting reasoning.
  \item Detective \(\leadsto\) option of providing the support asynchronously.
  \item Temptation \(\leadsto\) agent's ranking of reasoning.
  \end{enumerate}
\end{note}


\subsubsection{Detective}
\label{sec:detective}

\begin{note}[Practical matters]
  I should include a note that the factive inference goes through, but it's up to the agent to figure out how to make use of this.
  Here, the potential may be insufficient.

  Similar, in some ways, to have evidence that would not be recognised by the court do to some administrative error (though this is not to say that not reasoning is the same as an administrative error).
\end{note}

\begin{note}[Async]
  Somewhere in here mention the idea of asynchronous reasoning.
  The reasoning doesn't (or reasons don't) necessarily stay potential.

  This ties to bounded agency, and part of the `why' question.
\end{note}

\begin{scenario}
  Case file contains evidence, but also notes made by Lewis.
  It is a mix, then, of the evidence that Lewis has gathered and inferences that Lewis has drawn.

  Morse looks through the case file.
  Does some reasoning.
  Makes use of the notes made by Lewis, so forms a conditional:

  \begin{itemize}
  \item If the case file is sound, then you are able to establish cause for bringing Woodthrope in for questioning.
  \end{itemize}

\end{scenario}

Morse provides information about an ability that Lewis has.


Note, this is not the same kind of conditional as in path 1.
For, the consequent of the conditional does not draw directly from an ability mentioned in the antecedent of the conditional.

Some remark on Lewis' ability is implicit, as notes are contained.
However, it does not follow that the reasoning demonstrated in these notes in the basis of Morse's claim.

The conditional could be false due to the ability claim.
The case file is sound, it does establish cause for bringing Woodthrope in for questioning, but Lewis does not have the ability to establish cause for bringing Woodthrope in for questioning.

Interest is in after the consequent is detached.
Lewis is confident that the are able to establish cause for bringing Woodthrope in for questioning.
Path 2, but the scope is a little different.
The reasoning made by Lewis is analogous.

The structure of the conditional is difficult for the two alternatives.
Morse has the ability, but Morse has not reasoned to the fact.
Similar considerations suggest that transforming Morse's claim into an assertion

Lewis endorses Morse's evaluation of Lewis' ability.
Additional practical consideration --- Lewis needs to be confident that they are able to establish cause.



Reasoning is a little more complex.
Morse has provided a conditional --- Morse has not checked the inferences made by Lewis.
Lewis is in a position to endorse the case file --- evidence and inference alike, and then perform the factive inference.


Morse has done more reasoning, Lewis has done less.
More could be more helpful, and Lewis could be less reliant.



\subsubsection{Shopping}
\label{sec:shopping}

\begin{note}[Also include\dots]
  A note on having a stack of papers that one starts reading through.
\end{note}

\begin{note}[Difference between chess and shopping]
   The issue is that the agent hasn't worked through the reasoning --- \emph{not} that the agent is unaware of the reasoning required.
  This is an important distinction between the chess scenario and the shopping scenario.
\end{note}

\begin{note}[Main point]
  The key with this scenario is the simplicity of the explanation.
  If agent is in the clear, then this is because they have the supporting desire.
  If the agent is in a bind, then this is because they do not have the supporting desire.
  So, we don't need to fluctuate desires.

  Also something to the idea of an explanation.
\end{note}

The existence of chess strategies is, at least for most, uncommon and with little practical consequence.
Confidence of the ability, so can go to sleep, or as a way to provide assistance without providing novel information.
Also, two agents involved.

First scenario is common, practical consequence, and single agent.


\begin{scenario}[Shopping]

  Background:

  Friend recommends trying carambola.
  Agent forms a desire.
  Does some research.
  Carambola and star fruit are the same thing.
  Hence, desire for star fruit.
  Purchasing as a means to this end.
  Writes a note on the shopping list.

  Out shopping.
  Sees star fruit.
  Does recall carambola.
  Does not recall that carambola and star fruit are the same thing.
  Confident that they are able to reason from a desire that they have to purchasing star fruit.
\end{scenario}

\begin{note}[Required conditions]
  Here, the shopping list provides the first required condition, and some nebulous considerations support confidence that the agent has the ability to do the reasoning again.
\end{note}


\subsubsection{Weakness of will}
\label{sec:weakness-will}

\begin{note}[Idea]
  This combines idea from the previous two.
  From shopping, the idea of preferable explanations, but now from the viewpoint of the agent.
  From detective, the idea of providing the appropriate reasoning at an other point of time, here from the past --- or potentially the future/counterfactual perhaps.
\end{note}

\begin{note}[Counterfactual]
Also could be framed as counterfactual ability.
Cases of rational impairment and so on.

In a sense, the issue here is the strength of the conclusion.
It seems the conclusions obtained while sober often extend and hold when intoxicated.

However, by contrast, conclusions obtained with full information may not.
E.g.\ \cite{Smith:2004aa} or the miners paradox.
\end{note}

\section{Resistance}
\label{sec:resistance}


\subsection{Voluntarism and Hobson's Choice}
\label{sec:non-voluntarism}

\begin{note}[Grr]
  I think this belongs in the objection section, which might also help with structure.
  For, the worry here is that licensing reasoning is a form of voluntarism.
  One the one hand, I do not claim that the result of licensing is belief.
  Still, it seems to me this is relatively open --- functionally similar.

  Idea would be that reconstruct \citeauthor{Weatherson:2008uq}, hence obtain that licensing is voluntary, and therefore there is a problem with applying the factive inference?
  For, this involves a choice made by the agent, and that goes on to block any factive inference where the proposition is suitably independent.

  This is also somewhat suggested by the \citeauthor{Davidson:2001aa} motivation, where in a way there's a suggestion of the agent picking the reasons to believe something ---- however this in part focuses on the why and not the which.

  This is not to say that it is not possible for the agent to make the factive inference, but that it is not sound to do so.
  Right, kind of get the intuition that the agent would withdraw the factive inference if they were to reconsider the possibility that the carton in the fridge is empty.

  Then, the response is that it is a mistake to think that exercising the capacity is important in these cases.
  For, to the agent there is no issue of self control.
  For, in these cases the agent is confident that things would not go otherwise.
\end{note}

\begin{note}[Broad outline]
  The debate around voluntarism is difficult.
  What belief is, what voluntarism requires, whether cases can be excluded, etc.\
  Hence, unclear on what one obtains by voluntarism.
  Whether one has control over doxastic states.
  Whether there are deontic parallels between beliefs and actions.
  Understanding of justification.

  I am not inclined to take an absolute position, but I think that ability limits any voluntarist position in which failure to exercise a capacity to reason amounts to a voluntary act.

  Here, \citeauthor{Weatherson:2008uq}.

  \begin{quote}
    These conclusions that we leap to are voluntary beliefs; we could have avoided forming them.
    And not only could we have avoided these formations, but we would have if we had followed the methods for belief formation that we approve of.
    That seems enough, to me, to say the formation is voluntary.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[10]{Weatherson:2008uq})}
  \end{quote}

  Checking the fridge, keeping counterexamples in mind, and so on.
  \citeauthor{Weatherson:2008uq}'s argument, roughly, is that these cases involve failure to exercise a capacity, and whether to exercise the capacity to reason is up to us.

  Argument, roughly, is that if an agent is confident in their ability to reason, then the agent is confident that they could not have avoided forming them.

  Obtaining a conclusion by licensing reasoning is not the same as failure of self-control.


  Extreme cases, like \citeauthor{Ginet:2001aa} I have nothing to say about.
  However, cases such as those suggested by \citeauthor{Weatherson:2008uq}.
  Here, following approved methods is not so clear.
\end{note}

\begin{note}[The factive inference]
  I do not assume that the factive inference results in belief.
  \url{https://iep.utm.edu/doxa-vol/} has relies on Ginet, where acceptance or acting as if true seems appropriate.
  And, I think so parallels could be drawn between my cases and those Ginet discusses.

  So, this provides a kind of voluntarism, but suggests a finer issue than Ginet notes.
\end{note}

Interested in inferential \(\phi\) for which the factive inference can be made.

Plausible link:
\begin{enumerate}
\item Agent may believe \(\phi\) only if agent is able to reason to \(\phi\).
\end{enumerate}

Stronger:
\begin{enumerate}
\item Agent may believe \(\phi\) only if agent is confident that they are able to reason to \(\phi\).
\end{enumerate}

The `may' of the antecedent can be read as rational permissibility, etc.

Indirect argument is that an agent is able to believe \(\phi\) only if the agent has reasoned to \(\phi\).
Therefore, it seems the agent must be confident that they are able to reason to \(\phi\), as if the agent is not confident that they have witnessed their ability, then the agent would doubt that \(\phi\) is the case.
So, this isn't interesting if an agent believes that \(\phi\).

However, this won't do for investigating voluntarism.
First issue is that choice may be part of the reasoning the agent is confident that they are able to do.

So, the appropriate reading of reasoning here needs to exclude choice.
Yet, in doing so this assumes that voluntarism is false.


\begin{enumerate}
\item If it is not the case that an agent is confident that they are able to reason to \(\phi\), then it is not the case that the agent may believe \(\phi\).
\end{enumerate}

\begin{note}[Justification]
  The key idea with \citeauthor{Ginet:2001aa} is that sometimes a person was not justified in holding a belief.
  And, this seems to entail that the person had the choice to make the belief.

  This, then, is similar with \citeauthor{Weatherson:2008uq}, where justification is optional.

  So, justification, therefore voluntarism.

  Quick argument is:

  \begin{enumerate}
  \item (Agent was not justified.)
  \item Agent ought not have.
  \item Agent could not have.
  \item Agent had a choice.
  \end{enumerate}
  Therefore, voluntarism, at least in some cases.
  \citeauthor{Ginet:2001aa} is somewhat explicit about this.
  \citeauthor{Weatherson:2008uq} is similar, something the agent ought to have done, and therefore the agent had a choice.

  With \citeauthor{Ginet:2001aa} we have lack of justification.
  So, if a requirement of justification is placed for rational belief, then these cases are going to fail.
  With \citeauthor{Weatherson:2008uq} we have partial justification.
  And, as this is non-monotonic, same idea.

  Inclined to agree that the agent had a choice.
  However, it does not follow from this that it appeared to the agent that they had a choice.
\end{note}

\begin{note}[Weatherson]
  It seems that \textcite[10]{Weatherson:2008uq} suggests that we leap to these conclusions, and that if we follow reasoning patterns that we approve of, then we would not perform these leaps.
  Hence, a key part of the argument for these being voluntary (though not volitional) is that these inferences are akin to losing one's temper.

  However, if ability is added, then these are not cases similar to losing temper.
  For, one is not failing to perform some reasoning that would otherwise be done, but taking a license for the reasoning.
  The agent makes a mistake in licensing these reasons, but this, I think, blocks some of the appeal of the argument.
\end{note}

\begin{note}[Link to belief]
  Hence, \citeauthor{Ginet:2001aa} isn't quite correct.
  The agent is able to reason to at most one, and it is a mistake to think otherwise.
  Still, \citeauthor{Ginet:2001aa}'s diagnosis is on point --- the agent does \emph{stake} something.

  \begin{quote}
    There are all sorts of beliefs that we form in haste, where we could have stopped to consider the various realistic hypotheses consistent with the evidence, and doing so would have stopped us forming the belief.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[10]{Weatherson:2008uq})}
  \end{quote}
  Here, and in the following, \citeauthor{Weatherson:2008uq} focuses on exercising a capacity.

  However, there is a contrast with \citeauthor{Weatherson:2008uq}, who assumes, it seems, that the agent has performed sufficient reasoning, and questions whether the agent `should have' performed more reasoning.
  This then really does seem to be a case of voluntarism, as the agent decides where to stop, but going further may reverse the evidence --- but then unclear why this doesn't also apply to perceptual experience, as this may also be cut short.

  Also issue of how things appear to the agent.
  Noting that things could have gone otherwise doesn't seem compelling.
  Argue that here the agent was either irrational or did not observe a choice.
  So, \citeauthor{Weatherson:2008uq} may be right, in that things could have gone otherwise, but it's hard to square this with \emph{choice}.
  In a sense, the agent made a choice, but it seems something of a Hobson's choice.

  The point about perceptual beliefs is somewhat interesting.
  Need a case in which one could have avoided seeing something.
  So, think of an optical illusion, two lines appear to be the same length.
  Option of not seeing this.
  It is not clear to me where the difference is.

  However, this is achieved is by way of uniqueness.
  When there are multiple options, the same principle applies, but without much consequence.
  E.g.\ choosing cereal.
\end{note}

\begin{note}[Main idea]
  The point about non-voluntarism can be held independently from the broader point that I want to make.
  For, this is about restricting the choices of an agent, rather than providing the agent with choices, roughly stated.
  Hence, lack of ability make block, but it does not follow from this that instance of abilities opens.

  \begin{itemize}
  \item \emph{Therefore} I don't have anything robust to say about \emph{doxastic} voluntarism.
  \item Still, in these cases it's not clear that there is really voluntarism.
  \end{itemize}

  However, similarity in the sense of potential reasoning.
\end{note}

\begin{note}[What voluntarism is]
  The basic idea with non-voluntarism is that the agent does not have the option to form certain propositional attitudes.
  Primary case is belief --- \emph{doxastic} voluntarism (though the general idea extends to any attitude which may be the conclusion of reasoning).
  Motivating example: ???
\end{note}

\begin{note}[Something odd]
  Here, there's some odd.
  For, if focus is on cases where the agent does not have the ability, then this doesn't provide support for holding the opposing attitude.
  Unless, one has an exclusive disjunction.

  So the core idea here is that because the agent doesn't have the ability for, say, the negation, the agent does not obtain the particular attitude by volition.
  So, the key here is thinking in terms of conclusions of reasoning.
  Non-voluntary because exclusive conclusion, and the agent does not have the ability to reason to one of these.
  Doxastic stuff is interesting then, because it seems there is a unique attitude determined by the agent's evidence, whether belief, suspension, or disbelief.
\end{note}

\begin{note}[Hum]
  So the idea behind this kind of non-voluntarism is that the agent doesn't have the ability to reason to a particular conclusion.
  However, this isn't a good account of non-voluntarism and it doesn't say anything about what the agent does reason to.
  So, choosing breakfast cereals at the supermarket.
  Don't have the ability to reason to the conclusion that some particular cereal is any good.
  However, whatever cereal I do choose, it seems I do so voluntarily.
\end{note}

The main focus of the paper has been indirect access to reasons.

With non-voluntarism, the same ideas apply, but rule out certain conclusions.

It's the denial of an existential.

If the existential provides access and allows a conclusion to be adopted, and this holds in converse, then we've got a clear account of when an agent does not have the option of adopting a conclusion.

Hmm, there are two instances of this claim:
\begin{enumerate}
\item Adoption requires ability, hence if no ability then no option to adopt.
\item Ability along with exclusivity rules out certain options.
\end{enumerate}



\newpage

\printbibliography


\newpage

\section{Old notes}
\label{sec:old-notes}

The main motivation here is the common use of the idea of responding to reasons.
In particular, there's \citeauthor{Lord:2018aa} and others who hold the identity these, or \citeauthor{Broome:2013aa} with enkrasia, \citeauthor{Hieronymi:2018aa} with considerations, and others.
Representationalism and dispositionalismn, roughly.
If the proposition is true, then there's pressure.

\begin{note}[Functional role/function]
  The function of the attitude is (in part) determined by the reasons for which it is held.
  Individuate attitudes by their functional role, but an attitudes functional role does not (completely) determine its function.
\end{note}

\begin{note}[Quick argument]
  Quick argument is that reasons require direct response of a kind.
  Though I think I need to say more about direct response for this to be of interest.

  The basic idea is that without direct response there's no difference between the reason obtaining and the reason not obtaining, from the agent's point of view.
  In this sense, the argument is similar to those that could be made against certain forms of responding directly to reasons, etc.

  The response to this is that the second premise is false.
  But if this is the case then superveniece is false.
  So, I should use superveniece in the argument!

  And, the `insight' is that this is replaced by supervenience on mind + ability, roughly stated.
  The difficulty with ability is that this is not something that depends on the agent's mind, so to speak, because whether the agent is able to do something depends on how the world develops.

  Right, although the argument here is similar to the one used against Lord and co.\ it is not clear that it generalises.
  This is because I depend on the role of ability, and without this there is no argument.

  The argument against this, the one that suggests this is a framework issue, is that one may consider an agent's perception of their abilities to be sufficient.
\end{note}

\begin{note}[Schroeder]
  \textcite{Schroeder:2011aa} seems to argue for something similar.
  Roughly, don't need justification, just need guarantee that there are no defeaters.
  So, whether or not a belief is rational to have is down to whether or not there are defeaters.
  Hence, when we look at reasons, we end up looking at whether or there is defeat available.
  And so one `has' evidence in the sense that one lacks defeaters.

  So, quick summary is that:
  \begin{itemize}
  \item Justification entails defeats.
  \item Defeat is other reasons.
  \item Satisfy no defeat condition in other ways.
  \item In particular, by grating that other things can provide reasons.
  \end{itemize}

  This is quite similar to \citeauthor{Lord:2018aa}'s idea about comparative rationality.

  The trouble is that this allows an agent to go undefeated in what appear to be problematic ways.
  \textcite{Schmidt:2019aa} has an illustration with implicit biases.
  Here, as the agent fails to recognise some things as reasons, as problematic attitude is justified through lack of defeat in a way that it would not be if there were stronger requirements on justification.

  Here, I'd render the implicit bias as a search for ``talent''.

  As I don't say what it is for something to be a reason, I don't need to adopt \citeauthor{Schroeder:2011aa}'s position.
  I am only arguing for the claim that the agent obtains the result through a license.

  I may appeal to a similar idea --- in that an agent has a way to avoid defeat --- but I may differ in how this is established.
\end{note}

\section{Motivating quotes}
\label{sec:motivating-quotes}

Reasoning may not be necessary to respond to reasons, depending on how reasons are understood.
For example, the thin paper of a freshly printed book may be reason to perform a frictive raise of a page by thumb and finger in place of exposing the edge to one's fingertip.
Paper cuts hurt.
Still, I may do so as an instinctive response to the texture of the paper --- without reasoning.


for reacting for a sufficient normative reason
\begin{quote}
  A \(\phi\)s for a sufficient normative reason r just in case A’s \(\phi\)-ing is sustained or produced by the fact that r is a sufficient normative reason to \(\phi\).\nolinebreak
  \mbox{}\hfill\mbox{(\citeyear[142]{Lord:2018aa})}
\end{quote}

\begin{quote}
  Manifest Sufficient: What it is for A to \(\phi\) for a sufficient normative reason to \(\phi\) is for A to manifest knowledge about how to use r as the sufficient reason it is to \(\phi\).\nolinebreak
  \mbox{}\hfill\mbox{(\citeyear[143]{Lord:2018aa})}
\end{quote}

It seems that if the agent does not reason, then they do not react.

Follow up claim is that an agent is rational only if they \(\phi\) for a sufficient normative reason.
Rationality will be set aside, or at least put out of focus.
Interested in how an agent may be rational, arational, or irrational.

Similar claims:

\begin{quote}
  (R1\('\)) for an agent to C based on reason R involves not merely the agent’s representing R as justifying C---it also involves \emph{this latter representation (or its content) being part of the reason why the agent C's}.\nolinebreak
  \mbox{}\hfill\mbox{(\citeyear[197]{Neta:2019aa})}
\end{quote}

\begin{quote}
  (D1\('\)) \emph{basing} C on R involves the agent's exercising a disposition to C when both of the following conditions obtain: R, and the rest of the agent’s beliefs cohere with the proposition that R justiﬁes C'ing.\nolinebreak
  \mbox{}\hfill\mbox{(\citeyear[194]{Neta:2019aa})}
\end{quote}

In order for the agent to exercise their disposition, there must be some contact between the agent and the reasons.

(Might be able to fit externalism in here.)

\begin{quote}
  (Possessed Reasons) S possesses an epistemic reason that p to believe that q if and only if (1) that p is an epistemic reason to believe that q, and (2) S justiﬁably believes that p or S has a basic presentational attitude that is not in need of justiﬁcation with the content that p.\nolinebreak
  \mbox{}\hfill\mbox{(\citeyear[5]{Schmidt:2019aa})}
\end{quote}

\section{Somewhere notes}
\label{sec:somewhere-notes}

\begin{note}[Issues with simply talking about ability --- verifying vs.\ solving]
  Similar to calculators.
  \(7^{3} = 343\), but I do not consider the result of computer program a reason to hold that \(7^{3} = 343\).
  The program informed me that, given my understanding of arithmetic, I may hold that \(7^{3} = 343\).

  Compare to:
  \(\lim_{n \to \infty}\left(1 + \frac{1}{n} \right)^{n} = e\)
  This goes beyond my ability.
  If the computer program provides an explanation of how the result was derived, I may study the steps and identify ways to develop the ability, e.g.\ by developing an understanding of l'H\^{o}pital's rule.

  While there is an intuitive distinction between the ability to show that \(7^{3} = 343\) and the ability to show that \(\lim_{n \to \infty}\left(1 + \frac{1}{n} \right)^{n} = e\), there are intermediate cases which put pressure on what is meant by the ability to reason from \(\Sigma\) to \(\phi\).
  For example, I doubt I have the ability to solve \(\sqrt[5]{59049}\) without some assistance, but I do have the ability to show that \(9^{5} = 59049\), and hence the ability to verify that \(\sqrt[5]{59049} = 9\).

  I consider both the ability to solve and the ability as instances of ability to reason, but keeping track of the differences is not too important.
  Therefore, to keep things simple I take talk of the ability to reason to align with the ability to solve.
\end{note}

\end{document}
