%%% Local Variables:
%%% TeX-master: "master"
%%% End:

\chapter{Potentive entailment --- \AR{} and \WR{}}
\label{cha:potent-infer-attr}

\begin{note}[Overview]
  In this chapter focuses on understanding potentive entailment, potentive entailment with respect to (specific) abilities, and how potentive entailment with respect to (specific) abilities is used in the cases of interest.
\end{note}

\begin{note}[Potentive entailment]
  Used `potentive entailment' to capture the entailment from `ability to \emph{V} that \(\phi\)' to `\(\phi\) is the case'.
  Roughly, any entailment with the characteristic that in order for there to be some potential event \(e\), \(\psi\) must be the case.
\end{note}

\begin{note}[The focus point]
  Agent has information that admits of potentive entailment.
  Ability to reason to conclusion.
  Conclusion holds.
  And, premises.

  Begin the chapter with a more detailed account of what this entailment is.

  The focus of this chapter how an agent may use the potentive entailment.

  How understand and what options the agent has for using the \gen{}.

  Sketched two types of reasoning.
  \AR{} and \WR{}.

  \AR{}: the agent obtains support for the conclusion of reasoning on the basis of the support they have for having the attribute of being able to reason to the conclusion.
  Support the agent has for antecedent of entailment flows to the consequent.
  Pairing of ability and conclusion.

  \WR{}: obtain support for the conclusion on the basis of the premises.
  The agent establishes a relation of support on the basis of the \gen{} that they have the ability to witness reasoning which would establish a relation of support between premises and conclusion.

  Important distinction between \AR{} and \WR{} is support.
  \AR{}, support from potentive entailment.

  \WR{}, agent uses \gen{} from potentive entailment to establish relation of support between premises and conclusion.
  Important upshot of \WR{} is compatibility with~\ref{prem:ni}.
  In the scenario of interest, agent does not have the option of obtaining support for information about ability, and \WR{} does not require this.

  Important points about witnessing.
  \begin{itemize}
  \item The agent hasn't witnessing the reasoning they are able to do.
  \item Support the agent establishes is distinct from reasoning via the \gen{}.
  \item Relation of support that would be established.
  \end{itemize}

  Potentive entailment, events.

  So, there's always a verb.
  Understanding in terms of verb.
  Important.

  Entailment does not depend on reasoning from some attribute of the agent.
  Reverse.
  Agent has attribute due to potential event.

  In other words, always possible to rewrite information regarding ability in terms that do not mention ability.
  So, we are not required to take some property of the agent to understand entailment --- property of being able to \dots, however this is understood.
  (If reduce to property that is independent of event, then no clear account of relation of support between premises and conclusion.
  Get premises and get conclusion.)
  Hence, not required to appeal (directly) to ability attribute in order to obtain conclusion.

  Doesn't suit English so well, but makes sense.

  First step to \WR{}.
  Potential event in which agent reasons, and for the event to be potential, certain pre-requisites must be met.

  Second step is using the \gen{} to establish distinct support relation.

  Not required to route support through entailment.
  Entailment provides sufficient information to \emph{anticipate} relation of support that would be establishes by witnessing the reasoning.

  Summarising, three main points.
  \begin{enumerate}
  \item Entailment understood in terms of potential event.
  \item Support distinct from entailment.
  \item Support of basis of premises.
  \end{enumerate}

  This is in conflict with~\ref{denied-claim}.
  Relation of support is between premises and conclusion, etc.

  However, avoids issues arising from~\ref{prem:ni} in cases of interest, as it does not require support for potential event.

  Structure for main part of the chapter split in to section that serve to establish main points.
  Sketch worked backwards from \WR{} to premises, clarify why these things are important.
  Still, argument goes forward.
  Argue for potentive entailment and support independently of \WR{}.
  See \WR{} as building on these two things.
\end{note}

\begin{note}[Plan for chapter]
  The plan for the main part of the chapter is as follows:
  \begin{itemize}
  \item Potentive entailment.
  \item Support
  \item Two ways in which potentive entailment may be used --- \AR{} and \WR{}.
  \end{itemize}

  These sections are followed by optional sections.
  \begin{itemize}
  \item Differences between \AR{} and \WR{}.
  \item (Possibly) further notes on \WR{}.
  \item More on potentive entailment.
    \begin{itemize}
    \item Relation to ability modals.
    \item Interest in entailment itself.
    \end{itemize}
  \end{itemize}
\end{note}

\begin{note}[Wrapping up]
  So, this chapter concludes with a clear understanding of how potentive entailment relates to main argument.
  Understanding of \WR{} and \AR{}.
\end{note}

\begin{note}[Optional]
  May be optional sections of the chapter contain further remarks on potentive entailment, as it seems that this isn't something that's been discussed too much.
\end{note}

\section{Potentive entailment}
\label{sec:potentive-entailment}

\begin{note}[Overview]
  In this section we clarify potentive entailment.
  Provide an account of potentive entailment.

  Two things.
  \begin{enumerate}
  \item How potentive entailment is understood.
  \item How potentive entailment applies information about an agent's (specific) ability to perform some action.
  \end{enumerate}
  Following section then puts potentive entailment(s) to use.

  The section is primarily informal.
  Understand how an agent may use information that they have some (specific) ability (or other similar information).
  Begin with examples, and then provide an account of potentive entailment.

  In short, instance of potentive entailment is understood in terms of preconditions that must be met for a potential event.
  In cases of interest, the event is the agent witnessing ability to \emph{V} that \emph{p}.
  However, describe as potential event of \emph{V}ing that \emph{p}.

  Interest is that potentive entailment does not require ability.
  This means that \AR{} --- and in particular --- \WR{} does not necessarily reduce to ability, whatever ability turns out to be.
  Observed by instances of the same entailment where no agent is involved.

  Use of ability is due to potential events are a conceptual construct with no clear natural language parallel.

  This is not a kind of eliminativism regarding ability.
  Information of interest is obtained by entailment that does not require ability.
  Hence, we may bracket any additional aspects of ability.
  Continue to use ability when focusing on the agent over witnessing event.
  And, possibility is open for reducing to ability.

  No clear discussion in literature.
  On one hand, restricted instance of ability, or similar modal constructions.
  On the other hand, somewhat unique, as obtain information about how things are from a (restricted) possibility modal.
\end{note}

\subsection{The entailment}
\label{sec:entailment}

\begin{note}[Previous]
  We introduced potentive entailment when considering the following observation:
  \begin{itemize}
  \item\label{ent:ex:chess} Some agent \agent{} has the ability to demonstrate that some (particular) chess strategy exists only if the strategy exists.
  \end{itemize}
  In other words, it is necessary that some (particular) chess strategy exists in order for \agent{} to have the ability to demonstrate that it exists.
  Note that the antecedent does not require that the agent has witnessed their ability to demonstrate the existence of the strategy.
  Rather, the rules of chess determine which strategies exist, and a demonstration of some (particular) strategy is the result of applying the rules of chess to identify, rather than create the particular strategy.
\end{note}

\begin{note}[Expanding on intuition]
  This observation may be clarified by considering the contrapositive of~\ref{ent:ex:chess}:
  \begin{itemize}
  \item\label{ent:ex:chess:cont} If it is not the case that some (particular) chess strategy exists, then it is not possible for any agent to demonstrate that the strategy does exist.
  \end{itemize}

  Indeed, the choice of some (particular) chess strategy seems optional.
  The entailment appears valid on the basis of `demonstrate' alone, regardless of what is being demonstrated.
  \begin{itemize}
  \item\label{ent:ex:chess:var} \agent{} has the ability to demonstrate that \(\phi\) only if \(\phi\).
  \item\label{ent:ex:chess:var:cont} If \(\phi\) is not the case, then no agent has the ability to demonstrate that \(\phi\).
  \end{itemize}
  Hence, the entailment is understood primarily from the combination of ability and the verb `demonstrate'.
\end{note}

\begin{note}[Two useful properties of the verb]
  Observe two properties of the verb `demonstrate'.
  First, it is factive, if someone has demonstrated \(\phi\), then \(\phi\) must be the case.
  Second, non-causitive.
  Result of demonstrating may cause the demonstration to exist, but the strategy is distinct form the demonstration.\nolinebreak
  \footnote{
    Agent demonstrated what they were demonstrating.
    Or, demonstrated that thing they were demonstrating.
  }

  The two observations may be reinforced by considering parallels between `demonstrate' and `see'.
  Like `demonstrate', `see' if factive, and `see' is (at least typically) non-causitive.
  Consider:
  \begin{enumerate}
  \item\label{ent:ex:castle:see} Sam has the ability to see a sandcastle built by Taylor only if Taylor built the sandcastle.
  \end{enumerate}
  There is a reading of \ref{ent:ex:castle:see} on which Taylor need not have built a sandcastle.
  For example, the antecedent may be true because Sam's vision is in good order, or because Taylor would not destroy as sandcastle they built before Sam had the opportunity to look at it.
  Still, on the reading of interest, Taylor must have built a sandcastle in order for Sam to have the ability to see it.
  One way to aid this reading is to replace the indefinite `a' with a definite `the', but the reading of interest is available even if Sam has built multiple sandcastles.
\end{note}

\begin{note}[Interest in entailment]
  The entailment is of some interest.
  In both cases, it's ability.
  The agent hasn't (necessarily) witnessed the ability.
  Yet, consequence holds.

  Consider.

  It is easy to accommodate modals with the denial of the consequent.
  For example, epistemic modal `conceivable'.
  \begin{enumerate}
  \item Taylor has not built a sandcastle, but it is conceivable for Sam to see a sandcastle built by Taylor.
  \end{enumerate}

  Harder to accommodate ability.
  \begin{enumerate}
  \item Taylor has not built a sandcastle, but Sam has the ability to see a sandcastle built by Taylor.
  \end{enumerate}
  Force the reading suggested above.

  Hence, we've got verb, but ability is doing some work.
  Or, at least, particular reading of ability.
\end{note}

\begin{note}[Expanding on the modal]
  Ability attached to the verb, modal, the agent may perform the action.
  How to understand the modal, and whether an agent is required, will be of some focus below.

  Intuitively, there is no obstacle to the agent performing the action were they to be granted the opportunity.

  Consider chess again.

  Given the understanding the agent has, and the resources available to the agent, consider all possible strategies that the agent would identify given understanding by applying resources, and the (particular) strategy identified is one such strategy that would be identified.

  Of course, the agent may spend all their resources exploring unsuccessful avenues, or use the resources on something other than demonstrating the existence of chess strategies.

  Likewise, Taylor has the ability to see the sandcastle that Sam built.

  Sam built the sandcastle on the beach, consider all the ways that Taylor may walk along the beach and what Taylor looks at while walking, and on at least one such walk along the beach, Taylor sees the sandcastle.
  Or, from hotel room, all the viewing experiences, at least one in which Taylor sees the sandcastle.
  Perhaps Taylor needs to use binoculars and does not, or it just so happens that someone blocks the view of the sandcastle when Taylor looks in the right direction.

  {\color{red}
    Additionally, no guarantee that ability will be witnessed.
  }
\end{note}

\begin{note}[Turning to examples]
  Basic idea in hand, let us turn to some examples.
  We noted that there are different readings of ability.
  In each of the examples, the claim is not that consequent follows from any instance of the antecedent, but that that there is a reading of the antecedent on which the consequent does follow.
\end{note}

\begin{note}[Examples]
  We noted that simple instances of potentive entailment involve factive, non-causitive, verbs in which the relevant fact holds independently of whether the verb is witnessed.
  \begin{itemize}
  \item Sam has the ability to show that \(19\) is a prime number,
    \begin{itemize}
    \item[\(\leadsto\)] \(19\) is a prime number.
    \end{itemize}
  \item Taylor has the ability to derive the rule of Transposition for the propositional calculus.
     \begin{itemize}
    \item[\(\leadsto\)] Transposition is a rule for the propositional calculus.
    \end{itemize}
  \item Jesse has the ability to spot the differences between the two pictures.
     \begin{itemize}
    \item[\(\leadsto\)] There are differences between the two pictures.
    \end{itemize}
  \item Dana has the ability to learn that Frankie is good at juggling.
     \begin{itemize}
    \item[\(\leadsto\)] Frankie is good at juggling.
    \end{itemize}
  \end{itemize}

  Considered `see' given parallels to `demonstrate', other instances of verbs that do not focus on mental action.
  \begin{itemize}
  \item Corey has the ability to photograph the zebra in the pen.
     \begin{itemize}
    \item[\(\leadsto\)] There is a zebra in the pen.
    \end{itemize}
  \item X has the ability to hear that there is a waterfall nearby.
     \begin{itemize}
    \item[\(\leadsto\)] There is a waterfall nearby.
    \end{itemize}
  \item Addison has the ability to confirm that the meeting is tomorrow.
    \begin{itemize}
    \item[\(\leadsto\)] The meeting is tomorrow.
    \end{itemize}
  \end{itemize}
\end{note}

\begin{note}[Contrast]
  Noted that the verb is non-causitive.
  Question whether entailment is limited to the stated result of performing the verb.

  Provide a number of examples where the result of performing verb is not entailed, but some other precondition is.
  \begin{itemize}
  \item Corey has the ability to unlock the safe in the boardroom.
    \begin{itemize}
    \item[\(\nleadsto\)] The safe in the boardroom is unlocked.
    \item[\(\leadsto\)] There is a safe in the boardroom.
    \end{itemize}
  \item Wesley has the ability to persuade Leslie to read today's newspaper.
    \begin{itemize}
    \item[\(\nleadsto\)] Leslie has been persuaded to read today's newspaper.
    \item[\(\leadsto\)] Leslie is open to persuasion by Wesley.\nolinebreak
      \footnote{Note, nothing in particular follows from being persuaded to do something.}
    \end{itemize}
  \item Jesse has the ability to listen to the lecture that has been recorded.
    \begin{itemize}
    \item[\(\nleadsto\)] Jesse has listened to the lecture that has been recorded.
    \item[\(\leadsto\)] The lecture has been recorded and Jesse has (the option of obtaining) a copy of the recording.
    \end{itemize}
  \item Tanner has the ability to win at roulette.
    \begin{itemize}
    \item[\(\nleadsto\)] Tanner has won at roulette.
    \item[\(\leadsto\)] Tanner has sufficient funds to play roulette.
    \end{itemize}
  \end{itemize}

  Certain non-factive cases in which the negation of result is entailed.
  \begin{itemize}
  \item Jordan has the ability to falsely state that they have green eyes.
    \begin{itemize}
    \item[\(\nleadsto\)] Jordan has green eyes.
    \item[\(\leadsto\)] Jordan does not have green eyes.
    \end{itemize}
  \end{itemize}

  Stress that these entailments do not hold on any reading, but that there is a reading of `ability' on which the do hold.
\end{note}

\begin{note}[Key idea]
  Ability of interest involves an agent performing some action.
  Events come with preconditions.
  Ability of interest applies when sufficient collection of preconditions have been met.
  Potentive entailment draws out necessary preconditions.

  Potentive entailment understood in terms of preconditions for \emph{V}ing that \(\phi\).
\end{note}

\begin{note}[Local example]
  For example, there is potential for Smith to travel to London in time for tomorrows meeting.
  So, there is an aeroplane set to depart no later than midnight tonight for which Smith may purchase a ticket, and so on.

  This is `local' entailment.
  It does not look for necessary conditions for an event.
  For example, private jet.
  Given the way things are, no private jet.

  So, hard to determine whether a potentive entailment holds in general.
  May be some exception.
\end{note}

\begin{note}[Event]
  The examples provided so far have all been of the form `\emph{S} has the ability to \emph{V} that \(\phi\)'.
  Suggested that potentive entailment is understood in terms of preconditions for \emph{V}ing that \(\phi\).
  The primary role of ability is implicitly stating that the sufficient collection of preconditions have been met.

  Hence, we may abstract from ability.
  Examples of the same entailment which do not involve agents.

  \begin{itemize}
  \item Flowers are ready to bloom.
  \item These flowers bloom only if the temperature has been above \(5^{\circ}C\) for at least \(7\) days.
  \item The temperature has been above \(5^{\circ}C\) for at least \(7\) days.
  \end{itemize}

  \begin{itemize}
  \item The laptop is about to perform an update.
  \item The laptop starts to perform an update only if charge is greater than \(60\%\).
  \item The charge of the laptop is greater than \(60\%\).
  \end{itemize}

  \begin{itemize}
  \item The train will soon depart.
  \item There is a mechanism which prevents the train from moving if the doors are not closed.
  \item The doors of the train are closed.
  \end{itemize}

  The intuitive account of potentive entailment holds for these examples.
  Each of the linking premises is stated in terms of a precondition of an event to happen.
  Other linking premises which do not refer to some action may be available.
  Still, the examples provided appear sound.

  Laptop, don't need to have any additional information about the status of the computer.
\end{note}

\begin{note}[Moving on]
  Started with potentive entailment and ability.
  Motivated a basic idea, and observed that examples may be generated.
  Potentive entailment doesn't follow from ability alone, but from particular reading of ability.

  Introduced a handful of examples which do not involve agents, in which similar entailments apply.

  Share in common is that some event there is a possibility of an event occurring.
  With ability, event of agent witnessing ability.

  Introduce terminology of a \emph{potential event}, and characterise potentive entailment in terms of potential events.
\end{note}

\begin{note}[Potential event]
  A potential event is the combination of an event and a modal.
  Contrast with past, future, and possible events.

  Potential as a restriction on possible events.
  There is \emph{potential} for some event \(e\) to be witnessed if a sufficient collection of preconditions for \(e\) to occur have been met and \(\phi\) is a necessary precondition for \(e\) from the world of evaluation.
\end{note}

\begin{note}[Potentive entailment]
  Benefit of potential events is that potentive entailment follows from our stipulated understanding of what it means for there to be potential for some event.
  \begin{enumerate}
  \item In order for there to be potential for some event \(e\) to be witnessed, (precondition) \(\psi\) must be the case.
  \end{enumerate}
  Hence, we have termed this `potentive entailment' as consequent of the entailment follows from the `potential' construct of the antecedent.

  This means the entailment itself is not interesting.
  Note, however, that in examples given it's the description of the event that is doing the work.
\end{note}

\begin{note}[Understanding potentive entailment]
  Intuition for potentive entailment sketched above was that there is no obstacle to agent perform the action they are able to perform, given the opportunity to do so.

  This is follows from more proposed account of potentive entailment.
  For, precondition for event of witnessing ability is the absence of any obstacle that would prevent the ability from being witnessed.
\end{note}

\begin{note}[Type of entailment]
  May be useful to contrast type of entailment with, e.g.\ epistemic modals.
  For example `might'.
  Certain entailments about the agent's epistemic state.
  However, very little follows about what is the case beyond the agent's epistemic state.
  (Apart from statement that the agent is in such an epistemic state.)
\end{note}

\begin{note}[Standard semantics isn't much help]
  Common understanding of modals.

  The ``standard theory'' of modality developed by Kratzer has four important components.
  \begin{itemize}
  \item Some type of possible object.
  \item Modal base.
  \item Ordering source.
  \item Quantifier.
  \end{itemize}
  Take all possibilities in which something is true.
  Restrict the set of possible objects in line with the modal base.
  Order the restricted set of possibilities.
  Quantifier then indicates which of ordered possibilities to consider.

  Applies to ability modals.
  For example, \citeauthor{Mandelkern:2017aa} summarise orthodox account:
  \begin{quote}
    Informally, 0S can w1 is true just in case vwb c is true at some “best” world; in other words, just in case vwb c is compatible with some contextually salient set of worlds.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[304]{Mandelkern:2017aa})}
  \end{quote}
  Ordering source

  No clear account of why anything follows from the modal.
  Wouldn't expect potentive entailments.
  Modals for which potentive entailment does not hold (esp.\ alternative readings of ability).
  Rather, difficulty is that the theory provides an account of how to identify relevant possibilities.
  Filling in the template provides a way to restrict possibilities considered.

  Two choices, modal base or ordering source.
  Certain things must hold in order for a possibility to be considered part of the modal base, or appropriately ranked for the quantifier.

  Modal base is all events in which things that are true have been met.
  Ordering is flat.
  Quantifier is existential.

  This simply elaborates how the constraint noted worked.
  As modal base doesn't always require potentive entailment, something more is required.
\end{note}

\begin{note}[Actuality entailment]
  Unaware of previous work on (what we have termed) potentive entailment.
  Close relation is actuality entailments

    \textcite{Alxatib:2019wf} provides the following account of actuality entailments.
  \begin{quote}
    Actuality Entailments (AEs) are inferences from premises that appear to be modal, like (1a), but their content is that the modality is effectuated in the evaluation world --- (1b).

    \begin{enumerate}[label=(\arabic*)]
    \item
      \begin{enumerate}[label=\alph*.]
      \item Pierre a dû \hspace{26pt} prendre le \hspace{3.5pt} train \newline
        Pierre had.to.\textsc{pfv} take \hspace{14pt} the train\newline
        \hspace{-4pt} ‘Pierre had to take the train'
      \item \emph{Inference}: Pierre took the train.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[701]{Alxatib:2019wf})}
      \end{enumerate}
    \end{enumerate}
  \end{quote}

  Note, the reading of `had' in (1a) is `unambiguously deontic' (\citeyear[703]{Alxatib:2019wf}).
  English paraphrase does not carry the same entailment, but does seem to carry a corresponding implicature.

  Follows \textcite{Bhatt:1999wq} (implication, to avoid commitment to entailment).

  \begin{quote}
    We show that the English ability modal was able to is ambiguous between two readings which can be paraphrased as `managed to' and `had the ability to'.

    \dots

    The two readings associated with be able to allow different interpretive possibilities for indefinite/bare plural subjects.

    \begin{enumerate}[label=(\arabic*), ref=(\arabic*)]
      \setcounter{enumi}{317}
    \item A fireman was/Firemen were able to eat five apples.
      \begin{enumerate}[label=\alph*., ref=\alph*.]
      \item Yesterday at the apple eating contest, a fireman was/firemen were able to eat five apples. (Past episodic, actuality implication, existentially interpreted subject)
      \item In those days, a fireman were/firemen were able to eat five apples in an hour (Generic, no actuality implication, generically interpreted subject)\nolinebreak
        \mbox{}\hfill\mbox{(\citeauthor[172--173]{Bhatt:1999wq})}
      \end{enumerate}
    \end{enumerate}
  \end{quote}

  \citeauthor{Alxatib:2019wf} highlights the difficulty with actuality entailments:

  \begin{quote}
    AEs are surprising; if we assume that modals attribute their propositional argument to potentially non-actual worlds, something must be special to AE-licensers that leads to the inference of actuality.

    Whatever that special feature is, its effect is complex, and it interacts in nontrivial ways with other phenomena of theoretical interest.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[701]{Alxatib:2019wf})}
  \end{quote}

  Possible world, then the event takes place in the possible world.
  Had takes some ordering, so best world involved taking the train.
  This doesn't seem to explain why Pierre took the train.

  {\color{red} Similarly, doesn't follow from ability that it was witnessed.}
  Clear from two readings provided by \citeauthor{Bhatt:1999wq}.

  Similar with potentive.
  There is a possible world, but it's not obvious why this constrains the world of evaluation.

  Potentive entailment is distinct.
  Do not get that the modality is effectuated in the evaluation world.
  Rather, that the conditions required for modal hold in the evaluation world.
\end{note}

\begin{note}[Aspect]
  A different approach is aspect.
  \citeauthor{Hacquard:2006to} makes a proposal along these lines.
  Serves to further restrict ordering source.

  Understand potentive as identifying an aspect?

  Insightful for actuality entailments, but not so much for what we're interested in.
\end{note}

\begin{note}[English]
  As far as I am aware, there is no straightforward construction in English for expressing that an event is potential in the sense described.
  We are dealing with a specific sense of ability, so this is ruled out.
  Variants used to express ability are similarly broad, e.g.\ `can', `capable', `solvable', `doable', or more complex `this watering holds half a litre'.
  Possibility and related existential modals are broad.

  Hence, conceptual.
  Examples provided, hope to convince that the concept is familiar, and is not uncommon.
\end{note}

\begin{note}[Summarising]
  Potentive entailment associated with potential modality.
\end{note}

\subsubsection{Switching}
\label{sec:switching}

\begin{note}[Moving on]
  The understanding of potentive entailment provides an account of how information about a potential event provides one with information of how things are --- that sufficient collection of preconditions for event hold.

  A simple, but important, corollary is that we do not require any particular understanding of ability to understand how the agent in the scenarios of interest obtains information about what follows from their ability.
\end{note}

\begin{note}[Switching between]
  On the relevant reading of `ability', any information of the form:
  \begin{enumerate}
  \item\label{PE:ability:agent} \agent{} has the (specific) ability to \emph{V} that \(\phi\)
  \end{enumerate}
  May be recast as information that:
  \begin{enumerate}
  \item\label{PE:ability:event} There is a potential event of \agent{} \emph{V}ing that \(\phi\)
  \end{enumerate}
  For our interest in the attribution of an ability to the agent is just in providing information that there is a potential event in which the agent witnesses the action that they have the ability to perform.

  For example, we may take the potential entailment when applied to ability statements as derived from the above observation.
  \begin{enumerate}
  \item\label{derived:pe:link} If \agent{} has the (specific) ability to \emph{V} that \(\phi\), then there is a potential event of \agent{} \emph{V}ing that \(\phi\).
  \item\label{derived:pe:pe} In order for there to be a potential event of \agent{} \emph{V}ing that \(\phi\), (precondition) \(\psi\) must be the case.
  \item\label{derived:pe:result} If \agent{} has the (specific) ability to \emph{V} that \(\phi\), then \(\psi\) must be the case.
  \end{enumerate}
  The initial conditional~\ref{derived:pe:link} is the observation made, \ref{derived:pe:link} is potentive entailment, and~\ref{derived:pe:pe} is obtained by hypothetical syllogism.
\end{note}

\begin{note}[Why recasting is important]
  Recasting an agents (specific) ability to, for example, demonstrate the existence of some (particular) chess strategy in terms of there being a potential event in which the agent demonstrates the existence of some (particular) chess strategy will be central to our understanding of how an agent may use the \gen{} that they have the (specific) ability if the have the (general) ability in order to obtain support for the existence of the (particular) strategy prior to witnessing a demonstration.

  We have sketched to possibilities of interest, \AR{} and \WR{}.

  On the quick sketch of \AR{}, the agent traces support through potentive entailment.
  If the agent has support that they have the (specific) ability to demonstrate the existence of a (particular) strategy, then the agent may observe support for the existence of the (particular) strategy by virtue of the relevant instance of potentive entailment.

  On the quick sketch of \WR{}, the agent obtains support for the existence of the (particular) strategy on the basis of the support they have for the premises that they would use when witnessing their ability.

  Potential event has two roles.
  First, an additional instance of potentive entailment: the agent has support for the premises they would use when witnessing their ability follows by potentive entailment.
  Second, event of demonstrating.
  Sense in which the agent may appeal to premises as the event in potential, and so sufficient preconditions have been met for the agent to provide the demonstration.
  Only remaining task for the agent is to identify, rather than establish, what the relation of support is.

  For now we leave these accounts of \AR{} and \WR{} as sketches.
  Return in section~\ref{sec:ar-wr}.
\end{note}



\begin{note}
  Though not required, converse plausibly holds.
  Agent is performing action.
  Seems to provide reading of ability.

  Easier to see with past tense.
  Agent \emph{V}'d that \(\phi\).
  Agent was able to \emph{V} that \(\phi\).

  Change of focus to the agent rather than the potential event.

  Potentive shifts from past to future.
\end{note}

\begin{note}[More on switching]
  Some worries about what it is for there to be a potential event.
  Suitable analysis may depend on ability, or perhaps ability is analysed in terms of potential events.

  In short, while~\ref{PE:ability:agent} is natural, and our preferred statement, \ref{PE:ability:event} is equivalent for entailments of interests.
  Therefore, we will understand the use of potentive entailments involving ability in terms of potential events, rather than on the basis of any particular understanding of ability.

  What matters is the event, and what must be the case in order for the event to be witnessed.

  Important thing to stress is that consequent does not necessarily follow from agent possessing ability.

  Still some differences, deal with these after examples.
\end{note}

\begin{note}[Vetter]
  The account presented is also the opposite to \cite{Vetter:2013vf}.
  \textcite{Vetter:2013vf} reduces to potentiality of objects.

  What does this mean for the account given?
  Regardless of metaphysical project, is there an unstated Humean premise?

  It's motivated by anti-Humean metaphysics.
  Potentiality of an object.
  However, this doesn't really show too much.
  Constrains the appropriate interpretation of modality.
  However, it does not show that that potentive entailment relies on ability.

  Parallels to non-agentive cases remain.
  Potential events is preferred, but key is that the relevant entailment is separable from whatever it is ability turns out to be.
\end{note}

\begin{note}[Some notes from the linguistics literature]
  \citeauthor{Bhatt:1999ud} goes further, arguing that actuality entailments are cannot be due to ability attribution \citeyear[\S4.2]{Bhatt:1999ud}.
  \cite{Hacquard:2006to} argues against this.
  \citeauthor{Hacquard:2006to} also (seems to) link to events.
\end{note}

\begin{note}[Ability may entail more]
  Seen rewriting.
  Refrain from claiming that these are equivalent.

  Ability links to general ability, etc.\

  \textcite{Werner:2011tp} suggests that there's a hierarchy.
  Potentive entailment applies to opportunities.
  So, potential entails ability, but need not be the case that ability requires opportunity.

  The entailments of interest, however, may be recast.
\end{note}

\begin{note}[Still, ability]
  The claim here is that the two are roughly equivalent in the context of the entailments of interest.
  This does not require a general equivalence.

  However, because we're talking about an application of ability, things are different.
\end{note}

\begin{note}[Two important instances of potentive inference]
  Restate \gen{}.{\color{red} ?}
  Apply potentive inference.

  Two important instances of potentive inference
  \begin{enumerate}
  \item Conclusion is the case.
  \item Support for premises.
  \end{enumerate}
\end{note}

\begin{note}[Restriction on instances of potentive entailment]
  We get premises and conclusion.

  Here, the important thing is that if the agent doesn't already have the basics, then something further would need to be the case for there to be a potential event.

  Admittedly, there is no clear line.
  For, there are ways to expand the event.

  We're interested in certain examples as the agent has all of the resources required, so to speak.

  May resist account of potentive entailment, as it seems the entailment applies more generally.
  For example, same principle applies when it's possible for the agent to acquire some information.

  Events are flexible.

  To illustrate, place the reasoning examples behind a conditional.
  \begin{itemize}
  \item If you teach Sam \dots [factoring method], then Sam will have the ability to show that \(19\) is a prime number.
  \end{itemize}
  Intuitively, this is the result of assuming that some additional property holds of the agent.
  Hence, \(\alpha(s) \rightarrow \dots\).
  For, \(\alpha(s)\) will allow the attribution of ability to be true.

  Example, lighting a match.
  Have match and matchbox in hand.
  Have matchbox.
  Matchbox is in a draw.
  Etc.

  Resolved by placing constraints on the event.
\end{note}

\subsection{Summary of details}
\label{sec:summary-details}

\begin{note}[Summary]
  Examined potentive entailment in some detail.
  Key is preconditions for an event.
  Initial analysis followed preconditions for agent witnessing some action they have the ability to perform.
  Potentive entailment applies more generally.

  Provided initial sketch of \AR{} and \WR{}.
\end{note}

\begin{note}[To remember]
  Potential events.
  Sufficient collection of preconditions for event to be witnessed have been met.

  Two important instances.
  \begin{enumerate}
  \item Conclusion.
  \item Premises.
  \end{enumerate}
  Potentive entailment ensures that these are the case, among other things.
  Key is that all that remains is the agent reasoning from the premises to the conclusion.

  Agent is not required to reason from attribute of having the ability.
\end{note}

\section{Entailment and support}
\label{sec:entailment-support}

\begin{note}[Structure]
    The previous section provided an overview of potentive entailment, and introduced potential events.
  The following sections will explore the use of potentive entailment when an agent reasons with information that they have the ability to reason to some conclusion.
  The present section argues a premise that will be used in the following sections.

  Important premise.
  \begin{enumerate}
  \item\label{PE+S:diff-support} Instances in which information about an entailment allows an agent use information about entailment to establish support between premises and conclusion of the entailment independently of whatever support the agent has for the entailment.
  \end{enumerate}

  The upshot of~\ref{PE+S:diff-support} is that it is, at least conceptually, possible that any agent may recognise that a potentive entailment holds, and uses the entailment to establish support.

  If support followed entailment, then any instance of potentive entailment would require support for potential event/ability.
  Problem in scenarios of interest, in which agent does not obtain support for ability, hence does not obtain support for potential event.
  Open the possibility for using information to establish distinct relation of support.
  In particular, between premises and conclusion obtained from potential entailment.

  However, we motive~\ref{PE+S:diff-support} independently of potentive entailment and, in particular, \WR{}.
  \ref{PE+S:diff-support} considers entailment in general.
  Given motivation, apply to potentive entailment to provide understanding of \WR{}.
  Detailed in section~\ref{sec:wr}.
\end{note}

\begin{note}[Overview]
  Observe that entailments may be used to establish relation of support which is distinct from entailment.

  Clarify.
  Present a handful of basic examples.
  Clarify some potential issues.
  Refinement suitable for our purposes.
\end{note}

\begin{note}[Types of cases]
  Type of cases in which entailment from A to B and support from A to B.
  In contrast to support for A and support for entailment from A to B, so support for B.
\end{note}

\begin{note}[Simple example]
  Let us start with a simple scenario.

  \begin{scenario}[Tracking]
    We have an agent and an informer who are on an excursion.
    The informer is an experienced animal tracker, the agent is not.
    Some way through the excursion the informer stops to visually inspect some tracks on the ground, and the agent joins them.
    After the agent has had some time to inspect the tracks, the informer states ``I see these are bear tracks''.
  \end{scenario}

  At the expense of a natural utterance, we clarify the informers statement to provide the information that from visual inspection alone, the informer concluded that the tracks on the ground are bear tracks.
  In other words, the informer has provided information that visual perception of the tracks (non-deductively) entails the tracks are bear tracks.

  It is then straightforward for the agent to observe that the informer's statement entailments that the tracks on the ground are bear tracks, and therefore obtain support for the tracks on the ground being bear tracks on the basis of the support the agent has for the informer making a truthful statement.

  Entailment is something of a conditional.

  \begin{itemize}
  \item Support for the informer has provided testimony that the tracks on the ground are bear tracks, provides support that the tracks on the ground are bear tracks.
  \end{itemize}

  However, it seems (at least \emph{prima facie}) plausible that a direct relation of support may be established by the agent.
  For, the informer has provided information that visual perception of the tracks (non-deductively) entails the tracks are bear tracks, and the agent has visually inspected the tracks.
  So, it is the agent's visual inspection of the tracks that supports that the tracks are bear tracks.

  \begin{itemize}
  \item Visual inspection of the tracks on the ground provides sufficient support for holding that the tracks were made by a bear.
  \item I (the agent) have visually inspected the tracks.
  \item Visual inspection of the tracks supports that these are bear tracks.
  \end{itemize}

  This is the inverse of \citeauthor{Carroll:1895uj}'s Tortoise.

  Testimony, required support for moving from perception to classification of tracks.
  Direct takes the entailment, and obtains support through this.
  Intuitively, the agent has replicated a relation of support.

  Two come apart.
  Next time out.

  Tracker may be in a much better position, e.g.\ by showing how entailment may be derived from facts about bears and the present environment.
  Agent doesn't have this option.
\end{note}

\begin{note}[Perhaps this is too quick]
  Suggested \emph{prima facie} plausibility by contrast to \citeauthor{Carroll:1895uj}'s Tortoise.
  Perhaps a little too quick.
  Achilles presents the Tortoise with sufficient information.
  
\end{note}

\begin{note}[Problematic variant]
  Simple problematic variant.
  Absence of taurine in pet food entails that it is unsuitable for cats.

  Doesn't seem clear that an agent may obtain support for pet food being unsuitable for cats on lack of taurine.
  
\end{note}

\begin{note}[Back to tracking]
  Room to suggest that visual information alone isn't sufficient.
  Agent would not have arrived at bear tracks without information provided by informer.
\end{note}



\begin{note}[Hum]
  Want a case in which the agent really does have all the support needed.

  Consider demonstration of proof.
  Understand the material, proof is novel.

  Conclusion, presenter asserts truth of theorem.
  It's the application of familiar things that is novel.
  Presenter has provided information about how these may be applied.

  As before, may go with testimony, or some variant, such as presentation in institution and so on.
  Rather, seems the presentation allowed agent to establish support between premises and conclusion.

  Role of presenter was to provide information about how support may be obtained for theorem.
\end{note}

\begin{note}[Explanation]
  Here, it is not clear why the presenter needs to be involved in the support relation.
  There is (weak causal) dependency in the sense that the agent received information about how to obtain support from presenter.
\end{note}

\begin{note}[Special case?]
  Plausibility of the proof example is due to a particular feature.

  For example \textcite{Easwaran:2009tm} argues that certain mathematical proofs are \emph{transferable}.

  \begin{quote}
    On full consideration of a transferable proof, the reader will (if she has the right mathematical expertise) come to believe the conclusion of the argument.
    With a non-transferable proof, the reader may be competent, but may doubt the competence of the author to justify particular asserted claims, and thus remain uncertain of the claim.
    A proof is transferable just in case the sequence of propositions itself constitutes the proof --- nothing about the method by which the propositions were generated is essential.
    That is, mere consideration of the proposition suffices for a relevant expert to become convinced of the conclusion\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[354]{Easwaran:2009tm})}
  \end{quote}
  \citeauthor{Easwaran:2009tm} goes on to add \dots
  \begin{quote}
    \dots there is no \emph{particular} step for which testimonial justification is essential.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[355]{Easwaran:2009tm})}
  \end{quote}

  Transferable proof provides information about entailment, and reader may obtain support for conclusion by being provided with information.
  This is not required.
  Agent has the option of establishing support from premises to conclusion.

  Comparably, \textcite{Tymoczko:1979tx} identifies \emph{surveyablity} as a major characteristic of proofs.
  \begin{quote}
    [A proof] is an exhibition, a derivation of the conclusion, and it needs nothing outside of itself to be convincing.
    The mathematician \emph{surveys} the proof in its entirety and thereby comes to know the conclusion.
    \dots

    The proof relates the mathematical known to the mathematical knower, and the surveyability of the proof enables it to be comprehended by the pure power of the intellect-surveyed by the mind's eye, as it were.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[59--60]{Tymoczko:1979tx})}
  \end{quote}
  As with \citeauthor{Easwaran:2009tm}'s notion of transferability, \citeauthor{Tymoczko:1979tx}'s notion of surveyability suggests that a proof is required to be such that any suitable agent (e.g.\ mathematician with sufficient background) has the option of establishing support for the conclusion on the basis of the premises.
  Each step of the proof provides the agent with information about which entailment to use, but the information does not provide the agent with additional or independent support.\nolinebreak
  \footnote{%
    See also \cite{Fallis:2011uc}
    }
\end{note}

\begin{note}[Generalising]
  \begin{enumerate}
  \item\label{general-transferable} Information about entailment.
    Then, so long as agent does not require entailment to obtain support for conclusion, agent may use information from entailment to establish support.
  \end{enumerate}

  This excludes the Rehto case and gallery cases.
  


  If partial to initial examples, describes certain cases.
  Else, necessary condition.

  Cases of interest all involve reasoning, so consistent with this is a necessary condition for establishing distinct relation of support.
  Indeed, understanding of potentive entailment to cases of reasoning leads to this generalised condition.


  May wish to add, in line with~\ref{denied-claim} that the agent does the reasoning in order for a sufficient condition.
  All cases observed so far are compatible with~\ref{denied-claim}
\end{note}

\begin{note}[Tracks]
  Tracks remains somewhat intermediate.
\end{note}

\begin{note}[Translation]
  Still, develop a little more.
  Informer provides basics of translation.
  Now the agent has translated.
\end{note}

{
  \color{red}

  \begin{note}[\citeauthor{Easwaran:2009tm} as an example]
    Need a note on how to replicate \citeauthor{Easwaran:2009tm}'s case.
    This should probably be in the section on types of cases, and noted again here.
  \end{note}
}

\begin{note}[Summary]
  \begin{enumerate}
  \item Instances in which \gsi{} allows for establishing support relations, perhaps conforming to certain conditions. So,
  \item Potentive entailment need not (necessarily) establish support.
  \end{enumerate}
\end{note}

\section{\AR{} and \WR{}}
\label{sec:ar-wr}

\begin{note}[Overview]
  In section~\ref{sec:potentive-entailment} we detailed potentive entailment.
  In section~\ref{sec:entailment-support} we distinguished entailment from support.
  In this section we provide a detailed account of how potentive entailment may be used in scenarios of interest.

  A clearer understanding of \AR{} and \WR{}.

  Primary scenario information:
  \begin{itemize}
  \item \gsi{} that \agent{} has the (specific) ability to demonstrate that some (particular) chess strategy exists if they have the (general) ability to reason with the rules of chess.
  \end{itemize}
  Agent has support for having the (general) ability to reason with the rules of chess.
  Hence, agent is \emph{committed} to:
  \begin{itemize}
  \item Having the (specific) ability to demonstrate that some (particular) chess strategy exists.
  \end{itemize}
  Understood as:
  \begin{itemize}
  \item There is a potential event in which \agent{} demonstrates that some (particular) chess strategy exists
  \end{itemize}
  However, the agent does not obtain support via the \gsi{}.

  \begin{itemize}
  \item\label{ent:ex:chess} Potential event in which \agent{} demonstrates that some (particular) chess strategy exists only if the strategy exists.
  \item The strategy exists
  \end{itemize}

  \AR{} uses (variant of) potentive entailment to obtain support/traces a support relation through potentive entailment.

  \WR{} makes use of additional potentive entailment and support.
  In particular:

  \begin{itemize}
  \item Potential event in which \agent{} demonstrates that some (particular) chess strategy exists only if premises available to \agent{} for \agent{} to reason to the conclusion from.
  \item Premises are available to \agent{} to reason to the conclusion from.
  \end{itemize}

  So, premises available for the agent to reason to the conclusion from.
  In turn, a relation of support is established from the premises that are available to the agent to the conclusion.
\end{note}

\begin{note}[Diagram]
  Figure~\ref{fig:ARandWR:support} provides a simple visual representation of \AR{} and \WR{}.
  Potentive entailment is drawn with a broken line ending with a circle to indicate conclusion of entailment (%
  \(\begin{tikzpicture}[baseline=-0.63ex, ->, >=stealth']%
    \draw[-{Circle[open]}, dashed] (0,0) -- (.5,0);%
  \end{tikzpicture}\)%
  ), while support is drawn with an unbroken line ending with an arrow to indicate what is supported (%
  \(\begin{tikzpicture}[baseline=-0.63ex, ->, >=stealth']%
    \draw[->] (0,0) -- (.5,0);%
  \end{tikzpicture}\)%
  ).

  With \AR{} (subfigure~\ref{fig:AR:support}) support traces the instance of potentive entailment in which conclusion of reasoning is obtained from the potentive event of the agent reasoning.

  With \WR{} (subfigure~\ref{fig:WR:support}), premises and conclusion are obtained from potentive entailment, and support flows from premises to conclusion.

  \begin{figure}[h]
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[->, >=stealth', node distance=0cm, every text node part/.style={align=center}]
      \node [] (c) at (0,0) {};
      \node [] (d) at (-3,0) {};
      \node [] (e) at (3,0) {};
      \node [] (f) at (0,-2.1) {};

      \node (A) at (0,-.1) {Ability};
      \node (C) at (0,-2) {Conclusion};

      \draw [-{Circle[open]}, dashed, xshift=-4] (0,-.35) to  node[left] {} (0,-1.75);
      \draw [->, xshift=4] (0,-.35) to  node[right] {} (0,-1.75);
    \end{tikzpicture}
    \caption{\AR{}}
    \label{fig:AR:support}
  \end{subfigure}
  % \hfill
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[->, >=stealth', node distance=0cm, every text node part/.style={align=center}]
      \node [] (c) at (0,0) {};
      \node [] (d) at (-3,0) {};
      \node [] (e) at (3,0) {};
      \node [] (f) at (0,-2.1) {};

      \node (premise) at (0,-.1) {Premise};
      \node (conclusion) at (0,-2) {Conclusion};

      \node (x) at (-2,-1.05) {Ability};
      % \draw [->] (premise.270) to node[left] (3) {} (conclusion.90);
      \draw [->, xshift=-2] (0,-.35) to  node[right] {} (0,-1.75);

      % \node (4) [left of=3, xshift=-2cm] {};
      \draw [-{Circle[open]}, dashed] (x.0) to (premise);
      \draw [-{Circle[open]}, dashed] (x.0) to (conclusion);
      \draw [-{Circle[open]}, dashed] (x.0) to (-.4,-1.05);
    \end{tikzpicture}
    \caption{\WR{}}
    \label{fig:WR:support}
  \end{subfigure}
  \caption{Relations of support for \AR{} and \WR{}}
  \label{fig:ARandWR:support}
\end{figure}
\end{note}

\begin{note}[Difference with support]
  The significant difference is with support.
  \AR{} traces support from ability, while \WR{} traces support from premises available to the agent through to conclusion.
\end{note}

\begin{note}[Brief note on alternative]
  We do not claim that \AR{} and \WR{} are the only ways in which the agent may obtain support for conclusion.
  In particular,
  \begin{enumerate}
  \item Precondition of receiving information.
  \end{enumerate}
  In simple cases, all three may be available to an agent after receiving information.
  Case is designed with general to specific to rule out this option.
\end{note}

\subsection{\AR{}}
\label{sec:ar}

\begin{note}[The way to phrase this]
  Well, at some point the agent is in a position to attribute sufficient support to themselves.
  Start with the easiest case, ability, and then expand to other cases.
\end{note}

\begin{note}[Attribution]
  \AR{} establishes a relation of support between an agent's (specific) ability to reason to some conclusion, and some proposition which follows via potentive entailment.
  Take the information, and link.

  We have argued that potentive entailment is understood via preconditions for witnessing events of the ability.
  However, as the agent performs the action described by the verb, it makes sense to attribute the agent the property of being able, or in a position, to bring about the potential event.

  Properties are cheap.
  On my desk is a cup of coffee.
  The cup has the property of containing coffee.
  The coffee has the property of being in the cup.
  I have the property of having poured the coffee into the mug.
  Previous moments have the property of being moments for which I was pouring coffee in to the cup.
  And, I have the property of being in a position to drink the coffee in the cup.

  For sure, it's something that has not happened, but so long as there is sense to be made of a potential event, there's a corresponding property.

  Might reduce why this is true to something else, particular path of mental steps.
  But we're still going to have a property of this kind.

  Though potentive entailment is understood in terms of events, the property of being able to reason to some conclusion references some potential event and we may chain together a derived instance of potentive entailment.
  \begin{enumerate}
  \item As the agent has the (specific) ability, there is a potential event,
  \item Potential event only if \(\phi\) is a precondition of the potential event, therefore
  \item Agent has (specific) ability, \(\phi\) holds.
  \end{enumerate}
  As we are interested in the support appealed to by the agent, and not {\color{red} some kind of metaphysical} support relation, the derived instance of potentive entailment provides a route for the agent to transmit support they have for having the ability to the relevant precondition for the potential event.

  In short, it seems that derived potentive entailment is suitable for transmitting support.
  Whatever support the agent has for the (specific) ability also provides support for the preconditions for witnessing the (specific) ability.

  Countless examples.
\end{note}

\begin{note}[Ability is not strictly required for attribution]
  Described \AR{} with ability.
  Have seen that this can be reformulated in terms of potential event.
  The same pattern holds with potential event.

  For example, support for potential event, so conclusion holds.
\end{note}

\begin{note}[Example, fire]
  Alarm is ringing, so there is a fire.

  Same basic idea.
\end{note}

\begin{note}[Requires support for ability]
  Before turning away from \AR{}, let us stress that \AR{} requires the agent to have support for the (specific) ability in order to obtain support for the conclusion.
  Hence, if the agent does not have support for the (specific) ability, then they will not have the option of obtaining support for the conclusion via \AR{}.
\end{note}

\begin{note}[Relation to uRa]
  There is no immediate relation between \AR{} and~\ref{denied-claim}.

  \ref{denied-claim} talks about access to premises.
  \AR{} states that there is a support relation.

  \ref{denied-claim} enters the picture when observing that the agent has information about ability prior to witnessing ability.

  If the agent has information about (specific) ability and the agent has support for information, then extending support from ability to result is consistent with~\ref{denied-claim} as the only required premise is that the agent has the ability.
\end{note}

\begin{note}[Evidence of evidence]
  We have considered \AR{} from the perspective of potentive entailment.

  Variation.
  Following previous section, entailment.
  Support for support.
  Or, evidence of evidence.
\end{note}

\begin{note}[Evidence of evidence]
  \begin{quote}
    If E1 is evidence that E2 supports P, then E1 supports P.
  \end{quote}

  Trouble with this formulation.
  Following~\citeauthor{Feldman:2014un}
  Support that P entails Q, but it does not follow that this supports Q.
  Support for entailment, rather than consequent of entailment.
  (\citeyear[291]{Feldman:2014un})

  So, \AR{} is \emph{not} plausibly recast in terms of support for entailment providing support for conclusion.
  Rather, modify to include evidence for E2.

  \begin{quote}
    If E1 is evidence for E2 and E2 is evidence for P, then E1 supports P.\nolinebreak
    \footnote{
      \begin{quote}
        (EEE1) If E (non-conclusively) supports the claim that (some subject) S possesses evidence which supports p, then E supports p.\nolinebreak
        \mbox{}\hfill\mbox{(\citeyear[4]{Tal:2017uw})}
      \end{quote}
      Or, there is evidence.
    }
  \end{quote}

  So, information about ability provides evidence for premises, and then link comes for free, so to speak.

  Note that this is simply an instance of the previous version of \AR{} with an additional step.
  This is not true in general, but for our purposes we don't need to narrow the principle.\nolinebreak
  \footnote{
    Note to literature, esp.\ \citeauthor{Tal:2017uw}.
  }

  Remains a point of interest.
  Close to sketch of \WR{} made above, and described in more detail below.
\end{note}

\begin{note}[Evidence of evidence]
  Secondary interest is in \emph{de re} and \emph{de dicto}.
  Preparation for \WR{}.

  \citeauthor{Tal:2017uw} disambiguate \emph{de re} and \emph{de dicto} readings of EEE.
  Framed in terms of existence, in cases of interest, agent `has' the evidence/support.

  \begin{quote}
    For all \(e\) and \(p\), if \(e\) is evidence that there is evidence \(e'\) for \(p\), then \(e\) is evidence for \(p\).\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[8]{Tal:2017uw})}
  \end{quote}
  In example, this links the existence of premises.

  Support is not obtained from premises (which the agent has not reasoned from, and have not be `accessed'), but on the existence of premises for the conclusion (which the agent may `access' from potentive entailment).

  So, because existence we get support.

  \citeauthor{Tal:2017uw} suggest \emph{de dicto}.
  \begin{quote}
    For all \(e\), \(e'\) and \(p\), if
    \begin{enumerate*}[label=(\roman*), ref=(\roman*)]
    \item \(e\) is evidence for \(e'\) and
    \item \(e'\) is evidence for \(p\),
    \end{enumerate*}
    then \(e\) is evidence for \(p\).\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[8]{Tal:2017uw})}
  \end{quote}
  In example, this links the premises themselves.
  Premises do provide support.
  Here, this is close.
  The core idea of \WR{} is that the premises do the work.

  So, then, this provides an account that is somewhat close.
  Important thing is that the support transfers through to ability.

  Initial sketch will follow in this lines.
  Difficulty is with doxastic support.

  Granting propositional support \dots
  Seems agent is going to require support for ability in order to get conclusion.
  So, propositional aspect corresponds with \WR{}, but doxastic does not.
\end{note}

\begin{note}[Broader narrative]
  We've offered a variety of ways to understand \AR{}.
  Common thread is that the agent obtains support for conclusion from support for ability.

  EEE.
  Provided an variant of \AR{} when understood \emph{de dicto}.
  Similar to \WR{} when understood \emph{de re}, but remained issue with doxastic support.
\end{note}

\subsection{\WR{}}
\label{sec:wr}

\begin{note}[Overview]
  In section~\ref{sec:ar-wr} we outlined the key distinction between \AR{} and \WR{} for the purpose of the overarching argument of this thesis.

  Understanding \WR{}.
\end{note}

\begin{note}[General idea of \WR{}]
  The core idea of \WR{} is that the agent uses information that there is a potential event in order to claim support for the conclusion.

  The potential event involves the agent reasoning to some conclusion.
  Reasons from premises.

  As event of reasoning is potential, preconditions are satisfied.
  Hence, conclusion holds, and premises sufficient for conclusion in line with \ref{prem:bP}.


  The agent does not rely on support for there being a potential event, or support for having an ability, as in the case of \AR{}.
\end{note}

\begin{note}[Negative characterisation of \WR{}]
  Negative characterisation of \WR{} in terms of support that the agent does not appeal to.
  So, no support which goes straight to the conclusion.
\end{note}



\begin{note}[Two passes]
  Two passes at \WR{}.
  First pass assumes understanding of propositional support.
  In cases discussed, agent has option of appeal to independent propositional support for premises of reasoning.
  Core idea of \WR{} is that potential event of reasoning allows agent to extend to propositional support for the conclusion of reasoning.

  The core idea of \WR{} has a two primary purposes.
  As noted, allowing support.
  Also, going for things in the right way\dots

  Primary purpose of first pass is to introduce ideas.
  Understand the role of information as allowing a particular closure relation with respect to propositional support.

  Observe that this requires a particular understanding of propositional support, and criticise the pass for insufficient motivation even if understanding of propositional support is adopted.

  Leads to a second pass in which we introduce idea of deferred support.
  Core idea of deferred support is that link is created, but establishing the link is deferred.
  Role of information is in allowing the agent to defer establishing relation.

  Support `just is' the deferred support from establishing.
  `Little more' than temporal separation.

  Second pass is fairly minimal.
  E.g.\ doesn't depend on understanding of propositional support.
  One may (of course) add further conditions.
  Hence, pursue as sufficient, but real interest is in idea of deferring, whether or not this needs supplementation.
\end{note}

\begin{note}[No inherent conflict]
  These passes do not inherently conflict with~\ref{denied-claim}.

  Simplest to see in cases of memory loss.
  Provide some motivating independent of the intended application.
  Although true for both passes, delay discussion for second pass.

  Key is that these passes make room for conflict.

  Passes do conflict with a stronger refinements of~\ref{denied-claim}.
\end{note}

\subsubsection{First pass: Propositional support}
\label{sec:first-pass:-prop}

\begin{note}[Recap]
  Type of situations.
  Some general ability.
  Conditional information.
  Conclusion.
\end{note}

\begin{note}[Core idea]
  The motivating idea for our first pass at a detailed understanding of \WR{} is that so long as the information is true, then the agent has propositional support for conclusion.
  Following proposition/doxastic distinction is appropriate connexion.
  Appropriate connexion does not added support, rather allows the agent to make use of support.
  Appeal to potential event/ability allows agent to anticipate appropriate connexion.
  Hence, something a little weaker than doxastic support.

  Three important points here.
  \begin{enumerate}
  \item propositional support.
  \item information that propositional support.
  \item additional features connect agent to propositional support, and do not add support.
  \end{enumerate}

  Idea is that agent appeals to propositional support that they have.

  Key point of argument is that if agent has propositional support, then that is sufficient support for conclusion.
  Agent appeals to propositional support, which is premises.
  Role of \WR{} is in granting connexion between premises and conclusion.
\end{note}

\begin{note}[Propositional and doxastic support]
    Our use of support falls closer in line with doxastic justification as opposed to propositional justification.
  Roughly, following \textcite{Silva:2020aa}:

  \begin{quote}
    \textbf{Propositional Justification}: S has propositional justification to believe that p iff
    \begin{itemize}
    \item S has sufficient epistemic reasons to believe that p.
    \end{itemize}

    \textbf{Doxastic Justification}: S has a doxastically justified belief in p iff
    \begin{enumerate}[label=(\roman*), ref=(\roman*)]
    \item\label{dj:def:i} S has propositional justification to believe that p,
    \item\label{dj:def:ii} S believes that p, and
    \item\label{dj:def:iii} S's belief in p is appropriately connected to S's sufficient epistemic reasons to believe p.
    \end{enumerate}
  \end{quote}

  These are fairly neutral definitions.
  Basic idea is that the agent has propositional support, and doxastic support traces this.

  \ref{prem:bP} informs our understanding of sufficient epistemic reasons.
  So long as agent has reasoned, then those premises (and perhaps steps used, maybe lack of other premises) are sufficient epistemic reasons.
  No need for full account.
  In turn, ability/potential event involves sufficient epistemic reasons.

  Important point here is that propositional support alone doesn't do much.
  An agent may have propositional support for some proposition and either not recognise that they have propositional support, or fail to form any attitude toward the proposition in line with the propositional support they have.
\end{note}

\begin{note}[P/D Example]
  To illustrate the distinction between propositional and doxastic support, consider the following multiple choice question.

  \begin{figure}[H]
    \centering
    {
      \sffamily
      \newcommand{\pythagwidth}{3cm}
      \newcommand{\pythagheight}{5cm}
      \begin{tikzpicture}[box/.style={rectangle, rounded corners, draw=black, text width=15mm}]
        \begin{scope}[shift={(0,0)},rotate=270, scale=0.75]
          \coordinate [label={below right:}] (A) at (0, 0);
          \coordinate [label={above right:}] (B) at (0, \pythagheight);
          \coordinate [label={below left:}] (C) at (-\pythagwidth, 0);

          \coordinate [label={below:\(5\text{cm}\)}] (F) at (0,\pythagheight/2);
          \coordinate [label={left:\(3\text{cm}\)}] (G) at (-\pythagwidth/2, 0);

          \coordinate (D1) at (-\pythagheight, \pythagheight + \pythagwidth);
          \coordinate (D2) at (-\pythagheight - \pythagwidth, \pythagwidth);

          \draw [] (A) -- (C) -- (B) -- (A);
          \newcommand{\ranglesize}{0.3cm}
          \draw [line width=0.4pt] (A) -- ++ (0, \ranglesize) -- ++ (-\ranglesize, 0) -- ++ (0, -\ranglesize);
        \end{scope}

        \node (Answer) at (7,1.25) [text width=6cm]
        {
          What is the area of the given triangle?
          \begin{enumerate}[label=\Alph*.]
          \item \(4\text{cm}^{2}\)
          \item \(7.5\text{cm}^{2}\)
          \item \(16\text{cm}^{2}\)
          \end{enumerate}
        };
        \draw [rounded corners] (-1,-.5) -- (10,-.5) -- (10,2.75) -- (-1,2.75) -- cycle;
      \end{tikzpicture}
      \vspace{5pt}
    }
  \end{figure}

  \noindent The students have been taught:
  \[\text{Area of triangle} = \left[\sfrac{1}{2} \times \text{base} \times \text{perpendicular height}\right] (\text{square units})\]
  Perhaps the students have testimony of teacher, or perhaps have been given a proof.
  Either way, applied to given triangle provides sufficient epistemic reasons, and for simplicity \emph{stipulate} no other epistemic reason.\nolinebreak
  \footnote{Somewhat tricky as there may be ways to eliminate the two other options.
    Stipulate in order to ease a point made below.
  }

  Three variations.
  No propositional (entails no doxastic).
  Propositional and doxastic.
  Propositional and no doxastic.

  Consider a handful of students.
  First, guesses.

  remaining four clarify divide.
  First pair, clear instances.
  Second pair, more difficult cases.
  First is great case.
  Guess again, clearly no dox, though prop.

  Two students who have applied the formula, and calculated that \(\sfrac{1}{2} \times 5\text{(cm)} \times 3\text{(cm)} = 7.5(\text{cm}^{2})\).
  Both students have the correct answer.
  However, only one of the students has noted that \(3\text{cm}\) may be taken as the (perpendicular) height of the triangle because the triangle is a right angle.
  The other student has taken \(3\text{cm}\) to be the (perpendicular) height of the triangle because it is the length of one edge of the triangle.
  The student understands that the perpendicular height of a triangle may differ from the length of any given edge of a triangle, but due to exam pressure has overlooked this possibility.

  As both students understand how to apply the formula they have been taught, it seems both students have propositional support for the answer they have given.
  However, it seems only the former student also has doxastic support for the answer they have given.
  The latter student has the correct answer.
  However, the latter student's belief that the area of the triangle is \(7.5\text{cm}^{2}\) is not appropriately connected to the student's epistemic reasons to believe that the area of the triangle is \(7.5\text{cm}^{2}\).
  For, if the question had been altered so that the triangle was not a right angled triangle, the latter student would not have arrived at a misleading belief about the area of the triangle given the reasoning performed.\nolinebreak
  \footnote{
    Note, not saying that the student would not have arrived at the correct answer.
    For, the student may have clarified their reasoning if the answer given did not match a choice.
    Rather, if the same reasoning was applied (with different lengths) to a non-right angled triangle, the agent would not have correctly identified the perpendicular height of the triangle.
  }

  Third student who did not understand the formula but has it written down on a cheat sheet.
  The student sees that calculating the area of a triangle involves multiplying two numbers and dividing the result by two, and so believes that the area of the triangle is \(7.5\text{cm}^{2}\) because the only two numbers available are odd, recalls the result of multiplying two numbers is always odd, and that division by two of any odd (rational) number must involve a fraction.
  Certainly no doxastic support.

  Fourth student, guesses.

  Without a full account of sufficient epistemic reasons, unclear that the student has propositional justification.
  As the student did not understand the formula, lack sufficient epistemic reasons.
  However, possible to allow as the formula is in front of the student.\nolinebreak
  \footnote{Compare \citeauthor{Firth:1978vi}'s example with Holmes and Watson (\citeyear[218]{Firth:1978vi}).
    Watson is presented with all the evidence Holmes used to that the coachman committed the murder, and that this provides Watson with sufficient epistemic reasons regardless of whether or not Watson forms any attitude, but it is not clear that Watson has the understanding to piece together the evidence laid before them.}

  A clearer case of a student who lacks even propositional support may be a student who forms a belief that the area of the triangle is \(7.5\text{cm}^{2}\) without learning the formula, but because it is one of the options given, and one in four odds aren't too bad.
  No possibility of doxastic support.

  No stance on borderline cases.
  Rather, helpful because this highlights how two important conditions work.
  What it is to have sufficient epistemic reasons, and what it is for an agent's belief to be appropriately connected to the agent's sufficient epistemic reasons to believe.
\end{note}

\begin{note}[Takeaway]
  Student who have propositional support have so independently of whether the way they form a belief is appropriately connected.
  Whether doxastic considers how the agent forms the belief.

  Relation to cases of interest.
  If the information is true, then the agent has propositional support.
  For, result of reasoning would be good, and potential means that there's no opportunity to acquire new information.

  Agent does not have doxastic support.
  Some flexibility on what the third condition amounts to, but the overall argument is that there is an exception to~\ref{denied-claim}.
  Noted problems with basing.
  I see no interest in arguing that the term `doxastic support' applies to cases of interest.
  Given well-developed analyses of the basing relation, then leaves `doxastic support' to those analysis.

  Doxastic support requires an \emph{appropriate} connexion, but `appropriate' is one adjective among many.
  There are other adjectives --- or ways in which the agent may relate sufficient epistemic reasons to conclusion --- that may be of interest.

  Further, if information is true, then potential event seems a clear case.
  Unlike the second pair, things aren't too delicate.
  Agent reasons well, and potential event so avoid worries about the degree to which propositional support is in reach.
\end{note}

\begin{note}[Generalising a little]
  Propositional support is focus.
  Given definition, applies to p, some proposition.
  Extend to cover steps of reasoning.
  May always reduce to a proposition, if given some basic.
  Still, talk of steps.
\end{note}

\begin{note}[Agent doesn't need support to appeal to support]
  This is super important to stress that agent doesn't need support to appeal to support.
  Mistakes are made, even when reasoning.
  One uses a premise which one doesn't have propositional support for.
  For example, by something changing in the world.
\end{note}

\begin{note}[Where this is going]
  With a (sufficiently) neutral distinction between propositional and doxastic support in hand, we now turn to an argument for the claim that the agent is in a position to form an attitude to conclusion, where support appealed to are those premises that would be used in reasoning.

  For the agent to obtain doxastic support, need appropriate connexion, not additional support.

  Independent relation of propositional support between premises and conclusion.
  Premises --- whatever these happens to be --- provide the agent with propositional support for the conclusion, independent of whether the agent has, or will, do the reasoning.
  Conditional information, provides agent with information that general ability provides access to propositional support.
  That is, whatever the propositional support happens to be, if the information is true then the agent has access to propositional support.
  On a standard picture, the agent obtains doxastic support from propositional support if attitude toward conclusion is appropriately connected to propositional support.
  What is missing is an appropriate connexion.

  That is, two components.
  \begin{enumerate}
  \item Support
  \item How the agent uses this support to get conclusion.
  \end{enumerate}

  If information is true, then as the agent already has sufficient support for the conclusion on basis of premises, our task is to explain how information about ability/potential event allows the agent to appropriately connect attitude toward conclusion to premises.

  Propositional support alone doesn't do much.
  But the information is useful.
\end{note}

\begin{note}[Idea]
  Idea is to show that the agent may appeal to having propositional support for whatever the premises of reasoning are.
  Information then used to extend propositional support for premises to propositional support for conclusion.
  In turn, attitude toward conclusion based on propositional support, whatever that propositional support happens to be.

  Four key points to the argument, which we will work through.
  \begin{enumerate}[label=(V\arabic*), ref=(V\arabic*)]
  \item\label{W:fp:S:1} If there is a relation of propositional support between premises and conclusion of reasoning, then witnessing the reasoning does not provide an agent with \emph{additional required} support for the conclusion.\nolinebreak
    \footnote{May provide the agent with additional support, but it isn't required for the agent.}
  \item\label{W:fp:S:2} If support for general ability, agent may (plausibly) appeal to having propositional support for any premises or steps of reasoning which is an exercise of the relevant general ability.
  \item\label{W:fp:S:3} A potential event of witnessing is sufficient for the agent to hold that propositional support for premises of reasoning extend to conclusion.
  \item\label{W:fp:S:4} Attitude that conclusion is true based on propositional support for conclusion (and not that the agent has attitude toward propositional support).
  \end{enumerate}
  The four key points are then unified by the following pair of observations:
  \begin{itemize}
  \item From~\ref{W:fp:S:1} and~\ref{W:fp:S:2}, agent may hold that they have propositional support for conclusion.
  \item From~\ref{W:fp:S:3} and~\ref{W:fp:S:4}, Attitude toward conclusion based on premises used when witnessing.
  \end{itemize}
  Second observation may also use~\ref{W:fp:S:2}, given steps that would be used in reasoning.

  Figure~\ref{W:fp:steps:diagram} provides a (rough) visual representation of how the four steps fit together.
\end{note}

\begin{figure}[H]
  \centering
  \begin{tikzpicture}[scale=.5]
    \node at (0,0) (GA) {\parbox{2cm}{\centering General Ability}};
    \node at (8,0) (I) {\parbox{2cm}{\centering Information}};
    \node at (16,0) (AC) {\parbox{2cm}{\centering Attitude toward Conclusion}};


    \node at (0,-6) (PP) {\parbox{3cm}{\centering (Propositional) support for premises}};
    % \node at (8,6) {\parbox{3cm}{\centering Information}};
    \node at (16,-6) (PC) {\parbox{3cm}{\centering (Propositional) support for conclusion}};

    \node at (-2,-3) {\parbox{2cm}{\centering \ref{W:fp:S:2}}};
    \node at (8,-7) {\parbox{6cm}{\centering \ref{W:fp:S:1} --- and possibly~\ref{W:fp:S:2}}};
    \node at (18,-3) {\parbox{2cm}{\centering \ref{W:fp:S:4}}};
    \node at (8,-3) {\parbox{2cm}{\centering \ref{W:fp:S:3}}};

    \draw [-Implies,line width=1pt,double distance=1pt] (GA) -- (PP);
    \draw [-Implies,line width=1pt,double distance=1pt] (PC) -- (AC);
    \draw [->] (PP) -- (PC);

    \draw [-, dashed] (PP.30) -- (PC.150);
    \draw [-, dashed] (I.270) -- (PP.30);
    \draw [-, dashed] (I.270) -- (PC.150);

    \node[circle,draw=black, fill=white, inner sep=0pt,minimum size=4pt] (b) at (PP.30) {};
    \node[circle,draw=black, fill=white, inner sep=0pt,minimum size=4pt] (b) at (PC.150) {};
  \end{tikzpicture}
  \caption{Representation of important steps}
  \label{W:fp:steps:diagram}
\end{figure}

\begin{note}[Explaining figure]
  Trace the arrows.

  Top line, what the agent accesses.
  Bottom line, support.
\end{note}

\begin{note}[First key point]
  The first key point states:
  \begin{enumerate}
  \item If there is a relation of propositional support between premises and conclusion of reasoning, then witnessing the reasoning does not provide an agent with \emph{additional required} support for the conclusion.
  \end{enumerate}
  The point follows from the definitions of propositional and doxastic support, and independently of any particular account of what sufficient epistemic reasons are (or what support is).

  For, conditions~\ref{dj:def:i} and~\ref{dj:def:iii} of the given definition of doxastic support states that the agent has propositional support to believe that p, or equivalently that the agent has sufficient epistemic reasons to believe that p, given the definition of propositional support.
  Therefore, if sufficient epistemic reasons relied on additional (epistemic) reasons introduced by either condition~\ref{dj:def:ii} or condition~\ref{dj:def:iii}, then either:
  \begin{enumerate*}[label=(\roman*)]
  \item The sufficient epistemic reasons identified by the agent having propositional support are not sufficient for holding an attitude toward the conclusion --- a contradiction.
    Or
  \item The definitions of propositional and doxastic support are equivalent.
  \end{enumerate*}

  Assume for equivalence that some collection of the conditions for doxastic support introduce additional required support for the conclusion.
  As the epistemic reasons identified by propositional support are sufficient, then given the assumption made, propositional support must reference doxastic support in order to identify the additional epistemic reasons introduced by some collection of the conditions for doxastic support in order for the agent to have sufficient epistemic reasons to hold an attitude toward the conclusion.
  However, doxastic support in turn requires the agent to have propositional support by condition~\ref{dj:def:i}.
  So, in order for the agent to have doxastic support the agent must have propositional support, but given the assumption, in order for the agent to have propositional support, the agent must have (some part of) doxastic support.

  There need not be anything problematic with circular definition.
  Rather, the observation is that if the definitions are circular in this way, then the presence of condition~\ref{dj:def:i} as part of the definition of propositional support allows one to eliminate either either condition~\ref{dj:def:ii}, condition~\ref{dj:def:iii}, or both from the definition of doxastic support.

  Note, however, that condition~\ref{dj:def:iii} requires condition~\ref{dj:def:ii} to be true, as the agent's belief is required to be appropriately connected to the agent's sufficient epistemic reasons.
  Therefore, it seems that if condition~\ref{dj:def:iii} is a required epistemic reason then condition~\ref{dj:def:ii} must also be a required epistemic reason.
  Hence, the definitions collapse in to one another and there is no distinction between propositional and doxastic support.

  So, then leave out condition~\ref{dj:def:iii}, but this is the condition where things are different.
  Only appropriate connexion without further information would be reasoning, by~\ref{denied-claim}.
  Hence, given definitions and difference, then result wanted.

  As doxastic is the attitude, proposition is supported independently of whether or not the agent has reasoned.\nolinebreak
  \footnote{
    This is not to say that the agent is irrelevant. (Notably observed by \cite{Firth:1978vi} when introducing the terminology).
    Rather, that the agent has (propositional) support whether or not they have reasoned.
  }
  Therefore, as we're dealing with a potential event, then given the definitions of propositional and doxastic support \emph{and} given the truth of the information, then the agent has propositional support for the conclusion, no matter what sufficient epistemic reasons turn out to be.
\end{note}

\begin{note}[Closure principle]
  Summarise with a closure principle for propositional support:
  \[\propsupp{\phi} \land (\phi \ientails{} \psi) \vdash \propsupp{\psi}\]
  If reasoning would lead to conclusion, and agent has support for premises, then agent has support for conclusion.
  
  This simply states things about propositional support.
  Closure principles, because it states that \(\psi\) is a member of the class of things that are propositionally justified.
\end{note}

\begin{note}[Slight problem]
  This premise is important, but fairly weak.
  May be the case that the agent is required to reason to have propositional support (i.e.\ sufficient epistemic reasons).
\end{note}

\begin{note}[Concludes first step]
  This is the first step.
  Given definitions of propositional and doxastic support, the agent is not required to reason in order to have sufficient epistemic reasons for the conclusion.
\end{note}

\begin{note}[Second step]
  Second step:
  \begin{enumerate}
  \item[\ref{W:fp:S:2}] If support for general ability, agent may (plausibly) appeal to having propositional support for any premises or steps of reasoning which is an exercise of the relevant general ability.
  \end{enumerate}
  Phrased a little more naturally, though perhaps a little more controversially:
  \begin{enumerate}
  \item[\ref{W:fp:S:2}] In the scenarios of interest, the agent may (plausibly) \emph{believe} they have propositional support for any premises or steps of reasoning which is an exercise of the relevant general ability.
  \end{enumerate}
  Prefer to stay neutral.
  Still, highlighting belief, repeat a clarification from earlier.
  \ref{W:fp:S:2} does not require the agent to have support.
  Rather, \emph{appeal} to having propositional support.
  No plausible requirement that an agent may appeal to propositional support only if they do have propositional support.
  Motivated with changes to environment.

  Same applies to cases.
  Agent has support for general ability.
  May not have propositional support.

  Two examples.

  Agent has been taught, and teacher is bad.
  Agent does not have propositional support, but fair for the agent to appeal to having propositional support.

  Agent has learnt majority of rules, feedback that these are complete.
  However, additional rule stating an exception to rule that has been learnt.
  Given that the rules of chess are fairly compact, this takes some imagination, but provided some examples earlier.
  Seems plausible that the agent may appeal to having propositional support as from agent's perspective there.

  Still, as noted in concluding first key point, something substantial needs to be said about sufficient epistemic reasons in order for this second key point.
  Hence, role of qualifier.
  No direct argument.

  Here, rely on~\ref{prem:bP} again, though slightly expanded.
  Premises, or steps of reasoning are sufficient epistemic reasons.
  Nothing more to support with respect to reasoning.

  Consider validity.
  If Premises are true, then conclusion is true.

  Steps are fixed.
  Allow different steps.
  If Premises are true, and steps preserve truth, then conclusion is true.

  Soundness.
  Premises are true, steps preserve truth, then conclusion is true.

  Truth, but more generally some designated property.
  E.g.\ probability, or desirability.

  Vary from preservation.
  What matters is that the conclusion has the designated property.
  (May be probability example for this.)

  So, premises and steps are sufficient to ensure that conclusion has designated property.

  Concerns about what is required for ensuring, but hard to think of there being something in addition to premises and steps which is relevant to ensuring designated property.

  So, reasoning/demonstration (and hence exercise of general ability) is understood in terms of premises and steps.

  Granting this, question is whether agent may appeal to having propositional support from exercise of general ability.

  Role of general ability has two parts.
  First, no new information --- this is a strict reading.
  Already seen that propositional support/sufficient epistemic reasons whether or not agent reasons.
  Second, the agent doesn't stray from premises and steps that they (may claim to) have support for.

  This seems to capture something unremarkable.
  Consider arithmetic.
  \(((421 + 531) \times 5)/7\).
  General ability, so if you calculate, you will get the right answer.\nolinebreak
  \footnote{
    \(((421 + 531) \times 5)/7\) = \((300 + 40) \times 2\)
  }
  Checking propositional validity.

  Short term memory, names of people in a group.
  So long as group isn't too big, and names are familiar.

  Most common, parsing novel sentences.
  Take some book designed to teach reading.
  Some novel sentences, but understanding meaning.
  Somewhere on the way to The Waste Land this breaks down.
  Compositionality.

  Consider converse cases.
  Cases of reasoning where there is a necessary step or premise, and the agent lacks support.
  E.g.\ misunderstood a particular rule.
  Agent lacks support, and recognised, then lack general ability.

  Likewise, non-reasoning cases.
  Cooking.
  Experience, various recipes and styles, good dishes.
  Some general ability, mastered some skills.
  As long as novel recipe only requires those skills, expect the meal to turn out well.

  Perhaps agent may not have the skill to articulate support appealed to, but still appeal.
\end{note}

\begin{note}[Second pair of key points]
  We now turn to the remaining two key points.
  This is where things get a little more complex.
\end{note}


\begin{note}[Third key point]
  Previous key point~\ref{W:fp:S:2}, agent has propositional support for any premises and steps used when witnessing general ability.
  \ref{W:fp:S:1}, witnessing doesn't add.
  Third key point builds on~\ref{W:fp:S:1} and \ref{W:fp:S:2} given information about potential event of witnessing general ability.
  \begin{enumerate}
  \item[\ref{W:fp:S:3}] Information of a potential event of witnessing is sufficient for the agent to hold that propositional support for premises of reasoning extend to conclusion.
  \end{enumerate}

  In broad strokes, from~\ref{W:fp:S:1}, propositional support/sufficient epistemic reasons do not require reasoning.
  Therefore, if reasoning would lead to conclusion, and agent has support for premises, then agent has support for conclusion.
  Saw this with closure.

  From~\ref{W:fp:S:1}, if information is true, then attitude to antecedent condition of closure.
  Main claim is that agent does not require support for reasoning to extend attitude toward conclusion and form attitude toward consequent of closure condition.

  Here, the idea of \WR{}.
  Not strictly a propositional attitude.
  Instead, appeal to the potential event of witnessing reasoning.
  Ties attitude toward conclusion to that reasoning.
  That is, whatever those reasons are which are sufficient for propositional support, if agent does have propositional support.

  Second point is important.
  For, agent is appealing to \WR{}, hence relying on support for general ability as applied, rather than obtaining support for specific ability.

  {
    \color{red}
    {\color{green} This note needs to be cleaned up and stated in various other places.}
    Delicate.
    The agent is not obtaining support for specific ability.
    Instead, the agent is appealing to support for general ability that would be used if they were to witness the specific ability.
    Further, result is not immediately that the conclusion is true, but that the agent has propositional support for conclusion.

    Problem with support for specific ability was reasoning that otherwise the agent support would be misleading.
    Insight is that agent doesn't need to go directly to specific ability, as it may be built from elements of general ability.
    \WR{} is the key piece where the agent considers reasoning, and how the general ability interacts.
    Without witnessing, no appeal to the steps of reasoning, and support agent has for these.
  }
\end{note}

\begin{note}[Relation to closure]
  Begin by returning to closure principle for propositional support:
  \[\propsupp{\phi} \land (\phi \ientails{} \psi) \vdash \propsupp{\psi}\]
  This simply states things about propositional support.
  Closure principles, because it states that \(\psi\) is a member of the class of things that are propositionally justified.
  There's nothing about an agent's recognition in play here.

  To ease introduction of attitudes, consider an easier case.
  Knowledge.
  \[K(\phi) \land K(\phi \rightarrow \psi) \vdash K(\psi)\]
  Natural language, if agent knows that \(\phi\) and knows that \(\phi\) entails \(\psi\), then the agent knows that \(\psi\).
  Knowledge is factive.
  Note, switch to entailment, as proposition.
  So, it must (given agent's knowledge) be the case that \(\phi\) and that \(\phi\) entails \(\psi\), and hence it must be the case that \(\psi\).\nolinebreak
  \footnote{
    Variations on epistemic closure principle which do not require \(\geop{2}\).
    E.g.\ \citeauthor{Williamson:2000wx} formulates \emph{intuitive closure} as:
    \begin{quote}
      knowing \(p_{1},\dots,p_{n}\), competently deducing \(q\), and thereby coming to believe \(q\) is in general a way of coming to know \(q\).\nolinebreak
      \mbox{}\hfill\mbox{(\citeyear[117]{Williamson:2000wx})}
    \end{quote}
    Multi-premise, perhaps fine with knowledge, we restrict to single premise for the moment.

    \citeauthor{Hawthorne:2005tb}, generalisation
    \begin{quote}
      If one knows P and competently deduces Q from P, thereby coming to believe Q, while retaining one's knowledge that P, one comes to know that Q.\nolinebreak
      \mbox{}\hfill\mbox{(\citeyear[29]{Hawthorne:2005tb})}
    \end{quote}
    In terms of the formalism used:
    \[K(\phi) \land (\phi \ientails{} \psi) \Vdash K(\psi)\]

    \citeauthor{Hawthorne:2005tb}'s generalisation is important.
    Take similar restrictions to be implicit in main body.
    
  }

  Note, we're not interested in an unrestricted closure principle.
  Rather, observing that so long as some closure principle is true, then this seems to be an instance.

  Introduce a variant with propositional support.

  \[K(\propsupp{\phi}) \land K(\phi \rightarrow \psi) \vdash K(\propsupp{\psi})\]
  Natural language, if an agent knows that they have propositional support for \(\phi\), and the agent knows that \(\phi\) entails \(\psi\), then the agent knows that they have propositional support for \(\psi\).\nolinebreak
  \footnote{
    Originally in terms of belief, but as noted {\color{red} need to add}, generalises to other attitudes.
  }
  Here, reasoning as before, with the observation from~\ref{W:fp:S:1} that whatever secures knowledge of \(\phi\) provides sufficient epistemic reasons for \(\psi\), given possibility of reasoning.

  Use \(\Vdash\) to indicate permissibility of forming attitude to the right given attitudes to the left.

  \[K(\propsupp{\phi}) \land K(\phi \rightarrow \psi) \Vdash K(\propsupp{\psi})\]

  Example of difference.
  First, something standard.
  Second, knowledge of propositional support.
  Mnemonic for order of colours of the rainbow.
  Propositional support, sufficient epistemic reasons for order of colours of the rainbow.
  {
    \color{red}
    Might be easier with conditional structure and consequent.
  }

  May seem that the agent simply knows.
  Additional point in anticipation of next key point is that \(K(\propsupp{\phi}) \vdash K(\phi)\).
  Seems there's an equivalence here, as the converse certainly holds.
  Suggests that there aren't cases from perspective of attitude,  idea behind example, still, is different epistemic reasons.

  Perhaps clearer with potential event.
  If agent knows they have specific ability, then knows they have propositional support.
  However, as seen agent may then appeal to potentive entailment.
\end{note}

\begin{note}[Generalise closure]
  Return to \(\ientails{}\) and introduce some placeholders.

  \[\geop{1}(\propsupp{\phi}) \land \geop{2}(\phi \ientails{} \psi) \Vdash \geop{3}(\propsupp{\psi})\]

  Natural language, \dots
  Again, \(\Vdash\) to indicate permissibility of forming attitude to the right given attitudes to the left.

  Question is whether there are instances of \(\geop{1}\), \(\geop{2}\), and \(\geop{3}\), in parallel to \(K\).

  As with knowledge, not looking for general closure principle.
  Rather, there are cases.
\end{note}

\begin{note}[Claiming for \(\geop{1}\)]
  Talked in terms of claiming support.
  This provides instances for \(\geop{1}\).

  \[C(\propsupp{\phi}) \land \geop{2}(\phi \ientails{} \psi) \vdash \geop{3}(\propsupp{\psi})\]
  If agent claims propositional support for premises, some relation to reasoning, then some attitude toward conclusion.
\end{note}

\begin{note}[\(\geop{2}\)]
  \(\geop{2}\) is where \WR{} is important.

  From~\ref{W:fp:S:2}, plausible that the agent has support for any premises and steps following instance of general ability.

  Intuitive idea behind instance of \(\geop{2}\) is that it allows agent to appeal to premises and steps used in reasoning.

  Introduce \(W\).

  \[C(\propsupp{\phi}) \land W(\phi \ientails{} \psi) \vdash \geop{3}(\propsupp{\psi})\]

  Understanding of \(W\) is witnessing.
  Agent is committed to potential event, and hence committed to witnessing the reasoning.
  (Recall \ref{prem:ni} limits this to commitment.)
  \(W\) claim support for each premise or step of event.

  Important here is that the agent is not directly claiming support for ability, so to speak.
  Rather, endorses potential event, which reduces down to parts.
  Agent is only claiming support for parts.

  Observation is that by viewing from this perspective, agent is in a position to claim (proposition) support for parts, given understanding of propositional support.

  Consider~\ref{prem:ni} again.
  Trouble because the agent does not have the option of obtaining support for specific ability from general ability.
  The agent may not be able to do the reasoning.
  This may show that the agent does not have the general ability.
  May be misleading.
  Subtle, but important, difference is\dots that\dots agent is appealing to direct support.
  Problem with simple reasoning is that it's indirect --- the agent doesn't do anything with how the general ability extends.

  Given \(W\), then if the agent is misleading, then the trouble is same as if the agent performed the reasoning.
  There is a mistake with some premise or step.
  Important is that the agent is not appealing to not being misleading.
  Rather, the agent is appealing to use of general ability.
  Again, given \(W\) appealing to the propositional support, or sufficient epistemic reasons that the agent is in a position to claim that they have.

  Of course, if agent does not have general ability, then no witnessing.
  So, failure cases is not the same as agent reasoning with a misleading, but supported, premise or step.
  Agent may not reach conclusion.
  This may be why the agent gives up general ability when attempting to witness.
  Still, \emph{prior} to witnessing, this isn't so much of an issue.
  Given support for general ability, it is true that there's a potential event.

  Indeed, this distinguishes.
  \(W\) may fail in this way.
  As agent has not done reasoning, then may be that it is not possible for agent to reason.
  E.g.\ case of devious informer.

  However, this doesn't need to say much about how support works given \(W\).
  Return to \(K\).
  May turn out that one doesn't \(K\) that \(\phi\).
  So long as one does, the possibility of revising \(K\) doesn't show that the agent is not in a position to trace support from \(\phi\).

  {\color{red} As motivated} the role of witnessing is to apply general ability directly, so to speak.

  {
    \color{green}
    Does the agent get support for specific ability in this way?
    Arguably not, maybe, because \(W\) still has an important role.
    Then, there remains a significant puzzle about why the agent is in a position to claim support for conclusion.

    Okay, so agent falls short of support for ability because of \(W\).
    However, still gets support for conclusion?
    Well, so long as the agent is required to endorse, then so far the idea has been that the agent doesn't need to do the reasoning.

    So, \(W\) is doing \emph{something} important.
    It's something about non-voluntarism.

    Broken down and seen how the agent can't really avoid.
    Application of general ability really is supporting.
  }




  Agent is not appealing to support for general ability.
  Rather, how general ability functions when applied.
  Not support for general ability, per se, but rather support for premises and steps.

  Conflict with~\ref{denied-claim} is that the agent is not aware of what those premises and steps are.




  Why this doesn't require support.

  The important aspect of~\ref{W:fp:S:3} is that information is sufficient.
  So, information that this follows from general ability.

  For, then agent either gives up general ability, or is required to hold that they have ability.
  Of course, no support.

  So, as long as general ability, is potential event.
  However, and quite important, is that the agent is not obtaining support for specific ability/potential event on the basis that their support for general ability would be misleading.
  Rather, agent is observing that so long as it is true that there is a potential event, then support for general ability means that the agent has support they may appeal to when witnessing reasoning.

  Delicate, but the agent is not generating support for a novel proposition that they have specific ability, as would be the case with ability.
  Instead, observation is that the support they already have applies to novel proposition that conclusion is true.

  From this perspective, information is merely directing the agent as to \emph{what} follows from general ability.

  Summary of \(W\), then, is that permissible for agent to have attitude of \(W\) toward reasoning just in case support for stages.
\end{note}

\begin{note}[\(W\) is an attitude?]
  Nothing in particular rests on \(W\) as an attitude toward event of reasoning.
  If understand attitudes toward propositions in terms of attitude toward states of affairs, then fairly straightforward.
  If not, trust that there is some reformulation.
\end{note}

\begin{note}[\(\geop{3}\)]
  Finally, take \(\geop{3}\) as \(C\), in parallel with \(\geop{1}\).
  \[C(\propsupp{\phi}) \land W(\phi \ientails{} \psi) \Vdash C(\propsupp{\psi})\]
  Agent may claim to have propositional support for conclusion.
\end{note}

\begin{note}[Contraposing]
  Then, because the entailment from \(\phi\) to \(\psi\) extends support, nothing more is required.

  Consider contrapositive.
  \[\lnot C(\propsupp{\psi}) \Vdash  \lnot W(\phi \ientails{} \psi) \lor \lnot C(\propsupp{\phi})\]
  Agent may not claim that they have propositional support for \(\psi\), then either no witnessing reasoning, or may not claim that they have propositional support for \(\phi\).

  Both \(\lnot C\) and \(\lnot W\) are candidates.

  Depends on surrounding information.
  If agent is aware of required premises, then maybe \(\lnot C\).

  However, if agent is not aware of required premises, then \(\lnot C\) is tricky.
  Plausible that they are in a position to claim propositional support.
  However, unable to do the reasoning.

  Clean example is when one is stuck on a puzzle.
  It may be that one has all of the premises required to figure out the conclusion, but things break down with the potential to witness the required reasoning as missing some steps.
\end{note}

\begin{note}[Support for specific ability]
  Seems as though all of this combines to provide support for specific ability.
  For, specific ability breaks down into steps that the agent has support for.
  Yes.
  Key difference is that support isn't going via the \gen{}.
\end{note}

\newpage

\begin{note}
  Before an exam.
  Studied.
  If understand material, and instance is written, then everything needed for the answer.
  Phrased in this way, somewhat unlikely, but reassurance.
  All the student needs to do is build on their preparation.

  In first, agent doesn't have independent information to identify what propositional support is for.
  In main, agent is aware of what provides them with propositional support, and the conditional directs this.
\end{note}

\begin{note}[Conclusion first and second step]
  Idea is that the agent has is in a good position with respect to whatever premises would be used.
  Careful to phrase appropriately.
  Assuming information is true, this extends to the conclusion and so the agent has propositional support for the conclusion.
  However, not clear that the agent is in a position to hold that they have propositional support for conclusion.
\end{note}

{
  \color{red}
  \begin{note}[Access to propositional support]
    The agent does not have support that the premises support \(\phi\).
    However, the information about ability/potential event provides information about what the premises available support.
    Still, so long as there is a relation of propositional support, the agent does have propositional support for the conclusion.
  \end{note}
}

\begin{note}[Fourth key step]
  Final step is moving from attitude toward propositional support for conclusion to attitude toward conclusion.

  Given understanding of propositional support, then endorse the following:
  \[B(\propsupp{\phi}) \vdash B(\phi)\]

  Contraposition is more clearly true:
  \[B(\phi) \vdash B(\propsupp{\phi})\]
  If believe, then sufficient epistemic reasons.

  Biconditional.
  Seem inconsistent to hold that one has sufficient epistemic reasons to believe that \(\phi\) and that one does not believe \(\phi\).

  In part, turns on sufficient epistemic reasons.
  Roughly, on our understanding, no other attitude toward \(\phi\) on the belief spectrum would be supported by reasons.
  Potentially some objections, but these are puzzling.

  Bracket objections.

  Importance of final step here is why this holds.

  State that it is the belief that one has propositional support for the conclusion.
  This would be in line with~\ref{denied-claim}.
  This then traces back.

  However, following propositional support.
  Significant observation was no additional support is added.
  Hence, it seems appealing to propositional support is sufficient.

  Fail to see why the belief, other than antecedent commitment to~\ref{denied-claim}\dots
\end{note}

\begin{note}[EEE]
  Clearest case to be made is thinking in terms of evidence of evidence being evidence.
  Saw this when considering \AR{}.
  However, this would be to take belief as evidence?
\end{note}

\begin{note}[Objection]
  Objection here is that this reduces.
  One has belief of propositional support and acceptance.
  These two things are doing the work.
  So, have something in line with~\ref{denied-claim}.
  Mistake.
  Understanding of attitude to conditional is that there's no support involved.
  So, fail to see a clear account of why support is obtained from.
\end{note}

\begin{note}[Doxastic support?]
  Doxastic support adds to conditions to propositional support.
  Attitude, and relation of that attitude to sufficient epistemic reasons.
  Understood as a basing requirement.

  See in Chapter~\ref{cha:access} that the agent does not (plausibly) have doxastic support, as various accounts of basic requirements are in line with\ref{denied-claim}.

  In part, expected.
  Intuitively, agent is in distinct position from were they to establish doxastic support.

  Question is whether the agent may still use propositional support.
\end{note}

\begin{note}[First pass]
  Whatever it is that doxastic support and basing is, agent establishes this in potential event when witnessing.

  Plausibility here is that propositional and doxastic support do not different with respect to support.
  Rather, differ with respect to relation between agent and support.
\end{note}

\begin{note}[Trace link in examples given]
  
\end{note}

\begin{figure}[h!]
  \centering
  \begin{tikzpicture}
    \def\iHeight{2}
    \node at (4,\iHeight) {Information};
    \node at (0,0) {Premises};
    \node at (8,0) {Conclusion};
    \draw[->] (0,0) -- (8,0);
    \draw[->] (4,\iHeight) -- (8,0);
    \draw[->] (4,\iHeight) -- (0,0);
    \draw[->] (4,\iHeight) -- (4,0);
    \draw[green, dashed] (0,0) sin (1,.5) cos (2,0) sin (3,-.5) cos (4,0) sin (5,.5) cos (6,0) sin (7,-.5) cos (8,0);
  \end{tikzpicture}
  \caption{Sketch}
\end{figure}

\begin{note}[Expand tracking example]
  Consider tracking example.
  Here, on the relevant interpretation, the information provided to the novice allowed the novice to establish support relation.
  Understood here as providing information about to establish an appropriate connexion.
  And, given this information the novice goes ahead and establishes the (appropriate) connexion.

  Vary the example a little.
  Suppose the novice is provided with a book containing the information provided by the informer.
  Given understanding of base case, understand that the book is going to detail how to establish an appropriate connexion.
  Then, the novice reads the book, and fills in the detail.

  After reading the book, agent has doxastic support.

  Before reading the book, a more complex attitude.
  Conclusion on the basis of propositional support the novice has, and the result of establishing an (appropriate) connexion via the relevant contents of the book.
\end{note}

\begin{note}[Avoids problematic example]
  See how a problematic variant of the tracking example is avoided.
  Holmes and Watson.
  Holmes deduces, Watson looks on.
  This is one of those logic puzzles.
  It's the knave, or whatever.
  If it was just propositional support, then we'd be in some trouble.
  However, it's also the possibility of obtaining doxastic support.
  Watson lacks this, so don't get to claim.

  By contrast, if equals, then (Sherlock's brother) could claim, as they've observed Holmes and may do the reasoning.

  Maybe improve in which there's some initial evidence that one of the knights/knaves is untrustworthy, e.g. a criminal record.
  So, Watson would be fine believing this, that's all the evidence they have, without additional testimony.
  However, the brother couldn't.
\end{note}

\begin{note}[New example]
  Consider an abbreviated proof.
  Look at the premises and conclusion.
  So, have propositional support.
  Quite tired, so fail to see how the conclusion is obtained from premises.

  On the one hand, this has been reviewed, etc.\ so route to doxastic support.
  However, given understanding of material, then after some sleep and a cup of coffee, you'll recreate the reasoning in detail.

  Hence, hold the conclusion on the basis of premises, with a \future{} representing the appropriate connexion to be filled in.
\end{note}

\begin{note}[Existential]
  Support is flowing from the premises to the conclusion.
  It is not from ability.

  Difference is clearest when considering the instance of \AR{} in which the agent appealed to the attribute of having propositional support for the conclusion.
  In the case of \AR{} the agent appeals to having \emph{propositional support for the conclusion}.

  Here, the agent is appealing to \emph{that} propositional support, and `acceptance' that the propositional support leads to the conclusion.

  Subtle difference between appealing to the proposition that one has support for \(\phi\) and appealing to \(\psi\) which in turn supports \(\phi\).
\end{note}

\begin{note}[Contrast with \ref{denied-claim}]
  Noted that \ref{denied-claim} is understood with respect to doxastic, and here's where the incompatibility comes in.
  For, \ref{denied-claim} holds that a \future{} is no good.
\end{note}

\begin{note}[Key difference]
  The key difference between \AR{} and \WR{} is that with \WR{} the agent does not rely on ability/potential event for support.
  Rather, the agent relies on the support that they have for the premises which is independent of the ability information.

  Information in \WR{} does not --- and is not used to --- support the conclusion.
  Rather, it is the propositional support the agent has that does the work.
\end{note}

\begin{note}[Main motivation]
  Before turning to difficulties, there are a handful of things to say in favour of the first pass.
  Notably, that it provides a fairly clean expression of the core idea of \WR{}.
  Reducing to propositional support allows agent to appeal to reasons in support that they have not used.
  This is to some extend captured by propositional support.

  Two main sticking points.
  \begin{itemize}
  \item Weak attitude to relation between premises and conclusion --- one may require more.
  \item That the agent takes the propositional support to do the work.
    There remains some room to argue that the attitude toward propositional support for premises and attitude toward information are key.
    
  \end{itemize}
\end{note}

\subsubsection{Difficulty with first pass}
\label{sec:diff-with-first}

\begin{note}[Overview]
  The first pass assumed something about propositional support.
  That there is propositional support whether or not the agent does the reasoning.

  Whether or not agree with assumption, consider a pair of contrasting accounts of propositional support, and see how this assumption is important.

  After so doing, consider whether we can avoid assumption made.
\end{note}

\begin{note}[Different view of propositional]
  For example, \citeauthor{Turri:2010aa} argues for~\ref{Turri:PJ}.
  \begin{quote}
    \begin{enumerate}[label=(\textbf{PJ}), ref=(\textbf{PJ})]
    \item\label{Turri:PJ} Necessarily, for all \emph{S}, \emph{p}, and \emph{t}, if \emph{p} is propositionally justified for \emph{S} at \emph{t}, then p\emph{} is propositionally justified for \emph{S} at \emph{t} \textsc{because} \emph{S} currently possesses at least one means of coming to believe \emph{p} such that, were \emph{S} to believe \emph{p} in one of those ways, \emph{S}'s belief would thereby be doxastically justified.
    \end{enumerate}
  \end{quote}
  If so, then the availability of propositional support is secured by the potential event of reasoning.
  Hence, it seems that this reduces to a case of \AR{}.
  For, if the agent does not appeal to support for witnessing event, then the agent does not have grounds for holding that they have support for conclusion.
  It is not sufficient to observe that the agent has support so long as information about potential holds.
  Instead, the potential is doing the work in providing the agent with propositional support.

  Of course, \citeauthor{Turri:2010aa} doesn't require that the agent be aware.
  But this doesn't solve the problem.
  The issue is that the two instances of support coincide.

  It's somewhat straightforward to recast (\emph{PJ}) as `because the agent has the ability'.
  Indeed, \citeauthor{Turri:2010aa} speculates that propositional support is governed by abilities.
  Though, the exact relation between \citeauthor{Turri:2010aa}'s constraints and are use of ability is unclear.
  At the very least, \citeauthor{Turri:2010aa}'s seems weaker, as we require a sufficient collection of preconditions to be satisfied.
\end{note}

\begin{note}[Note]
  The difficulty is that if \citeauthor{Turri:2010aa} is followed, then there's no support to do the work.
  This does not mean that the premises are unavailable.
  Instead, the premises are inert.
\end{note}

\begin{note}[Same from \citeauthor{Goldman:1979ui}]
  \citeauthor{Goldman:1979ui} proposes \emph{ex ante} justification.
  \begin{quote}
    Person \emph{S} is \emph{ex ante} justified in believing \emph{p} at \emph{t} if and only if there is a reliable belief forming operation available to \emph{S} which is such that if \emph{S} applied that operation to his total cognitive state at \emph{t}, \emph{S} would believe \emph{p} at \emph{t}-plus-delta (for a suitably small delta) and that belief would be \emph{ex post} justified.\nolinebreak
    \mbox{}\hfill\mbox{(\citeauthor[21]{Goldman:1979ui})}
  \end{quote}
  Note that \citeauthor{Goldman:1979ui} talks of the `total cognitive state' of the agent at \emph{t}-plus-delta.
  It seems clear that the cognitive state of the agent at \emph{t} is relevant on in so far as the delta in \emph{t}-plus-delta is suitably small.
\end{note}

\begin{note}[Example?]
  However, following present line of thought, propositional support is a derived relation.
  It is a relation derived from some `attribute'.

  Clearest to see by recalling reasoning above.
  Project from event.
\end{note}

\begin{note}[Basic point]
  The observation here is that these accounts may taken as trouble for \WR{}, and in turn as partial support for \AR{}.
  Partial support for \AR{} as these accounts of propositional support are of propositional rather than doxastic support, and \AR{} is concerned with doxastic support.
  So, need to be furnished to show that an agent has the option of obtaining support for the conclusion of the reasoning that they are able to perform.

  It seems rather that this is an objection to the basic idea of \WR{}.
\end{note}

\begin{note}[This is trouble from \WR{}/Something about evidential relations]
  Not that these come easy.

  Basic understanding of propositional support.
  Seems support is a relation between premises and conclusion, or base and proposition.

  Common to talk in terms of `\emph{p} is propositional justified for \emph{S}'.
  Here, though, expanded.
  Sufficient reasons to believe that \emph{p}, and \emph{S} has those reasons.

  And, \textcite{Silva:2020aa} highlights troubles with evidential relations, and epistemic reasons.

  Similarly, because \emph{S} has ability, \emph{S} ought not to hold that \dots
\end{note}

\begin{note}[Bracketing possible issue]
  A possible lesson to be drawn from \citeauthor{Goldman:1979ui} is that there is no clear relation of support between premises and conclusion.
  Don't make sense to subdivide the agent's total cognitive state, or separate the means by which the agent may come to believe \emph{p}.

  This is the foundation of a challenge to~\ref{prem:bP}.

  However, this isn't too much of a concern.
  Important for our purposes is preconditions.
  Talk of premises, is intuitive, what we're after, though, is some way of obtaining support which doesn't reduce to \AR{}.
\end{note}

{
  \begin{note}[The problem]
    The problem here is somewhat difficult.
    Following \citeauthor{Turri:2010aa}, it is the case that the agent has propositional support.
    However, the issue is whether the agent has the option of using the propositional support in order to obtain a kind of doxastic support.
    And, arguably this would lead to some conflict with~\ref{prem:ni}.

    However, this isn't quite right.
    For, the relevant issue was that the agent isn't able to obtain support from general ability.
    This doesn't prevent the agent obtaining support from propositional support that's granted.

    Still, there does seem to be an issue.
    For, with the first pass, the agent has propositional support whether or not they have doxastic support.
    The basis for propositional support is general ability + potentive entailment.

    Here, why does the agent have propositional support?
    There's a witnessing event.
    Is the agent is a position to hold that they have propositional support?
    Well, the agent isn't in a position to use ability as a step in support.
    Seems like a conflict with~\ref{prem:ni}.

    The difference is that the propositional support doesn't depend on the agent doing anything.
    This is a difference with \AR{}.
    For, with \AR{} the agent is using whatever support they have for ability.
    Here, ability grants propositional support.

    Basic point
    \begin{itemize}
    \item These accounts of propositional support mirror \AR{}.
      The difference is that \AR{} deals with a sort of doxastic support, while these concern propositional support.
    \end{itemize}
    And the first pass

    It's like, there's some doxastic support for propositional support.
    Isn't this at the core of the first pass?
    This does create some difficulty, as there's a way if the agent relies on general ability, but not if specific ability is required.

    Built in to the first pass is the idea that the agent has a good relation to the basis.
    If the relation of support is independent of doxastic support, then there's a fairly straightforward account of why this is the case.
    For, the agent has good doxastic support for their general ability, whatever that amounts to.
  \end{note}

  \begin{note}[Still thinking]
    Core idea is that on the first pass, the agent doesn't need any additional information in order for the premises to be propositional support for \(\phi\).
    Whatever it is that `directs' the propositional support is something other than the reasoning that the agent is able to perform.

    This is not so on G\&T.
    For, on G\&T, the propositional support to be propositional support for the conclusion, there's an additional component of what may be done with the support/premises.

    Either way, the agent doesn't have access to something that establishes that the premises are propositional support for the conclusion.
    The difference is whether or not this matters?

    Information about entailment, agent doesn't obtain support for this.
    However, the agent doesn't require support, on the basic understanding.
    There's no further aspect to propositional support before the availability of the relevant epistemic reasons.

    The agent doesn't have support that these are sufficient epistemic reasons for \(\phi\).

    So, granting entailment, have propositional support.
    Fits in the sort of prop -> conclusion schema.

    However, with G\&T, propositional support only by granting entailment.

    The entailment, and that there's ability, is required to get propositional support.
  \end{note}
}

{
  \color{green}
  \begin{note}[Developing the objection]
    This doesn't show there's anything particularly problematic with the first pass.
    It requires a particular understanding of propositional support, but so long as G\&T isn't true, then there's no problem.

    This is something of a technicality.
    For sure, this works.
    And, there's something of an argument for why G\&T don't hold up.
    For G\&T would require the agent to obtain support for ability.

    However, there's no argument for the understanding of propositional support unless the first pass is unique.

    Provides a solution which is somewhat consistent, but that's about it.

    Further, G\&T are in line with the basic idea.
    That is, propositional support in the same way that the agent seems to get support.
    The issue is that we're arguing that the agent has some access to the propositional support.
    So, it's a constraint motivated by a solution adopted without additional argument for why that solution needs to be adopted.

    The issue, then, is that this isn't illuminating.
    Fit various pieces together, but there's no clear understanding of why it makes sense to fit the pieces together in this way.

    This might be all that one could hope for, but perhaps we can do better.
  \end{note}
}

\begin{note}[Summarising]
  These issues with the first pass do not suggest that the first pass is false.
  Rather, the methodological concerns raised suggest that the reasons are somewhat lacking.
  If you're convinced, then go ahead --- I think there is something to be said.
  The second pass will be compatible with, but independent of, the first.
  Revisit this after the second pass is complete.
\end{note}

\subsubsection{Second pass: \future{} support}
\label{sec:second-pass:-futures}

\begin{note}[Following from problem]
  Noted G\&T.

  For, the potential event does the relevant work.
  With G\&T, this is used to identify propositional support.

  Raised a direct problem from first pass.
  In short, due to constraints imposed, agent isn't in a position to hold that they have support for conclusion.
  Led to a broader criticism of the first pass.

  Core insight of G\&T, though, is that witnessing may be put to work.
  As seen {\color{red} need to add} there's no way to figure out how the proposals really work without looking at potential events.
  At least for \citeauthor{Turri:2010aa}, the main claim is the priority of doxastic support.

  Question is whether there's a variation of G\&T where information from potentive entailment allows the agent to (`directly') claim support/base\dots
\end{note}

\begin{note}[Difference to G\&T]
  Start with differences\dots as these are important for the proposal.

  Difference between current case and G\&T is information about potential event.

  Suggest that this allows agent to defer reasoning while obtaining support.

  Allows the agent to form an attitude toward the conclusion, such that witnessing event in which agent establishes support is \emph{deferred}.
\end{note}

\begin{note}[Deferring]
  So, the intuition here is that one takes a standard case of reasoning.
  Two things.
  Claiming a basing relation.
  Establishing the basing relation.

  Often come together.
  Separate these.

  View as two different tasks.
  Understood this way, these tasks may be separated.

  Agent claims a basing relation and defers establishing.\nolinebreak
  \footnote{
    Note here on other use of deferring.
    Used when talking about infinitivism.
    Common idea, but the current interest is compatible with finitism/well-foundedness.
  }
  Information is used to maintain that establishing is deferred.
  (And not, for example, wished for.)

  Issue here is support.

  Basic motivation is that so long as the agent has the resources, then so long as the agent appeals to those resources, the agent obtains support (of a kind).
  This is in keeping with the first pass.
  Difference is that we don't reduce to resources (this is roughly how propositional support is understood).
  Rather, whatever those resources are, support is understood in terms of deference.
  Support is just what would be witnessed.

  In a slogan, the agent defers, rather than refers to that support.

  Agent defers.
  Introduce an intermediary.
  A \future{}.
  \future{} does the job of supporting conclusion.
  Does this job by being a placeholder, in effect.
  Unique thing about a future is that it doesn't matter when the details are filled in.
  Does the job of providing support because there's a guarantee that it may be filled in.

  Important here is that the guarantee that it may be filled in is not the source of support.
  The guarantee allows things to work/for this to be permissible.

  Agent sets up \future{}, takes support, defers establishing.

  Understand the support provided from an external perspective by filling it in.
  Here, parallel to G\&T.

  In relation to G\&T, the distinction is in the agent appealing to the same thing as what provides them with propositional support.
  Similar to the first pass, amounts to the agent obtaining support for propositional support, roughly.
  However, here, the support for propositional support is just the source of propositional support.

  Key, again, is that the agent is not appeal to support they have that there is such a potential event.
  Rather, the agent is appealing to the relation of support that would be established by witnessing the potential event.

  This is the understanding of deferral.

  Intuition for why this provides support is that it is in certain respects functionally equivalent to propositional support.
  One both accounts of propositional support, agent has support.
  Common way of understanding things.

  Agent defers transforming that propositional support into doxastic support.
  However, that the agent is so deferring allows the agent to appeal.
  Here, it is the deference that is doing the work.
  If called for, then provide the relevant support.

  The idea, then, is that deferred support functions in the suitably similar ways.
  It is a \emph{kind} of support that the agent may appeal to.
  Prefixing an adjective is difficult.
  Fake passport won't let someone board a plane.
  Likewise for corrected typogrophical mistake.
  Small elephant is an elephant, and Deferred compensation is compensation.
\end{note}


\begin{note}[Examples of deferring]
  Separation of this kind of common.
  For example, purchasing and paying.
  Purchase a car, but with a loan.
  Have not, in some sense, payed for the car.

  With the loan analogy, so kind of guarantee is typically required.
  Analogy extends in this respect.
  Agent needs some kind of guarantee that they may establish support.
  This is the role of the information.

  As noted, the agent is in a position to use the information, but not derive support from the information.
  Here, the agent uses the information to set up a relation of support, and the information simultaneously functions as a guarantee for deferred establishment, or filling in.

  Deferred shipment?

  Another example is with language.
  Referring term, but assigning reference is deferred.
  Not sure how to design an example, though.
\end{note}


\begin{note}[After examples]
  Key idea, then, is that relation is created, witnessing is deferred.

  First pass, primary worry was that it wasn't particularly illuminating.
  It seems to me that second pass fares better.
  See the information as providing a guarantee.
  Motivated by understanding what the information (if true) entails.

  Independent of any particular account of propositional support.
  In contrast to the first pass, then, the agent is not appealing to support that they already have for propositional support, so to speak.
  Idea of propositional support continues to inform understanding of the support the agent has, but this is because the two kinds of support share the common feature that the agent has not witnessed any demonstration.

  First pass relied on this idea that the agent was in a position to form a belief that they had propositional support.
  Here, what is doing the work is the opportunity to provide (doxastic) support.

  What we miss from the first pass is an argument (assuming information is true) that the agent has propositional support.
  However, we retain an account of why it makes (at least some) sense for the agent to claim support.

  One may continue to hold that independent propositional support has a role, and is part of the explanation.
  For example, some story about support having propositional support.
  However, this is a non-essential component of the proposal.

  A \future{} is a kind of token that the agent may point to, whose availability is governed by sufficient guarantee.
  And, this provides a kind of support.
\end{note}

\begin{note}[Novelty]
  The novelty of the proposal is \dots

  the split between claiming and establishing, and deferring establishing
  support

  The split simply requires developing (conceptual) vocabulary.
  Nothing in particular follows from deferring if it never occurs.
  Support is the substantive component.
  Certain things do follow.
  However, by itself there is no incompatiblity with~\ref{denied-claim}.
  The incompatiblity arises from application to these cases.

  Useful observation, as can introduce concepts with compatible examples.
  Do so with the problem of forgotten evidence.
  Offers some useful distinctions and predictions.

  Turn to extending into the future.
  So long as we've been careful, this doesn't follow from anything claimed.
  However, closed the gap.
\end{note}

\begin{note}[Figures]
  \begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
      \centering
      \begin{tikzpicture}[->, >=stealth', node distance=0cm, every text node part/.style={align=center}]
        \node [] (c) at (0,0) {};
        \node [] (d) at (-3,0) {};
        \node [] (e) at (3,0) {};
        \node [] (f) at (0,-2.1) {};

        \node (A) at (0,-.1) {P};
        \node (C) at (0,-2) {C};

        \draw [->, xshift=4] (0,-.35) to  node[right] {} (0,-1.75);
      \end{tikzpicture}
      \caption{\AR{}}
      \label{fig:AR:support}
    \end{subfigure}
    % \hfill
    \begin{subfigure}{.5\textwidth}
      \centering
      \begin{tikzpicture}[>=stealth', node distance=0cm, every text node part/.style={align=center}]
        \node [] (c) at (0,0) {};
        \node [] (d) at (-3,0) {};
        \node [] (e) at (3,0) {};
        \node [] (f) at (0,-2.1) {};

        \node (A) at (0,-.1) {P};
        \node (C) at (0,-2) {C};

        \draw (-.1,-1.8) -- (-.3,-1.8) -- (-.3,0) -- (.3,0) -- (.3,-1.8) -- (.1,-1.8);

        \draw [->, xshift=4] (0,-.35) to  node[right] {} (0,-1.75);
      \end{tikzpicture}
      \caption{\AR{}}
      \label{fig:AR:support}
    \end{subfigure}
    \caption{Relations of support for \AR{} and \WR{}}
    \label{fig:ARandWR:support}
  \end{figure}
\end{note}


\begin{note}
  First part.
  Reasoning as a function.
  Allows one to abstract and introduce a \future{}.

  \future{} gets paired with a potential.
  Fulfil \future{} just in case true that potential.

  Introduced in terms of our use case.
  Fairly general.
  Use from premises instead.

  Parallel to quantifiers.
  Here, get truth of existential by possibility of updating assignment function where \(x\) is turned into a constant, effectively.
  Could also take a distinct understanding of a variable.
  Benefits to having two quantifiers, but quite possible to rewrite rules in this way.
  Interpretation where \(x\) is something between a variable and a constant.

  \future{} works the same, but slightly more complex.
  \future{} is introduced with background potential.
  Then, updated when potential is witnessed.

\end{note}




\newpage

\begin{note}[\future{}]
  Suggestion is to introduce idea of a \future{}.

  Understanding of doxastic support is appropriate connexion.
  Information about ability means that appropriate connexion may be established.
  A \future{} stands in place of the relation, it fixes that the attitude is connected to premises, etc.
  So, whatever the appropriate connexion would be, any resolution of the \future{} will satisfy that connexion, and the information about ability (in part) allows the agent to be confident that they may fulfil the \future{}.
\end{note}

\newpage


\begin{note}[Starting out the problem of forgotten evidence]
  Goldman's Problem of Forgotten Evidence.

  \begin{quote}
    Many justified beliefs are ones for which an agent once had adequate evidence that she subsequently forgot. At the time of epistemic appraisal, she no longer possesses adequate evidence that is retrievable from memory.
  \end{quote}

  Here, interest in the problem is for what \citeauthor{Goldman:2011vn} terms `preservative memory':
  \begin{quote}
    Preservative memory does not create or generate justifiedness `from scratch', but instead transmits a belief's justifiedness (or unjustifiedness) from one time to a later time.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[259--260]{Goldman:2011vn})}
  \end{quote}
  Time shifted instance of cases we're interested in, where agent has done the reasoning at some point in the past, and has information about result of reasoning on this basis.

  \begin{quote}
    People frequently fail to recall their original sources of evidence for things they know or justiﬁably believe.
    First, they often don’t have memory-based beliefs about their original sources.
    [Second] they rarely have memory experiences of speciﬁc perceptual episodes (what psychologists call `episodic' memories) in which they were exposed to relevant observational evidence.
    It is extremely implausible to claim that for every moment at which a justiﬁed belief is stored in your mind, you undergo an episodic memory experience of one or more past (perceptual) experiences that constituted your evidence.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[266--267]{Goldman:2011vn})}
  \end{quote}

  Here, preservative memory transmits.
  Example of way I'm understanding this by a conditional.
  Takes a lot of steps to reason from A to B.
  \(A \rightarrow B\) as a preservative memory.

  Goldman presents this against (particular kind of) internalism.
  But this isn't quite right.
  Particular kind of internalism.
  It may be that all internalists hold this synchronosity requirement, but I'm not clear on why this needs to be the case.
  Not so much our interest.
  \cite{Korcz:2019tl} sketches out the general response from internalist lines.

  Of interest here is that this remains compatible with the basic idea of epistemic debt.
  Remains clear that the agent requires resources to re-establish the relevant beliefs.
  So, we're not assuming anything strong.

  Perhaps better to frame this as forgotten basis.
\end{note}

\begin{note}[Substantial premise?]
  The substantial premise here is that evidence of interest may go beyond what one has at a particular time.
  This is substantial, but consistent with~\ref{denied-claim}.
  So, granting this does not sneak in an assumption against~\ref{denied-claim}.
\end{note}

\begin{note}[Example: Lost]
  Running.
  Note down times in a book.
  End of year, note fastest time.
  Form belief.
  Accuracy of notebook.
  Time passes, remember speed, but have forgotten evidence.
  No way to recover evidence.

  Might still hold memory does the job, clear this is a different basis.
\end{note}

\begin{note}[Example: Regained]
  Proving theorem.
  Write down.
  Hold theorem to be true.
  Forget proof.
  Paper is destroyed.
  Need to reprove.

  Here, there's something to be done.
  Problem to be solved like any other, but understand what the solution is.
  And, measure of the resources required.
\end{note}

\begin{note}[~\ref{denied-claim}]
  The kind of considerations here are compatible with~\ref{denied-claim}, as the agent has (at some point in the past) reasoned from premises to conclusion.
\end{note}

\begin{note}[Difference between scenarios?]
  Built in difference between these two cases.
  Does this make a difference to support?

  It seems there is some difference.
  Going via `why' questions.
  Suspect that it is plausible that one need answer with memory in the first, but not the second.
  Indeed, seems puzzling for the second.
  Returns to what is now a running theme, which is that proofs don't seem to work if testimony is required.
  Hence, if I'm relying on memory, seems analogous to testimony, and it doesn't seem I can hold on the basis of a premises (and proof).
  
\end{note}



\begin{note}[Coffee]
  First observation is that there's an understanding of work to be done.
  Second is that in the memory case, the agent has information about what that work would be.

  Add to this the idea that the agent retains support.

  On \citeauthor{Goldman:2011vn}'s view, this is because preservative memory is `a cognitive belief-retaining process that is able to transmit justiﬁedness from an earlier to a later time' (\citeyear[261]{Goldman:2011vn}).
  Here, original evidence does the work.

  However, additional observation is that the agent has the resources to (re-)establish.
  Or, there is a potentive event in which agent establishes \dots
  This provides a distinction between the two cases.

  Further, we find a difference between a difficult case.

  This is the coffee addict.

  To the extent Joe would do well when (re)establishing, it seems we're good.

  Here we do get something different from the first pass.
  For, propositional support would remain the same.
  Instead, it's that the potential reasoning would work out well given revisions to Joe that does the work.
  This isn't accounted for by the presence of propositional support.
\end{note}


\begin{note}[Sketch]
  Provides some understanding of what is at issue.
  Epistemic debt, in the sense of resources required to (re)base theorem.
  To what extent this matters, in general, is a distinct question.
  Terminology may seem leading, but memory is derivative in these types of cases.
  Something else is doing the work.

  Important, in the sense that proposition is held on some basis.
  

\end{note}



{
  \color{red}
  \begin{note}[Intuition: messages]
    Intuitive way to understand is in terms of messages.
    The agent creates an envelope with an address to the relation of support.
    This envelope is passed forward.
    At some point, when the agent has the time or resources, the agent establishes the relation of support.
    This information is written down, placed in the envelope, and is sent.

    Want to send the letter.
  \end{note}

  \begin{note}[Card example]
    Give receiver a card, no funds.
    Receiver won't use the card before \(t\).
    Add funds before \(t\).

    But this just is a credit card, in a sense.
    Pay now, with security of salary arriving before credit needs to be paid.

    So, this is debt, or a promise.
  \end{note}
}

{
  \begin{note}[Notes]
    On the revised version of the first pass (to be completed) there is no need to deal with the idea of a \future{}, as witnessing is there to explain the way in which the `entailment' works.
    The second pass, then, is where the idea of a \future{} is introduced.

    The agent is not extending propositional support that is already available to the agent.
    Instead, we've got something that's really asynchronous.
  \end{note}

}

\begin{note}[Is this only surface deep?]
  Introduced the idea of a \future{}.
  Allowed an agent to establish doxastic support on basis of `pre-existing' propositional support.

  The primary problem with the first pass in terms of propositional support stems from the possibilities of reducing propositional support to doxastic support.
  Hence, if reduction, then the understanding of \WR{} in terms of propositional support reduces to an instance of \AR{} --- support for premises that the agent appeals to just is the support the agent has for ability, or potential event in which agent witness the relevant action.

  Due to role of propositional support, then, any variation on the basic idea will inherit this issue.
  Tentatively, then, \WR{} requires a particular understanding of propositional support.

  Note, this is only a problem for one part of the first pass.
  Do not have the option of relying on pre-existing support relation.

  That the premises must stand in an existing support relation may be challenged.

  We have already seen that it is plausible that any support obtained prior to witnessing the reasoning is distinct from the support that would be obtain by witnessing the reasoning.

  Suggestion is that support flows through `\future{}' relation of support.
  Avoids propositional support.
  Additional benefits.
\end{note}

\begin{note}[Support]
  Well, the point here is that the support relation may be considered with an reference that has not yet been fixed.

  So, instead of taking a `pre-existing' support relation, as in the case of propositional support, obtain support because the support established in potential event may be `brought forward' by establishing premises and relation whose referent is `deferred'.

  The novelty here is that support transmits through `deferred' support.
\end{note}

\begin{note}[Asynchronous]
  Intuitively, this is asynchronous.
  The agent establishes relation of support given information.
  Then, at some other times details exactly what the relation of support is.
  The unique thing in these cases is that the agent has information about what the result of the deferred detailing is, and thus has the option of establishing a relation of support to be filled in.

  Always in terms of potential witnessing event.
  Information the agent has grants witnessing event.
  Preserved under variation of premises, so long as potential event remains.

  Contrast to propositional support, which did not require anything asynchronous.
\end{note}

\begin{note}[Promises]
  Introduced in \textcite{Liskov:1988vo}.
  Decouple process of establishing relation support, and detailed what the relation of support is.

  Information that the agent has the ability, or that there is a potential event, is used to create a promise.
  However, support is distinct from this.
\end{note}

\begin{note}[The really important thing]
  Support is flowing from the premises to the conclusion.
  It is not from ability.

  If propositional support that does not reduce to ability, then no need to take this as a primitive.
  If not, then perhaps.
\end{note}

\begin{note}[Why does the agent obtain support?]
  A \future{} is something of a primitive.
  And support is very general.
  So, not really possible to work from some more basic premises.

  Instead, consider it a hybrid of the two types of propositional support considered.
  Like general propositional support, holds whether or not agent has done reasoning.
  Like \citeauthor{Goldman:1979ui} etc.\ potential events inform.

  Not assuming propositional support.
  Or, assuming that information about potential event may not provide information about pre-existing relation of support.
  So, where does support come from?

  Well, we've got a \future{}.
  Associated promise.
  The promise is not providing support.

  What is added is specification of how agent obtains support for conclusion.

  The potential event, then, ensures that support may be obtained.

  Support for conclusion because potential event provides sufficient information guarantee relation of support may be established.
  What remains is fixing the specifics.

  The support for the conclusion just is the support that the agent would obtain from witnessing.
  The thing is that the reasoning part is the only thing that's missing.
  It's the details that are deferred.
  I.e.\ asynchronous.

  Illustration with standard case, then cutting a pasting for a different temporal order.
\end{note}

\begin{note}[Different from strategies/plans]
  With a \future{} comes a potential event, something to be done.
  However, this is distinct from a strategy or a plan, which is a representation of something to be done.
  That is, a \future{} is \emph{not} a plan.
  A \future{} is simply a placeholder.
\end{note}

\begin{note}[Social parallels]
  Relationship between inter-personal and intra-personal agency.

  Difficulty with inter-personal as testimony.
  However, have noted from \citeauthor{Easwaran:2009tm} that certain cases information about entailment and support come apart.

  This relates to `buck-passing' (\citeyear{Baker:2018aa})
  \textcite{Baker:2018aa} suggest `strong buck-passing'

  \begin{quote}
    \textbf{Strong B-P:} When challenged to produce the evidence that justifies her belief that p, A can acknowledge that she is unable to do so by herself, without help from her source, without thereby undermining her claim to know that p.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[8]{Baker:2018aa})}
  \end{quote}
  \citeauthor{Baker:2018aa} don't directly argue for strong buck-passing.
  Instead, suggest that it has certain advantages given independent commitments regarding testimony.

  Kind of considerations that motivate \citeauthor{Easwaran:2009tm}'s view on transferability suggest plausibility of buck-passing.
  Place as intermediary between two skilled mathematicians.
  Intermediary will pass the buck to presenter when questioned by agent.
  For, proof is transferable.
  And, intuitively does so because testimony is not required.

  The agent then doesn't seem to be in the same position.
\end{note}

\begin{note}[Other cases]
  Thinking back to the tracking case may be helpful.
  In the case, information allowed the agent to establish (doxastic) relation of support.

  If propositional support doesn't work as expected, then prior the agent did not have propositional support.
  (This is a plausible reading of \citeauthor{Turri:2010aa}'s remarks on the more fundamental stuff that goes on with support, though could be avoided.)

  The difference is that the information is restricted in the case of interest.
  But the \future{} \emph{functions} in an analogous way.
  It just doesn't carry (sufficient) information about the relation.
\end{note}


\begin{note}[How support works]
  In the case of reasoning, the result will be that the agent has information about premises.
  Here, it is important to note that the agent has `propositional' support for the premises, independent of the ability information.
  So, the agent does not need to appeal to the existence of the event as a premise in obtaining support for the conclusion.
  The only relevant support the agent has is the support for the premises.
\end{note}

\begin{note}[Similar applications of the basic idea]
  Introduce idea that this is something of a placeholder.
  Perhaps use the example from names with an as yet unidentified reference to provide additional motivation.

  The idea is similar in principle.
  There is someone out there in the world.
  Just as there is support that the agent may use.
  So, the remaining task is to fix the interpretation of the name.
  Likewise, the remaining task for the agent is to witness the relation of support.

  In both cases, establishing the additional stuff is useful.
  Foremost, resolves the possibility that the `\future{}' may not be resolved.
  And, other minor benefits in terms of further information.
\end{note}

\begin{note}[Giving up on synchronous support]
  This is something of a cost.
  Cost captured in large part by~\ref{denied-claim}.

  Difficult.
  For, if basic understanding of propositional support, then still require something to explain how the agent transforms this to doxastic support.

  Still, two plausible pictures.
  Pre-existing propositional support.
  Support obtained through use of a \future{}.
\end{note}

\begin{note}[Upshot]
  Main upshot is relation of support.

  One nice upshot is that there is a clear link between the support obtained prior to reasoning, and the support obtained by reasoning.
  It's filling in the deferred reasoning.

  May expand.
  For example, with a promise to resolve the support relation.

  Another upshot is that ???
\end{note}


\subsubsection{Generating potentive inference and \future{}}
\label{sec:generaling-future}

\begin{note}[Idea]
  Here, setting up for weakness of will.
  Idea is that second pass doesn't require the agent to `have' support already.
  This means that one may take a generalisation of potentive inference which allows for some incoming information, etc. and apply the idea of a \future{} to get something much more general, so long as the relevant guarantee is in place.
\end{note}


\subsection{Distinction between \AR{} and \WR{}}
\label{sec:dist-betw-ar}

\begin{note}[Overview]
  The important difference is what supports the conclusion.

  Here, we suggest that further differences depend on additional commitments.
\end{note}


\begin{note}[Key Issue]
  The key issue is whether the agent obtains support for all the relevant preconditions of witnessing the ability by witnessing.
  And, whatever follows from this, e.g.\ in terms of commitments and so on.

  If so, then anything that follows from \AR{} also follows from \WR{}.
  Conversely, as the agent does not obtain information about how the ability is witnessed, it seems what follows from \WR{} also follows from \AR{}.
\end{note}

\begin{note}[Interesting case]
  Interesting case to think about, in which the agent obtains support for what follows from witnessing, but intuitively not for some other precondition.
  \begin{itemize}
  \item Ability to reason to \(\phi\).
  \end{itemize}
  Entailment applies to \(\phi\).
  Entailment doesn't seem to apply to reasoning to \(\lnot\phi\) as misleading.
\end{note}

Understanding of ability is such that there is always a potential witnessing event.

\ref{denied-claim} and~\ref{prem:ni} are universal claims.
\ref{prem:ab} is an existential claim.
\ref{denied-claim} and~\ref{prem:ni} clash in scenarios where the possibility captured in~\ref{prem:ab} is realised.

The collection of~\ref{denied-claim},~\ref{prem:ni}, and~\ref{prem:ab} is in tension.

There is an additional secondary premise:

\begin{note}[Two ways to understand ability and support]
\begin{enumerate}
\item\label{prem:ability} Two ways to obtain conclusion given ability.
  \begin{enumerate}
  \item Attribution.
  \item Witnessing.
  \end{enumerate}
\end{enumerate}

\ref{prem:ability} does not make a claim about any particular use of ability.
As a template, conceptually (or logically) coherent.
If there's a problem, then it's because there are further constraints on understanding of support.
\end{note}

\section{Miscellaneous}
\label{sec:misc}

\subsection{Metabelief}
\label{sec:metabelief}

\begin{note}[Idea]
  A possible solution I've overlooked is the idea of some belief of the form of a metabelief that if one has information about ability, then it's true.
  Something of a background belief.
  Put to work in various contexts.
  For example, testimony, problem of forgotten evidence, and so on.

  Somewhat close to induction, maybe?
\end{note}

\begin{note}[Reduction?]
  From a certain point of view this seems to be an instance of~\ref{prem:ni}.

  I mean, the difficulty here is the way in which the agent gets to the information.
  That is, this kind of metabelief in a sense, provides exceptions to~\ref{prem:ni}.

  I don't find this particularly plausible.
  In a sense, it works.
  So long as agent goes from truth to truth.
  But something more is needed.
  Understand that affirming the consequent is bad.
  However, when I use it, always find.
  So, form metabelief.

  Affirming is bad, regardless of use.
  Inclined to think the same is true here, and~\ref{prem:ni} highlights why.
\end{note}

\subsection{\citeauthor{Audi:1983ux} on \citeauthor{Lehrer:1971aa}}
\label{sec:lehrer}

\begin{note}[Lehrer]
  \citeauthor{Lehrer:1971aa}'s cases are somewhat of interest.

  Here, we have an agent who seems to have both propositional some proposition.
  The propositional support is stipulated as unquestionably good, take this to be established however one likes.
  However, obtaining doxastic support is difficult, and the agent does not recognise that they have propositional support.
  Instead, the agent forms a contrary attitude based on contrary propositional support.

  So we have:
  \begin{enumerate}
  \item\label{L:gl:prop:p} Propositional support for \(\phi\)
  \item\label{L:gl:prop:not-p} Propositional support for \(\lnot\phi\)
  \end{enumerate}
  Were the support for \(\phi\) is stronger than the support for \(\lnot\phi\).
  And, the haven't has established doxastic support for \(\lnot\phi\).
  As the agent has not established doxastic support for \(\phi\) (due to difficulty), the agent believes \(\lnot\phi\).

  The agent then is then informed by some source that the agent has (stronger) propositional support for \(\phi\).
  The agent then goes and establishes doxastic support for \(\phi\).
  However, due to the complexities involved, the agent is not swayed by the doxastic support.
  For example, some errors.
  However, because the source provided information that propositional support is stronger, agent revises attitude in favour of \(\phi\).
\end{note}

\begin{note}[Example]
  \citeauthor{Lehrer:1971aa} specific example involves a questionable source, and it is unclear whether there's much to be said for the agent.

  Variant with student.
  Student attempts to prove something.
  It's quite difficult, and the agent's intuitive understanding of the domain guides them to \(\lnot\phi\).
  So, student has strong belief that \(\lnot\phi\) is the case, though lacks knowledge --- the student has not ruled out that \(\phi\) is the case.
  Teacher suggests that the material establishes \(\phi\).
  Student takes a second look, and following the formalism, proves that \(\phi\).
  However, the agent has no intuitive understanding (some of the) key steps in the proof.
  So, the agent relies on the teacher.
\end{note}

\begin{note}[Possible to read \citeauthor{Lehrer:1971aa}'s example as similar]
  If the agent obtains support for \(\phi\), then it seems this is due to the propositional support the agent has, rather than the doxastic support that the agent forms.
\end{note}

\begin{note}[\textcite{Audi:1983ux}]
  \citeauthor{Audi:1983ux} presents a neat summary of how the argument may go:
  \begin{quote}
    Since
    \begin{enumerate*}[label=(\arabic*)]
    \item\label{Audi:divergence:1} the justification of the belief that \emph{p} is \emph{q}, which is good evidence for \emph{p}, and
    \item\label{Audi:divergence:2} S believes \emph{q}, and sees its full evidential bearing on \emph{p},
    \item\label{Audi:divergence:3} S has good evidence for \emph{p}.
      Hence,
    \item\label{Audi:divergence:4} S has a justification for the belief that \emph{p}.
      Thus,
    \item\label{Audi:divergence:5} if S believes \emph{p}, then even if his believing \emph{p} is not to any degree sustained by his believing \emph{q}, he justifiably believes \emph{p}, and the (or a) justification of this belief is based on his belief that \emph{q}.
    \end{enumerate*}
    \nolinebreak
    \mbox{}\hfill\mbox{(\citeauthor[406]{Audi:1983ux})}
  \end{quote}
  \citeauthor{Audi:1983ux} suggests the argument falters from step~\ref{Audi:divergence:4} to~\ref{Audi:divergence:5}.
  In short, the agent doesn't get doxastic support from proposition support.
\end{note}

\begin{note}[Important difference]
  There is an important difference between the two types of cases.
  In the \citeauthor{Lehrer:1971aa} type cases, the agent discards the doxastic support.
  In our type of case, the agent has not yet obtained doxastic support (implicit has been that the agent would obtain doxastic support).

  So, in our cases, there is scope to reject~\ref{Audi:divergence:5}.
  Do need some kind of sustaining, and the use of information about ability establishes the relevant sustaining.
\end{note}

\begin{note}[Notes for the moment]
  Todo is to work through \citeauthor{Audi:1983ux} in some detail and see if there's a stronger argument against the position I endorse.

  A potentially important point is that there's no counterfactual dependency in \citeauthor{Lehrer:1971aa}'s cases, while there is some kind of counterfactual dependency in the cases of interest.

  Should check: \textcite{Tierney:2012tt}.
\end{note}


\subsection{Additional observations}
\label{sec:addit-observ}

\begin{note}[Trouble with modals]
  We have sketched potentive entailment.
  However, noting the interaction between a modal and a verb.

  Understanding of why the entailment works has been left largely to intuition.

  The specifics of potentive entailment are not too important, so we may omit the detour.
  Still, even for those willing to make the detour it is not clear how long it would take, or where it would lead.

  Difficulty is seen by taking a straightforward treatment of the modals involved.

  `There is potential for' and `agent S has the (specific) ability to' are modals.

  Standard first pass at modals, via possible worlds and accessibility relations.

  Before continuing further, the presence of difficulty may be quickly noted by noting the similarities between potentive and actuality entailments.
  \textcite{Alxatib:2019wf} provides the following account of actuality entailments.
  \begin{quote}
    Actuality Entailments (AEs) are inferences from premises that appear to be modal, like (1a), but their content is that the modality is effectuated in the evaluation world --- (1b).

    \begin{enumerate}[label=(\arabic*)]
    \item
      \begin{enumerate}[label=\alph*.]
      \item Pierre a dû \hspace{26pt} prendre le \hspace{3.5pt} train \newline
        Pierre had.to.\textsc{pfv} take \hspace{14pt} the train\newline
        \hspace{-4pt} ‘Pierre had to take the train'
      \item \emph{Inference}: Pierre took the train.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[701]{Alxatib:2019wf})}
      \end{enumerate}
    \end{enumerate}
  \end{quote}

  Note, the reading of `had' in (1a) is `unambiguously deontic' (\citeyear[703]{Alxatib:2019wf}).
  English paraphrase does not carry the same entailment, but does seem to carry a corresponding implicature.

  Potentive entailment is related, but it is not (necessarily) the \emph{content} on the modality that is effectuated in the evaluation world (though it may be).
  Following the account of actuality entailments, \citeauthor{Alxatib:2019wf} highlights the basic problem:

  \begin{quote}
    AEs are surprising; if we assume that modals attribute their propositional argument to potentially non-actual worlds, something must be special to AE-licensers that leads to the inference of actuality.

    Whatever that special feature is, its effect is complex, and it interacts in nontrivial ways with other phenomena of theoretical interest.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[701]{Alxatib:2019wf})}
  \end{quote}

  Possible world, then the event takes place in the possible world.
  Had takes some ordering, so best world involved taking the train.
  This doesn't seem to explain why Pierre took the train.

  Similar with potentive.
  There is a possible world, but it's not obvious why this constrains the world of evaluation.

  With examples, it is clear that there is an entailment.
  Substituting different verbs and results, entailment goes away.

  This isn't too helpful.
  For, we would see what is required to be the case at the possible world.
  However, the consequent of a potentive entailment holds at the world of evaluation.

  Of the form \(\Diamond \phi \rightarrow \psi\).
  So, \(\lnot \psi \rightarrow \Box \lnot \phi\).

  Potential clue.
  Restrictor.
  In effect, the potentive entailment is drawing out information about the restrictor/modal base.

  Figuring out the relevant construction of modal base \dots well \dots
  Something of a dead end.
\end{note}

\begin{note}[More on actuality entailment]
  The potentive entailment is not an actuality entailment.

  \begin{quote}
    \begin{enumerate}
    \item Yesterday, John was able to eat five apples in an hour. (past episodic)
    \item In those days, John was able to eat five apples in an hour. (past generic)
    \end{enumerate}
    (315a) implicates that John actually ate five apples in an hour.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[173]{Bhatt:2008aa})}
  \end{quote}

  \begin{quote}
    (317) Last night, a masked assailant attacked me on my way home.
    I was able to wrestle him to the ground.
    \#But I didn't do anything since I am a pacifist.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[174]{Bhatt:2008aa})}
  \end{quote}

  Key here is the entailment is restricted to the event, and the modal needs to be in the past tense.
  (\textcite{Pinon:2003te} has some nice examples.)
  Of course, potentive entailment applies.
  Certain conditions had to be in place in order for there to have been a witness of ability.
  Still, these seem to be distinct as they do not conform to the same restriction placed on actuality entailment.

  There is some work on the difficulties involved in obtaining the actuality entailment.
  \citeauthor{Bhatt:2008aa,Bhatt:1999ud} argues that the entailment doesn't follow from ability attribution.
\end{note}


\subsection{Agentive modals}
\label{sec:agentive-modals}

\begin{note}[Summary]
  This is something of an appendix to the present chapter.
  The goal is to review the literature on agentive modals, and highlight that there is some difficulty with obtaining a clear understanding of potentive entailment from the proposals made.
\end{note}

\begin{note}[Agentive modals]
  Agent is able to \dots

  Ability modal.

  \begin{enumerate}
  \item It is possible that Y stole the jewels.
  \item S has the ability to prove that Y stole the jewels.
  \end{enumerate}

  The ability statements of interest are an instance of agentive modality.
  \cite{Mandelkern:2017aa}
  \cite{Maier:2013vk}
  \cite{Schwarz:2020aa}
  \cite{Willer:2021ur}
  \cite{Maier:2021te}

  Some proposals, and some issues.
  E.g.\ Kratzer on `can'.
  The dart board problem.

  For the moment, leave the literature on ability modals aside.
  Focus is on specific ability.
  And, in particular, ability to reason.
  Literature focuses on non-mental actions.
  Throwing darts, unlocking safes, etc.
  In most cases the result of witnessing the ability depends on witnessing the ability.
  If the agent does not throw the dart, it will not land on the board.
  If the agent does not unlock the safe, then the safe will not be unlocked.

  Some further details in section~\ref{sec:agentive-modals}
\end{note}

\begin{note}[No volition]
  Tempting to restate in terms of volition.
  For example, paper.
  Presents some difficulty, especially given the observation that the agent may not at present have the volition.
  For, then to evaluate the entailment, need to consider some counterfactual possibility.

  S is able to prove that Y stole the jewels.

  This is because S is heavily involved.
  S has no volition to do so.
  This would result in estrangement for S.
  Without some complexity, it seems that in order to assume S has the volition, we would need to assume that S was not involved.
  Therefore, in turn, that the jewels were not stolen, or that the resulting proof would be different from what it actually is.
\end{note}

\begin{note}[Potentive entailment and modals]
  Given sufficient context, instances of the potentive entailment apply.
  There are darts available, there is a safe.

  Further, focusing on the modal aspect leads us to some difficulties.
  The entailment tells us about how things are in order for something to be possible.
  It is not clear how to conceptualise this.
  Consider possibility.
  In general, no potentive entailment.
  It is possible that the sun rises from the west.
  Unclear what follows about how things actually are from this.

  Properties of the accessibility relation?
\end{note}

\begin{note}[???]
  Doesn't rule out property.
  Don't get into the ontology of potential events.
  So, may reduce.
  Still, from the perspective of reasoning, not required.
  Entailment follows from potential, and potential may require attribution of ability, but only from some ontological perspective.
\end{note}


\section{Formal?}
\label{sec:formal}

\subsection{Obtaining potentive entailments}
\label{sec:obta-potent-enta}

\begin{note}[Quick sketch]
  This is an optional section.
  We explained potentive entailment and given examples.

  Reader may wish for a technical account.
  In this section we sketch one such account.

  We do not argue that the account is wholly adequate.
  However, functional at first pass.

  Two things to do.
  \begin{enumerate}
  \item Establish some equivalence between potential and ability.
  \item Given an account of the potentive entailment.
  \end{enumerate}

  Start by taking a simple possibility understanding of the modal and show how potential and ability fit.
  We will then build on the possibility understanding to fix potentive entailment.
\end{note}

\subsection{Modal}
\label{sec:modal}

\begin{note}[Potentive]
  The potentive is straightforward to analyse.

  Fairly clear understanding of event semantics.

  Here, existential quantification over events is replaced by a modal.

  This requires some non-standard existential, but we're not too interested in providing an analysis suitable for semantics.
\end{note}

\begin{note}[Ability]
  Our understanding of ability is basically the same as potentive.

  Ability functions as an equivalent quantifier.
\end{note}

\begin{note}[Avoid ability?]
  A simple corollary of the above observations potentive entailment does not require ability.

  If it is possible to provide information about potential event of reasoning without attributing ability, then we don't need to speak of ability at all, perhaps with the exception of generating intuitive scenarios.

  May wonder how important ability is.

  Difficult case.
  Go for externalism, and co-reference.
  State a conclusion, but the agent would not reason to the conclusion under that description.

  There's a potential event, but it isn't clear that the agent has the ability.

  Doubt this is possible, as agent needs to do something.
  And, ability this seems sufficient for an ability statement.
  So, continue to work with ability.
\end{note}

\begin{note}[Some formal stuff]
  \[(\text{Able}(s,e) \land (V(e) \land \text{agent} = s \land \text{result}(e) = \phi))\]
  There is some event \(e\), such that \emph{s} is able to bring about, and \(e\) consists of \emph{s} \emph{V}ing with the result that \(\phi\).

  The quantification here is somewhat familiar to Lewis' counterpart theory.

  Understand ability as relating the agent directly to an event.
  Alternative it to take a truth value.
  \((\text{Able}(s,\exists (V(e) \land \text{agent} = s \land \text{result}(e) = \phi))\).

  Close to having a possible world with \(\phi\) and accessibility relation.
  Interpret the non-standard existential in this way, if it helps.
  There is some possible world and some event in that world, such that the agent at the world of evaluation is able to perform the event witnessed at the possible world.

  In both cases, it's the role of the event.

  \begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
      \centering
      \begin{tikzpicture}[
        ]
        \node{S is able to V that p}
        child {node {Able}}
        child {node {S V that p}
          child {node {S}}
          child {node {V that p}
            child {node {V}
            }
            child {node {that p}
            }
          }
        };
      \end{tikzpicture}
    \end{subfigure}
    %
    \begin{subfigure}{.5\textwidth}
      \centering
      \begin{tikzpicture}[
        ]
        \node{Potential for S to V that p}
        child {node {Potential}}
        child {node {S V that p}
          child {node {S}}
          child {node {V that p}
            child {node {V}
            }
            child {node {that p}
            }
          }
        };
      \end{tikzpicture}
    \end{subfigure}
  \end{figure}
  Suggestion here is that there's really nothing too interesting.
  In both cases it seems possible to have a complete description of the witnessing event prior to the introduction of a modal.
  Only complexity involved is projecting agent from event in order to apply ability.
\end{note}


\begin{note}[Breaking things down]
  An instance of potentive entailment has an antecedent and consequent.
  As may be seen from the examples provided, there are no particular constraints on the consequent of a potentive entailment.
  The antecedent of potentive entailments of interest, however, have two main components:
  \begin{itemize}
  \item\label{pe:part:event} An event.
  \item\label{pe:part:modal} A `potentive' modal applied to the event
  \end{itemize}
  The event in turn has three important components:
  \begin{enumerate}
  \item\label{pe:part:agent} An agent.
  \item\label{pe:part:verb} A verb describing some action performed by the agent.
  \item\label{pe:part:result} Some result of a successful performance of the action described by the verb.
  \end{enumerate}

  Gave a gloss of potentive entailment.

  Key observation 1.
  Possible consequents are determined by the event, rather than the modal.
  Obtain consequent because of the modal.

  So, each of the examples, we obtain the same entailment on the assumption that the event described has happened.

  Contrast.
  Potential for \(e_{1}\) and potential for \(e_{2}\), so potential for \(e_{3}\).
  E.g.\ conjunction introduction.

  In other words, the consequent does not hold because the event is a \emph{potential} event.
  Or, that this is `epistemic'.

  Well, consequent because the event of the antecedent requires the consequent.

  So, that the potential provides a way to get the consequent prior to the event happening.
  No instance of potentive entailment where the consequent follows because the event is potential.
  This is not to deny that there are cases in which entailment relies on potential.

  So, here explaining why the work is done primarily by the verb.
  Might think that using `discovers' is a counterexample.
  Only possible because the action involved is for the moment potential.
  However, the verb itself does the work here.
  Get the consequent that the agent hasn't done the reasoning, but understanding this as simply shifting temporal index.

  So, the important of this key observation is that we further reduce interest in ability.
  We've seen that alternative modal may be used.
  And now that the modal is of secondary importance.

  So, property is seen as surface level.

  Two candidates for the antecedent.
  \begin{quote}
    \begin{enumerate}
    \item There is a potential event in which \emph{S} \emph{V}s that \(\phi\).
    \item \emph{S} has the ability to \emph{V} that \(\phi\).
    \end{enumerate}
  \end{quote}
\end{note}


\subsection{Entailment}
\label{sec:entailment-1}




\begin{note}[Counterfactual]
  One option is counterfactual.
  This is true, and then consider all of those things some that if they we're true, potential wouldn't be true.
  Consider change to the actual world that would result from false consequent, and figure out whether potential still holds.

  Problem here is that counterfactuals are tricky.

  Minimal change may still result in potential.
  Chess example, if strategy doesn't exist, then it's not clear how to understand this.
  Some other rules of chess, and strategy may still exist.
\end{note}

\begin{note}[More direct]
  Preferred option is to consider all witnessing events.
  No matter how things turn out, the truth of \(\phi\) persists throughout event.

  What about changes?
  So, there's some potential event, because of some change to the rules of chess.
  Hence, there is a possible event, but relies on an unexpected development.
  Problem with potential?
  Arguably same issue holds for ability.

  However, it's then going to be the case that there is some change.
  Problem here when it comes to reasons, as the agent doesn't have the reasons available.

  Observation here is that \(\phi\) is an enabling condition.
  Potential just in case that it does not depend on further enabling conditions that are not yet the case.


  So, suggestion that if something holds throughout every event, then it holds of the actual world.
  Basically, this rules out an enabling condition that is not true.

  Hence, \(\phi\) is an enabling condition, and does not require additional enabling conditions.
\end{note}

\begin{note}[Still issue of underspecified event]
  Returning to the matchbox.
  Different preconditions.
  Well, depends on how the event is understood.

  Use this idea to suggest some troubles.
  By, extending events to include establishing what seem to be preconditions.
  Suggest that this is taken care of by understanding of event.
\end{note}

\begin{note}[Some issues with ability]
  Even so, not clear that additional features of ability are desirable.
  For example, conditional analysis.
  S has the ability to \(\phi\), understood as S would \(\phi\) if S tried to.
  (\citeyear[\S4]{Mandelkern:2017aa})
  And act conditional analysis
  \begin{quote}
    there is some practically available action A such that the closest world where S tries to do A is a world where S does \(\phi\)\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear[\S5]{Mandelkern:2017aa})}
  \end{quote}
  Or \cite{Schwarz:2020aa}, who distinguishes two readings.
  \begin{quote}
    \begin{enumerate}[label=\textbf{\alph*.}]
    \item \emph{S} can \(\phi\) (effectively) iff there are (highest-ranked) accessible worlds at which \emph{S} \(\phi\)s.
    \item \emph{S} can \(\phi\) (transparently) iff there are (highest-ranked) accessible worlds at which \emph{S} \(\phi\)s \emph{transparently}.
    \end{enumerate}
    \emph{S} \(\phi\)s \emph{transparently} iff \emph{S} \(\phi\)s as a result of a volitional state that warrants believing that she will \(\phi\) provided that \(\phi\)ing is under her volitional control.
  \end{quote}

  \begin{quote}
    a world is accessible iff it is under the agent’s volitional control --- that is, iff it would result from some available variation of the agent's volitional state.\nolinebreak
    \mbox{}\hfill\mbox{(\citeyear{Schwarz:2020aa})}
  \end{quote}

  Accessible world in which agent has volition.

  
  Counterfactual considerations.
  
  Noted that potential events don't require agents, hence if volitional states of agents, then holds whether volition is precondition for restricted cases.

  Demonstrate someones innocence.
  Well, transparecy.

  Potentive entailment follows even if agent has no volition.
\end{note}

\begin{note}[Transformative experience?]
  \citeauthor{Paul:2014aa}, maybe.
\end{note}