\chapter{Directions}
\label{cha:binding}

\begin{note}
  \autoref{cha:intro} introduced two questions, \qWhy{} and \qHow{}, and motivated a constraint between answers to \qWhy{} and \qHow{}.

  \autoref{cha:var} introduced \qWhyV{} and \qHowV{}, and a variant constraint.

  \fc{}, and \requ{}.

  In this chapter, link \fc{1} and \requ{1} to \qWhyV{}.
\end{note}

\begin{note}
  Chapter introduced \requ{1}.
  \requ{3} focus on some concrete stuff: \fc{1}.

  However, \qWhyV{} is stated with respect to \ros{}.
\end{note}


\begin{note}
  \autoref{cha:requs} introduced \requ{1}.
  In this chapter, link \requ{1} to \qWhyV{}.
\end{note}

\begin{note}
  Three sections:
  \begin{TOCEnum}
  \item
    \TOCLine{cha:binding:sec:requRos}
  \item
    \TOCLine{cha:binding:sec:requ-qWhyV}
  \item
    \TOCLine{cha:binding:sec:requ-iC}
  \end{TOCEnum}
\end{note}

\section{\requ{3} and \ros{1}}
\label{cha:binding:sec:requRos}

\begin{note}
  We being by observing a key way in which \requ{1} interact with \ros{1}:

  \begin{proposition}[\requ{3} and \ros{1}]
    \label{prop:requ-ros}
    \cenLine{
      \begin{itemize*}[noitemsep, label=\(\circ\)]
      \item
        Agent: \vAgent{}
      \item
        Propositions: \(\phi\), \(\psi\)
      \item
        Values: \(v\), \(v'\)
      \item
        \pool{3}: \(\Phi\), \(\Psi\)
      \item
        Event: \(e\)
      \item
        \mbox{ }
      \end{itemize*}
    }

    \begin{itemize}
    \item
      \(\pvp{\psi}{v'}{\Psi}\) being a \requ{} of \(e\).
    \end{itemize}

    \emph{Entails}:

    \begin{itemize}
    \item
      \begin{itenum}
      \item[\emph{If}:]
        A \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) fails to hold, for \vAgent{}, through \(e\).
      \item[\emph{Then}:]
        \(e\) is not an event in which \vAgent{} is concluding \(\pv{\phi}{v}\) from \(\Phi\).
      \end{itenum}
    \end{itemize}
    \vspace{-\baselineskip}
  \end{proposition}

  \begin{argument}{prop:requ-ros}
    Assume \(\pvp{\psi}{v'}{\Psi}\) is a \requ{}.

    Now, suppose a \ros{} fails to hold between \(\pv{\psi}{v'}\) and \(\Psi\) in \(e\).

    By \autoref{prop:fcs-only-if-pot-support}, \(\pv{\phi}{v}\) from \(\Psi\) is not a \fc{} for \vAgent{}.

    Therefore, by the definition of a \requ{}, the agent is not concluding.
  \end{argument}
\end{note}

\begin{note}
  Intuitively, \autoref{prop:requ-ros} states that, whatever \ros{1} amount to in practice, if a \ros{} fails to hold, from an \agpe{}, then no concluding.

  % \ros{} capture distinctive relation between conclusion and \pool{}.
  % \supportII{}, holds without \wit{}.
  % \fc{}, holds.
  % Hence, the proposition.
\end{note}

\section{\requ{3} and \qWhyV{}}
\label{cha:binding:sec:requ-qWhyV}

\begin{note}
  \reQuestion{questionWhyV}

  \begin{proposition}[\requ{3} and \qWhyV{}]
    \label{prop:requ-WhyV}
    \cenLine{
      \begin{itemize*}[noitemsep, label=\(\circ\)]
      \item
        Agent: \vAgent{}
      \item
        Propositions: \(\phi\), \(\psi\)
      \item
        Values: \(v\), \(v'\)
      \item
        \pool{3}: \(\Phi\), \(\Psi\)
      \item
        Events: \(e\), \(e^{\flat}\)
      \item
        \mbox{ }
      \end{itemize*}
    }

    \begin{itenum}
    \item[\emph{If}:]
      \ref{prop:requ-WhyV:if:concludes},~\ref{prop:requ-WhyV:if:concluding}, and~\ref{prop:requ-WhyV:if:requ} hold:
      \begin{enumerate}[label=\alph*., ref=(\alph*), series=propRequWhyVSeries]
      \item
        \label{prop:requ-WhyV:if:concludes}
        \(e\) is an event in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\).
      \item
        \label{prop:requ-WhyV:if:concluding}
        \(e^{\flat}\) sub-event of \(e\) in which \vAgent{} is concluding \(\pv{\phi}{v}\) from \(\Phi\).
      \item
        \label{prop:requ-WhyV:if:requ}
        \(\pvp{\psi}{v'}{\Psi}\) is a \requ{} of \(e^{\flat}\)
      \end{enumerate}
    \item[\emph{Then}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=propRequWhyVSeries]
      \item
        \label{prop:requ-WhyV:tn:answer}
        \(\pvp{\psi}{v'}{\Psi}\) is, in part, an answer to \qWhyV{}.
      \end{enumerate}
    \end{itenum}
    \vspace{-\baselineskip}
  \end{proposition}

  \begin{argument}{prop:requ-WhyV}
    Suppose \ref{prop:requ-WhyV:if:concludes},~\ref{prop:requ-WhyV:if:concluding}, and~\ref{prop:requ-WhyV:if:requ} hold.

    Now, suppose a \ros{} fails to hold between \(\pv{\psi}{v'}\) and \(\Psi\) in \(e^{\flat}\).

    \autoref{prop:requ-ros}, \(e^{\flat}\) is not an event in which \vAgent{} is concluding \(\pv{\phi}{v}\) from \(\Phi\).

    Hence, does not develop.

    By assumption, does develop.

    Hence, \ros{} holds.

    This gets us the a condition and conditional.
  \end{argument}
\end{note}

\begin{note}
  Key.

  Intuition is that \tC{}.
  Therefore, matters whether or not \fc{}.
  Hence, matters whether or not \ros{}.
\end{note}

\begin{note}
  This is not merely some statement about \tC{}.

  Intuitively, if \tC{} then something about what secures the agent's concluding as \tC{0}.

  Stronger.
  \requ{} is such that this is part of what makes the act an act of concluding.

  Put it this way.
  Concern about \tC{0}.
  Then, it may still be the agent is concluding.

  With \requ{}, this is not the case.
\end{note}

\begin{note}
  Before turning to \issueConstraint{}, apply to the pair of \scen{1} which satisfy conditions from \autoref{cha:requs}.
\end{note}

\begin{note}
  \color{blue}

  The description here\dots
\end{note}

\subsection{Applied}
\label{sec:consequences}


\begin{note}
  \scen{1} which satisfy conditions from \autoref{cha:requs}.
  \begin{itemize}
  \item
    \autoref{scen:squish}.

    \(\pv{\text{\sqE{} is sound}}{\text{True}}\) from some \pool{} \(\Psi\).
    Where, previous proof of \(\pv{\text{\sqE{} is sound}}{\text{True}}\) from \(\Psi\).
  \item
    \autoref{illu:gist:sudoku}.

    Interactive \scen{0}, in which  repeat reasoning to some partial or full solution to Sudoku puzzle.
  \end{itemize}
\end{note}

\begin{note}
  \autoref{scen:squish}

  It seems does explain, in part, why.
  For, rehearsing, no \ros{}, no \fc{}, then stop.

  Likewise with Sudoku.
  Not only that you concluded, but that you would repeat.

  At issue is \tC{}.
\end{note}

\begin{note}
  In both cases, \wit{}.
  Indeed, \wit{} follows from construction of \illu{1}.
  Motivating idea was of repetition.
  Repetition, requires original event.
  And, original event serves as a \wit{}.
\end{note}

\begin{note}
  It seems, also, that explain why I did not conclude lost keys.
  And, why kettle logic is bad.
\end{note}


\section{\requ{3} and \issueConstraint{}}
\label{cha:binding:sec:requ-iC}

\begin{note}
  With \autoref{prop:requ-WhyV} we observe the way in which \tC{0}, \fc{1}, and \requ{1} may come together to provide counterexamples to \issueConstraint{}.

  In short, we need some instance in which an agent concludes \(\pv{\phi}{v}\) from \(\Phi\) such that \(\pvp{\psi}{v'}{\Psi}\) is a \requ{} of the agent concluding \(\pv{\phi}{v}\) from \(\Phi\), yet the agent does not have a \wit{} for the \ros{} between \(\pv{\phi}{v}\) and \(\Psi\).

  In full detail:

  \begin{proposition}
    \label{prop:requ-WhyV-ces}
    \cenLine{
      \begin{itemize*}[noitemsep, label=\(\circ\)]
      \item
        Agent: \vAgent{}
      \item
        Propositions: \(\phi\), \(\psi\)
      \item
        Values: \(v\), \(v'\)
      \item
        \pool{3}: \(\Phi\), \(\Psi\)
      \item
        Events: \(e\), \(e^{\flat}\)
      \item
        \mbox{ }
      \end{itemize*}
    }

    \begin{itenum}
    \item[\emph{If}:]
      \ref{prop:requ-WhyVCes:if:concludes},~\ref{prop:requ-WhyVCes:if:concluding},~\ref{prop:requ-WhyVCes:if:requ},~and~\ref{prop:requ-WhyVCes:noW} hold:
      \begin{enumerate}[label=\alph*., ref=(\alph*), series=propRequWhyVSeries]
      \item
        \label{prop:requ-WhyVCes:if:concludes}
        \(e\) is an event in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\).
      \item
        \label{prop:requ-WhyVCes:if:concluding}
        \(e^{\flat}\) sub-event of \(e\) in which \vAgent{} is concluding \(\pv{\phi}{v}\) from \(\Phi\).
      \item
        \label{prop:requ-WhyVCes:if:requ}
        \(\pvp{\psi}{v'}{\Psi}\) is a \requ{} of \(e^{\flat}\)
      \item
        \label{prop:requ-WhyVCes:noW}
        No \wit{}.
      \end{enumerate}
    \item[\emph{Then}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=propRequWhyVSeries]
      \item
        \label{prop:requ-WhyVCes:tn:answer}
        \(\pvp{\psi}{v'}{\Psi}\) is a counterexample to \issueConstraint{}.
      \end{enumerate}
    \end{itenum}
    \vspace{-\baselineskip}
  \end{proposition}

  \begin{argument}{prop:requ-WhyV-ces}
    \ref{prop:requ-WhyVCes:if:concludes},~\ref{prop:requ-WhyVCes:if:concluding},~\ref{prop:requ-WhyVCes:if:requ} parallel the same conditions from \autoref{prop:requ-WhyV}.
    Therefore, by~\autoref{prop:requ-WhyV}, \(\pvp{\psi}{v'}{\Psi}\) answers, in part, \qWhyV{}.

    However, by~\ref{prop:requ-WhyVCes:noW}, the agent does not have a \wit{}.

    Therefore, answer, in part, to \qWhyV{} such that no \wit{}.
  \end{argument}

  \autoref{prop:requ-WhyV-ces} does not guarantee the existence of counterexamples to \issueConstraint{}.
  And, as we were careful not to presuppose counterexamples to \issueConstraint{} when developing \tC{0}, \fc{1}, and \requ{1}, we have no yet seen any explicit counterexamples to \issueConstraint{}.

  In \autoref{cha:ces} we will provide examples which satisfy the conditions of \autoref{prop:requ-WhyV-ces}.
\end{note}

\begin{note}
  Though, for preview.
  \autoref{illu:gist:sudoku}.
  Suppose fill in each square, and such that concluding solution.
  Then, other squares are \fc{1}.
\end{note}


\begin{note}
  The remainder of this chapter will briefly consider a handful of issues.
\end{note}


\section{Interest}
\label{sec:interest}

\begin{note}
  So, established dependence as captured by conditional.

  Does this really capture why the agent concluded?
\end{note}


\section{Considerations}
\label{sec:objection}

\subsection*{Factivity}

\begin{note}
  Non-factive explanation.

  No, \requ{1} require that \(\pv{\psi}{v'}\) from \(\Psi\) \emph{is} a \fc{}.
  Hence, if \(\pvp{\psi}{v'}{\Psi}\) answers \qWhyV{} via \requ{}, then there is a \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\).
\end{note}

% \subsubsection{Concluding}
% \label{sec:concluding}

% \begin{note}
%   It is not clear the following suggestion holds.
%   \begin{suggestion}
%     If \(e\) is event which may develop, then \(e\) is event in which concluding.

%     {
%       \color{red}
%       This is where the problem is.
%       I don't think this is obvious.

%       We have assumed that if \(e^{sub}\) \emph{is} an event of concluding, then may develop.

%       However, this suggestion is the converse.
%     }
%   \end{suggestion}
% \end{note}

% \begin{note}
%   For, \(e\) is an event in which the agent throws a dart at the centre of the dartboard.
%   However, at the initial stage of \(e\), it is not the case that the agent is sure to throw the dart at the centre of the dartboard.

%   There is a difference between how the event developed, and how the may have developed.

%   So, this idea isn't right in general.

%   Problem.
%   For, if existential account of progressive, then get explain how things came to be simply by focusing on what happened.

%   I do have an answer to this, which is that the role of the \fc{} is what happened.

%   Okay, so hang on.
%   For an agent to be concluding, it does not need to be the case that the event is guaranteed to develop in a way such that things work out.

%   However, it does need to be the case that there is some way things work out.

%   And, the way in which \requ{1} work is that failure means there is no way in which things work out.
% \end{note}

% \begin{note}
%   There are ways to approach this:
%   \begin{itemize}
%   \item
%     Deny the premise.

%     If event in which an agent concludes, it need not be the case that the agent was concluding throughout all the relevant sub-events.

%     Then, no issue is resolved.
%   \item
%     Deny that the event was an event in which the agent concluded.

%     Specifically, narrow the relevant event.
%     For, we have some initial event, which develops in two a larger event, which finishes with an event in which the agent concludes \(\pv{\phi}{v}\).
%     So long as final sub-event, then the agent concludes.
%     The issue only arises from the apparent link to earlier (sub-)events.
%     But, if otherwise, then motivation to reject these as (sub-)events of an event in which the agent concludes.
%   \item
%     Shift perspective.

%     What it true after the fact need not be true as things are developing.
%     This is \citeauthor{Boylan:2020aa}'s approach.
%   \end{itemize}

%   I am inclined to consider the former.
%   When speak on concluded, just picking out an event.
%   Naturally event to some default event.
%   However, flexible.

%   So, here \citeauthor{Boylan:2020aa} and darts.
%   I was able to, sure, but only after things hand developed so far.

%   Additionally, consider picture.
%   Drew a dog.
%   However, not the case that drawing a dog throughout associated event.
%   Started out as a doodle.

%   Ran 10k.
%   However, started out, plan was to run 5k.
%   Interesting consequence here is that not running 5k.
%   For, supposing extension came about by choice, something changed, and hence no force to finish at 5k.

%   Running 10k includes running 5k.
%   But, in a more basic case, running.
%   Extends to drawing.

%   In the case of concluding, have reasoning.
% \end{note}

\subsection*{\ros{3}}

\begin{note}
  Here's the thing.
  It is somewhat unclear what it is for a \ros{} to hold.

  We haven't clearly captured something from the \agpe{}, so to speak.
  However, there's no good way to do this.

  \begin{itemize}
  \item
    If go solely from \agpe{}, then \agpe{} is mistaken.
  \item
    If go solely from without \agpe{}, then \agpe{} doesn't matter.
  \end{itemize}

  \requ{3} aim to bridge this gap.

  In particular, \ninf{}.
\end{note}

\subsection*{Embedding}
\label{sec:embedding}

\begin{note}
  \ros{}.
  However, know \fc{}, therefore, it need not be the case that \ros{} answers.

  Complex, so separate chapter.
\end{note}


\section{The agent's involvement}
\label{sec:infl}

\begin{note}
  Consider the following \scen{0}:

  \begin{scenario}[Apples]%
    \label{scen:apples}%
    Grey is walking to town.
    Grey notices a bicycle for sale.
    Grey purchases the bicycle, gets on the bicycle, and starts cycling to town.
  \end{scenario}

  \noindent%
  The basic structure of \autoref{scen:apples} is simple:
  \begin{itemize}[noitemsep]
  \item
    An initial event is in progress. \hfill (Grey is walking to town.)
  \item
    Some other event happens. \hfill (Grey notices and purchases the bicycle.)
  \item
    The initial event is not longer in progress. \hfill (Grey is cycling to town.)
  \end{itemize}

  \noindent%
  Our interest is with the detail:

  \begin{itemize}
  \item
    The initial event is not longer in progress due to an action the agent performed.
  \end{itemize}

  \noindent%
  When an agent stops an event in progress by performing some action, we say the agent exerted `\ninf{}' over the initial event.
  Hence, Grey exerted `\ninf{}' over whether or not they were walking to town.

  Still, an agent does not need to exert \ninf{} to have \ninf{}.
  Grey may have continued walking to town after noticing the bicycle for sale.

  We define an agent having \ninf{} over an event as follows:

  \begin{definition}[\ninf{2}]
    \label{def:ninf}
    \cenLine{
      \begin{VAREnum}
      \item
        Agent: \vAgent{}
      \item
        Event: \(e\)
      \item
        Event description: \(\alpha\)
      \item
        \mbox{ }
      \end{VAREnum}
    }

    \begin{itemize}
    \item
      \vAgent{} has \ninf{} over whether or not \(\text{Prog}(e, \alpha)\) is true.
    \end{itemize}

    \emph{If and only if}

    \begin{itemize}
    \item
      Both~\ref{def:ninf:action} and~\ref{def:ninf:prog} are true:
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
      \item
        \label{def:ninf:action}
        There is some action \(b\) that \vAgent{} may (immediately) do.
      \item
        \label{def:ninf:prog}
        \(\text{Prog}(e', \alpha)\) would be not be true if \vAgent{} does \(b\).
      \end{enumerate}
    \end{itemize}
    \vspace{-\baselineskip}
  \end{definition}

  \noindent%
  Applied to \autoref{scen:apples}:

  \begin{itemize}[noitemsep]
  \item
    The agent is Grey.
  \item
    The event \(e\) spans some period of time which starts when or after Grey set out for town, and includes Grey noticing the bicycle for sale.
  \item
    \(\alpha\) is the description `Grey walks to town'.
  \item
    An instance of \(b\) is the action `Grey purchases and rides the bicycle'.
  \end{itemize}

  \noindent%
  Of course, with additional detail given, other actions may satisfy \(b\) action of \autoref{def:ninf}.
  For example, Grey may have turned back home or raided the local orchard.
\end{note}

\begin{note}
  The following table lists a few additional examples of \ninf{0}:

  \begin{center}
    \bgroup
    \def\arraystretch{1.125}
    \begin{tabular}{R{.45\textwidth} L{.45\textwidth}}
      Event description \(\alpha\) & Action \(b\) \\
      \hline
      Finish a book late at night. & Turn off the lights. \\
      Listen to a (full) speech. & Leave before the speech is over. \\
      Play a game of chess. & Flip the board in frustration.
    \end{tabular}
    \egroup
  \end{center}

  \noindent%
  Having \ninf{} over whether or not event is in progress is common, but there are also various events an agent does not have \ninf{} over.
  Here, event description and background condition which blocks.

    \begin{center}
    \bgroup
    \def\arraystretch{1.125}
    \begin{tabular}{R{.45\textwidth} L{.45\textwidth}}
      Event description \(\alpha\) & Background condition \\
      \hline
      Take a shower. & Has been in the shower for a while. \\
      Play chequers & Has made a few moves. \\
      A bank robbery & Is in prison. \\
    \end{tabular}
    \egroup
  \end{center}

  \noindent%
  We briefly comment on the first two examples:

  \begin{itemize}
  \item
    If you've been in the shower for a while, then whatever happens it remains the case that you were taking a shower.
  \item
    Likewise, if you have made a few moves, then what events it remains the case you were playing chequers.
    The contrast between playing chequers and playing a game of chess is the scope of the event.
    One may play chequers (or chess) without playing a full game of chequers (or chess).
  \end{itemize}
\end{note}


\begin{note}%
  \nocite{Peacocke:2021aa}%
  \ninf{2} is a general phenomenon.
  Our specific interest in with whether an agent has \ninf{} over whether they are \emph{concluding} \(\pv{\phi}{v}\) from \(\Phi\).
  In particular, \requ{1} rely on an agent having \ninf{} over concluding \(\pv{\phi}{v}\) from \(\Phi\).
  Still, before turning to \requ{1} we establish there are cases in which has \ninf{} over concluding \(\pv{\phi}{v}\) from \(\Phi\).

  \begin{proposition}[\ninf{2} over concluding]%
    \label{prop:ninfConcl}%
    There are instances in which an agent exerts \ninf{0} over whether or not they are concluding \(\pv{\phi}{v}\) from \(\Phi\).
  \end{proposition}

  \begin{argument}{prop:ninfConcl}
    Consider an agent \vAgent{}, some proposition-value pair \(\pv{\phi}{v}\), \pool{} \(\Phi\), and event \(e\).

    We make two observations:

    \begin{enumerate}[label=\arabic*., ref=(\arabic*), noitemsep]
    \item
      By \assuPP{2}, in order for \(e\) to be an event in which \vAgent{} is concluding \(\pv{\phi}{v}\) from \(\Phi\), there must be some \progAdj{0} development \(e^{\sharp}\) of \(e\) such that \(e^{\sharp}\) is an event in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\).
    \item
      There are often actions which if performed by \vAgent{} would result in an event \(e^{+}\), where \(e^{+}\) is a development of \(e\), and there is no \progAdj{0} development of \(e^{+}\) in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\).

      In particular it may be the case that:
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
        \label{prop:ninfConcl:obs:2:concludes}
      \item
        \(e^{+}\) does not develop into an event in which \vAgent{} \emph{concludes \(\pv{\phi}{v}\) from \(\Phi\)}.
      \item
        \label{prop:ninfConcl:obs:2:diffPoll}
        \(e^{+}\) does develop into an event in which \vAgent{} concludes \(\pv{\phi}{v}\) \emph{from \(\Phi\)}.
      \end{enumerate}
    \end{enumerate}

    \noindent%
    We illustrate \ref{prop:ninfConcl:obs:2:concludes} and \ref{prop:ninfConcl:obs:2:diffPoll} turn:

    \begin{itemize}
    \item
      Suppose \vAgent{} is playing a game of chess against an opponent.
      The opponent claims checkmate, and \vAgent{} beings to determine whether or not they are in checkmate.

      Still, \vAgent{} may flip the board, scattering pieces everywhere.
      And, with pieces scattered everywhere, \vAgent{} does not have sufficient resources to determine whether or not they were in checkmate.

      Hence, while determining whether or not they are in checkmate, \vAgent{} has \ninf{} over whether they are concluding they are in checkmate.
    \end{itemize}

    \begin{itemize}
    \item
      Suppose \vAgent{} is working on a homework problem which asks for solutions to the quadratic equation \(2x^{2} - x - 1 = 0\).
      \vAgent{} starts to work on the problem via factorisation, and is making slow, but steady, progress.

      Still, \vAgent{} understands the quadratic formula.
      And, \vAgent{} may use the quadratic formula to solve the quadratic equation.
      However, if \vAgent{} uses the quadratic formula, the relevant \pool{} \(\Phi\) must expand to include the details regarding the quadratic formula.

      Hence, while working on the quadratic equation, \vAgent{} has \ninf{} over whether they are concluding \(x = 1\) or \(x = -\sfrac{1}{2}\) from \(\Phi\).
      For, the agent may turn to concluding \(x = 1\) or \(x = -\sfrac{1}{2}\) from some expanded or variant \pool{} \(\Phi'\).
    \end{itemize}

    Abstracting a little:
    There are cases in which there is nothing which prevents an agent from making unavailable some proposition-value pair necessary for the agent to reach some conclusion.
    And, there are cases in which an agent may chose to appeal to additional proposition-value pairs in order to reach a conclusion.%
    \footnote{
      It does not follow the agent had a choice over how event develops, if the agent does not exert \ninf{}.
      It may be that if the agent continued the event, they would have concluded \(\pv{\phi}{v}\) from \(\Phi\).
      And, may remain the case that \(\pv{\phi}{v}\) from \(\Phi\) is a \fc{}.
    }
  \end{argument}
\end{note}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% TeX-engine: luatex
%%% End:
