\chapter*{Change log}
\label{cha:changes}


\begin{itemize}
\item
  The variants to \qWhy{} and \qHow{} are now termed `\qWhyV{}' and `\qHowV{}'.
\item
  The intuitive constraint on answers to \qWhy{} by answers to \qHow{} is referred to via `\issueInclusion{}', likewise `\issueConstraint{}' for the variants.
  \begin{itemize}
  \item
    The goal with this notation is to keep the questions present when stating the constraints in order for easier recall of what the constraints amount to.
  \end{itemize}
\item
  Slight revision to \qWhyV{}.
  \begin{itemize}
  \item
    It is now the case that \qWhyV{} asks whether there is some sub-event of the event in which the agent concludes such that, if a \ros{} failed to hold at the sub-event, the agent would not have concluded.

    The purpose of this is to ease the construction of counterexamples to \issueInclusion{}.

    However, I also think this condition is better suited, as it apples to cases of complex concluding, and avoids worries over \ros{1} which fall outside the event in which the agent concludes.
  \end{itemize}
\item
  Drop `from the \agpe{}' in favour of `for the agent'.
  \begin{itemize}
  \item
    `the \agpe{}' shifts evaluation to how things are for the agent.
    `for the agent' captures \agpe{our} on the agent.
    Strictly, I only need the latter, and shifting perspectives seems to add --- rather than reduce --- complexity.
  \end{itemize}
\item
  Understand concluding as a sub-instance of reasoning.
  \begin{itemize}
  \item
    This allow me to talk in terms of whether or not reasoning amounts to concluding.
  \end{itemize}
\item
  Introduce the idea of reasoning/concluding being \sR{}.
  \begin{itemize}
  \item
    The role of \sR{} is to help capture the idea that conclusions are general.
    E.g.\ conclusion via arithmetic competence, understanding the rules of chess, knowing how to prove syntactic theorems, and so on.
  \item
    In turn, this motivates the existence of \requ{1}.
  \end{itemize}
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% End:
