\chapter{Clarification}
\label{cha:clar}

\begin{note}
  \autoref{cha:introduction} introduced the focal point of this document:
  The issue of whether a particular relation holds between answers to two distinct questions.
  Issue: \issueInclusion{}.
  Answers to why an agent concludes  --- answers to \qWhy{} --- constrained by how an agent concluded --- answers to \qHow{}.
  Our overall goal is to argue that there are counterexamples to \issueInclusion{}.

  The purpose of the present chapter is clarification.
  At the close of this chapter we will have variants of \qWhy{}, \qHow{}, and \issueInclusion{} and an understanding of how the variants relate to the initial questions and relation.

  Purpose of variants is to provide clarity.
  As a result, slight generalisation.
\end{note}

\begin{note}
  The chapter is split into two parts.
  In the first part we develop some foundations.
  Second part, foundations to develop variants.
  For each variant, link to initial question.

  \begin{itemize}
  \item
    Concluding \hfill \autoref{cha:clar:sec:CCC:pvp}
    \begin{itemize}
    \item
      What we are interested in.
    \end{itemize}
  \end{itemize}
\end{note}

\section{Concluding, concludes, conclusion}
\label{cha:clar:sec:CCC}

\begin{note}
  \qWhy{}, \qHow{}, and \issueInclusion{} are all stated with respect to concluding.
  Variations developed below will likewise stated with respect to concluding.
\end{note}

\begin{note}
  Our interest is in concluding.
  In this section, overview by considering the interaction between three terms:
  `concluding', `concludes', `conclusion'.

  Roughly, we hold:

  \begin{itemize}
  \item
    A conclusion of an agent is the state of a proposition being paired with a value by the agent.
  \item
    An event in which an agent concludes results in a conclusion of an agent.
  \item
    An event of concluding is such that an event in which an agent concludes is in progresses.
  \end{itemize}

  Hence, we understand `concluding' in terms of `concludes', and `concludes' in terms of `conclusion'.
  The characterisation of conclusions as proposition-value pairings is fundamental to the presentation of this document, and our initial focus will be on how such a pairing is understood.
  The events in which an agent concludes or is concluding are then understood in terms of what the event results in (`concludes') or is progressing towards (`concluding').

  In general, we understand a conclusion as the result of reasoning.
  Hence, an event in which an agent concludes is an event in which the agent reasons, and an event of concluding is an event of reasoning.

  Key distinction is that reasoning need result in the agent pairing a proposition with a value.
  \phantlabel{reasoning-vs-concluding-progressive}

  Indeed, we will often contrast concluding with reasoning.
  For, if the agent is concluding, then event in which the agent concludes is in progress.
  The event may be interrupted, and the agent may fail to conclude.
  However, if the event is not interrupted, will result in a conclusion.

  But contrast, the same need not be true of reasoning.
\end{note}

\subsection{Conclusions as proposition-value pairings}
\label{cha:clar:sec:CCC:pvp}

\begin{note}
  Basic assumption:

  \begin{assumption}
    \label{assu:concluding:pvp}
    For an agent \vAgent{}:

    \begin{itemize}
    \item
      A conclusion is a pairing of a proposition with a value, from some \vAgent{}'s perspective.
    \end{itemize}

    Where:
    \begin{itemize}[noitemsep]
    \item
      A proposition is some state of affairs.
    \item
      A value captures an evaluation of a proposition.
    \end{itemize}
  \end{assumption}

  Propositions are states of affairs, whether actual, possible, true, false, ideal, or regrettable.
  Values capture how the agent evaluates the state of affairs.
  Conclusion is pairing proposition with some value.

  The converse need not be the case; a proposition may be paired with some value from an agent's perspective, without the pairing being a conclusion.
  The role of \autoref{assu:concluding:pvp} is to capture what a conclusion amounts to.
\end{note}

\begin{note}
  Before discussing the details of \autoref{assu:concluding:pvp}, we present some examples of proposition-value pairings:

  \begin{itemize}
  \item
    The bag is heavy.\newline
    \mbox{ }\hfill%
    \(\pv{\text{The bag is heavy}}{\text{True}}\)
  \item
    The cyclist isn't avoiding potholes.\newline
    \mbox{ }\hfill%
    \(\pv{\text{The cyclist is avoiding potholes}}{\text{False}}\)
  \item I like bitter coffee.\newline
    \mbox{ }\hfill%
    \(\pv{\text{Bitter coffee}}{\text{Desirable}}\)
  \item
    It's too bad the balloon is deflating.\newline
    \mbox{ }\hfill%
    \(\pv{\text{The balloon is deflating}}{\text{Unfortunate}}\)
  \item
    The dog shouldn't be drinking from the pond.\newline
    \mbox{ }\hfill%
    \(\pv{\text{The dog isn't drinking from the pond}}{\text{Ought-to-be}}\)
  \item
    There is no chance \dots
    \mbox{ }\hfill%
    \(\pv{\text{\dots}}{\text{Improbable}}\)
  \end{itemize}

  Nothing in particular hangs on these examples.
  In particular, the relevant values may be restricted to `true' and `false' and the corresponding propositions expanded.
  For example:
  \begin{itemize}
  \item
    The dog shouldn't be drinking from the pond.\newline
    \mbox{ }\hfill%
    \(\pv{\text{The dog shouldn't be drinking from the pond}}{\text{True}}\)
  \end{itemize}

  However, odd, at least to me.
  Conclusion is about how bitter the coffee is, state of affairs is distinguished from agent's perspective on the state of affairs.
\end{note}

\begin{note}
  Compound:
  \begin{itemize}
  \item I like how bitter the coffee is.\newline
    \mbox{ }\hfill%
    \(\pv{\text{The coffee is bitter}}{\text{True}}\)\newline
    \mbox{ }\hfill%
    \(\pv{\text{The coffee is bitter}}{\text{Desirable}}\)
  \end{itemize}

  Likewise, from the agent's perspective, it may be the case that the proposition that the dog is sleeping is evaluated as both true and desirable.
  For example, the agent may evaluate the proposition as true because the agent perceives the proposition to be the case.
  And, the agent may evaluate the proposition as desirable because the agent is planning to take the dog on a long walk later in the day.
\end{note}

\begin{note}
  We will make use of the following notation:
  \begin{itemize}
  \item
    Lower case letters of the Greek alphabet, \(\phi, \psi, \dots\) correspond to propositions, i.e.\ states of affairs.
  \item
    The Latin letter \(v\) corresponds to a some value.
    And in cases where more than one value may be relevant we will write \(v', v'' \dots\).
    However, \(v, v'\), and \(v''\), etc., may all correspond to the same value.
  \item
    For any proposition \(\phi\) and value \(v\), we abbreviate the pairing of \(\phi\) and \(v\) as \(\pv{\phi}{v}\).
  \end{itemize}

  In general, any occurrence of \(v\) may be read as `true'.
  When speaking abstractly, nothing depends on particular value.

  \begin{itemize}
  \item
    On occasion we use \(\overline{v}\) to indicate some value other than \(v\) of the same type as \(v\) and \(v_{?}\) to indicate \(\phi\) is not paired with any proposition of the same type as \(v\).

    In summary, the notation on the left is in accordance with the sentence on the right with a default reading below:
    \begin{itemize}
    \item
      \(\pv{\phi}{v}\) \hfill \(\phi\) has value \(v\).%
      \newline
      \mbox{ }\hfill \(\phi\) is true.
    \item
      \(\pv{\phi}{\overline{v}}\) \hfill \(\phi\) has some value other than \(v\) of the same type.%
      \newline
      \mbox{ }\hfill \(\phi\) has some value other than true of the same type.%
      \newline
      \mbox{ }\hfill I.e.\ \(\phi\) is false.
    \item
      \(\pv{\phi}{v_{?}}\) \hfill \(\phi\) is not evaluated to have a value of type \(v\).%
      \newline
      \mbox{ }\hfill \(\phi\) is not evaluated as true or false.
    \end{itemize}
  \end{itemize}
\end{note}

\begin{note}
  We have seen a few examples of what conclusions \emph{are} given \autoref{assu:concluding:pvp}.
  The motivating idea behind \autoref{assu:concluding:pvp} is that an agent's evaluation of a proposition is fundamental.

  In other words, the respective evaluations of a proposition as true and of a proposition as desirable may function analogously to beliefs and desires in folk-psychology.
  Indeed, an agent evaluating a proposition as true may be treated as equivalent to the agent believing the proposition is true, and the agent evaluating a proposition as desirable as equivalent to desiring the (truth of the) proposition.%
  \footnote{
    \label{fn:belief-is-difficult}
    Though I don't think belief is really so straightforward.

    Consider the Jeremy Goodman's example of three-horse race from~\textcite{Hawthorne:2016wv}:
    \begin{quote}
      Assume that horse A is more likely to win than horse B which in turn is more likely to win then horse C (so the probabilities of winning could be known to be 45, 28, 27\%).
      In this case it seems ﬁne to say `I think horse A will win' or `I believe horse A will win'.%
      \mbox{ }\hfill\mbox{(\citeyear[1440]{Hawthorne:2016wv})}
    \end{quote}
    As \citeauthor{Hawthorne:2016wv} observe: ``[I]t is awful to say, in this case, `I think horse A will win but I don't believe it will'.''
    (\citeyear[1440, fn.17]{Hawthorne:2016wv})
  }

  If you are inclined to the folk-psychological picture, then the benefit of speaking in terms of proposition-value pairing from the agent's perspective is an easy way to talk about how things are from the perspective of the agent, rather than recasting the agent's perspective in terms of the propositional attitudes the agent has.

  And, if you are not inclined to the folk-psychological picture then the sketched equivalence should suggest how to understand the way in which proposition-value pairing are fundamental.
  If an agent evaluates some proposition \(\phi\) as true then \(\phi\) is the case, from the agent's perspective, etc.
\end{note}

\begin{note}
  In particular, we distinguish proposition-value pairing from a proposition-value pairing \emph{given various assumptions}.
  When we speak of the proposition `Rover will fall asleep soon' pairing with the value `true', from an agent's perspective, then Rover \emph{will} fall asleep soon, from the agent's perspective.
  By contrast, if the agent has been entertaining the idea that Rover is tired then the agent is entertaining the idea that the proposition `Rover is tired' has the value `true', but we do not consider the proposition and valid paired.
\end{note}

\begin{note}
  \phantlabel{mention:concluding-non-factive}
  Further, we allow for the possibility that some proposition is paired with some value from the perspective of an agent, though in reality things are otherwise.
  Hence, we do not require, for example, that an agent concludes \(\phi\) is true only if \(\phi\) is the case.

  Following an example of \citeauthor{Williams:1979wi}, an agent may conclude it is true that the stuff is gin, while in fact the stuff is petrol (\citeyear[18]{Williams:1979wi}).
  A slightly more involved case is given in the footnote to this sentence.%
  \footnote{
    An agent may conclude \(0.999\dots \ne 1\).
    And, the agent may, when concluding, hold themselves to have a conventional understanding of real numbers.

    The qualification is important, there are various interpretations under which \(0.999\dots \ne 1\), but (it is convention that) the Archimedean property holds for real numbers.

    Still, the agent may have failed to grasp the Archimedean property does not hold for real numbers, and so may reason that, though \(0.999\dots\) approaches \(1\), there must be \emph{some} difference between \(0.999\dots\) and \(1\) --- no matter how small --- and some difference between to things is sufficient to establish that they are not equal.
  }
\end{note}

\begin{note}
  We will not impose an explicit restrictions on which proposition may be paired with which values, nor on the circumstances under which propositions may be paired with values.

  However, we will try to keep things intuitive.
\end{note}

\subsection{Conclusions from pools of premises}
\label{sec:pools-premises}

\begin{note}

  \begin{assumption}
    \label{assu:concluding:pools}
    For an agent \vAgent{}:

    \begin{enumerate}
    \item[\emph{If}:]
      \vAgent{} concludes \(\phi\) has value \(v\).
    \item[\emph{Then}:]
      \vAgent{} concludes \(\phi\) has value \(v\) from some pool of premises \(\Phi\).
    \end{enumerate}
    Where:
    \begin{itemize}
    \item
      A pool of premises is some collection of proposition-value pairings.
    \end{itemize}
    \vspace{-\baselineskip}
  \end{assumption}

  \autoref{assu:concluding:pools} is primarily a matter of convenience.
  In various cases it is intuitive that an agent concludes \(\phi\) has value \(v\) from some premises, and we will have interest in keeping track of which premises an agent concludes from.

  For a handful of brief examples, consider the following:

  \begin{itemize}[noitemsep]
  \item
    \emph{A} testified that \(\phi\) is true, so \(\phi\) is true.
  \item
    \(\phi\) would be satisfactory for every member of the group, so \(\phi\) ought to be the case.
  \item
    The song is produced by \emph{B}, so listening to it is desirable.
  \item
    The device reads `\(\phi\)' and is reliable, so \emph{not}-\(\phi\) is improbable.
  \end{itemize}

  Each sentence may be used to identify a conclusion, marked by `so' with some relevant premises.
  I doubt each sentence captures the full extent of the premises involved, but details regarding the premises will not be of interest.

  Further, it is not clear that concluding always involves specific premises.
  For example, consider the parallel between the~\citeauthor{Ramsey:1929tf} test for conditionals and a Fitch-style rule for conditional introduction in propositional logic.%
  \footnote{
    \textcite{Read:1995wf} describe the test as follows:

    \begin{quote}
      One should believe a conditional. `if \emph{A} then \emph{B}' if one would come to believe \emph{B} if one were to add A to one's stock of beliefs.%
      \mbox{ }\hfill\mbox{(\citeyear[47]{Read:1995wf})}
    \end{quote}

    A Fitch-style rule for conditional introduction in propositional logic is as follows --- Cf. (\cite[206]{Barwise:1999tu}), (\cite{Pelletier:2021vp}):
    \begin{center}
      \begin{fitch}
        \ftag{\scriptsize i}{\fa \fh P} & \\
        \ftag{\scriptsize }{\fa \fa \vdots} & \\
        \ftag{\scriptsize j}{\fa \fa Q} & \\
        \ftag{\scriptsize j+1}{\fa P \rightarrow Q} & \(\rightarrow\)\textbf{Intro:} \emph{i}--\emph{j} \\
      \end{fitch}
    \end{center}

    The rule states that at any point in a proof, one may assume \(P\), then, after deriving \(Q\) from the assumption of \(P\), one may discharge assumption of \(P\) and introduce the conditional \(P \rightarrow Q\).
    Note, the assumption of \(P\) on line \emph{i} corresponds to adding \(P\) to collection of propositions proved or assumed up to line \emph{i}, and hence to one's stock of beliefs.

    Now, both the \citeauthor{Ramsey:1929tf} test and the Fitch-style rule for conditional introduction describe a clear \emph{processes} for which a conditional is a conclusion, but there may not be any \emph{premises} associated with the conclusion.
    To illustrate, consider the following derivation which does not involve any premises:

    \begin{center}
      \begin{fitch}
        \ftag{\scriptsize 1}{\fa \fh P \land Q} & \\
        \ftag{\scriptsize 2}{\fa \fa Q} & \(\land\)\textbf{Elim:} \emph{1} \\
        \ftag{\scriptsize 3}{\fa (P \land Q) \rightarrow Q} & \(\rightarrow\)\textbf{Intro:} \emph{1}--\emph{2} \\
      \end{fitch}
    \end{center}
  }
  However, \autoref{assu:concluding:pools} splits the difference by allowing the relevant pool of premises to be the empty set.
\end{note}

\subsection{Concludes and concluding}
\label{cha:clar:sec:CCC:c-and-c}

\begin{note}
  \autoref{cha:clar:sec:CCC:pvp} made the assumption that conclusions are pairings of a proposition \(\phi\) with a value \(v\), from the perspective of an agent.

  In this section we turn to two events concerning conclusions:
  \begin{itemize}
  \item
    The event in which an agent concludes.
  \item
    The event in which an agent is concluding.
  \end{itemize}
  This section will focus on the event in which an agent concludes.
\end{note}

\begin{note}
  We start with an assumption regarding an event in which an agent concludes:

  \begin{assumption}[Concludes is inclusive]
    \label{assu:concluding:span}
    For an agent \vAgent{}, proposition-value pair \(\pv{\phi}{v}\), and pool of premises \(\Phi\):

    \begin{itemize}
    \item
      The event in which an agent concludes \(\pv{\phi}{v}\) from \(\Phi\) spans the agent moving from the premises of \(\Phi\) to the conclusion that \(\phi\) has value \(v\).
    \end{itemize}
    \vspace{-\baselineskip}
  \end{assumption}

  The key feature of \autoref{assu:concluding:span}  is the \emph{scope} of concluding.
  The event of an agent is not limited to the agent pairing proposition \(\phi\) with value \(v\), but includes how the agent comes to pair \(\phi\) with \(v\).

  \autoref{assu:concluding:span} implicitly characterises an event in which an agent concludes via what a conclusion (and pool of premises) is.

  A slightly more natural paraphrase of \autoref{assu:concluding:span} states that the event in which an agent concludes \(\pv{\phi}{v}\) from \(\Phi\) spans the agents \emph{reasoning} to \(\pv{\phi}{v}\) from \(\Phi\).

  Indeed, we will continue to speak in terms of reasoning to ease things a little.
\end{note}

\begin{note}
  Rather than being an assumption proper, I'm inclined to think that \autoref{assu:concluding:span} identifies a particular sense of the term `concludes'.
  The sense of concludes which \emph{includes} the relevant reasoning leading up to some conclusion and does not focus only on the more-or-less instantaneous event in which the agent forms the relevant conclusion.

  In this respect, \autoref{assu:concluding:span} is less of an assumption and more of an indication about the sense in which I will use `concludes'.
\end{note}

\begin{note}
  To illustrate, we contrast to instances of `concludes'.
  The first is from \textcite{Gardner:1986wp} and the second from \textcite{Bratman:1979aa}.

  The following passage from \citeauthor{Gardner:1986wp}'s discussion of Newcomb's problem:

  \begin{quote}
    A large number of those who recommended taking only the second box performed the expected-value calculation and concluded that, provided the probability that the Being was correct was at least .5005, they would take only the second box.%
    \mbox{ }\hfill\mbox{(\citeyear[166]{Gardner:1986wp})}
  \end{quote}

  On my reading, \citeauthor{Gardner:1986wp} distinguishes the performing the expected-value calculation from the conclusion that they would take the box given a certain probability.

  In contrast to the passage from \citeauthor{Gardner:1986wp}, consider the following passage from \citeyear{Bratman:1979aa}:

  \begin{quote}
    Sam thinks both that in certain respects his drinking would be, \emph{prima facie}, best, and that in certain other respects his abstaining would be, \emph{prima facie}, best.
    Weighing these conflicting considerations he concludes that it would be best to abstain, rather than drink.%
    \mbox{ }\hfill\mbox{(\citeyear[156]{Bratman:1979aa})}
  \end{quote}

  It seems to me \citeauthor{Bratman:1979aa} describes includes the weighing of conflicting considerations in the event of concluding --- there is no `and' to distinguish the event of Sam weighting the conflicting considerations and the event in which Sam concludes that it would be best to abstain, rather than drink.
\end{note}

\begin{note}
  In addition, it seems to me that whether or not one defaults to thinking of a more-or-less instantaneous event or an inclusive event comes apart in multi-agent cases.

  For example, consider Sam and Max working on some problem \(p\) together.
  Sam and Max trade ideas back and forth, and settle on an answer \(a\).

  Consider the events described by the following sentence:
  \begin{enumerate}[label=\arabic*., ref=(\arabic*)]
  \item
    \label{Cing:SandM:j}
    Sam and Max (jointly) conclude \(a\) is an answer to problem \(p\).
  \item
    \label{Cing:SandM:s}
    Sam concludes \(a\) is an answer to problem \(p\).
  \item
    \label{Cing:SandM:m}
    Max concludes \(a\) is an answer to problem \(p\).
  \end{enumerate}

  My default is to consider the events captured by \ref{Cing:SandM:s} and \ref{Cing:SandM:m} in line with \citeauthor{Gardner:1986wp}.
  When considering Sam or Max in isolation, the event in which Sam (or Max) concludes more-or-less instantaneous event.
  Though, the relevant events may be expanded to include the trading of ideas by appending `by trading ideas with Max/Sam'.

  By contrast, I read \ref{Cing:SandM:j} in line with \citeauthor{Bratman:1979aa}.
  When considering Sam and Max as a pair, in which a non-distributive reading of `conclude' is forced by the parenthetical `jointly', the event includes the trading of ideas back and forth.
  Though, the relevant event includes sub-event in which Sam and Max separately evaluate that \(a\) is an answer to problem \(p\).
\end{note}

\begin{note}
  Our understanding of `concluding' is that an event in which an agent is concluding some proposition-value pair \(\pv{\phi}{v}\) from some pool of premises \(\Phi\) is just an event such that the event in which the agent concludes \(\pv{\phi}{v}\) from \(\Phi\) is in progress.

  In other worlds, an event of concluding involves some reasoning from some sub-set of the pool of premises \(\Phi\).

  In this respect, an event of concluding need not involve the agent pairing \(\phi\) with \(v\), it need only be the case that if the relevant event went on uninterrupted, then event would develop into an event in which the agent concludes \(\pv{\phi}{v}\) from \(\Phi\), and hence pairs \(\phi\) with \(v\).

  As noted on \autopageref{reasoning-vs-concluding-progressive}, an important distinction between reasoning and concluding is that we don't get this.
  {
    \color{red} Up to here.
  }
\end{note}

\subsubsection{Reasoning}
\label{sec:reasoning-1}

\begin{note}
  We have assumed that concluding is an instance of reasoning, and more specifically that concluding involves an agent reasoning from some pool of premises to some conclusion, where both premises and conclusions are understood in terms of proposition-value pairings.
  In this respect, the assumptions we have made place constraints on certain instances of reasoning.
  However, aside from understanding reasoning in terms of proposition-value pairings, we do not place further constraints on reasoning.

  Note, the absence of placed constraints does not imply that reasoning is unconstrained.
  Rather, we adopt a neutral stance on what may count as instance of reasoning.
\end{note}

\begin{note}[No constraints]
  To illustrate, consider the contrast between \citeauthor{Broome:2013aa}'s (\citeyear{Broome:2013aa}) rule following account of reasoning and \citeauthor{Wedgwood:2006ui}'s (\citeyear{Wedgwood:2006ui}) reason-based account of reasoning.

  \citeauthor{Broome:2013aa}'s rule following account of reasoning is unconstrained in terms of the rules an agent may follow.
  This aspect  of \citeauthor{Broome:2013aa}'s account is highlighted in the following passage:

  \begin{quote}
    [S]hould we exclude this bizarre rule: from the proposition that it is raining and the proposition that if it is raining the snow will melt, to derive the proposition that you hear trumpets.
    Following this rule would lead you to believe you hear trumpets when you believe it is raining and believe that if it is raining the snow will melt.
    If you did this, should we count you as reasoning?

    I think we should.
    If you derive this conclusion by operating on the premises, following the rule, we should count you as reasoning.
    \dots
    I think we should not impose a limit on rules.%
    \mbox{}\hfill\mbox{(\citeyear[233]{Broome:2013aa})}
  \end{quote}

  By constraint, \citeauthor{Wedgwood:2006ui}'s reason-based account of reasoning:

  \begin{quote}
    Reasoning, I shall assume, is the process of \emph{revising ones beliefs or intentions, for a reason}.%
    \mbox{ }\hfill\mbox{(\citeyear[600]{Wedgwood:2006ui})}
  \end{quote}

  \citeauthor{Wedgwood:2006ui} understands reasons in terms of intelligibility.%
  \footnote{
    Strictly, \citeauthor{Wedgwood:2006ui} understanding reasoning in terms of dispositions that respond to what `rationalizes' (\citeyear[672]{Wedgwood:2006ui}) and \citeauthor{Wedgwood:2006ui} considers `rationalizes' and  `makes intelligible' as equivalent.
    Therefore, the following conditional, states a sufficient rather than necessary condition which leads to \citeauthor{Wedgwood:2006ui}'s assumption, rather than being an expansion of what \citeauthor{Wedgwood:2006ui}'s assumption amounts to.
    I find this particularly confusion.
  }

  \begin{quote}
    If a set of antecedent mental states makes it rational for one to form a new belief or intention, then those antecedent mental states are surely of a suitable type and content so that it is \emph{intelligible} that they could represent one's reason for forming that belief or intention.\newline
    \mbox{ }\hfill\mbox{(\citeyear[662]{Wedgwood:2006ui})}
  \end{quote}

  Now, perhaps the presence of the rule in \citeauthor{Broome:2013aa}'s example makes it intelligible that the agent concludes that they hear trumpets from the relevant premises.
  However, there is also a clear sense in which the reasoning in \citeauthor{Broome:2013aa}'s example in \emph{unintelligible}.

  \citeauthor{Wedgwood:2006ui} provides the following contrasts to clarify their understanding of intelligibility:

  \begin{quote}
    [T]he belief that the \emph{Oxford Dictionary of National Biography} says that Hume died in 1776 seems a mental state of a suitable type and content so that it could intelligibly represent one's reason for believing that Hume died in 1776.
    On the other hand, it is not (except in the presence of some rather extraordinary background beliefs) a mental state of a suitable type and content so that it could intelligibly represent one's reason for believing that every even number is the sum of two primes.%
    \mbox{ }\hfill\mbox{(\citeyear[662]{Wedgwood:2006ui})}
  \end{quote}

  Does the rules that the agent follows in \citeauthor{Broome:2013aa}'s example count as a sufficiently extraordinary background belief?
  Indeed, \citeauthor{Broome:2013aa} do not require that, in general, an agent has beliefs concerning of the rules they follow in reasoning (\citeyear[Cf.][\S13.2]{Broome:2013aa}).
\end{note}

\begin{note}
  By refraining from placing any further constraints on reasoning we remain neutral on whether an unconstrained approach to reasoning is line with \citeauthor{Broome:2013aa} is correct, or whether a constrained approach to reasoning in line with \citeauthor{Wedgwood:2006ui} is correct.

  Still, in general, we aim to consider instances of reasoning (and concluding) which are intuitive.
  Hence, we hope that the instances of reasoning we consider are compatible with whatever way reasoning is understood.
\end{note}

\subsection{Attitudes}

\begin{note}
  Conclusion of reasoning is a proposition-value pairing.
  In general, this does not provide information about the attitude that the agent holds toward the proposition.

  For example, conclude that \(\phi\) has value `true'.
  Conclusion may amount to knowledge, belief, or some other veridical attitude.

  We will have little interest in propositional attitudes.
  Our interest is in concluding, and it is rarely the case that one concludes that they have some attitude toward a proposition.
  Conclude that the cat is on the mat, do not conclude that I believe the cat is on the mat.

  Set aside interest in attitudes when concluding.
  Interest will be in proposition-value-premises pairings from agent's perspective, as will be discussed further in \autoref{cha:introduction:sec:agents-perspective}.
\end{note}

\begin{note}
  Some difficulty in understanding answers to \qWhy{} and agent concludes.
  Evaluations are not attitudes.
  However, attitude entail evaluations.
\end{note}

\begin{note}
  \citeauthor{Davidson:1963aa}, reasons in terms of attitudes.

  \begin{quote}
    \emph{R} is a primary reason why an agent performed the action \emph{A} under the description \emph{d} only if \emph{R} consists of a pro attitude of the agent toward actions with a certain property, and a belief of the agent that \emph{A}, under the description \emph{d}, has that property.%
    \mbox{ }\hfill\mbox{(\citeyear[687]{Davidson:1963aa})}
  \end{quote}

  However, foundation of (pro-)attitude is proposition-value pairing.
  So, pro-attitude, evaluation with something like desire, and belief with evaluation of true.

  In this respect, \citeauthor{Davidson:1963aa} is agent neutral.
  Primary reason is not seen from agent's point of view.
  Instead, from our point of view.
  However, entailed (or corresponding) account from agent's point of view.%
  \footnote{
    Clearer given principle \citeauthor{Smith:1987vk} derives from the Humean Theory of Motivation, as captured by~\ref{Smithh:HtM:2}:
    \begin{quote}
      \begin{enumerate}[label=\textsc{P1}., ref=(\textsc{P1})]
      \item
        \label{Smithh:HtM:2}
        Agent A at t has a motivating reason to \(\phi\) only if there is some \(\psi\) such that, at t, A desires to \(\psi\) and believes that were he to \(\phi\) he would \(\psi\).%
        \mbox{ }\hfill\mbox{(\citeyear[36]{Smith:1987vk})}
      \end{enumerate}
    \end{quote}

    Understand desire of A to \(\psi\) in terms of the evaluation of \(\psi\) as desirable, and the belief as evaluating if do \(\phi\) then \(\psi\).

    \citeauthor{Smith:1987vk} suggests comparison to \textcite{Davidson:1963aa}.
    Note, in particular \citeauthor{Smith:1987vk}'s use of `motivating reason' is equivalent to \citeauthor{Davidson:1963aa}'s use of `primary reason' rather than `reason'.
  }

  So, \citeauthor{Davidson:1963aa}'s constraint in terms of cause is a little more delicate.
\end{note}

\begin{note}
  Hope this is straightforward.%
  \footnote{
    Discussion by \citeauthor{Collins:1997wn} and \citeauthor{Dancy:2000aa}.
  }
  Contrast is possible, from agent's point of view it is that agent has relevant propositional attitudes.

  Consider the follow passage from \citeauthor{Hume:2011aa}'s \hyperlink{cite.Hume:2011aa}{Treatise}:

  \begin{quote}
    ’Tis also obvious, that this emotion rests not here, but making us cast our view on every side, comprehends whatever objects are connected with its original one by the relation of cause and effect.
    Here then reasoning takes place to discover this relation; and according as our reasoning varies, our actions receive a subsequent variation.
    But ’tis evident in this case, that the impulse arises not from reason, but is only directed by it.
    ’Tis from the prospect of pain or pleasure that the aversion or propensity arises towards any object: And these emotions extend themselves to the causes and effects of that object, as they are pointed out to us by reason and experience.%
    \mbox{ }\hfill\mbox{(\hyperlink{cite.Hume:2011aa}{T.2.3.3})}
  \end{quote}

  The passage captures means-end \emph{reasoning}.
  Evaluate an object according to the prospect of pain or pleasure.
\end{note}

\subsection{Notation}

\begin{note}
  In previous sections introduced key aspects of how we understand reasoning.
  In this section we introduce some core notation that we will use throughout the remainder of the document with respect to concluding.
\end{note}

\begin{note}
  \begin{itemize}
  \item
    We use upper case letters of the Greek alphabet, \(\Phi, \Psi, \dots\), to refer to collections of proposition-value pairings.

    For example, \(\Phi = \{ \pv{\phi}{v}, \pv{\psi}{v'}, \dots \}\).

    \(\Phi\) will often be a pool of premises relative to some conclusion.
  \item
    \(\pvp{\phi}{v}{\Phi}\) abbreviates the association of some proposition-value pair \(\pv{\phi}{v}\) with a collection of proposition-value pairings \(\Phi\).

    Usually \(\pvp{\phi}{v}{\Phi}\) will abbreviate \(\pv{\phi}{v}\) being a conclusion from the pool of premises \(\Phi\).
  \end{itemize}
\end{note}

\section{\qWhy{}, \qHow{}, and \issueInclusion{}}
\label{sec:variations-qwhy-qhow}

\begin{note}
  \autoref{cha:introduction} introduced \qWhy{}, \qHow{}, and \issueInclusion{}.

  Recall:
  \vspace{-\baselineskip}
  \begin{quote}
    \questionWhyBasic*
  \end{quote}

  \begin{quote}
    \questionHowBasic*
  \end{quote}

  \begin{quote}
    \issueInclusionFirst*
  \end{quote}
\end{note}

\begin{note}
    Example, pairing of \(23 \times 15 = 345\) and the testimony of the calculator that \(23 \times 15 = 345\) answers, in part, why the agent concluded \(23 \times 15 = 345\) in \autoref{illu:gist:calc}.
    Slightly more natural to say `the testimony of the calculator that \(23 \times 15 = 345\)', but \emph{paring}.

    Observed that, intuitively, pairing of \(23 \times 15 = 345\) and whatever pool of premises would be associated with the agent applying their understanding of arithmetic does not answer, in part, why the agent concluded \(23 \times 15 = 345\).
\end{note}

\begin{note}
  Our overall goal is to motivate a rejection of \issueInclusion{}.
  However, our immediate goal is to clarify \qWhy{} and \qHow{}.

  For, both \qWhy{} and \qHow{} are broad questions which turn on the way in which the respective instances of `why' and `how' are understood.
  Hence, without establishing a clear understanding of the way in which the instances are to be understood, it is unclear how to motivate a rejection of \issueInclusion{}.

  For example, there may be plausible answers to \qWhy{} which are not also answers to \qHow{} but fail to be counterexamples to \issueInclusion{} as the relevant sense of `why' and `how' are not the senses of `why' and `how' that \issueInclusion{} (intuitively) holds with respect to.

  Indeed, as a simultaneous constraint on answers to \qWhy{} and \qHow{}, \issueInclusion{} has a role in narrowing the possible senses of `why' and `how' at issue.
  However, if \issueInclusion{} is rejected, then, naturally, \issueInclusion{} cannot perform this role.
\end{note}

\begin{note}
  We will clarify \qWhy{} and \qHow{} via relations of \support{}.
  In broad outline:


  Given an agent has concluded \(\pv{\phi}{v}\) from \(\Phi\):
  Consider some arbitrary proposition-value pair \(\pv{\psi}{v'}\) and pool of premises \(\Psi\):
  \begin{itemize}
  \item
    Eliminate the relevant instance of `why' in favour of whether pairing \(\phi\) and \(v\) depended on a relation of \support{} holding between \(\pv{\phi}{v}\) and \(\Psi\).
  \item
    Eliminate the relevant instance of `how' in favour of whether or not there is an event in which agent concludes \(\pv{\psi}{v'}\) from \(\Psi\), and hence `\witness{1}' the \ros{}.
  \end{itemize}

  Depends on understanding of relations of \support{}.

  Core idea, \ros{}.

  If agent concludes, then relation of \support{} when pairing.

  Hence, establishing a relation of \support{} amounts to an event in which an agent concludes.
  Likewise, depends.

  To get counterexample, depends on \ros{} such that there is no relevant event in which the agent concludes \(\pv{\psi}{v'}\) from \(\Psi\).

  Possibility will be given by two things:

  \ros{} does not necessarily require witnessing.

  Way in which dependence is understood.
\end{note}


\section{\support{2}}
\label{cha:clar:support}

\begin{note}
  Outline the role \ros{1} will have.
  In this section we state the relevant ideas in full.
\end{note}

{
  \color{red} Include some examples.
}

\paragraph{\supportI{}}
\label{cha:clar:support:I}

\begin{note}
  \begin{idea}[\supportI{}]
    \label{idea:support}
    For an agent \vAgent{}, a proposition-value pair \(\pv{\phi}{v}\), pool of premises \(\Phi\), and event \(e\):

    \begin{itemize}
    \item[\emph{If}]
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
      \item
        \(e\) is an event in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\).
      \end{enumerate}
      \item[\emph{then}]
        \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
        \item
          When \vAgent{} pairs \(\phi\) with \(v\) as a sub-event of \(e\), (a relation of) \emph{\support{}} holds between \(\pv{\phi}{v}\) and \(\Phi\), as \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\), from \vAgent{}' perspective.
        \end{enumerate}
      \end{itemize}
      \vspace{-\baselineskip}
  \end{idea}

  \supportI{} captures way in which pool of premises are related to conclusion by event in which agent concludes.

  In this respect, static account of how the agent has come to pair \(\phi\) with \(v\).
  However, allow for the possibility that \support{} regardless of whether agent has concluded \(\pv{\phi}{v}\) from \(\Phi\).

  Intuitively, \support{} between \(\pv{\phi}{v}\) and \(\Phi\) is always an answer to \qWhyV{}.
  For, if \support{} failed to hold, then the event would not be an event in which the agent concludes \(\pv{\phi}{v}\) from \(\Phi\).

  Important role of \supportI{} is to capture, in a static way, relationship between \(\pv{\phi}{v}\) and \(\Phi\) that has been established by reasoning from \(\pv{\phi}{v}\) to \(\Phi\) when agent pairs \(\phi\) with \(v\) to form a conclusion.

  Little interest in what \support{} amounts to.
\end{note}

\begin{note}
  Note, however, that \supportI{} is if-then conditional.
  The converse to \supportI{} does not necessarily hold.
\end{note}

\begin{note}
 ~\supportI{} is distinct from~\citeauthor{Boghossian:2014aa}'s Taking Condition:%
  \footnote{
    There are various objections to the taking condition.

    See, for example,~\textcite{Hlobil:2014tq}, \textcite{McHugh:2016vp}, and~\textcite{Wright:2014tt}.

    \citeauthor{Hlobil:2014tq} argues against the Taking Condition as it distracts from what accounts of reasoning out to explain, rather than arguing against the Taking Condition directly.

    \citeauthor{McHugh:2016vp} summarise various objects to the taking condition, and present district arguments against against (distinct) ideas in favour of the taking condition.
    In particular,~\supportI{} is closer to what \citeauthor{McHugh:2016vp} term the `Consequence Condition' (\citeyear[cf.][316]{McHugh:2016vp}), which \citeauthor{McHugh:2016vp} also (indirectly) argue against.
    However, \citeauthor{McHugh:2016vp} does not consider an alternative account of what distinguishes concluding from any other action, and as~\supportI{} is designed to capture this distinction, it is unclear to me whether \citeauthor{McHugh:2016vp}'s arguments apply to~\supportI{} (if, indeed, they are sound).

    \citeauthor{Wright:2014tt} denies that reasoning must involve a state which connects premises to conclusions. (\citeyear[Cf.][33-34]{Wright:2014tt})
    Note,~\supportI{} is compatible with \citeauthor{Wright:2014tt}'s objection.
  }

  \begin{quote}
    (Taking Condition):
    Inferring necessarily involves the thinker \emph{taking} his premises to support his conclusion and drawing his conclusion because of that fact.%
    \mbox{}\hfill\mbox{(\citeyear[5]{Boghossian:2014aa})}
  \end{quote}

  \begin{quote}
    The intuition behind the Taking Condition is that no causal process counts as inference, unless it consists in an attempt to arrive at a belief by figuring out what, in some suitably broad sense, is supported by other things one believes.%
    \mbox{}\hfill\mbox{(\citeyear[5]{Boghossian:2014aa})}
  \end{quote}

  In short, \citeauthor{Boghossian:2014aa} assumes that inferring is a causal process, and the role of the Taking Condition is to distinguish the specific process of inferring from some other causal process.
  Of course, \citeauthor{Boghossian:2014aa} states the Taking Condition in terms of inferring, but extends to concluding.

  In contrast, we do not require that \support{} has any particular role an event in which an agent concludes \(\pv{\phi}{v}\) from \(\Phi\).
  As mentioned, static (and partial) perspective on dynamic process.
\end{note}

\begin{note}
  \phantlabel{Wright-simple-supportI}
  Indeed, our understanding of \support{} is close to \citeauthor{Wright:2014tt}'s (\citeyear{Wright:2014tt}) `Simple Proposal':
  \begin{quote}
    \dots consider instead the proposal, not that the status of the transition as inferential depends on the thinker's judgments about his reasons, but that it depends on \emph{what his reasons are}.
    We want his acceptance of the premises to supply his \emph{actual} reasons for accepting the conclusion.

    \mbox{}\hfill\(\vdots\)\hfill\mbox{}

    Call this the Simple Proposal.
    It says that a thinker infers q from p\(_{1}\) \(\cdots\) p\(_{\text{n}}\) when he accepts each of p\(_{1}\) \(\cdots\) p\(_{\text{n}}\), moves to accept q, and does so for the reason that he accepts p\(_{1}\) \(\cdots\) p\(_{\text{n}}\).%
    \mbox{}\hfill\mbox{(\citeyear[33]{Wright:2014tt})}
  \end{quote}

  \citeauthor{Wright:2014tt}'s simple proposal is that, from the agent's perspective, the relation between pool of premises and conclusion need not be part of why agent moves to accept conclusion.
  Considering how the agent concludes \(\pv{\phi}{v}\) from \(\Phi\) is sufficient.

  \begin{quote}
      What is needed, then, is an account of, or at least some insight into, what it is for certain intentional states of a thinker to be his actual reasons for his transition to another intentional state.

      [Which avoids] committing to the notion that doing something for certain reasons must involve a state that somehow registers those reasons as reasons for what one does.%
      \mbox{}\hfill\mbox{(\citeyear[34]{Wright:2014tt})}
    \end{quote}

  Still, there is an important between~\supportI{} and \citeauthor{Wright:2014tt}'s Simple Proposal.
  For,~\supportI{} is an entailment, while \citeauthor{Wright:2014tt}'s Simple Proposal is an identity statement.
  Inferring, on the Simple Proposal, is an agent accepting some conclusion for the reason that they accept some (pool of) premises.
 ~\supportI{} does not entail that concluding is nothing more than pairing \(\phi\) with value \(v\) as a result of \(\Phi\).

  Goal is to argue that there is more to concluding, no matter how premises are understood.
\end{note}


\paragraph{\supportII{}}
\label{cha:clar:support:II}

\begin{note}
  \begin{idea}[\supportII{}]
    \label{idea:support:possible}
    For an agent \vAgent{}, a proposition-value pair \(\pv{\phi}{v}\), and pool of premises \(\Phi\):

    \begin{itemize}
    \item
      It is possible for there to be \support{} between \(\pv{\phi}{v}\) and \(\Phi\) without \vAgent{} having concluded \(\pv{\phi}{v}\) from \(\Phi\), from \vAgent{}' perspective.
    \end{itemize}
    \vspace{-\baselineskip}
  \end{idea}

  Note, \supportII{} does not require there exist instances of \support{}.
  \autoref{cha:fcs} will focus on argument that there are instances of \support{} without event of in which agent concludes.
  These we will term \fc{1}.%
  \footnote{
    \citeauthor{Firth:1978vi}'s (\citeyear{Firth:1978vi}) distinction between doxastic and propositional justification (or warrant).
    See also \citeauthor{Silva:2020aa} (\citeyear{Silva:2020aa}) --- esp.\ fn.\ 1.

    {\color{red}
      Compare \citeauthor{Firth:1978vi}'s example with Holmes and Watson (\citeyear[218]{Firth:1978vi}).
      Watson is presented with all the evidence Holmes used to that the coachman committed the murder, and that this provides Watson with sufficient epistemic reasons regardless of whether or not Watson forms any attitude, but it is not clear that Watson has the understanding to piece together the evidence laid before them.
    }
  }

  \supportII{} establishes the \emph{possibility} of \support{} answering why, without the proposition-value-premises pairing being involved in how.

  Still, looking ahead a little, \supportII{} should not be of any immediate concern.
  For, suppose consider an instance of \support{} without event in which agent concludes.
  There mere existence of such an relation does not show that the relation is relevant to why.
\end{note}

\subsubsection{\fc{3}}
\label{cha:clar:support:II:fcs}

\begin{note}
  \supportI{} and \supportII{}.

  To avoid mystery, possibility given by \fc{3}.
  \fc{} just in case, roughly, some action such that event results from performing action is an event in which concludes in progress.
\end{note}

\begin{note}
  Also important, converse: If no \ros{} then not a \fc{}.
\end{note}

\subsection{\witness{3}}
\label{cha:clar:support:W}

\begin{note}
  We define \witness{} as follows:

  \begin{definition}[A \witness{2}]
    \label{def:witnessing}
    For an agent \vAgent{}, proposition-value pair \(\pv{\phi}{v}\), and pool of premises \(\Phi\):

    \begin{enumerate}[label=]
    \item
      \begin{enumerate}[label=\alph*., ref=(\alph*), series=WitnessDef]
      \item
        \vAgent{} has a \emph{\witness{0}} for \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).
      \end{enumerate}
    \item
      \emph{If and only if:}
    \item
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=WitnessDef]
      \item
        There is some event \(e\) such that \(e\) is an event in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\).
      \end{enumerate}
    \end{enumerate}
    \vspace{-\baselineskip}
  \end{definition}

  If \(e\) is event of concluding \(\pv{\phi}{v}\) from \(\Phi\), then when agent pairs \(\phi\) with \(v\), the agent has a \witness{} for \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).

  There event of concluding and the event which serves to \witness{} are the same.
\end{note}

\begin{note}
  One potential objection to \autoref{def:witnessing} is the idea that there may be instances where an agent reasoned to \(\phi\) having value \(v\) but did not conclude \(\phi\) has value \(v\).
  Yet, at some point later strengthened the result of reasoning to a conclusion.

  Hence, in line with \supportII{}, one may think the reasoning still serves to \witness{0} a  \ros{} between \(\phi\) and \(v\).%
  \footnote{
    Further, may be relevant for answering questions.
  }

  For example, do a proof but worry about particular step.
  Investigate step, and strengthen.
  Strictly, have not concluded \(\pv{\phi}{v}\) from \(\Phi\).
  Rather, from previous reasoning and premise that reasoning was sound.

  Still, further proof, and would not conclude if prior proof was not sound.

  Plausible to weaken \autoref{def:witnessing} to reasoning.
  Hence, reasoning later seen to be sound would qualify.
\end{note}

\section{\qWhyVnP{} and \qHowV{}, and \issueConstraint{}}
\label{sec:variants-initial}

\begin{note}
  In \autoref{sec:variations-qwhy-qhow} we outlined variations of \qWhy{} and \qHow{}, and in \autoref{cha:clar:support}, \support{}.

  In this section, we briefly state the variations, and observe how the variations are linked.
  We defer in-depth to following sections.
  The role of the present section is to provide an initial understanding of the two questions and how they interact in order to ease discussion of the respective details.
\end{note}

\subsection{\qWhyVnP{}}
\label{sec:variants-initial:qwhyvnp}

\begin{note}
  As forecast in \autoref{sec:variations-qwhy-qhow}, eliminate `why' in favour of whether pairing \(\phi\) and \(v\) depends on \ros{}.

  \begin{restatable}[\qWhyVnP{}]{question}{questionWhyVnP}
    \label{q:why:v:nP}
    Given an agent \vAgent{}, proposition-value pair \(\pv{\phi}{v}\), pool of premises \(\Phi\), and event \(e\) in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\):

    \begin{quote}
      Which proposition-value-premises pairings \(\pvp{\psi}{v'}{\Psi}\) are such that, when \vAgent{} pairs \(\phi\) with \(v\):

      \begin{enumerate}[label=]
      \item
        \begin{enumerate}[label=\alph*., ref=(\alph*), series=qWhyVnPdef]
        \item
          \label{q:why:v:a}
          \support{2} between \(\pv{\psi}{v'}\) and \(\Psi\) holds, from \vAgent{}' perspective.
        \end{enumerate}
      \end{enumerate}

      And:

      \begin{enumerate}
      \item[\emph{If}:]
        \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=qWhyVnPdef]
        \item
          \label{q:why:v:if}
          \support{2} between \(\pv{\psi}{v'}\) and \(\Psi\) failed to hold, from \vAgent{}'s perspective.
        \end{enumerate}
      \item[\emph{Then}:]
        \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=qWhyVnPdef]
        \item
          \label{q:why:v:then}
          \vAgent{} would not have concluded \(\pv{\phi}{v}\) from \(\Phi\).
        \end{enumerate}
      \end{enumerate}
    \end{quote}
    \vspace{-\baselineskip}
  \end{restatable}

  \qWhyVnP{} captures when a \ros{} is, in part, why an agent concludes \(\pv{\phi}{v}\) from \(\Phi\) by two conditions.
  First, simple, \ros{} holds.
  Second, \emph{if-then} conditional.

  \ref{q:why:v:a} expresses the simple idea that \support{} holds from the agent's perspective.
  Take this as basic necessary condition that \support{} holds.
  \emph{If-then} conditional captures dependence, and \ref{q:why:v:a} ensures that what conclusion depends on is present.

  \emph{If-then} conditional.
  Between \support{} and whether or not the event is such that the agent concludes.
  This captures are simple idea of dependence.
  Defer discussion to \autoref{sec:dependence}.

  Role of the \emph{if-then} conditional is to capture sense in which concluding \(\pv{\phi}{v}\) from \(\Phi\) depends on \ros{} holding between \(\pv{\phi}{v}\) and \(\Phi\).

  If dependence, then \ros{}, in part, answers `why' the agent concluded \(\pv{\phi}{v}\) from \(\Phi\).

  For present purposes, key observation is that answers to \qWhyVnP{} are given in terms of \ros{1}.

  Setting aside what \ros{1} amount to, the consequent of the \emph{if-then} conditional \ref{q:why:v:then} is a subjunctive, and evaluating subjunctives is quite difficult.
  Indeed, I have no general account of how to evaluate \ref{q:why:v:then} when \ref{q:why:v:then} is set apart from an agent's perspective.%
  \footnote{
    For example, intuitively it should not be the case that the relation of support and the conclusion that it would be good to get some coffee answers, in part, why the agent concluded some theorem is true from some pool of premises.
    Though, it may well be the case that the agent would have been too tired to concludes the theorem without the aid of the coffee.
  }
  This is, in part, by design.
  The way in which \issueInclusion{} constrains answers to \qWhy{} in terms of answers to \qHow{} is taken to be substantial.
  In this respect, similar constraint is seen to be substantial due to the way in which the constraint constrains the understanding of the \emph{if-then} conditional.

  Indeed, argue against a parallel constraint, and therefore my understanding of the \emph{if-then} conditional would be of little interest at this point.
  For, given in full it would be the case that the constraint fails to hold.

  The core idea is that \emph{if} dependence as captured by the \emph{if-then} conditional, then answer to \qWhy{}.
\end{note}

\begin{note}
  Plausible holds for basic cases.
  If testimony was no good, would not conclude.
  And various other cases.

  Without a clear account of what depending amounts to, there is no deductive argument that holds in general.
  However, intention is that trivially holds for \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).
\end{note}

\begin{note}
  We link \qWhyV{} and \qWhy{} in the following way:

  \begin{restatable}[\qWhy{} and \qWhyV{}]{link}{linkSupportWhy}
    \label{link:why:support:pvpp}
    For an agent \vAgent{}, and proposition-value-premises pairings \(\pvp{\psi}{v'}{\Psi}\):

    \begin{itemize}
    \item[\emph{If}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
      \item
        \support{2} between \(\pv{\psi}{v'}\) and \(\Psi\) is, in part, an answer to \qWhyV{}.
      \end{enumerate}
    \item[\emph{Then}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
      \item
        \(\pvp{\psi}{v'}{\Psi}\) is, in part, an answer to \qWhy{}.
      \end{enumerate}
    \end{itemize}
    \vspace{-\baselineskip}
  \end{restatable}

  Key thing is dependence captured links to why.
  Agent would not conclude \(\pv{\phi}{v}\) from \(\Phi\) unless \ros{} holds been \(\pv{\psi}{v'}\) and \(\Psi\) from the agent's perspective.

  In short, \autoref{link:why:support:pvpp} states that \support{} between \(\pv{\psi}{v'}\) and \(\Psi\) which answers \qWhyV{} is sufficient for \(\pvp{\psi}{v'}{\Psi}\) to answer \qWhy{}, in part.

  Note, \autoref{link:why:support:pvpp} only amounts to sufficiently, and only captures a partial answer to \qWhy{}.

  Sufficiency, converse does not hold, there may be cases where \(\pvp{\psi}{v'}{\Psi}\) answers \qWhy{} but there is no corresponding \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) that answers \qWhyV{}.
  Indeed, \qWhy{} is not restricted to \ros{1}.

  Partiality, in the case of \qWhy{}  language is used to allow for other things to answer.
  In case of \qWhyV{}, for multiple \ros{}.

  Hence, we are not committed to relations of \support{} capturing answers to \qWhy{}.
\end{note}

\subsection{\qHowV{}}
\label{sec:variants-initial:qhowv}

\begin{note}
  Variant on \qHow{} is as follows:

  \begin{restatable}[\qHowV{}]{question}{questionHowV}
    \label{q:how:v}
    Given event \(e\) where agent concludes \(\pv{\phi}{v}\) from \(\Phi\), which proposition-value-premises pairing are such that:

    There is an event \(e'\) either prior or identical to \(e\), such that \(e'\) is event in which \vAgent{} witnesses \support{} between \(\pv{\psi}{v'}\) from \(\Psi\).
  \end{restatable}

  Following \ros{1} as answers to \qWhyVnP{}, \qHowV{} concerns \witness{1} for \ros{1}.

  In this respect, parallel to \issueInclusion{}
  \ros{} is only an answer to \qWhyVnP{} if the agent has a \witness{}.
\end{note}

\begin{note}
  \begin{restatable}[\qHow{} and \qHowV{}]{link}{linkHowWitnessing}
    \label{link:how-witnessing}
    For any proposition-value-premises pairing \(\pvp{\psi}{v'}{\Psi}\):
    \begin{itemize}
    \item[\emph{If}]
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
      \item
        \(\pvp{\psi}{v'}{\Psi}\) is, in part, an answer \qHow{} due to \support{} holding between \(\pv{\psi}{v'}\) and \(\Psi\).
      \end{enumerate}
    \item[\emph{then}]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
      \item
        \(\pvp{\psi}{v'}{\Psi}\) is, in part, an answer \qHowV{}.
      \end{enumerate}
    \end{itemize}
    \vspace{-\baselineskip}
  \end{restatable}
\end{note}

\begin{note}
  Has a \witness{0} is weak.
  Event in which \dots

  View having a \witness{0} as a necessary constraint.
  Constraint, without being too constraining.
  Do not want to rule out plausible accounts of concluding.
  In this respect, think of things which are sufficient.

  For example, causal theory.
  If causal, then constrain why by causes.
  And, if cause then has a \witness{0}.

  Rules, then \witness{0} to rules.

  Contrast, exercising disposition.
  In this case, exercise of the disposition results in a \witness{0}.

  So long as account requires having a \witness{0}, then variant to \qHow{} captures way in which account is of interest.
\end{note}

\begin{note}
  However, allows for the \witness{} to be distinct from event.%
  \footnote{
    To illustrate, consider an agent working on some mathematical problem.

    As part of their work on the problem the agent concludes the hypotenuse of some right-angled triangle is \(\sqrt{74}\text{cm}\) by use of the Pythagorean theorem.

    Further, the agent has, at some point in the past proved the Pythagorean theorem from more basic principles.

    Now, generally speaking, it seems to me it may be the case that the agent concludes the hypotenuse of the triangle is \(\sqrt{74}\text{cm}\), in part, from those more basic principles.
    For example, the agent may have just completed their proof of the Pythagorean theorem and the reasoning from the more basic principles to the hypotenuse of the triangle may be considered a single unified instances of reasoning, with an intermediary conclusion.

    Still, suppose the agent proved the Pythagorean theorem some years ago.

    Perhaps the agent's reasoning from more basic principles continues to provide, in part, an answer to how the agent concluded the hypotenuse of the triangle is \(\sqrt{74}\text{cm}\).
    There may be a gap of some years, but it may be the case that the agent uses the Pythagorean theorem (in some sense of the word) \emph{because} they concluded the theorem from more basic principles.

    {
      \color{red}
      Hence, \support{}, and this in part answers \qWhyVnP{}.
    }

    On the other hand, one may be inclined to hold that the more basic principles the agent proved the Pythagorean theorem from have no role in explaining how the agent concluded the hypotenuse of the triangle is \(\sqrt{74}\text{cm}\) in the present.
    Rather, the Pythagorean theorem is a more-or-less fundamental premise of the agent's present reasoning.

    At best, the agent's memory of reasoning from more basic principles to the Pythagorean theorem may, in part, answer how the agent concluded hypotenuse of the triangle is \(\sqrt{74}\text{cm}\).
    The reasoning from the more basic principles, given that it happened so long ago, is irrelevant.
  }
\end{note}

\subsection{\issueConstraint{}}
\label{sec:variants-initial:issue}

\begin{note}
  Case of \(\pv{\phi}{v}\) from \(\Phi\).
  \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) satisfies account of conditions of \qWhyVnP{}, and hence is an answer to \qWhyVnP{}.
  Further, as agent concludes, the agent has a \witness{0} for the \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).
  Therefore, answer to \qHowV{}.
\end{note}

\begin{note}
  \issueConstraint{}:

  \begin{restatable}[\issueConstraint{}]{issue}{rIssueConstraint}
    \label{issue:has-witnessed}
    For an agent \vAgent{}, proposition-value pairs \(\pv{\phi}{v}\), \(\pv{\psi}{v'}\), and pools of premises \(\Phi\), \(\Psi\):

    \begin{enumerate}
    \item[\emph{If}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
      \item \vAgent{} concluded \(\pv{\phi}{v}\) from \(\Phi\).
      \end{enumerate}
    \item[\emph{And}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
      \item
        \vAgent{} would not have concluded \(\pv{\phi}{v}\) from \(\Phi\), if \support{} between \(\pv{\psi}{v'}\) and \(\Psi\) failed to hold, from \vAgent{}' perspective.
      \end{enumerate}
    \item[\emph{Then}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
      \item
        \vAgent{} has a \witness{0} for the \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\).
      \end{enumerate}
    \end{enumerate}
    \vspace{-\baselineskip}
  \end{restatable}

  In short, \issueConstraint{} holds that a \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) is an answer to \qWhyV{} \emph{only if} the \ros{} is (also) an answer to \qHowV{}.
  In other words, being an answer to \qHowV{} is a necessary condition on being an answer to \qWhyV{}.
\end{note}

\begin{note}
  \color{red}
  Key thing, this is `substantial'.
  Sense of dependence captured by \qWhyVnP{} is not trivially that of having a \witness{}.
  Still, plausible that dependence is so captured.
\end{note}

\begin{note}
  View \issueConstraint{} as a `direct' constraint on answers \qWhyVnP{} and \qWhy{}.
  Or, as a consequence of \issueInclusion{} and proposed links between \qWhy{} and \qWhyVnP{} and \qHowV{} and \qHow{}.
\end{note}

\begin{note}
 Following:

  \begin{restatable}[]{proposition}{propVariationsAndInclusion}
    \label{prop:support-and-witnessing}
    Grating a positive resolution to \issueInclusion{}, and given \autoref{link:why:support:pvpp} and \autoref{link:how-witnessing}:
    \begin{enumerate}
    \item[\emph{If}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*)]
      \item \vAgent{} concluded \(\pv{\phi}{v}\) from \(\Phi\).
      \end{enumerate}
    \item[\emph{And}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
      \item
        \vAgent{} would not have concluded \(\pv{\phi}{v}\) from \(\Phi\), if \support{} between \(\pv{\psi}{v'}\) and \(\Psi\) failed to hold, from \vAgent{}' perspective.
      \end{enumerate}
    \item[\emph{Then}:]
      \begin{enumerate}[label=\alph*., ref=(\alph*), resume]
      \item
        \vAgent{} has witnessed \support{} between \(\pv{\psi}{v'}\) and \(\Psi\).
      \end{enumerate}
    \end{enumerate}
  \end{restatable}

  \autoref{prop:support-and-witnessing} is straightforward.
  A visual representation is given in~\autoref{fig:relations-between-whys-and-hows}.
\end{note}

\begin{figure}[H]
  \centering
  \begin{tikzpicture}
    \tikzset{ansStyle/.style={
        draw=gray,
        text width=.45\textwidth,
        rounded corners=2pt,
      }
    }
    %
    \node[ansStyle] (whyO) at (0,0) %
    {\qWhyV{} is answered by support between \(\pv{\psi}{v'}\) and \(\Psi\).};
    %
    \node[ansStyle] (whyA) at (2,-1.5) %
    {\qWhy{} is answered by \(\pvp{\psi}{v'}{\Psi}\).};
    %
    \node[ansStyle] (howA) at (4,-3) %
    {\qHow{} is answered by \(\pvp{\psi}{v'}{\Psi}\).};
    %
    \node[ansStyle] (witA) at (6,-4.5) %
    {\qHowV{} is answered by witnessed \support{} between \(\pv{\psi}{v'}\) and \(\Psi\).};
    %
    \path[->] ($(whyO.south)!0.9!(whyO.south west)$) edge [out=270, in=180] (whyA);
    \path[->] ($(whyA.south)!0.9!(whyA.south west)$) edge [out=270, in=180] (howA);
    \path[->] ($(howA.south)!0.9!(howA.south west)$) edge [out=270, in=180] (witA);
    %
    \node[text width=.5\textwidth] (1) at (1,-.8) %
    {Via~\autoref{link:why:support:pvpp}.};
    %
    \node[text width=.75\textwidth] (2) at (4.5,-2.25) %
    {Via a positive resolution to~\issueInclusion{}.};
    %
    \node[text width=.5\textwidth] (3) at (5,-3.625) %
    {Via~\autoref{link:how-witnessing}.};
    %
    % \draw[->, gray] ($(whyA.north)!0.9!(whyA.north east)$) to [out=90, in=0] ($(whyO.east)$);
    %
    % \node[text width=.5\textwidth, text=gray] (1p) at (8,-.8) %
    % {Via~\autoref{link:why:pvpp:support}.};
  \end{tikzpicture}%
  \caption{Relation between positive answers to questions.}
  \label{fig:relations-between-whys-and-hows}
\end{figure}

\begin{note}
  As with \issueInclusion{}, \issueConstraint{} distinguishes classes of theories.
  A positive resolution to \issueInclusion{} will not directly provide general answer to \qWhy{} or \qHow{}.
  Though, a positive answer will rule out certain answers.
\end{note}

\section{\issueConstraint{} and embedding}
\label{sec:constraints-and-embeddings}

\begin{note}
  Have seen \issueConstraint{}.

  \ros{3}.

  Important detail.

  It need not be the case that an agent has a \witness{0} for a \ros{0} in order for \ros{} to be involved in answering \qWhyVnP{}.
\end{note}

\begin{note}
  Motivated the \emph{if-then} conditional of \qWhyVnP{} as capturing dependence relevant to answering why an agent concludes \(\pv{\phi}{v}\) from \(\Phi\).

  We have not yet seen any examples to suggest that there are cases in which concluding \(\pv{\phi}{v}\) from \(\Phi\) depends on \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\)%
  \footnote{
    Where either \(\phi \ne \psi\), \(v \ne v'\), \(\Phi \ne \Psi\).
  }
  Still, I have expressed my intent.

  Above, we observed how~\supportI{} and~\supportII{} may combine in such a way that \support{} holds between \(\pv{\psi}{v'}\) and \(\Psi\) (from an agent's perspective), though the agent has does not have a \witness{0} for the \ros{0} between \(\pv{\psi}{v'}\) from \(\Psi\) --- or more naturally stated, though the agent has not concluded \(\pv{\psi}{v'}\) from \(\Psi\).

  Indeed, this is exactly what we will argue for.

  To ease some concerns, and to anticipate an important issue that we will consider later,%
  \footnote{
    This distinction will return in \autoref{cha:zSpAwhy}.
  }
  this section outlines an important distinction.
\end{note}

\begin{note}
  Consider the following distinction:
  \begin{enumerate}[label=\arabic*., ref=(\arabic*)]
  \item
    \label{Embed:no}
    A \ros{0} between \(\pv{\psi}{v'}\) and \(\Psi\).
  \item
    \label{Embed:yes}
    A \ros{0} between \(\Phi\) and \(\pv{\phi}{v}\), where:
    \begin{itemize}
    \item
      \(\Phi\) contains the proposition-value-premises pairing:
      \begin{itemize}
      \item
        \(\pv{\text{A \ros{} between }\pv{\psi}{v'}\text{ and }\Psi}{\text{True}}\)
      \end{itemize}
    \end{itemize}
  \end{enumerate}

  \ref{Embed:no} is a straightforward \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\).
  By contrast, \ref{Embed:yes}, is a \ros{} between \(\pv{\phi}{v}\) and \(\Phi\), where the \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) is \emph{embedded} as a premise.
\end{note}

\begin{note}
  Now, suppose an agent does not have a \witness{0} for the \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\).
  The upshot of the distinction between~\ref{Embed:no} and~\ref{Embed:yes} is as follows:

  \begin{itemize}
  \item
    If the \ros{0} of \ref{Embed:no} is, in part, an answer to \qWhyVnP{} then the \ros{0} is a counterexample to \issueConstraint{}.
  \item
    If the \ros{0} of \ref{Embed:yes} is, in part, an answer to \qWhyVnP{} then the \ros{0} is \emph{not} a counterexample to \issueConstraint{}.
  \end{itemize}

  Distinction, but what is the difference?

  \ros{}, from agent's perspective.
  Hence, \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) and the proposition that there is a \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) paired with the value `True' seems equivalent.

  Whether there is a significant difference between the two, this is something I am not clear on.
  This is not the focus.
  Rather, the difference is \emph{how} the \ros{} functions with respect to the agent pairing \(\phi\) with \(v\).
  Whether the \ros{} functions as a premise when the agent concludes \(\pv{\phi}{v}\), or whether the \ros{} functions in a way that is different to a premise.

  What we capture by \ros{} as answer to \qWhyVnP{} and proposition-value pair which captures \ros{} is not necessarily a difference in reference, but a difference in function.%
  \footnote{
    Idea is somewhat familiar from propositional logic.
    Certain kind of equivalence between proof and conditional.
    It is possible to find a corresponding conditional to any proof with a finite number of premises, proof captures derivation of conclusion from premises.

    Corresponding conditional is not a premise, nor any part, of the proof.

    For example, consider a proof from \(P\) and \(P \rightarrow Q\) to \(Q\) by conditional detachment.
    Corresponding conditional is \((P \land (P \rightarrow Q)) \rightarrow Q\).
    However, not part of the proof.

    Intuitive distinction between what a proof and a conditional refer to.
    However, informally there is no difficulty in treating a proof as a premise.
    \(P\), and I have a proof of \(P \rightarrow Q\), therefore \(Q\).
  }
\end{note}

\begin{note}
  Start to see a difference by considering \(\pv{\phi}{v}\) and \(\Phi\).
  For, \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).
  However, immediate difficulties if the proposition that there is a \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) paired with the value `True' is a member of \(\Phi\).

  Likewise, \ros{} between the single premise and \(\pv{\phi}{v}\) is, intuitively, distinct from \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).

  \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) results from an event in which an agent concludes \(\pv{\phi}{v}\) from \(\Phi\).
  By contrast, \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) results from an event in which an agent concludes \(\pv{\phi}{v}\) from the \ros{} between \(\pv{\phi}{v}\) and \(\Phi\).
\end{note}

\begin{note}
  Significance for arguments is that dependence captured by \qWhyVnP{} does not amount to the \ros{} being a premise.
\end{note}

\section{Literature}
\label{cha:clar:literature}

\begin{note}
  \autoref{sec:variants-initial} introduced variants to \qWhy{}, \qHow{}, and \issueInclusion{}.

  Linked together.

  In short, having a \witness{0} for a \ros{} is necessary for the \ros{} to, in part, explain why an agent concluded.

  Primary motivation is intuition.
  \scen{1} such as \autoref{illu:gist:calc}.

  Motivated via \citeauthor{Davidson:1963aa}.
  Though, \citeauthor{Davidson:1963aa} was a little more general.

  In this section we collect a handful of extracts from the literature which suggest this intuition is not merely an intuition, but a common theoretical constraint.

  Provide extract.
  Observe how plausibly understood in terms of \witness{} and constraint.

  In many cases, constraint is given by identification with \witness{}.
  In turn, understand this to implicitly constrain an answer to why.

  With causal accounts, more or less immediate.
  Nothing that is non-causal
\end{note}


\subsection{Causal}
\label{cha:clar:literature:causal}

\begin{note}
  Causal theories of reasoning.

  Broadly, premises stand in a causal relation to conclusion.

  Cause is something which happens, therefore \witness{}.
  What is relevant to the activity is given why causal process..
\end{note}

\subsubsection{\textcite{Armstrong:1968vh}}

\begin{note}
  We being with~\cite{Armstrong:1968vh}'s (\citeyear{Armstrong:1968vh}) account of inferring.

  \begin{quote}
    We are not concerned here with logicians' questions about inference, but solely with the psychological process of inferring.
    The primary sense of the word is that in which it involves acquiring a belief on the basis of a belief already held.

    \mbox{}\hfill\(\vdots\)\hfill\mbox{}

    \dots to say that A infers \emph{p} from \emph{q} is simply to say that A's believing \emph{q} \emph{causes} him to acquire the belief \emph{p}.
    And the sense of `cause' employed here is the common or billiardball sense of `cause', whatever that sense is.%
    \mbox{}\hfill\mbox{(\citeyear[194]{Armstrong:1968vh})}
  \end{quote}

  \citeauthor{Armstrong:1968vh} tightens the account of inference a little in order to avoid including any belief \emph{r} in the causal chain leading to an agent acquiring the belief \emph{p} as a premise, but we set these details aside.
  (\citeyear[195--197]{Armstrong:1968vh})%
  \footnote{
    Indeed, any disagreement with \citeauthor{Armstrong:1968vh}'s restriction is of no real interest to us.
    For, if we grant that the relevant instance of causation provides a \witness{} for a \ros{}, then, re-expressed, \citeauthor{Armstrong:1968vh}'s revisions narrow down the \witness{1} of interest.
  }

  \citeauthor{Armstrong:1968vh} talks about `inference' rather than `conclusion'.
  However, plausibly the same thing.
  Belief \(\phi\) only if pair \(\phi\) with value `true'.
\end{note}

\begin{note}
  Of some interest.
  \citeauthor{Armstrong:1968vh} traces the causal account of inference to ~\citeauthor{Moore:1962up} and Hume.
\end{note}

\paragraph{\textcite{Boghossian:2014aa}}

\begin{note}
  Seen above.
  Causal process.

  \citeauthor{Boghossian:2014aa}'s Taking Condition narrows the relevant causal processes.
  However, causal processes, and hence to matter, causally involved.
  If causally involved, then witness.
\end{note}

\subsection{Indeterminate}
\label{sec:indeterminate}

\paragraph{\textcite{Wright:2014tt}}

\begin{note}
  \citeauthor{Wright:2014tt}'s (\citeyear{Wright:2014tt}) `Simple Proposal'.
  Appealed to the Simple Proposal above on \autopageref{Wright-simple-supportI} to help clarify \supportI{}.

  Here, observation is on acceptance and move.
  Recall, the core of the Simple Proposal is the following idea:

  \begin{quote}
    [A] thinker infers q from p\(_{1}\) \(\cdots\) p\(_{\text{n}}\) when he accepts each of p\(_{1}\) \(\cdots\) p\(_{\text{n}}\), moves to accept q, and does so for the reason that he accepts p\(_{1}\) \(\cdots\) p\(_{\text{n}}\).%
    \mbox{}\hfill\mbox{(\citeyear[33]{Wright:2014tt})}
  \end{quote}

  Accepting and moving provides a \witness{}, and inferring is understood via the \witness{}.
\end{note}

\paragraph{\textcite{Broome:2002aa}}

\begin{note}
  The same observation extends to \citeauthor{Broome:2002aa}'s (\citeyear{Broome:2013aa}) rule following account of (active) reasoning.

  \begin{quote}
    Active reasoning is a particular sort of process by which conscious premise-attitudes cause you to acquire a conclusion-attitude.
    The process is that you operate on the contents of your premise-attitudes following a rule, to construct the conclusion, which is the content of a new attitude of yours that you acquire in the process.\newline
    \mbox{ }\hfill\mbox{(\citeyear[234]{Broome:2002aa})}
  \end{quote}

  Understand relation of \support{} entailed by an event in which an agent concludes \(\pv{\phi}{v}\) from \(\Phi\) by~\supportI{} in terms of having followed a rule.
  However, if this entailment holds then the converse entailment, that the agent concluded by following the rules that gave rise to relation of \support{} does not hold.
\end{note}

\subsection{Non-causal}
\label{sec:non-causal}

\paragraph{\textcite{Harman:1973ww}}

\begin{note}
  \begin{quote}
    Reasons may or may not be causes; but explanation by reasons is not causal or deterministic explanation.
    It describes the sequence of considerations that led to belief in a conclusion without supposing that the sequence was determined.%
    \mbox{ }\hfill\mbox{(\citeyear[52]{Harman:1973ww})}
  \end{quote}

  Sequence of considerations provides a \witness{}.
\end{note}

\paragraph{\textcite{Hieronymi:2011aa}}

\begin{note}
  More broadly, though similar.
  \citeauthor{Hieronymi:2011aa}'s (\citeyear{Hieronymi:2011aa}) account of acting for reasons.

  \begin{quote}
    The proposal starts with this simple thought: whenever an agent acts for reasons, the agent, in some sense, takes certain considerations to settle the question of whether so to act, therein intends so to act, and executes that intention in action.

    If this much is uncontroversial (and, under some interpretation, I believe it must be), we can use it as a form for filling out.
    I propose, then, that we explain an event that is an action done for reasons by appealing to the fact that the agent took certain considerations to settle the question of whether to act in some way, therein intended so to act, and successfully executed that intention in action.
    I suggest that \emph{this} complex fact, \dots is the reason that rationalizes the action---that explains the action by giving the agent’s reason for acting.\newline
    \mbox{ }\hfill\mbox{(\citeyear[431]{Hieronymi:2011aa})}
  \end{quote}

  So, reason is the complex fact.
  Complex fact gives the reason the agent acted, and so content of constituent considerations from agent's perspective.

  In particular, note here that everything is directed at the question.
  Premise-conclusion relationship.

  As with \citeauthor{Harman:1973ww}, capture the trace, which is given by a \witness{}.
\end{note}

\subsection{Normative}

\begin{note}[Responding to reasons]
  As final motivation, consider the proposal at the core of \citeauthor{Lord:2018aa}'s (\citeyear{Lord:2018aa}) thesis that being rational is to correctly respond to reasons.

  \begin{quote}
    \textbf{Correctly Responding:} What it is for A's \(\phi\)-ing to be ex post rational is for A to possess sufficient reason S to \(\phi\) and for A's \(\phi\)-ing to be a manifestation of knowledge about how to use S as sufficient reason to \(\phi\).%
    \mbox{}\hfill\mbox{(\citeyear[143]{Lord:2018aa})}
  \end{quote}

  An agent's action is rational only if the action is a manifestation of some know-how.
  \citeauthor{Lord:2018aa} summaries:

  \begin{quote}
    \dots when one manifests one's know-how, dispositions that are directly sensitive to normative facts are manifesting. Thus, the competences involved in the relevant know-how make one directly sensitive to the normative facts%
    \mbox{}\hfill\mbox{(\citeyear[16]{Lord:2018aa})}
  \end{quote}

  For our purposes, following example of manifesting know-how directly relates to reasoning:

  \begin{quote}
    The most salient disposition [when appealing to \emph{p} as a reason]%
    \footnote{Note, \citeauthor{Lord:2018aa} (explicitly) not talking about believing that \emph{p} is a reason, but argues that the cited disposition to present both when appealing to p as a reason and believing that \emph{p} is a reason.}
    is the disposition to (competently) use \emph{p} as a premise in reasoning.%
    \mbox{}\hfill\mbox{(\citeyear[25]{Lord:2018aa})}
  \end{quote}

  Hence, suppose an agent concludes.
  Then, if the agent does not witness reasoning from pool of premises, it seems the agent does not manifest know-how, which is required for the appeal to meet \citeauthor{Lord:2018aa}'s account of rational action.

  Of course, that the noted disposition is the most salient does not rule out alternative, less noteworthy, dispositions.
  However, it is unclear to me how to \emph{manifest} know-how without a \witness{}.
\end{note}

\begin{note}[Illustration]
  Clear that there is no manifestation of understanding of arithmetic.
\end{note}

\subsection{Embedding}
\label{sec:embedding}

\begin{note}
  So, in initial cases, plausible that constraint in terms of having a \witness{}.

  In other cases, embedding.
\end{note}

\begin{note}
  An initial borderline case is \citeauthor{Boghossian:2014aa}'s taking condition.
  Depending on how `taking' is understood, embedded within \ros{}.
  In particular, distinguished proposition-value pairs from attitudes, and hence this does not amount to reducing the taking condition to a doxastic condition.
\end{note}


\subsubsection{\textcite{Thomson:1965vv}}

\begin{note}
  \citeauthor{Thomson:1965vv} suggests a an account of reasoning such that an agent reasons from \(\phi\) to \(\psi\) just in case the agent believes that \(\phi\) is a reason for \(\psi\).
  \begin{quote}
    The claim which the 'formula' of p.\ 285\nolinebreak
    \footnote{
      The `formula' in question:
      \begin{quote}
        Now reasoning should surely involve drawing a conclusion from a set of premisses.
        But you can't be said to draw the conclusion that \emph{q} from \emph{p} if for all you know in knowing that \emph{p} it would at best be a matter of luck if \emph{q} as well.
        So to ``reason'' from \emph{p} by itself to \emph{q} isn't really to be reasoning; it's like saying one thing, and then taking a chance on it that something else is also true---like taking a leap in the dark, or more prosaically, like guessing.'
        (From here on I shall refer to this as the `\emph{formula}'.)\nolinebreak
        \mbox{}\hfill\mbox{(\citeyear[285]{Thomson:1965vv})}
      \end{quote}
    }
    above was to support was this:
    suppose \emph{p} does not imply \emph{q}, and suppose a man says `\emph{p}, so \emph{q}';
    then he is not reasoning in saying this unless he believes that \emph{r}, where the conjunction of \emph{p} and \emph{r} implies \emph{q}, and \emph{r} is a suppressed premiss of his reasoning.\par
    But suppose such a man believes that \emph{p} is reason for \emph{q}; would this not be enough?
    `It would if ``\emph{p} is reason for \emph{q}'' were construed as a suppressed premiss of his argument'.
    Then let us so construe it.\newline
    \mbox{}\hfill\mbox{(\citeyear[294]{Thomson:1965vv})}
  \end{quote}
  Causation is absent from \citeauthor{Thomson:1965vv}.
  Does not imply that \citeauthor{Thomson:1965vv}'s proposal is independent of causation, but motivated does not appeal to causation.
\end{note}

\subsubsection{\textcite{Longino:1978wv}}

\begin{note}
  \citeauthor{Longino:1978wv}'s (\citeyear{Longino:1978wv}) account of inferring seems explicit.
  \begin{quote}
    S infers at t that p from x if and only if
    \begin{enumerate}[label=\arabic*]
    \item
      S at t comes to believe that p, and
    \item
      S's epistemic reason for believing that p at t is x, i.e.,
      \begin{enumerate}[label=\alph*]
      \item
        S takes x to be evidence that p, and
      \item
        S's taking x to be evidence that p causes S to believe that p.\newline
        \mbox{}\hfill\mbox{(\citeyear[22]{Longino:1978wv})}
      \end{enumerate}
    \end{enumerate}
  \end{quote}
  Causation between mental states, but explanatory relation between things.
\end{note}

\subsection{\ros{3}?}

\begin{note}
  A recent account of reasoning given by \cite{Valaris:2014un} (\citeyear{Valaris:2014un}) is separate from \witness{} and embedding.%
  \footnote{
    For simplicity we ignore \citeauthor{Valaris:2014un}'s distinction between basic and non-basic instances of reasoning.
    The excerpts concern non-basic reasoning.
  }

    \begin{quote}
    Suppose that one believes \emph{R} and that \emph{p} follows from \emph{R}.
    What else might it take for one to count as believing \emph{p} by reasoning from \emph{R}?
    The crucial point here is that, if one believes both \emph{R} and that \emph{p} follows from \emph{R}, then --- barring inattention or irrationality --- one thereby believes \emph{p}.
    \dots
    In general, the relation between believing that one has conclusive evidence for a proposition and believing that proposition is constitutive, not merely causal.%
    \mbox{ }\hfill\mbox{(\citeyear[110 ]{Valaris:2014un})}
  \end{quote}

  Distinct from \witness{} because only interest is belief.
  Distinct from embedding because constitutive.
  In other words, the agent does not reason from their belief.
  Rather, reasoning is the belief.

  Inclined to understand in terms of \ros{}.
  For our purposes, role of \ros{} is to capture relationship between premises and conclusion.
  However, understood in a particular way, may amount to a belief.

  Still, not so straightforward.
  How does on get the belief that \emph{p} follows from \emph{R}?
  This, to my mind, is what is at issue.
  However, it seems that this is not how things are for \citeauthor{Valaris:2014un}.

  \begin{quote}
    [R]easoning just is believing that one’s conclusion follows from one’s premisses, and thereby believing one’s conclusion.%
    \mbox{ }\hfill\mbox{(\citeyear[112]{Valaris:2014un})}
  \end{quote}

  Unless belief is process, then it seems reasoning understood in this way is instantaneous.

  I am not sure what to make of this.
\end{note}


\section{Wrangling}
\label{cha:clar:sec:wrangling}
\label{cha:clar:cha:clar:support-qWhy}
\label{cha:clar:expand:qWhy}

\begin{note}
  \autoref{cha:introduction} introduced two questions, \qWhy{} and \qHow{}, and motivated a constraint between answers to \qWhy{} and \qHow{}.

  \autoref{sec:variants-initial} introduced variants of \qWhy{} and \qHow{}, and a variant constraint.

  \autoref{cha:clar:literature}, in addition to intuition, constraint seems to often be a theoretical assumption.

  Purpose of variants is to motivate counterexamples to constraint.
  Specifically in terms of answers to \qWhyVnP{} which are not answers to \qHowV{}.
  In other words, \ros{} such that \ros{} explains, in part, why agent concludes but is such that the agent does not have a \witness{} for the \ros{}.

  In this section we outline in rough form how we will (attempt) to provide counterexamples.

  In short, need:
  An agent, event in which agent concludes \(\pv{\phi}{v}\) from \(\Phi\), and \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\) such that:

  \begin{itemize}
  \item
    The agent does not have a \witness{} for the \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\).
  \item
    The \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\), in part, answers \qWhyVnP{}.
  \end{itemize}

  Our goal is motivate a general method for generating examples in which some \ros{} for which an agent does not have a \witness{} such that the \ros{} answers \qWhyVnP{}.
\end{note}

\subsection{\ros{3} without a \witness{}}

\begin{note}
  Immediate that an agent may not have a \witness{} for some \ros{}.

  Novel conclusions, as understood in this document, are common.
  Pair a proposition with some value.

  For example, enumerate all the tautologies of propositional logic.
  As \citeauthor{Harman:1973ww} notes, clutter, and there may be little point in deriving the tautologies.
  However, regardless of worth, it is not the case that have a \witness{} for most.

  Likewise, conclusions with respect to actions.
  For example, which particular style of coffee would like as the queue shortens and the time to place an order approaches.
\end{note}

\begin{note}
  More difficult, is \ros{}.

  As sketched in \autoref{cha:clar:support}, idea of a \fc{}.
\end{note}

\begin{note}
  \fc{} is such that action such that after performing action, event in which concludes is in progress.
  In other worlds, the agent would be concluding by performing the action.

  Delicacy.
  \fc{1} and \ros{} from the agent's perspective.

  Two issues:

  \begin{enumerate}
  \item
    If independent of agent's perspective, then it may be the case that \fc{} without any prior recognition from agent.
  \item
    If dependent on agent's perspective, then it may be the case that not a \fc{}.
  \end{enumerate}

  Two issues are important.
  Without agent's perspective, then unclear that get \ros{} of interest for answer to \qWhyVnP{}.
  Given agent's perspective, unclear that we get a \ros{}.
\end{note}

\begin{note}
  Second issue is particularly pressing.
  For, explanations.
  \emph{Factive}.

  Get \ros{} by \fc{}.
  However, may not be the case that \fc{}.
\end{note}

\begin{note}
  Our strategy is to avoid both problems by focusing on cases in which the agent \emph{knows} that \(\pv{\psi}{v'}\) from \(\Psi\) is a \fc{}.

  Hence, suitable link to the agent's perspective, as the agent is aware that \fc{}.
  And, avoid failure of \fc{} by factivity of knowledge.

  In this respect the understanding of \fc{1} in terms of action such that concluding is important.
  With the exception of more-or-less instantaneous actions, future may develop in surprising ways.

  For example, plausible that an agent knows when they strike the cue ball in a certain way, a particular red ball will land in a pocket.
  However, not plausible that the agent knows where the cue ball will come to rest after the red ball lands in the pocket.
  Hence, agent does not know their following more, and so on.

  In parallel, an agent may have no guarantee that they will not be interrupted, etc.
  Hence, in most cases it seems implausible that an agent knows they will concluded.
  Yet, to be concluding does not require completion.

  With respect to \fc{}, whether event in which the agent concludes would be in progress.

  Instances in which an agent knows that concluding would be in progress exist.
  For example, consider basic arithmetic.
  Whether or not \(4131 + 1533 = 5664\) is a \fc{}.%
  \footnote{
    More generally, take any \(n\) and \(m\) such that the process is adding \(n\) and \(m\) would not take too long.
  }
  If you started, would be determining whether or not the equality holds.

  In most cases we will push a little further than addition.
  However, share the same pattern of the conclusion following from the application of some collection of rules which an agent knows.

  For example, enrich the collection of mathematical operations to include subtraction, multiplication, division, square-roots and so on.

  Beyond mathematics, but close, formal logic.
  In particular, theoretical results such tautologies of propositional logic, or meta-theoretical results which are generated from a common method, such as completeness proofs of various modal logics via canonical models.

  And, finally games.

  If you know the appropriate strategy, play first, and so desire, then it is a \fc{0} that any game of noughts and crosses will either end in a win for you or a draw.%
  \footnote{
    For details, see~(\cite[94--96]{Gardner:1983wn}).
  }

  Sudoku puzzles.
  Rules are simple, and I expect that if you have some experience with solving Sudoku puzzles, then you know that the solution to the Sudoku puzzle is a \fc{}.
  In the worst case scenario, you have the option to brute force the solution to the puzzle.

  A slightly more interesting example is chess problems.
  In particular, there is plausibly some bound where solution to a problem fails to be a \fc{}.
  However, any problem within the bound is a \fc{}.
  May not know where the bound is.
  Yet, solutions to some problems within the bound are know to be \fc{1}.
  For example, whether or not there is an available move for some piece is a \fc{1}, but whether there is a sequence of move that will result in checkmate for either player is often not (known) to be a \fc{}.
\end{note}

\begin{note}
  So, via \fc{1} obtain instances of a \ros{1} holding from an agent's perspective without the agent having a \witness{0} for the \ros{0}.

  Hence, candidate \ros{} that may be answers to \qWhyVnP{} such that the agent does not have a \witness{0} for the \ros{0}.

  However, in order for \ros{} to be an answer, in part, to \qWhyVnP{}, dependence.
\end{note}

\begin{note}
  This does not provide a complete solution to problem of factivity.
  For, what distinguishes one case from the other?

  However, this is nothing unique to cases under consideration, so long as relevant instances of \fc{} are plausibly knowledge.

  Though, this still differs from attitudes.
  Here is where embedding is interesting.
  If under constraint of agent's perspective, and \fc{}, then why not embed \fc{} as a premise.
\end{note}

\begin{note}
  Following, distinction between \ros{} answering, in part, \qWhyVnP{} and a \ros{} being embedded in some \ros{}.
  In particular, \ros{} between some \(\pv{\psi}{v'}\) and \(\Psi\) such that distinct from \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) being embedded within the \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) as a premise.
\end{note}

\begin{note}
  Rule out possibility of embedding proposed answers in this way.

  However, this will turn on the way in which dependence holds.
\end{note}

\subsection{Dependence}

\begin{note}
  Now, need it to be the case that if \ros{} failed to hold, then would not conclude.

  Suitable link between conclusion of \(\pv{\phi}{v}\) form \(\Phi\) and \ros{} between \(\pv{\psi}{v'}\) and \(\Psi\).

  \fc{3} serve an equally important role.

  For, if \fc{} then \ros{}.
  Conversely, if no \ros{} then not \fc{}.
  Hence, if fails to be \ros{}, then fails to be \fc{}.
  In turn, agent concludes only due to \fc{}, then suitable link.
\end{note}

\begin{note}
  Difficulty.
  How is it the case that the agent concludes only due to \fc{}?

  Method is to consider a variant of \qWhyVnP{}.
\end{note}

\begin{note}
  \begin{restatable}[\qWhyV{}]{question}{questionWhyV}
    \label{q:why:v}
    Given an agent \vAgent{}, proposition-value pair \(\pv{\phi}{v}\), pool of premises \(\Phi\), and event \(e\) in which \vAgent{} concludes \(\pv{\phi}{v}\) from \(\Phi\):

    \begin{quote}
      Which proposition-value-premises pairings \(\pvp{\psi}{v'}{\Psi}\) are such that, when \vAgent{} pairs \(\phi\) with \(v\):

      \begin{enumerate}[label=]
      \item
        \begin{enumerate}[label=\alph*., ref=(\alph*), series=qWhyVDef]
        \item
          \support{2} between \(\pv{\psi}{v'}\) and \(\Psi\) holds, from \vAgent{}' perspective.
        \end{enumerate}
      \end{enumerate}

      And, from \vAgent{}' perspective:

      \begin{enumerate}
      \item[\emph{If}:]
        \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=qWhyVDef]
        \item
          \support{2} failed to hold between \(\pv{\psi}{v'}\) and \(\Psi\) when pairing \(\phi\) with \(v\)(, from \vAgent{}' perspective).
        \end{enumerate}
      \item[\emph{Then}:]
        \begin{enumerate}[label=\alph*., ref=(\alph*), resume*=qWhyVDef]
        \item
          \(e\) would not have been an event in which \vAgent{} concluded \(\pv{\phi}{v}\) from \(\Phi\).
        \end{enumerate}
      \end{enumerate}
    \end{quote}
    \vspace{-\baselineskip}
  \end{restatable}

  \fc{3} provide an account of how get the link:

  \begin{itemize}
  \item
    \support{2} failed to hold between \(\pv{\psi}{v'}\) and \(\Psi\) when pairing \(\phi\) with \(v\)(, from \vAgent{}' perspective).
  \item
    \(\pv{\psi}{v'}\) failed to be a \fc{} from \(\Psi\).
  \item
    \(e\) would not have been an event in which \vAgent{} concluded \(\pv{\phi}{v}\) from \(\Phi\).
  \end{itemize}

  Given that \ros{1} are something of an abstraction, interest is really in whether \fc{}.
\end{note}

\begin{note}
  The idea is:

  Counterexamples.

  One option is to specify (apparent) counterexamples so that the truth of the \emph{if-then} conditional follows.
  Then, at issue is whether analysis is correct.
  It may be that the truth of the conditional does not follow.

  Other option, specify (apparent) counterexamples so that the \emph{if-then} conditional holds from the agent's perspective.
  Then, at issue is whether the agent's perspective is correct.

  Trade a issue about analysis of counterexamples for a issue about what the counterexample achieves.

  Preference for the second option is ease of specifying examples.
  Build up an understanding of how and why such examples arise, and then try to figure out whether they result in anything substantial rather than attempting to analyse examples.

  On first, whether analysis is correct.

  On second, whether agent is correct.
\end{note}

\begin{note}
  So, dependence is captured from the agent's perspective and task is to construct \scen{1} such that this is the case.

  Two issues:
  \begin{enumerate}
  \item
    Is it the case that \scen{1} exists?
    Do\fc{1} ever matter in this way?
  \item
    Is the agent's perspective lead to truth of conditional from \qWhyVnP{}?
  \end{enumerate}

  We will not sketch \scen{1} here.
  Interest is with the relation between agent's perspective on conditional and conditional.
\end{note}

\subsubsection{Perspective}

\begin{note}
  Subdividing problem further, there are two concerns.

  \begin{enumerate}
  \item
    Is agent's perspective informative?
  \item
    Granting true from agent's perspective, is informative, may it still be the case that \ros{} fails to answer \qWhyVnP{}.
  \end{enumerate}

  Roughly, motivation to think agent's perspective tells us anything about what actually happens.
  And, even if it does, do things work out in as they do from the agent's perspective.

  Develop the concerns in a little more detail.
\end{note}


\paragraph{Perspective alone}

\begin{note}
  The \emph{if-then} conditional is characterised from the agent's perspective, in part, to allow for ease considering possible answers to \qWhyV{}.
  And, a significant portion of this document will focus on providing examples.

  However, as the \emph{if-then} conditional is characterised from the agent's perspective a problem arises.
  For, it may be the case that that \emph{if-then} conditional holds from the agent's perspective but does not hold independently of the agent's perspective.
  Hence, the sense of dependence captured by \qWhyV{} is not equivalent with the intuitive sense of dependence captured by considering whether or not the \emph{if-then} conditional holds independently of the agent's perspective.

  The observation that the \emph{if-then} conditional may hold from the agent's perspective while failing to hold independently of the agent's perspective is clearest when considering conditionals more general.

  For example, suppose an agent has taken a gamble on a coin landing heads.
  The coin lands heads, and the agent receives a prize.
  From the agent's perspective, if the coin failed to lands heads, then the agent would not have received the prize.
  However, the agent was set to receive the prize for participating in the gamble, regardless of whether the coin landed heads.%
  \footnote{
    The present point is similar to issues raised by \citeauthor{Harman:1973ww} (\citeyear{Harman:1973ww}) regarding the proposed equivalence between reasons for which an agent believes something with reasons the agent would offer if asked to justify their belief.
  As \citeauthor{Harman:1973ww} notes, an agent may offer reasons because they think they will convince their audience, not because the agent is compelled by the reasons, etc.
  (\citeyear[Ch.2]{Harman:1973ww})

  To the extent that \citeauthor{Harman:1973ww}'s point is that what holds from an agent's perspective need not actually be the case, the point in the same.
  However, to the extent that \citeauthor{Harman:1973ww} relies on an under-specification of what holds from an agent's perspective --- i.e.\ the distinction between whether \(\phi\) has value \(v\) from the agent's perspective or whether the agent evaluates as true the proposition that their audience is responsive to \(\phi\) having value \(v\), the point is distinct.
  }

  So, switching back to \qWhyV{}, it may be the case that, though from the agent's perspective they would not have concluded \(\pv{\phi}{v}\) from \(\Phi\) if \support{} failed to hold between \(\pv{\psi}{v'}\) and \(\Psi\), the agent would have concluded \(\pv{\phi}{v}\) from \(\Phi\) regardless.
\end{note}


\begin{note}
  In order for \qWhyV{} to be of interest, must be cases where the agent's perspective is correct.

  \begin{proposition}
    \label{prop:why-n-p-link}
    Instances where \(\pvp{\psi}{v'}{\Psi}\) answers \qWhyVnP{} in virtue of answering \qWhyV{}
  \end{proposition}

  Find instances which witness the truth of \autoref{prop:why-n-p-link}.

  Stress, \autoref{prop:why-n-p-link} does not amount to an entailment.
  They may be cases where agent's perspective returns an answer to \qWhyV{} which is not an answer to \qWhyVnP{}.
\end{note}

\begin{note}
  So, the only thing to do is ensure the agent's perspective is correct.

  However, motivation in similar style to \fc{1}.
  \fc{3} focus on whether agent would conclude.
  Pair is knowing that the agent would not conclude.
  So, in parallel fashion, knowledge.
\end{note}

\paragraph{Quarantine}

\begin{note}
  So, embedding.

  Basically, concern about not being a \fc{}.
  Then, adding premise that is a \fc{} doesn't do any work.
\end{note}

\begin{note}
  Still, this isn't quite enough.
  What about some other explanation.

  If there is some general method to quarantine, then avoid worries about the link breaking.
  Deny the proposition holds.
  Separate agent's perspective from what happens.

  However, if no general method to quarantine.
  Then, more difficult.
  Something problematic about agent.

  Whether break the agent's perspective from what matters.

  Task: \fc{} matters from agent's perspective, but does not matter apart.
  Argue that this is not possible.
  To do this, relevant \fc{} does not embed.

  Does not function as an attitude.
\end{note}

\paragraph{Unsorted}

\begin{note}
  Start with \citeauthor{Davidson:1963aa}.
  Observe, attitudes, rather than the contents of attitudes.
  Here, this relates to \citeauthor{Dancy:2000aa} and \citeauthor{Collins:1997wn}.
  Whether the attitude explains or whether the contents of the attitude explain.

  However, \citeauthor{Davidson:1963aa} is pushed further, whether the attitude explains in the right way.
  Deviant causal chains.
\end{note}

\begin{note}
  Now, our interest is from the agent's perspective.
  Hence, we are not looking for anything beyond the agent's attitude, following \citeauthor{Davidson:1963aa}.

  However, in contrast to \citeauthor{Davidson:1963aa}, \ros{} does not reduce to an attitude.
  Connexion between \(\pv{\phi}{v}\) and \(\Psi\) captured by \ros{} parallels the causal relation \citeauthor{Davidson:1963aa} identifies between reason and action.

  Paraphrase \citeauthor{Davidson:1963aa} in our account by saying the \ros{} holds between content of reason and action.

  Therefore, have a middle ground.
  On the one hand, not looking for \ros{1} to explain --- \ros{1} are only of interest from an agent's perspective.
  On the other hand, \ros{} without \witness{} --- it must still be the case that \ros{} matters, even though the agent has not concluded \(\pv{\psi}{v'}\) from \(\Psi\).
\end{note}

\begin{note}
  As a middle ground, inherit the problematic aspect of \citeauthor{Dancy:2000aa}.
  It may be the case that the \emph{if-then} conditional fails.
  And, may be tempted to generalise in the style of \citeauthor{Davidson:1963aa}.
  Agent's perspective that the \emph{if-then} conditional holds, and in turn this is viewed as a premise.
  As we have seen above, as a premise, of no direct interest.
\end{note}

\begin{note}
  So, look.
  The thing is that in contrast to \citeauthor{Dancy:2000aa}, I am not looking for an entailment.

  Instead, the point is that agent's perspective provides an understanding of how dependence holds, and it turns out that the agent's perspective is correct.

  If so, the issue is motivating this and avoiding embedding.
\end{note}

\begin{note}
  Therefore, require a \witness{} in order to ensure that the \ros{} exists.
\end{note}

\begin{note}
  Factive and perspective is correct.
  If this is the case, then need a method of reducing to something factive.
  The only plausible way to reduce to something factive is to embed within a \ros{}.
  No embedding in relations of support.
  So, either reject factive or reject perspective.

  This is interesting, because typically the case that motivate factive by observing that it preserves the role of the agent's perspective.
\end{note}

\subsection{\qWhyVnP{} and \qWhyV{}}
\label{cha:clar:expand:qWhy:variant}

\subsubsection{The \ros{} between \(\pv{\phi}{v}\) and \(\Phi\)}

\begin{note}
  Before turning to dependence, let us briefly observe that the \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) should always, intuitively, be, in part, an answer to \qWhyV{}.

  For, when agent pairs \(\phi\) with \(v\), then by \supportI{}, it is the case that \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) holds from the agent's perspective.
  Hence, \ref{q:why:v:a} must be true.

  Likewise, immediately the case that if \support{} failed to hold, then the agent would not have concluded \(\pv{\phi}{v}\) from \(\Phi\).
  For, by the same reasoning, when the agent pairs \(\phi\) with \(v\), then by \supportI{}, it is the case that \ros{} between \(\pv{\phi}{v}\) and \(\Phi\) holds from the agent's perspective.
  Therefore, if \support{} fails to hold between \(\pv{\phi}{v}\) and \(\Phi\), then \(e\) is not an event in which the agent concludes \(\pv{\phi}{v}\) from \(\Phi\).

  Now, the conditional when set aside from the agent's perspective may be true, it need not be the case that the conditional is true from the agent's perspective.
  However, we are working at some level of abstraction, and hence we assume the agent recognises the truth of the \emph{if-then} conditional.
  Indeed, we have merely expressed in artificial terms a truism:
  The agent would not have concluded \(\pv{\phi}{v}\) from \(\Phi\) if the agent had failed to conclude \(\pv{\phi}{v}\) from \(\Phi\).
\end{note}

\begin{note}
  With the core case of \support{} between \(\pv{\phi}{v}\) and \(\Phi\) being an answer to \qWhyV{} in hand, we turn to an in depth discussion of the kind of dependence captured by the \emph{if-then} conditional of \qWhyV{}.

  Our task is to balance a form of dependence that \emph{may} lead to counterexamples to \issueInclusion{} with an account of dependence that is compatible with the intuition that motivates \issueInclusion{}.
  In other words, the dependence should be such that answers to \qWhyV{} are constrained by the condition that the agent has a \witness{} for the relevant \ros{}.
\end{note}

\subsection{Difficulties}
\label{sec:qwhyv-subs-paragr}

\begin{note}
  Might be suspect, given voluntarism about concluding.
  But, this, I think, is a mistake.
  There's no suggestion that agent may choose whether or not to conclude in these types of cases.
  No choice over whether conditional is true.
\end{note}

\subsection{\citeauthor{Owens:2006tw}}

\begin{note}
  For example, \citeauthor{Owens:2006tw} argues for a belief expression model of assertion in which the rationality of a belief formed by an agent via testimony is connected to justification of the testifier:

  \begin{quote}
    Trusting an expression of belief by accepting what a speaker says involves entering a state of mind which gets its rationality from the rationality of the belief expressed.
    This state's rationality depends on the speaker's justification for the belief he expresses, not on his justification for the action of expressing it.
    And to hear a speaker as making a sincere assertion, as expressing a belief, is \emph{ceteris paribus} to feel able to tap into \emph{that} justification (whether or not his assertion was directed at you) by accepting what he says.%
    \mbox{}\hfill\mbox{(\citeyear[123]{Owens:2006tw})}
  \end{quote}

  On the view advanced by \citeauthor{Owens:2006tw}, justification.
  View in terms of \support{}.

  \support{} directly.
  Rationality of agent is rationality of speaker.

  However, `depends'.

  Distinction between rationality of state, and relation between rationality of state and rationality of state.

  Inclined to think \citeauthor{Owens:2006tw} is arguing for the former.%
  \footnote{
    \begin{quote}
      If we are to believe what the speaker indicates he believes, either the speaker must justify this belief to us, or we must supply some justification of our own
      \dots
      Neither act can be part of a rationality preserving mechanism for belief.%
      \mbox{ }\hfill\mbox{(\citeyear[123--124]{Owens:2006tw})}
    \end{quote}
  }
  Though, it is not clear to me that embedded isn't a viable option.

  Regardless, distinction that is important.
\end{note}

\begin{note}
  Same distinction holds for answers to \qWhyV{}.

  It may be the case that \support{} between \(\pv{\psi}{v'}\) and \(\Phi\) is, from the agent's perspective, involved in concluding \(\pv{\phi}{v}\) from \(\Phi\).

  However, no immediate move from this to \support{} being, in part, an answer to \qWhyV{}.
\end{note}

\subsection{Summary}
\label{cha:clar:expand:issue:summary}

\begin{note}
  Three key things.

  Support.
  Witnessing.
  Issue.
\end{note}

\begin{note}
  Focus on \issueConstraint{}.
  \vspace{-\baselineskip}
  \begin{quote}
    \rIssueConstraint*
  \end{quote}
  Sufficient clarity on both `why?' and `how?'.
  Link we have argued for.
  And, further, independently of argument, it seems to me that a positive resolution to \issueConstraint{} is equally compelling as positive resolution to \issueInclusion{}.
\end{note}

\begin{note}
  This is the important thing, and in this respect it doesn't matter whether past or present.
  Whether a \support{} holds only if witnessed.
  Whether resolution to \qWhy{} only if the agent has witnessed.
\end{note}

\begin{note}
  Difficulty with all of this is that the accounts seem to be consistent, but do not explicitly motivate this constraint.
\end{note}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% End:
