\chapter{Additional examples of \fc{1}}
\label{cha:addit-exampl-fcs1}

\subsection{\scen{3} where some \prop{0}-\val{0} pair is a \fc{}}

\begin{note}[Propositional logic]
  \begin{scenario}[Propositional theorems]
    \label{illu:sketch:prop-logic}
    Suppose an agent has a good grasp of propositional logic.
    In particular:
    The agent has a good understanding of some method to construct semantic proofs.
    For example, by constructing truth tables, or reasoning about valuation functions.
  \end{scenario}

  Given the agent's understanding of propositional logic, the following is a \fc{}:
  \begin{itemize}
  \item
    For any valuation \(v\), \(v \vDash ((P \rightarrow Q) \rightarrow P) \rightarrow P \)
  \end{itemize}

  There's nothing particularly special about the formula.
  Given a good understanding, any formula of a reasonable length will do.

  Note, the agent is concluding.
  It's fine for the agent to work things through on a piece of paper.
\end{note}


\begin{note}[Poppies]
  To finish, we take something from literature:

  \begin{scenario}[Poppies]
    \label{illu:fc:poppies}
    \mbox{ }
    \vspace{-\baselineskip}
    \begin{quote}
      Was Tarquinius Superbus in seinem Garten mit den Mohnköpfen sprach, verstand der Sohn, aber nicht der Bote.

      [What Tarquinius Superbus said in the garden by means of the poppies, the son understood but the messenger did not].\newline
      \mbox{ }\hfill\mbox{(\cite[190]{Hamann:1822vp}/\cite[3]{Kierkegaard:1983ta})}
  \end{quote}
  \vspace{-\baselineskip}
  \end{scenario}

  \noindent The quote is from the epigraph to~\citeauthor{Kierkegaard:1983ta}'s \hyperlink{cite.Kierkegaard:1983ta}{Fear and Trembling}.
  \hyperlink{cite.Kierkegaard:1983ta}{H.\ Hong and E.\ Hong} detail the relevant background:

  \begin{quote}
    When the son of Tarquinius Superbus had craftily gotten Gabii in his power, he sent a messenger to his father asking what he should do with the city.
    Tarquinius, not trusting the messenger, gave no reply but took him into the garden, where with his cane he cut off the flowers of the tallest poppies.
    The son understood from this that he should eliminate the leading men of the city.%
    \mbox{ }\hfill\mbox{(\citeyear[339]{Kierkegaard:1983ta})}
  \end{quote}

  \noindent For Superbus' son, but not for the messenger the following was a \fc{} from some \pool{}:

  \begin{enumerate}[label=C\thescenarioCounter., ref=(C\thescenarioCounter)]
  \item
    \label{illu:fc:poppies:c}
    \pv{\propI{Eliminate the leading men of the city}}{\valI{Should}}
  \end{enumerate}

  \noindent Or, at least, Superbus \emph{expected}~\ref{illu:fc:poppies:c} be a \fc{} for his son {\color{blue} after the son sees the poppies}.
\end{note}

\subsection{\scen{3} where a \prop{0}-\val{0} pair is not a \fc{}}

\paragraph*{Lack of capacity}

\begin{note}[Chess II]
  Consider \autoref{illu:fc:chess:II} in the same context as \autoref{illu:fc:chess:I}:

  \begin{scenario}[\citeauthor{Emms:2000aa}' Puzzle 150 (\citeyear[33]{Emms:2000aa})]%
    \label{illu:fc:chess:II}%
    \mbox{ }\hfill%
    \begin{adjustbox}{minipage=\linewidth,scale=0.8}
      \centering
      \newchessgame[
      setwhite={ka5,pa3,pb4,pc4,pe5,pf6,bg5,bh5},
      addblack={pa6,pb7,pc6,pe6,pf7,kc7,nd7,nd4},
      ]%
      \setchessboard{showmover=false}%
      \chessboard
    \end{adjustbox}%
    \label{fig:chess:intro}%
    \hfill\mbox{ }

    \begin{center}
      It is possible for Black to checkmate in four moves?
    \end{center}
    \vspace{-\baselineskip}
  \end{scenario}

  \noindent The conclusion of interest is:

  \begin{enumerate}[label=C\thescenarioCounter., ref=(C\thescenarioCounter)]
  \item
    \label{illu:fc:chess:II:c}
    \pv{\propI{Black checkmates in four moves}}{\valI{Possible}}
  \end{enumerate}

  The difference between \autoref{illu:fc:chess:II} and \autoref{illu:fc:chess:I} is the difficulty of the puzzle.%
  \footnote{
    \citeauthor{Emms:2000aa} suggests:
    \textquote{%
      \variation{1... Nb6!}%
      (threatening \variation{2... Nb3\#})%
      \variation{2. b5}%
      (or \variation{2. Bd1 Nxc4+} \variation{3. Ka4 b5\#})%
      \variation{2... c5!}%
      \variation{3. bxa6 Nxc4+}%
      \variation{4. Ka4 b5\#}%
      \textbf{(0-1)}%
    }
    (\citeyear[46]{Emms:2000aa}).
  }
  An agent may do an action described by `begin an attempt to solve\dots'.
  However, a basic understanding of chess does not imply the capacity to work through a complex sequence of moves in the relevant situation.

  Note, this sense of capacity is not limited to the possibility of concluding.
  There may be a possible event in which the agent concludes~\ref{illu:fc:chess:II:c}.
  For, the agent may get lucky and consider a suitable sequence of four moves.
  However, the possibility of a lucky sequence of events does not secure the truth of the progressive.
  For example, there is a possible event in which one wins the lottery after purchasing a ticket, but purchasing a ticket does not entail an event in which one wins the lottery is in progress.
  For some, chess puzzles aren't sufficiently fun to put the effort in.%
  \footnote{
    Specifically,~\ref{illu:fc:chess:II:c} was not a \fc{} for me.
    I gave up after fifteen minutes or so.
  }
\end{note}

\paragraph*{Novel information}

\begin{note}
  \begin{scenario}[Where's Wally]
    \label{illu:fc:wally}
    An agent has a book containing numerous drawings of scenes in which various characters are doing a variety of things.
    Somewhere in each scene is a character called `Wally', identifiable by a collection distinguishing features.
    These features include a red and white striped jumper, blue trousers, short brown wavy hair, and so on.

    The agent has searched through a scene, and has identified a character.
    However, the character is wearing glasses, and whether Wally wears round glasses is not a feature the agent kept in mind.
  \end{scenario}

  \begin{enumerate}[label=C\thescenarioCounter., ref=(C\thescenarioCounter)]
  \item
    \label{illu:fc:wally:c}
    \pv{\propI{The character identified is Wally}}{\valI{True}}
  \end{enumerate}

  It's not a \fc{}, as the agent needs to get some novel information.
\end{note}

\paragraph*{Conflict}

\begin{note}
  \begin{scenario}[Knowing whether and belief]%
    \label{ill:fcs:kw}%
    \citeauthor{Barker:1975un} suggests the following two principles hold with respect to knowing whether:

    \begin{enumerate}[label=(\Alph*), ref=(\Alph*)]
    \item
      \label{Barker:1975un:A}
      If \emph{S} knows whether \emph{p} and \emph{S} believes that \emph{p}, then \emph{p}.
    \item
      \label{Barker:1975un:B}
      If \emph{S} knows whether \emph{p} and \emph{S} believes that not-\emph{p}, then not-\emph{p}.%
      \mbox{ }\hfill\mbox{(\citeyear[281]{Barker:1975un})}
    \end{enumerate}
  \end{scenario}

  \noindent The conclusions of interest are:

  \begin{enumerate}[label=C\Alph*., ref=(C\Alph*)]
  \item
    \label{ill:fcs:kw:cA}
    \pv{\propI{If \emph{S} knows whether \emph{p} and \emph{S} believes that \emph{p}, then \emph{p}}}{\valI{True}}
  \item
    \label{ill:fcs:kw:cB}
    \pv{\propI{If \emph{S} knows whether \emph{p} and \emph{S} believes that not-\emph{p}, then not-\emph{p}}}{\valI{True}}
  \end{enumerate}

  \noindent I expect neither~\ref{ill:fcs:kw:cA} nor~\ref{ill:fcs:kw:cB} are \fc{1}.
  For, rather than conclude either~\ref{ill:fcs:kw:cA} or~\ref{ill:fcs:kw:cB} one will find a counterexample.%
  \footnote{
    For example, consider an agent \emph{A} playing speed chess.
    It's the end game, and \emph{A} believes they have a winning strategy.
    \emph{A} knows whether they have a winning strategy, but doesn't have time to work through the details.
    Given \ref{Barker:1975un:A}, \emph{A} has a winning strategy.
    \emph{A} does not have a winning strategy.
  }
  And, given a counterexample one will not conclude the principle is true.
\end{note}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% TeX-engine: luatex
%%% End:
